### 2015-12-16 outline.tex
add rough initial outline of project idea

\documentclass[12pt]{article}

\addtolength{\textwidth}{1.4in}
\addtolength{\oddsidemargin}{-.7in} %left margin
\addtolength{\evensidemargin}{-.7in}
\setlength{\textheight}{8.5in}
\setlength{\topmargin}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.5in}
\renewcommand{\baselinestretch}{1.0}
\setlength{\parindent}{0pt}
\linespread{1.1}

\usepackage{amssymb, amsmath, amsthm, bm}
\usepackage{graphicx,csquotes,verbatim}
\usepackage[backend=biber,block=space,style=authoryear]{biblatex}
\setlength{\bibitemsep}{\baselineskip}
\usepackage[american]{babel}
%dell laptop
\addbibresource{C:/Users/Kristy/Dropbox/Research/xBibs/tradeagreements.bib}
%\addbibresource{C:/Users/Kristy/Documents/Dropbox/Research/xBibs/tradeagreements.bib}
\renewcommand{\newunitpunct}{,}
\renewbibmacro{in:}{}

\DeclareMathOperator*{\argmax}{arg\,max}
\usepackage{xcolor}
\hbadness=10000

\newtheorem{proposition}{Proposition}
\newcommand{\ve}{\varepsilon}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\ta}{\theta}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\btw}{\bm{\tau^{tw}}}
\newcommand{\ga}{\gamma}
\newcommand{\Ga}{\Gamma}
\newcommand{\de}{\delta}

\begin{document}
\begin{center}
  Preliminary Outline for Dispute Length Project
\end{center}

\vskip.3in
Main idea: extend SOP$\_$repeated model to endogenize length of dispute
\begin{itemize}
	\item Adapt SOP$\_$repeated (or SOP)
		\begin{itemize}
			\item Note: Chad wonders if repeated game / self-enforcement constraint is essential to story
		\end{itemize}
	\item When is it worth it for lobby to exert effort to prolong trade war?
	\item Chad and Maurizio Zanardi are working on a paper on AD 5-year reviews
		\begin{itemize}
			\item After five years, they come up for review 
				\begin{itemize}
					\item Some AD measures get removed, some not, some go to dispute
					\item This is, of course, conditional on getting to five years
				\end{itemize}
			\item 40 percent of all WTO disputes have to do with AD, but of course not all AD measure go to dispute
			\item They have the data, but are not exploiting cross-industry variation
				\begin{itemize}
					\item Instead, aggregate variation, things like recessions, exchange rates
				\end{itemize}
			\item They don't have a theory for the cross-industry variation, because the economic determinants are meaningless after five years
				\begin{itemize}
					\item No injury, import surges: they've been protected for five years. No variation in new economic date b/c they've been insulated
					\item What's the economic test? There really isn't one. ``Would there be injury if we removed the duty?''
					\item Politics could be that theory (my theory from above)
						\begin{itemize}
							\item Q: Does hiring of lawyers for AD procedure get caught up in LDA data?
						\end{itemize}
				\end{itemize}
		\end{itemize}
\end{itemize}

\end{document}

### 2015-12-16 outline.tex
reorganize outline for preliminary direction of project

@@
 \vskip.3in
-Main idea: extend SOP$\_$repeated model to endogenize length of dispute
+Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
 \begin{itemize}
-	\item Adapt SOP$\_$repeated (or SOP)
+	\item Note that this is not trade war (as far as I know: check with Chad): foreign is applying $\tau^{*a}$ in most / all cases
 		\begin{itemize}
-			\item Note: Chad wonders if repeated game / self-enforcement constraint is essential to story
+			\item When is it worth it for lobby to exert effort to renew AD measure?
 		\end{itemize}
-	\item When is it worth it for lobby to exert effort to prolong trade war?
+\end{itemize}
+
+\newpage
+\begin{itemize}
 	\item Chad and Maurizio Zanardi are working on a paper on AD 5-year reviews
@@
 				\end{itemize}
-			\item 40 percent of all WTO disputes have to do with AD, but of course not all AD measure go to dispute
 			\item They have the data, but are not exploiting cross-industry variation

### 2015-12-16 outline.tex
add basic structure and intuition

@@
 \begin{itemize}
-	\item Note that this is not trade war (as far as I know: check with Chad): foreign is applying $\tau^{*a}$ in most / all cases
+	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
 		\begin{itemize}
+			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
+		\end{itemize}
 	\item When is it worth it for lobby to exert effort to renew AD measure?
+	\item Lobby must be able to trigger the AD measure in the first place
+		\begin{itemize}
+			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
+			\item Need uncertainty, asymmetric information, something
+			\item In my model, it is symmetric political uncertainty about how legislators (modeled in reduced form as position of median legislator) will vote
+		\end{itemize}
+	\item In this setup, need ``dispute'' to last for 5 periods (years)
+		\begin{itemize}
+			\item Then can extend it.
+			\item \textbf{Q}: for five more years?
 		\end{itemize}

### 2015-12-16 outline.tex
add section on cross-industry variation

@@
 
+\vskip.5in
+Possible cross-industry variation
+\begin{itemize}
+	\item Industry / lobby gets richer / more insulated for five years
+		\begin{itemize}
+			\item This could lead to differences in budget constraint if that were in model
+			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
+				\begin{itemize}
+					\item \textbf{Q}: This is one of the arguments for escape clause, no?
+				\end{itemize}
+		\end{itemize}
+	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
+	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
+\end{itemize}
+
 \newpage

### 2015-12-16 outline.tex
add section on ML's decision and uncertainty driving differential outcome

@@
 		\end{itemize}
+	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
+		\begin{itemize}
+			\item Uncertainty could be an answer, \textit{and} it varies across industry
+			\item \textbf{Q}: Is this a plausible story?
+		\end{itemize}
+	\item Also have to adapt model to cross-industry to get necessary variation
+		\begin{itemize}
+			\item I've already done some of this leg-work for the NSF proposals, thinking about PTA project
+		\end{itemize}
 \end{itemize}
@@
 	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
+\end{itemize}
+
+\vskip.5in
+Median Legislator's Condition
+\begin{itemize}
+	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
+		\[
+		  W_{ML}\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W_{ML}\left( \bta,\ga(e,\ta)\right)
+		\]
+		\begin{itemize}
+			\item Need to make sure this is not always the case.
+			\item Median legislator still has to balance (weighted) producers and consumers.
+			\item If $\ga = 1$, would pick optimal tariff.
+			\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
+		\end{itemize}
 \end{itemize}

### 2015-12-18 SOP_example.m
add copy of submitted_example.m from sop-rie as SOP_example.m

@@ -1,0 +1,75 @@
+%Maintaining symmetry, I want to try a bigger intercept for the gamma
+%function PLUS probabilistic one-sided breaking (same gamma as lobby4).
+
+%gamma: 1.25 + cn^.2
+%cn = .00166
+% tn = (8*(1 + .00156^.1)-5)/(68-8*(1 + .00156^.1)) = 0.12592
+
+tn = (8*(1.25 + .00166^.2)-5)/(68-8*(1.25 + .00166^.2));
+
+a=.2;
+tns=tn;
+ta = [0:.001:.1259];
+tad = size(ta,2);
+c=[0:.00005:.005];
+tac = size(c,2);
+[ta,c]=meshgrid(ta,c);
+
+lhs = (8*(1.25 + (c).^a)-5).*(tn-ta) + (4*(1.25 + (c).^a)-34).*(tn^2-ta.^2)-3.*(tns-ta)+9.*(tns^2-ta.^2);
+
+%add e to gamma
+e1=.25; e2=.25;
+up = (8*(1.25 + (c).^a +e1)-5).*(tn-ta) + (4*(1.25 + (c).^a +e1)-34).*(tn^2-ta.^2)-3.*(tns-ta)+9.*(tns^2-ta.^2);
+low = (8*(1.25 + (c).^a -e2)-5).*(tn-ta) + (4*(1.25 + (c).^a -e2)-34).*(tn^2-ta.^2)-3.*(tns-ta)+9.*(tns^2-ta.^2);
+spread = up - low;
+b = up./spread;
+for j=1:tad
+    if lhs(1,j)< 0
+        b(1,j) = 0;
+        else
+        b(1,j) = 1;
+     end; 
+     for i=2:101
+        if up(i,j) < 0
+        b(i,j) = 0;
+        elseif low(i,j) > 0
+        b(i,j) = 1;
+      end
+    end
+end
+
+l = b;
+l2 = 4/49*((1+tn).^2);
+l3 = l.*l2;
+l4 = 4/49*((1+ta).^2);
+l5 = l3 + (1-l).*l4 - c;
+[M,I] = max(l5,[],1);
+opt_C = (I -1)/20000;
+%plot(TA,opt_C);
+
+
+TA = [0:.001:.125];
+
+for j=1:tad
+  B(j) = b(I(j),j);
+end
+
+E=B;
+E2 = 21/49*(2-2*tn^2);
+E3 = E*E2;
+E4 = 21/49.*(2-2*TA.^2);
+E5 = (1-E).*E4;
[…]

### 2015-12-18 outline.tex
add note about uncertainty over retaliation to outline
run example with no retaliation and add notes to outline

@@
 			\item Need to make sure this is not always the case.
+				\begin{itemize}
 					\item Median legislator still has to balance (weighted) producers and consumers.
@@
 				\end{itemize}
+			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
+			\item Need to check exec's SOC
+		\end{itemize}
+	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
 \end{itemize}

### 2015-12-18 SOP_example.m

@@ -1,5 +1,4 @@
-%Maintaining symmetry, I want to try a bigger intercept for the gamma
-%function PLUS probabilistic one-sided breaking (same gamma as lobby4).
+%Going to adapt SOP-RIE example for no retaliation
 
 %gamma: 1.25 + cn^.2
 %cn = .00166
@@ -8,19 +7,18 @@
 tn = (8*(1.25 + .00166^.2)-5)/(68-8*(1.25 + .00166^.2));
 
 a=.2;
-tns=tn;
 ta = [0:.001:.1259];
 tad = size(ta,2);
 c=[0:.00005:.005];
 tac = size(c,2);
 [ta,c]=meshgrid(ta,c);
 
-lhs = (8*(1.25 + (c).^a)-5).*(tn-ta) + (4*(1.25 + (c).^a)-34).*(tn^2-ta.^2)-3.*(tns-ta)+9.*(tns^2-ta.^2);
+lhs = (8*(1.25 + (c).^a)-5).*(tn-ta) + (4*(1.25 + (c).^a)-34).*(tn^2-ta.^2);
 
 %add e to gamma
 e1=.25; e2=.25;
-up = (8*(1.25 + (c).^a +e1)-5).*(tn-ta) + (4*(1.25 + (c).^a +e1)-34).*(tn^2-ta.^2)-3.*(tns-ta)+9.*(tns^2-ta.^2);
-low = (8*(1.25 + (c).^a -e2)-5).*(tn-ta) + (4*(1.25 + (c).^a -e2)-34).*(tn^2-ta.^2)-3.*(tns-ta)+9.*(tns^2-ta.^2);
+up = (8*(1.25 + (c).^a +e1)-5).*(tn-ta) + (4*(1.25 + (c).^a +e1)-34).*(tn^2-ta.^2);
+low = (8*(1.25 + (c).^a -e2)-5).*(tn-ta) + (4*(1.25 + (c).^a -e2)-34).*(tn^2-ta.^2);
 spread = up - low;
 b = up./spread;
 for j=1:tad
@@ -45,10 +43,9 @@ l4 = 4/49*((1+ta).^2);
 l5 = l3 + (1-l).*l4 - c;
 [M,I] = max(l5,[],1);
 opt_C = (I -1)/20000;
-%plot(TA,opt_C);
-
-
 TA = [0:.001:.125];
+plot(TA,opt_C);
+
 
 for j=1:tad
[…]

### 2015-12-20 outline.tex
add motivation to outline

@@
 \end{center}
+
+\vskip.3in
+Need to motivate question
+\begin{itemize}
+	\item How long do deviations from trade agreement tariffs last? What are the determinants of these deviations?
+	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
+	\item Whether it's a dispute or it's a measure (what does Chad call these?) like AD or escape clause that has not been disputed, it won't be granted for no reason
+\end{itemize}
 

### 2015-12-20 outline.tex
expand section on cross-industry variation

@@
 		\begin{itemize}
-			\item I've already done some of this leg-work for the NSF proposals, thinking about PTA project
+			\item I've already done some of this leg work for the NSF proposals, thinking about PTA project
 		\end{itemize}
@@
 \begin{itemize}
+	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
 	\item Industry / lobby gets richer / more insulated for five years
@@
 			\item This could lead to differences in budget constraint if that were in model
+			\item May not need budget constraint if extra budget allows them to invest in technology
+				\begin{itemize}
+					\item Come to question of whether protection and technological upgrading are complements or substitutes
+					\item Lobbies that have more to gain have more opportunity to \textit{either} gather strength to become more competitive \textit{or} become more politically powerful to seek more protection
+					\item Perhaps some cross-industry measure of restraints on political strategy that would push toward substituting to technological
+				\end{itemize}
 			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
@@
 		\end{itemize}
-	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
 	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)

### 2015-12-20 extended-abstract.tex
save outline as extended-abstract and write into paragraph

--- 2015-12-20 outline.tex
@@
 \setlength{\parindent}{0pt}
-\linespread{1.1}
+\linespread{1.2}
 
@@
 \begin{center}
-  Preliminary Outline for Dispute Length Project
+  Temporary Trade Barriers: How Long Do They Last?
 \end{center}
+
+\vskip.2in
+Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011).
+A significant literature has explored the question of which industries receive protection through TTBs and under what conditions.
+This project asks a related but distinct question: given that a product receives protection, what detrmines the length of that protection?
 

### 2015-12-21 extended-abstract.tex
write second paragraph, move some of outline around

@@
 \begin{center}
-  Temporary Trade Barriers: How Long Do They Last?
+  Temporary Trade Barriers: How Long Do They Last?\\
+	Kristy Buzard
 \end{center}
@@
 A significant literature has explored the question of which industries receive protection through TTBs and under what conditions.
-This project asks a related but distinct question: given that a product receives protection, what detrmines the length of that protection?
+This project asks a related but distinct question: given that a product receives protection, what determines the length of that protection?
+\\
+
+This question can be addressed in the context of renewals of trade remedies under the WTO agreements.
+Normally, temporary measures such as anti-dumping and counter-vailing duties have a five-year sunset provision that is subject to renewal by the U.S.
+International Trade Commission.
+Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that it continues in force.
+
+The continued imposition of a TTB is not in general costless. We might assume then, that the International Trade Commission (ITC) only grants renewals when it finds the benefits outweigh the costs.
 
 \vskip.3in
-Need to motivate question
 \begin{itemize}
-	\item How long do deviations from trade agreement tariffs last? What are the determinants of these deviations?
 	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
-	\item Whether it's a dispute or it's a measure (what does Chad call these?) like AD or escape clause that has not been disputed, it won't be granted for no reason
 \end{itemize}
@@
 \vskip.5in
+Median Legislator's Condition
+\begin{itemize}
+	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
+		\[
+		  W_{ML}\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W_{ML}\left( \bta,\ga(e,\ta)\right)
+		\]
+		\begin{itemize}
+			\item Need to make sure this is not always the case.
+				\begin{itemize}
+					\item Median legislator still has to balance (weighted) producers and consumers.
+					\item If $\ga = 1$, would pick optimal tariff.
+					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
+				\end{itemize}
+			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
+			\item Need to check exec's SOC
+		\end{itemize}
+	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
+\end{itemize}
+
+\vskip.5in
 Possible cross-industry variation
@@
 	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
-\end{itemize}
-
-\vskip.5in
-Median Legislator's Condition
-\begin{itemize}
-	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
-		\[
-		  W_{ML}\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W_{ML}\left( \bta,\ga(e,\ta)\right)
-		\]
-		\begin{itemize}
-			\item Need to make sure this is not always the case.
-				\begin{itemize}
-					\item Median legislator still has to balance (weighted) producers and consumers.
-					\item If $\ga = 1$, would pick optimal tariff.
-					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
-				\end{itemize}
-			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
-			\item Need to check exec's SOC
-		\end{itemize}
-	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
 \end{itemize}

### 2015-12-24 extended-abstract.tex
change title, proof 1st 2 paragraphs, add to outline

@@
 \begin{center}
-  Temporary Trade Barriers: How Long Do They Last?\\
+  Temporary Trade Barriers: When Will They End?\\
 	Kristy Buzard
@@
 Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011).
-A significant literature has explored the question of which industries receive protection through TTBs and under what conditions.
-This project asks a related but distinct question: given that a product receives protection, what determines the length of that protection?
+A significant literature has explored the question of which industries receive protection through TTBs and under what conditions this happens.
+This project asks a related but distinct question: given that a product receives protection, what determines the duration of the protection it receives?
 \\
@@
 This question can be addressed in the context of renewals of trade remedies under the WTO agreements.
-Normally, temporary measures such as anti-dumping and counter-vailing duties have a five-year sunset provision that is subject to renewal by the U.S.
+Normally, temporary measures such as anti-dumping and counter-vailing duties are imposed with a five-year sunset provision that is subject to renewal by the U.S.
 International Trade Commission.
 Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that it continues in force.
+\\
+
+Set up model
+\begin{itemize}
+	\item Take trade agreement tariff as given
+	\item Lobby exerts effort to convince ITC to apply anti-dumping duties (AD determined endogenously)
+\end{itemize}
 
@@
 	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
+	\item It's about how hard the lobby lobbies, how much reaction they get
 \end{itemize}

### 2015-12-24 extended-abstract.tex
finish adding to outline from written notes

@@
 \begin{itemize}
-	\item Take trade agreement tariff as given
-	\item Lobby exerts effort to convince ITC to apply anti-dumping duties (AD determined endogenously)
+	\item Take trade agreement tariff as given ($\tau^a_i$)
+	\item Lobby exerts effort to convince ITC to apply anti-dumping duties (AD determined endogenously); there is a given amount of uncertainty for each $i$
+	\item Given that lobby gets an ITC measure in first round of game and it stay stays in place, there is another round five years later; at this point, $\tau^{AD}$ is given
+	\item Lobby decides how much effort to put forth given $\tau^{a}$, $\tau^{AD}$, $\ta$
 \end{itemize}
@@
 			\item Need uncertainty, asymmetric information, something
-			\item In my model, it is symmetric political uncertainty about how legislators (modeled in reduced form as position of median legislator) will vote
+			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
+				\begin{itemize}
+					\item Directly about strength of evidence? (indirectly about retaliation / dispute)
+					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
+					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors?
+					\item Does Congressional uncertainty transfer over to ITC uncertainty?
+				\end{itemize}
 		\end{itemize}
@@
 	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
+		\begin{itemize}
+			\item In first round, $\tau^{AD}$ is endogenous. It's exogenous in second round of play.
+		\end{itemize}
 	\item Industry / lobby gets richer / more insulated for five years
@@
 		\end{itemize}
+	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC's decision-making process
 	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)

### 2015-12-24 extended-abstract.tex
half introduce model, but not sure where to explain uncertainty

@@
 
-Set up model
+In many countries, the crucial actors in the imposition of TTBs are advocates for the industry that would be protected and an administrative body that has been granted authority to make decisions about whether a given TTB is WTO-legal.
+In the United States, this body is the International Trade Commission (ITC).
+For ease of exposition and because I would ultimately like to test this theory using U.S.
+data, I will refer to the actors in this model as lobbies and the ITC.
+\\
+
+In this model, there are two phases of interaction between any given industry seeking protection and the ITC.
+In both cases, all the actors take most-favored-nation (MFN) tariffs as given.
+In the first phase, when no TTB is in place, an industry exerts effort to convince the ITC to enact a TTB for its product.
+The ITC then must decide whether the maintain the MFN tariff or impose the TTB barrier.
+Importantly, we assume that this decision is not deterministic, with the amount of uncertainty varying by industry.
+
 \begin{itemize}
-	\item Take trade agreement tariff as given ($\tau^a_i$)
-	\item Lobby exerts effort to convince ITC to apply anti-dumping duties (AD determined endogenously); there is a given amount of uncertainty for each $i$
 	\item Given that lobby gets an ITC measure in first round of game and it stay stays in place, there is another round five years later; at this point, $\tau^{AD}$ is given
@@
 \vskip.3in
-Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
 \begin{itemize}

### 2015-12-24 outline.tex
update outline from extended-abstract outline

@@
 		\end{itemize}
-\end{itemize}
-
-\vskip.5in
-Possible cross-industry variation
-\begin{itemize}
-	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
-	\item Industry / lobby gets richer / more insulated for five years
-		\begin{itemize}
-			\item This could lead to differences in budget constraint if that were in model
-			\item May not need budget constraint if extra budget allows them to invest in technology
-				\begin{itemize}
-					\item Come to question of whether protection and technological upgrading are complements or substitutes
-					\item Lobbies that have more to gain have more opportunity to \textit{either} gather strength to become more competitive \textit{or} become more politically powerful to seek more protection
-					\item Perhaps some cross-industry measure of restraints on political strategy that would push toward substituting to technological
-				\end{itemize}
-			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
-				\begin{itemize}
-					\item \textbf{Q}: This is one of the arguments for escape clause, no?
-				\end{itemize}
-		\end{itemize}
-	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
 \end{itemize}
@@
 	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
+\end{itemize}
+
+\vskip.5in
+Possible cross-industry variation
+\begin{itemize}
+	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
+		\begin{itemize}
+			\item In first round, $\tau^{AD}$ is endogenous. It's exogenous in second round of play.
+		\end{itemize}
+	\item Industry / lobby gets richer / more insulated for five years
+		\begin{itemize}
+			\item This could lead to differences in budget constraint if that were in model
+			\item May not need budget constraint if extra budget allows them to invest in technology
+				\begin{itemize}
+					\item Come to question of whether protection and technological upgrading are complements or substitutes
+					\item Lobbies that have more to gain have more opportunity to \textit{either} gather strength to become more competitive \textit{or} become more politically powerful to seek more protection
+					\item Perhaps some cross-industry measure of restraints on political strategy that would push toward substituting to technological
+				\end{itemize}
+			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
+				\begin{itemize}
+					\item \textbf{Q}: This is one of the arguments for escape clause, no?
+				\end{itemize}
+		\end{itemize}
+	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC's decision-making process
+	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
 \end{itemize}

### 2015-12-24 extended-abstract.tex
cut down outline in extended-abstract for final run at writing it up

@@
 			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
-			\item Need uncertainty, asymmetric information, something
 			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
@@
 		\end{itemize}
-	\item In this setup, need ``dispute'' to last for 5 periods (years)
-		\begin{itemize}
-			\item Then can extend it.
-			\item \textbf{Q}: for five more years?
-		\end{itemize}
 	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
@@
 		\end{itemize}
-	\item Also have to adapt model to cross-industry to get necessary variation
-		\begin{itemize}
-			\item I've already done some of this leg work for the NSF proposals, thinking about PTA project
-		\end{itemize}
-\end{itemize}
-
-\vskip.5in
-Median Legislator's Condition
-\begin{itemize}
-	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
-		\[
-		  W_{ML}\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W_{ML}\left( \bta,\ga(e,\ta)\right)
-		\]
-		\begin{itemize}
-			\item Need to make sure this is not always the case.
-				\begin{itemize}
-					\item Median legislator still has to balance (weighted) producers and consumers.
-					\item If $\ga = 1$, would pick optimal tariff.
-					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
-				\end{itemize}
-			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
-			\item Need to check exec's SOC
-		\end{itemize}
-	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
 \end{itemize}
@@
 	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
+	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
 \end{itemize}
 
-\newpage
+\vskip.3in
+Chad and Maurizio Zanardi are working on a paper on AD 5-year reviews
 \begin{itemize}
-	\item Chad and Maurizio Zanardi are working on a paper on AD 5-year reviews
-		\begin{itemize}
-			\item After five years, they come up for review 
-				\begin{itemize}
-					\item Some AD measures get removed, some not, some go to dispute
-					\item This is, of course, conditional on getting to five years
-				\end{itemize}
 	\item They have the data, but are not exploiting cross-industry variation
@@
 	\item They don't have a theory for the cross-industry variation, because the economic determinants are meaningless after five years
-				\begin{itemize}
-					\item No injury, import surges: they've been protected for five years. No variation in new economic date b/c they've been insulated
-					\item What's the economic test? There really isn't one. ``Would there be injury if we removed the duty?''
 	\item Politics could be that theory (my theory from above)		
-						\begin{itemize}
-							\item Q: Does hiring of lawyers for AD procedure get caught up in LDA data?
-						\end{itemize}
-				\end{itemize}
-		\end{itemize}
 \end{itemize}

### 2015-12-24 extended-abstract.tex
delete more outline unnecessary for abstract

@@
 
-In this model, there are two phases of interaction between any given industry seeking protection and the ITC.
-In both cases, all the actors take most-favored-nation (MFN) tariffs as given.
+In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, all the actors take most-favored-nation (MFN) tariffs as given. \\
+
 In the first phase, when no TTB is in place, an industry exerts effort to convince the ITC to enact a TTB for its product.
 The ITC then must decide whether the maintain the MFN tariff or impose the TTB barrier.
-Importantly, we assume that this decision is not deterministic, with the amount of uncertainty varying by industry.
+Importantly, we assume that the decisions of the ITC are not deterministic, with the amount of uncertainty varying by industry.
+\\
 
-\begin{itemize}
-	\item Given that lobby gets an ITC measure in first round of game and it stay stays in place, there is another round five years later; at this point, $\tau^{AD}$ is given
-	\item Lobby decides how much effort to put forth given $\tau^{a}$, $\tau^{AD}$, $\ta$
-\end{itemize}
+Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision under the WTO.
+At this point, the interaction is essentially the same with the industry first exerting effort and then the ITC deciding whether to extend the TTB or to revert to the MFN tariff.
+The essential strategic difference is that at this point the level of the TTB is taken as exogenously set at the level determined in the first round of interaction.
+\\
 
-The continued imposition of a TTB is not in general costless. We might assume then, that the International Trade Commission (ITC) only grants renewals when it finds the benefits outweigh the costs.
+An industry's decision about how much, if any, effort to exert depends on a number of factors.
+Among them are the gap between the applied tariff it faces and the protection it would receive under a TTB, the cost of seeking the TTB, and, crucially, the probability that its request will be granted.
+That it, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the ITC's decision-making process.
+\\
+
+Thus we turn to the question of how the ITC decides whether to grant a TTB.
+The imposition of a TTB, or continuation of one already in place, is not in general costless.
+We might assume then, that the ITC only grants renewals when it finds the benefits outweigh the costs.
+If the ITC's rulings are uncertainty from the point of view of the lobby, it must be that the lobby cannot perfectly predict how the
 
@@
 		\begin{itemize}		
-	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
-	\item It's about how hard the lobby lobbies, how much reaction they get
-\end{itemize}
-
-\vskip.3in
-\begin{itemize}
-	\item Note that this is not trade war: foreign is applying $\tau^{*a}$ in most / all cases
-		\begin{itemize}
-			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
-		\end{itemize}
-	\item When is it worth it for lobby to exert effort to renew AD measure?
-	\item Lobby must be able to trigger the AD measure in the first place
-		\begin{itemize}
-			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
 			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
@@
 			\item \textbf{Q}: Is this a plausible story?
-		\end{itemize}
 		\end{itemize}

### 2015-12-26 extended-abstract.tex
write paragraph on sources of uncertainty

@@
 We might assume then, that the ITC only grants renewals when it finds the benefits outweigh the costs.
-If the ITC's rulings are uncertainty from the point of view of the lobby, it must be that the lobby cannot perfectly predict how the
+If the ITC's rulings are uncertain from the point of view of industry, it must be that the industry cannot perfectly predict the outcome of any given proceeding.
+\\
 
-\vskip.3in
-		\begin{itemize}		
-			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
-				\begin{itemize}
-					\item Directly about strength of evidence? (indirectly about retaliation / dispute)
-					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
-					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors?
-					\item Does Congressional uncertainty transfer over to ITC uncertainty?
-				\end{itemize}
-		\end{itemize}
-	\item Why would there be variation in one lobby's incentives between $t=1$ (original application of AD) and $t=6$ when it comes up for renewal?
-		\begin{itemize}
-			\item Uncertainty could be an answer, \textit{and} it varies across industry
-			\item \textbf{Q}: Is this a plausible story?
-		\end{itemize}
+This uncertainty may derive from several sources.
+The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB.
+Indirectly, this may indirectly reflect the ITC's preferences about the costs of disputes and retaliation by trade partners.
+Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to consumers and trading relations.
+This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question.
 
@@
 \begin{itemize}
-	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart)
+	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart); or the incentives could be different
 		\begin{itemize}
 			\item In first round, $\tau^{AD}$ is endogenous. It's exogenous in second round of play.
+			\item Uncertainty could be an answer, \textit{and} it varies across industry
 		\end{itemize}

### 2015-12-26 extended-abstract.tex
proof first two pages of extended-abstract

@@
 For ease of exposition and because I would ultimately like to test this theory using U.S.
-data, I will refer to the actors in this model as lobbies and the ITC.
+data, I will refer to the actors in this model as industries and the ITC.
 \\
@@
 In the first phase, when no TTB is in place, an industry exerts effort to convince the ITC to enact a TTB for its product.
-The ITC then must decide whether the maintain the MFN tariff or impose the TTB barrier.
+The ITC then must decide whether to maintain the MFN tariff or impose the temporary trade barrier.
 Importantly, we assume that the decisions of the ITC are not deterministic, with the amount of uncertainty varying by industry.
@@
 Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision under the WTO.
-At this point, the interaction is essentially the same with the industry first exerting effort and then the ITC deciding whether to extend the TTB or to revert to the MFN tariff.
+At this point, the interaction is similar to that during the first phase, with the industry first exerting effort and then the ITC deciding whether to extend the TTB or to revert to the MFN tariff.
 The essential strategic difference is that at this point the level of the TTB is taken as exogenously set at the level determined in the first round of interaction.
@@
 The imposition of a TTB, or continuation of one already in place, is not in general costless.
-We might assume then, that the ITC only grants renewals when it finds the benefits outweigh the costs.
+We might assume then that the ITC only grants renewals when it finds the benefits outweigh the costs.
 If the ITC's rulings are uncertain from the point of view of industry, it must be that the industry cannot perfectly predict the outcome of any given proceeding.
-\\
+That is, the industry does not know with precision how the ITC weighs the costs and benefits of granting protection.\\
 
@@
 The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB.
-Indirectly, this may indirectly reflect the ITC's preferences about the costs of disputes and retaliation by trade partners.
+Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners.
 Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to consumers and trading relations.

### 2015-12-26 extended-abstract.tex
write paragraph on cross-industry questions

@@
 This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question.
+\\
+
+An important question in this model is why an industry that receives protection as a result of the original interaction concerning the imposition of the TTB would fail to get it renewed.
+At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome.
+In addition, having the level of the TTB set by the original interaction serves to reduce the industry's incentive to exert effort on the margin.
+\\
+
+In addition, some factors that affect both the ITC's and the industry's decision-making can change significantly over the course of a five-year period.
+Most of these factors display at least some variation across industries.
+\\
+
+Because a TTB insulates an industry from competition, when receiving such protection, and industry should be able to increase profits.
+The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary.
+Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection.
+These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the ITC.
+\\
 
 \vskip.5in
-Possible cross-industry variation
 \begin{itemize}
-	\item Lobby facing same uncertainty, behaving in same manner may get different outcome in the two draws (five years apart); or the incentives could be different
-		\begin{itemize}
-			\item In first round, $\tau^{AD}$ is endogenous. It's exogenous in second round of play.
-			\item Uncertainty could be an answer, \textit{and} it varies across industry
-		\end{itemize}
-	\item Industry / lobby gets richer / more insulated for five years
-		\begin{itemize}
-			\item This could lead to differences in budget constraint if that were in model
-			\item May not need budget constraint if extra budget allows them to invest in technology
-				\begin{itemize}
-					\item Come to question of whether protection and technological upgrading are complements or substitutes
-					\item Lobbies that have more to gain have more opportunity to \textit{either} gather strength to become more competitive \textit{or} become more politically powerful to seek more protection
-					\item Perhaps some cross-industry measure of restraints on political strategy that would push toward substituting to technological
-				\end{itemize}
-			\item This could lead to differences in ability to deal with technological gap with foreign competitors 
-				\begin{itemize}
-					\item \textbf{Q}: This is one of the arguments for escape clause, no?
-				\end{itemize}
-		\end{itemize}
 	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC's decision-making process

### 2015-12-29 extended-abstract.tex
finish text to submit to InsTED

@@
 \vskip.2in
-Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011).
+Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers (TTBs) on a not-infrequent basis (Bown 2011\footnote{Bown, Chad P., ``Taking Stock of Antidumping, Safeguards and Countervailing Duties, 1990-2009,'' The World Economy v34, n12 (December 2011): 1955-1998.}).
 A significant literature has explored the question of which industries receive protection through TTBs and under what conditions this happens.
@@
 
-This uncertainty may derive from several sources.
+There are several possible sources of this uncertainty.
 The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a TTB.
@@
 At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome.
-In addition, having the level of the TTB set by the original interaction serves to reduce the industry's incentive to exert effort on the margin.
+Moreover, having the level of the TTB set by the original interaction serves to reduce the industry's incentive to exert effort on the margin.
 \\
@@
 
-\vskip.5in
-\begin{itemize}
-	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC's decision-making process
-	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
-	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
-\end{itemize}
+Another interesting dimension along which there is uncertainty for the ITC is in its evaluation of the probability with which trading partners will dispute or retaliate against a TTB.
+This not only varies across TTBs, but may vary across time.
+In particular, the ITC can observe whether a dispute has been filed during the first five years of a TTB and update its beliefs about future retaliation in a way that varies across industries.
+\\
 
-\vskip.3in
-Chad and Maurizio Zanardi are working on a paper on AD 5-year reviews
-\begin{itemize}
-	\item They have the data, but are not exploiting cross-industry variation
-		\begin{itemize}
-			\item Instead, aggregate variation, things like recessions, exchange rates
-		\end{itemize}
-	\item They don't have a theory for the cross-industry variation, because the economic determinants are meaningless after five years
-	\item Politics could be that theory (my theory from above)		
-\end{itemize}
+There is much to be learned about the workings of the world trading system by examining the duration of deviations from base tariff commitments.
+I plan a project whose first stage is theoretical with a second, later stage in which the theory is tested on a data set of renewal decisions for anti-dumping measures.
 

### 2016-04-11 extended-abstract.tex
fix typos and expositional awkwarness in extended abstract

@@
 International Trade Commission.
-Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that it continues in force.
+Conditional on a TTB being granted and applied for five years, one would like to know what determines whether a renewal order is granted so that the measure continues in force.
 \\
@@
 
-In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, all the actors take most-favored-nation (MFN) tariffs as given. \\
+In this model, there are two phases of interaction between any given industry seeking protection and the ITC.
+In both cases, I assume that all actors take most-favored-nation (MFN) tariffs as given.
+\\
 
@@
 Among them are the gap between the applied tariff it faces and the protection it would receive under a TTB, the cost of seeking the TTB, and, crucially, the probability that its request will be granted.
-That it, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the ITC's decision-making process.
+That is, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the ITC's decision-making process.
 \\
@@
 Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners.
-Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to consumers and trading relations.
+Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to up- and down-stream industries, consumers and trading relations.
 This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question.
@@
 
-Because a TTB insulates an industry from competition, when receiving such protection, and industry should be able to increase profits.
+Because a TTB insulates an industry from competition, when receiving such protection, an industry should be able to increase profits.
 The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary.

### 2016-04-12 outline.tex
add section for beginning model; add pdftex package so I can bookmark
add sectioning

@@
 \linespread{1.1}
+
+\usepackage[pdftex,
+bookmarks=true,
+bookmarksnumbered=false,
+pdfview=fitH,
+bookmarksopen=true]{hyperref}
 
@@
 \vskip.3in
+\section{Motivation}
 Need to motivate question
@@
 \vskip.3in
-Main idea: adapt SOP model to predict whether anti-dumping measures get renewed
+\section{Main Idea}
+Adapt SOP model to predict whether anti-dumping measures get renewed
 \begin{itemize}
@@
 \vskip.5in
-Median Legislator's Condition
+\section{Median Legislator's Condition}
 \begin{itemize}
@@
 \vskip.5in
-Possible cross-industry variation
+\section{Cross-industry Variation}
 \begin{itemize}
@@
 \newpage
+\section{Model}
+What are the \textit{essential} insights I want to capture?
+
+\newpage
+\section{Chad and Maurizio's project}
 \begin{itemize}

### 2016-04-12 outline.tex
fill out notes on start of model

@@
 		\[
-		  W_{ML}\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W_{ML}\left( \bta,\ga(e,\ta)\right)
+		  W\left( \tau^{AD},\tau^{*a},\ga(e,\ta)\right) > W\left( \bta,\ga(e,\ta)\right)
 		\]
@@
 \section{Model}
-What are the \textit{essential} insights I want to capture?
+What are the \textit{essential} insights/predictions I want to capture?
+\begin{enumerate}
+	\item uncertainty about ITC's preferences impacts lobby's incentives to exert effort
+	\item cross-industry variation in whether AD duties are renewed
+\end{enumerate}
+
+\vskip.2in
+Do I need two stages? What happens with only one stage?
+\begin{enumerate}
+	\item Given $\tau^{AD}$, lobby chooses $e$
+	\item $\ta$ realized
+	\item ITC decides between $\tau^{AD}$ and $\tau^a$ using
+	  \[
+		  W\left(\ga(e,\ta), \tau^{AD},\tau^{*a}\right) > W\left(\ga(e,\ta), \tau^a, \tau^{*a}\right)
+		\]
+\end{enumerate}
+
+\vskip.2in
+This is simple because there's only one lobby, action in only one country
+\begin{itemize}
+	\item Although there may be pressure from foreign
+	\item Or in a three-country model: third country benefits from discrimination against foreign $\left( * \right)$
+\end{itemize}
+
+\vskip1in
+Next steps:
+\begin{enumerate}
+	\item Check BS GE model
+	\item Check on how results from JMP would translate given no punishments
+	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$
+\end{enumerate}
 

### 2016-04-26 outline.tex
integrate notes into outline from two weeks ago
update outline with notes on translation of JMP model

@@
 					\item If $\ga = 1$, would pick optimal tariff.
-					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^{AD} < \tau^{AD}$, depends on which is closer in welfare terms 
+					\item If $\ga$ is so low that $\tau^N < \tau^a$, then agreement will hold. If $\tau^a < \tau^N < \tau^{AD}$, depends on which is closer in welfare terms 
 				\end{itemize}
 			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
-			\item Need to check exec's SOC
+			\item Exec's SOC doesn't matter: going to take $\bta$ as given.
+But need to worry about lobby and leg SOCs.
+I've convinced myself that the relevant results from my JMP go through for this objective function, so SOCs go through too (given the right assumptions to get concavity for leg, or possibly the argumentation from trade war section supplied by RoIE editor)
 		\end{itemize}
 	\item There could also be uncertainty about the probability that foreign will dispute the AD measure; that could change from the original to the renewal
+		\begin{itemize}
+			\item Could reduce form this, or not
+		\end{itemize}
 \end{itemize}
@@
 
+\vskip.5in
+Notes
+\begin{enumerate}
+	\item I don't think a more general model like BS1999 will work; I need to be able to pick apart the elements of the welfare function to separate out $\ga(e,\ta)$ in order to do my proofs
+\end{enumerate}
+
 \vskip1in
@@
 \begin{enumerate}
-	\item Check BS GE model
-	\item Check on how results from JMP would translate given no punishments
 	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$

### 2016-04-26 outline.tex
add more notes throughout outline

@@
 	\item If lobbies have to exert effort to achieve higher-than-MFN tariffs, when will it be worthwhile for them to do so?
-	\item Whether it's a dispute or it's a measure (what does Chad call these?) like AD or escape clause that has not been disputed, it won't be granted for no reason
+	\item Whether it's a dispute or it's a temporary trade barrier (TTB) like AD or escape clause that has not been disputed, it won't be granted for no reason
 \end{itemize}
@@
 		\begin{itemize}
-			\item This means disputes/non-adherence to MFN tariffs must happen on the equilibrium path
-			\item Need uncertainty, asymmetric information, something
+			\item This means disputes/non-adherence to MFN tariffs must happen on eqm path
 			\item In my model, it is symmetric political uncertainty about how ITC will rule. Why would there be uncertainty?
 				\begin{itemize}
-					\item Directly about strength of evidence? (indirectly about retaliation / dispute)
+					\item Directly about strength of evidence? (indirectly about retaliation / dispute?)
 					\item Differential valuation about harm to industry---how central the industry is, how politically powerful
 					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors?
-					\item Does Congressional uncertainty transfer over to ITC uncertainty?
+					\item Does Congressional uncertainty transfer over to ITC uncertainty? NEED to argue that it does if we're going to use the political uncertainty data that I'm generating
 				\end{itemize}
 		\end{itemize}
-	\item In this setup, need ``dispute'' to last for 5 periods (years)
+	\item In this setup, need ``dispute'' to last for 5 periods (years); 4 for safeguard
 		\begin{itemize}
@@
 		\begin{itemize}
-			\item Uncertainty could be an answer, \textit{and} it varies across industry
+			\item Political uncertainty could be an answer, \textit{and} it varies across industry
 			\item \textbf{Q}: Is this a plausible story?
@@
 			\item In first round, $\tau^{AD}$ is endogenous. It's exogenous in second round of play.
+			\item \textbf{Q}: Is it really exogenous? What does data say about whether renewals are at same level as original TTB?
 		\end{itemize}
-	\item Industry / lobby gets richer / more insulated for five years
+	\item Industry / lobby gets richer / more insulated for five years (or poorer if not insulated enough)
 		\begin{itemize}
 			\item This could lead to differences in budget constraint if that were in model
-			\item May not need budget constraint if extra budget allows them to invest in technology
+			\item May not need budget constraint if extra budget allows them to invest in technology or politics
 				\begin{itemize}
@@
 					\item Lobbies that have more to gain have more opportunity to \textit{either} gather strength to become more competitive \textit{or} become more politically powerful to seek more protection
+						\begin{itemize}
+							\item Is there an incentive to \textit{not} get stronger technologically?
+						\end{itemize}
 					\item Perhaps some cross-industry measure of restraints on political strategy that would push toward substituting to technological
@@
 	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)
+		\begin{itemize}
+			\item If the dist'n doesn't change, only the outcome, I'd just be observing draws from the same distribution, driven by same behavior.
+			\item I guess this is something I want to be able to tease apart?
+\textit{If} uncertainty plays an important role, is it just the outcome that's changing, or the underlying uncertainty and thus the behavior?
+			\item Can I get at this with the data I have (i.e. \textit{will} have, shortly)?
+		\end{itemize}
 \end{itemize}
 
-\newpage
+\vskip1in
 \section{Model}
@@
 \begin{enumerate}
-	\item Given $\tau^{AD}$, lobby chooses $e$
+	\item Given $\tau^{AD}$, lobby chooses $e$ given the dist'n of $\ta$
 	\item $\ta$ realized
@@
 \begin{enumerate}
+	\item Email Chad with questions
 	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$

### 2016-05-04 outline.tex
add chad's answers to outline

@@
 					\item \textbf{Q}: What are all the factors that have weight in ITCs decision-making? Are they influenced by other political factors? 
+					\textbf{A}: (Per Chad's email on 4/26/16, his and Gene Grossman's 2008 WTR) The data is useless b/c Commerce has never used counterfactual analysis.
 					\item Does Congressional uncertainty transfer over to ITC uncertainty? NEED to argue that it does if we're going to use the political uncertainty data that I'm generating
@@
 			\item Then can extend it.
-			\item \textbf{Q}: for five more years?
+			\item \textbf{Q}: for five more years? \textbf{A}: broadly looks true in data (to my casual glance)
+			\item Safeguards are rarely renewed (retaliation allowed after 3 years)
 		\end{itemize}
@@
 			\item \textbf{Q}: Is it really exogenous? What does data say about whether renewals are at same level as original TTB?
+			\item \textbf{A}: The statements are of the form ``As a result of the respective determinations by the Department and the ITC that revocation of the antidumping duty order on CTL plate from the PRC and termination of the Agreements on CTL plate from Russia and Ukraine would likely lead to continuation or recurrence of dumping and material injury to an industry in the United States, pursuant to section 751(d)(2) of the Act, the Department hereby gives notice of the continuation of the antidumping duty order on CTL plate from the PRC and the continuation of the Agreements on CTL plate from Russia and Ukraine.
+The effective dates of continuation will be the date of publication in the Federal Register of this Continuation Notice.
+Pursuant to sections 751(c)(2) and 751(c)(6) of the Act, the Department intends to initiate the next five-year sunset reviews of the antidumping duty order on CTL plate from the PRC and the Agreements on CTL plate from Russia and Ukraine not later than November 2019.'' \url{https://www.federalregister.gov/articles/2015/12/21/2015-32022/continuation-of-antidumping-duty-order-on-certain-cut-to-length-carbon-steel-plate-from-the-peoples}
 		\end{itemize}
@@
 		\end{itemize}
-	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC's decision-making process
+	\item Even if AD economic conditions can't be measured / don't bind, doesn't mean that real economic conditions don't play into ITC/DOC's decision-making process
+		\begin{itemize}
+			\item DOC initiates sunset review, determines whether dumping would continue
+			\item ITC investigates whether expiry of AD would lead to recurrence or continuation of injury
+		\end{itemize}
 	\item Uncertainty could change, so behavior would change (this would be hard to pick up in the data that I have)

### 2016-05-04 outline.tex
finalize modeling decisions before deriving first results

@@
 			\item \textbf{Q}: Are all cases of renewal ones of no punishment, i.e. target country is applying MFN tariff?
+			\item I'm going to go with this for now, given Chad's answer that Safeguards are usually not renewed b/c retaliation is authorized after three years
 		\end{itemize}
@@
 			\item \textbf{Q}: Is this a plausible story?
+			\item In current, simple model, this doesn't matter. I only look at $t=6$ decision, but cross industry
 		\end{itemize}
@@
 \vskip.5in
-\section{Median Legislator's Condition}
+\section{Decision-maker's Condition}
 \begin{itemize}
-	\item I believe I have to change the legislature's condition to be more like the cheater's payoff for this context
+	\item Have to change the legislature's condition to be more like the cheater's payoff for this context
 		\[
@@
 			\item Seems to work okay in Matlab example: just pushes up break probability, trade agreement tariff; reduces gamma and effort (``SOP$\_$example.m'')
+				\begin{itemize}
+					\item Makes sense: ITC/DOC doesn't get to set $\bta$ here. Just makes break decision given $\bta$ and $\btn$, where $\btn$ is AD duty, not actually Nash tariff
+				\end{itemize}
 			\item Exec's SOC doesn't matter: going to take $\bta$ as given.
@@
 			\item Could reduce form this, or not
+			\item This is reduced significantly; up until 2008, only four disputes over sunset reviews according to Chad's 2008 WTR
 		\end{itemize}
@@
 \begin{enumerate}
-	\item Email Chad with questions
 	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$

### 2016-05-06 presentation.tex
add presentation, copied from SOP ES_NASM_06_16_13

%\documentclass{beamer} 
\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

\usecolortheme{beaver}
\useinnertheme{default}
\setbeamertemplate{itemize item}[triangle]
\setbeamertemplate{itemize subitem}[triangle]
\setbeamertemplate{itemize subsubitem}[circle]
\setbeamertemplate{enumerate items}[default]
\setbeamertemplate{blocks}[upper=block head,rounded]
\setbeamercolor{item}{fg=black}
\usefonttheme{serif} %should allow ccfonts to take effect

\usepackage{cite}
\usepackage{times, verbatim,xcolor,bm}
\usepackage{amsbsy,amssymb, amsmath, amsthm}
\usepackage{booktabs}
%David miller's fonts
	\usepackage[T1]{fontenc}
	\usepackage[boldsans]{ccfonts}
	\usepackage[euler-hat-accent]{eulervm}

\newcommand{\al}{\alpha}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\btn}{\bm{\tau^{tw}}}
\newcommand{\ga}{\gamma}
\newcommand{\ve}{\varepsilon}
\newcommand{\ta}{\theta}

\newenvironment{changemargin}[2]{% 
  \begin{list}{}{% 
    \setlength{\topsep}{0pt}% 
    \setlength{\leftmargin}{#1}% 
    \setlength{\rightmargin}{#2}% 
    \setlength{\listparindent}{\parindent}% 
    \setlength{\itemindent}{\parindent}% 
    \setlength{\parsep}{\parskip}% 
  }% 
  \item[]}{\end{list}}

	\let\Tiny=\tiny

\title[Temporary Trade Barriers: When Will They End?\hspace{2.15in}\insertframenumber/\inserttotalframenumber]{Temporary Trade Barriers: \\ When Will They End?}
\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\date{May 13, 2016}

\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

\section{Overview}
\subsection{Preview}
\begin{frame}
\frametitle{Political Economy of Trade Agreements}
In most models, a single actor in each country makes trade policy. Modeling policy-making power more richly:
\pause
\begin{itemize}[<+->]
	\item reconciles `Protection for Sale' model to the data
  \item generates lobbying for the purpose of disrupting trade agreements  
	\item adds new role for trade agreements 
\end{itemize}
\end{frame}

\begin{frame}{Preview of Results}
\begin{itemize}[<+->]
	\item Higher trade agreement tariffs induce lobbies to decrease effort 
		\begin{itemize}
			\item Reduces probability of trade war / ratification failure
		\end{itemize}
	\item Executives negotiate tariffs to discourage lobbying
		\begin{itemize}
			\item Produces higher tariffs than executives prefer
			\item Reduces equilibrium lobbying effort
			\item Trade agreement as political commitment device
		\end{itemize}
	\item Tariff levels and optimal lobbying depend on how much political uncertainty is present
\end{itemize}
\end{frame}

\begin{frame}{Outline of Talk}
\begin{enumerate}[<+->]
	\item Background and Motivation
	\item Economic and Political Structure
	\item Results for a Special Case: Certainty
	\item Full Results: Political Uncertainty
	\item Conclusion
\end{enumerate}
\end{frame}

\begin{frame}{Standard Unitary Government Model}
Grossman $\&$ Helpman government welfare function:
				\[
				  C + aW
				\]
\pause
		\begin{itemize}[<+->]
			\item Government auctions tariffs/subsidies: lobbies pay for $a$-weighted welfare loss
			\item Estimated $a$'s far too large
				\begin{itemize}
					\item Implies that governments respond very little to lobbying effort
					\item Inconsistent with observed large tariffs relative to small lobbying effort
				\end{itemize}
		\end{itemize}
\end{frame}

\begin{frame}{Trade Agreements and Separation of Powers}
  \pause
  Take special case of `Protection for Sale' model (single lobby) and generalize government structure
  \pause
		\begin{itemize}[<+->]
			\item Executives can make trade agreement
			\item Legislatures retain final authority: can break agreement and start trade war / fail to ratify
			\item Trade war is subgame of the trade-agreement-setting game
				\begin{itemize}
  				\item Executives consider lobbying incentives and possibility of trade war when forming agreement
				\end{itemize}
		\end{itemize}
\end{frame}

\subsection{}
\begin{frame}
\frametitle{Related Literature}
\small Protection for Sale: Grossman $\&$ Helpman (1994)
\begin{itemize}
  \item \footnotesize Empirics: Goldberg $\&$ Maggi (1999), Gawande $\&$ Bandyopadhyay (2000), Mitra, Thomakos, $\&$  Ulubasoglu (2002)
  \item \footnotesize Mitra, Thomakos, $\&$  Ulubasoglu (2006), Bombardini (2008)
	\item \footnotesize Trade Wars and Trade Talks: Grossman $\&$ Helpman (1995)
\end{itemize}

\vskip.05in
\small Political economy shocks
\begin{itemize}
	\item \footnotesize Feenstra $\&$ Lewis (1991), Bagwell $\&$ Staiger (2001, 2005)
\end{itemize}

\vskip.05in
\small Separated powers
\begin{itemize}
	\item \footnotesize Mansfield, Milner $\&$ Rosendorff (2000), Song (2008)
\end{itemize}

\vskip.05in
\small Political uncertainty
\begin{itemize}
	\item \footnotesize Milner $\&$ Rosendorff (1997), Le Breton $\&$ Zaporozhets (2007) %legislators are agents, symmetric case very hard
\end{itemize}

		%\item Autocracy vs. Democracy: Mitra, Thomakos and Ulubasoglu (2002), Aidt and Gassebner (2010)
\end{frame}

\section{Model}
\subsection{Economic and Political Structure}
\begin{frame}{Timeline}
\pause
\begin{enumerate}
	\item {\bfseries Formation}
		\begin{enumerate}[i.]
			\pause
			\item Executives set trade policy in international agreement
		\end{enumerate}
	\pause
	\item \textbf{Ratification / Maintenance}
		\begin{enumerate}[i.]
			\pause
			\item Firms lobby legislatures to break agreement
			\pause
			\item Uncertainty is resolved
			\pause
			\item Legislatures decide to break or abide by agreement
			\pause
		\end{enumerate}
	\item \textbf{Trade War} (if agreement is broken)
	\pause
		\begin{enumerate}[i.]
			\item Firms lobby legislatures to set high trade-war tariff
			\pause
			\item Uncertainty is resolved
			\pause
			\item Legislatures decide trade-war tariff
		\end{enumerate}
\pause
	\item Private actors make production, consumption decisions
\end{enumerate}
\end{frame}

\begin{frame}{Economy}
\begin{itemize}
	\item Two countries: home and foreign (${}^*$)
	\item Separable in three goods: $X$ and $Y$ (traded) and numeraire
	\item Demand identical for both goods in both countries
	\item Supply: $Q_X^*(P_X) > Q_X(P_X)$ $\forall P_X$; symmetric for $Y$ 
		\begin{itemize}
			\item Home net importer of $X$, net exporter of $Y$
		\end{itemize}
\end{itemize}

\vskip.2in
\pause
Home levies $\tau$ on $X$, Foreign levies $\tau^*$ on $Y$
\pause
\begin{itemize}
	\item $P_X=P_X^W + \tau$ and $\pi_X(P_X)$ increasing in $\tau$
\end{itemize}

\pause
\vskip.2in
Non-tradable specific factors motivates political activity

\end{frame}

\begin{frame}{Political Structure}
In each country (focus on Home):
\pause
\begin{itemize}[<+->]
	\item A Unitary Executive
		\begin{itemize}
			\item Delegated authority to make trade agreement
		\end{itemize}
		%\pause
	\item A Non-unitary Legislature
		\begin{itemize}[<+->]
			\item Can withdraw delegation, break agreement, and set trade-war tariff
			\item Susceptible to influence of lobbying
			\item Decision determined by median legislator
		\end{itemize}
%\pause
	\item A Single Lobby
		\begin{itemize}
			\item Represents import-competing sector, $X$ ($Y$ in foreign)
		\end{itemize}	
\end{itemize}

\end{frame}

\subsection{The Players}
\begin{frame}
\frametitle{Executive Branch}
Trade agreement negotiated by unitary executive:
$$W_E = \mathit{CS}_X(\tau) + \mathit{CS}_Y(\tau^*) + \ga_E \pi_X(\tau) + \pi_Y(\tau^*) + \mathit{TR}(\tau)$$

\vskip.2in
\begin{itemize}
	\item $\mathit{CS_i(\cdot)}$: consumer surplus
	\item $\pi_X(\tau)$: profits of import-competing industry
	\item $\pi_Y(\tau^*)$: profits of exporting industry
	\item $\mathit{TR}(\tau)$: tariff revenue
	\item $\ga_E$: weight on profits in the import-competing industry
\end{itemize}

\end{frame}

\begin{frame}{Non-Unitary Legislature}
  Decisions determined by preferences of Median Legislator:
\[
  W_{\mathit{ML}} = \mathit{CS}_X(\tau) + \mathit{CS}_Y(\tau^*) + \ga(e,\ta) \pi_X(\tau) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
\]
\vskip-.1in
\pause
\begin{itemize}
	\item $\ga(e,\ta)$: weight on import-competing industry profits
		\begin{itemize}
			\pause
			\item $e$: lobbying effort
			\pause
			\item $\ta$: uncertain element in determination of ML's identity
		\end{itemize}
\end{itemize}

\pause
\vskip.1in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumptions on $\ga(e,\ta)$}
\begin{enumerate}
  \pause
	\item $\ga(e,\ta)$ is increasing and concave in $e$ for all $\ta \in \Theta$.
  \pause
  \item $\ga(e,\ta) \geq \ga_E \geq 1 \ \forall \ta$ 
\end{enumerate}
\end{beamerboxesrounded}
\end{frame}

\begin{frame}
\frametitle{Lobby}
\vskip.2in
Lobby chooses effort to maximize:
\begin{multline*}
  \left\{1-\Pr\left[ \text{TradeWar}(e_b,\bta)\right]\right\} \ \pi(\tau^a) \\
     + \Pr\left[ \text{TradeWar}(e_b,\bta) \right] \left[ \pi(\tau^{\mathit{tw}}) - e_{tw} \right] - e_b
\end{multline*}

\vskip.2in
\begin{itemize}
	\item $e_b$: Lobbying effort for break decision
	\item $e_{tw}$: Lobbying effort for trade-war tariffs
	\item $\bm{\tau^a} = (\tau^a,\tau^{*a})$: tariff under an agreement
	\item $\bm{\tau^{\mathit{tw}}} = (\tau^{\mathit{tw}},\tau^{*\mathit{tw}})$: tariff when agreement is broken
\end{itemize}

\end{frame}

\section{Certainty}
\subsection{Results: The Certain Case}
\begin{frame}{Timeline}
\begin{enumerate}
	\item \textbf{Formation}
		\begin{enumerate}[i.]
			\item Executives set trade policy in international agreement
		\end{enumerate}
	\item \textbf{Ratification / Maintenance}
		\begin{enumerate}[i.]
			\item Firms lobby legislatures to break agreement
			\item Legislatures decide to break or abide by agreement
		\end{enumerate}
	\item {\color{gray} \textbf{Trade War} (if agreement is broken)}
		\begin{enumerate}[i.]
			\item {\color{gray} Firms lobby legislatures to set high trade-war tariff}
			\item {\color{gray} Legislatures decide trade-war tariff}
		\end{enumerate}
	\item {\color{gray} Private actors make production, consumption decisions}
\end{enumerate}
\end{frame}

\begin{frame}{Highlight: Separation of Powers}
\pause
\textbf{Legislature}
\pause
\begin{itemize}
	\item Breaks agreement if median legislator prefers $\bm{\tau^{\mathit{tw}}}$ to $\bta$
\end{itemize}

\pause
\vskip.1in
\textbf{Lobby}
\pause
\begin{itemize}[<+->]
	\item Given the $\bta$ it faces, lobby knows what $e_b$ is required to break the agreement
 	\item Lobby pays this $e_b$ if: \hskip.2in $\bm{\pi}(\bm{\tau^{\mathit{tw}}}) \bm{- e_{tw}  - e_b > \pi}(\bm{\tau^a})$
\end{itemize}

\pause
\vskip.13in
\textbf{Executives}
\pause
\begin{itemize}[<+->]
	\item Set $\bta$ to make paying $e_b$ unprofitable
		\begin{itemize}
			\item[$\Rightarrow$] $e_b=0$, agreement remains in force
		\end{itemize}
	\item High tariffs, no lobbying, no trade disruptions
\end{itemize}
\end{frame}

\section{Full Results}
\begin{frame}{Political Uncertainty Illustration}
\pause
An Example (Bagwell $\&$ Staiger 2005)
\pause
\begin{itemize}[<+->]
	\item $D(P_i) = 1 - P_i$
	\item $Q_X(P_X) = \frac{P_X}{2}$, $Q_Y(P_Y) = P_Y$
	\item $P_X^W = \frac{4-3\tau}{7}$, $P_X = \frac{4+4\tau}{7}$
	\item $\ga(e,\ta) = 1.25 + e^{0.2} + \ta$ 
		\begin{itemize}
			\item $\ta \sim U[-0.25,0.25]$
		\end{itemize}
	\item $\ga_E = 1$
\end{itemize}

\end{frame}

\subsection{Ratification / Maintenance Stage}
\begin{frame}{Timeline}
\begin{enumerate}
	\item {\color{gray} \textbf{Formation}}
		\begin{enumerate}[i.]
			\item {\color{gray} Executives set trade policy in international agreement}
		\end{enumerate}
	\item \textbf{Ratification / Maintenance}
		\begin{enumerate}[i.]
			\item {\color{gray} Firms lobby legislatures to break agreement}
			\item Legislatures decide to break or abide by agreement
		\end{enumerate}
	\item {\color{gray} \textbf{Trade War} (if agreement is broken)}
		\begin{enumerate}[i.]
			\item {\color{gray} Firms lobby legislatures to set high trade-war tariff}
			\item {\color{gray} Legislatures decide trade-war tariff}
		\end{enumerate}
	\item {\color{gray} Private actors make production, consumption decisions}
\end{enumerate}
\end{frame}

\begin{frame}{Legislature}
  Legislature breaks trade agreement if median legislator's utility is higher under trade war than trade agreement
  \begin{itemize}
		\item Median legislator's identity is uncertain through $\ta$
	\end{itemize}

	\pause
  \vskip.2in
  Probability that Legislature breaks agreement: \\
	\pause
  \vskip.1in
    $b(e_b,\bta,\btn,\ta)$ probability median legislator prefers $\tau^{tw}$ to $\tau^a$ for a given $\ta$
\end{frame}

\begin{frame}{Timeline}
\begin{enumerate}
	\item {\color{gray} \textbf{Formation}}
		\begin{enumerate}[i.]
			\item {\color{gray} Executives set trade policy in international agreement}
		\end{enumerate}
	\item \textbf{Ratification / Maintenance}
		\begin{enumerate}[i.]
			\item Firms lobby legislatures to break agreement
			\item {\color{gray} Legislatures decide to break or abide by agreement}
		\end{enumerate}
	\item {\color{gray} \textbf{Trade War} (if agreement is broken)}
		\begin{enumerate}[i.]
			\item {\color{gray} Firms lobby legislatures to set high trade-war tariff}
			\item {\color{gray} Legislatures decide trade-war tariff}
		\end{enumerate}
	\item {\color{gray} Private actors make production, consumption decisions}
\end{enumerate}
\end{frame}

\subsection{Formation Stage}
\begin{frame}{Timeline}
\begin{enumerate}
	\item \textbf{Formation}
		\begin{enumerate}[i.]
			\item Executives set trade policy in international agreement
		\end{enumerate}
	\item {\color{gray} \textbf{Ratification / Maintenance}}
		\begin{enumerate}[i.]
			\item {\color{gray} Firms lobby legislatures to break agreement}
			\item {\color{gray} Legislatures decide to break or abide by agreement}
		\end{enumerate}
	\item {\color{gray} \textbf{Trade War} (if agreement is broken)}
		\begin{enumerate}[i.]
			\item {\color{gray} Firms lobby legislatures to set high trade-war tariff}
			\item {\color{gray} Legislatures decide trade-war tariff}
		\end{enumerate}
	\item {\color{gray} Private actors make production, consumption decisions}
\end{enumerate}
\end{frame}

\begin{frame}{Total Break Probability}
$B(\bta) = b(e_b(\bta),\bta)$
\pause
\begin{itemize}[<+->]
	\item Both direct and indirect effects of raising $\bta$ are negative
		\begin{itemize}
			\item $B(\bta)$ decreasing in $\bta$
		\end{itemize}
\end{itemize}
\pause
\vskip.2in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
   The total probability that the trade agreement will be broken is decreasing in the trade agreement tariffs.
\end{beamerboxesrounded}

\end{frame}

\begin{frame}{Executives' Tradeoff}
\[
  \Pr\left[ \text{TradeWar}(\bta) \right] \bm{W_E}(\btn) + \left\{1- \Pr\left[ \text{TradeWar}(\bta) \right]\right\} \bm{W_E}(\bta)
\]
\pause
\vskip.2in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 5}
    The executives face the following trade off when choosing $\bta$: higher tariffs decrease the probability that the trade agreement will be broken, but they also decrease welfare when the agreement is in force.
\end{beamerboxesrounded}
\end{frame}

\begin{frame}{Trade Agreements}

\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 4}
  The executives maximize their welfare by either (a) trading off reductions in the probability that the agreement will be broken with reductions in welfare under the agreement or (b) raising tariffs sufficiently high to ensure that the trade agreement will remain in force.
\end{beamerboxesrounded}
\end{frame}

\begin{comment}
\begin{frame}{Comparing Government Structures}
\begin{changemargin}{-1cm}{-1cm}
\begin{table}
\centering
  \begin{tabular}{lrrrr}
		\toprule
			Structure & $\bta$ & Lobbying & $B(\bta)$ & $\expect[\bta]$ \\
			\midrule
			Unitary, No Agreement & ---- & 0.0017 & 0 & 0.129 \\
			Unitary, Agreement & 0.118 & 0.0027 & 0 & 0.118 \\
			\\
			Exec-led Agreement (.25) & 0.078 & 0.0007 & 0.48 & 0.102 \\
			Exec-led Agreement (.00) & 0.106 & 0.0000 & 0 & 0.106 \\
			& {\color{gray}(.105)} & {\color{gray}(.0025)} & {\color{gray}(1)} & {\color{gray}(.129)} \\
		\bottomrule
	\end{tabular}
	\end{table}
\end{changemargin}
\end{frame}

\begin{frame}{Comparative Systems}
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Conjecture}
    Lobbying effort and tariffs are reduced by the presence of executive branches who form a trade agreement.
\end{beamerboxesrounded}

\pause
\vskip.2in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Corollary}
    Tariffs are lower in countries with separated powers than in those with unitary governments.
\end{beamerboxesrounded}
\end{frame}
\end{comment}

\begin{frame}[label=Uncertainty]
\frametitle{Uncertainty}
\begin{itemize}[<+->]
	\item Added intuition for lobbying incentives and tariff-setting behavior
  \item High tariffs, low but positive lobbying effort
  \item Possibility of trade disruptions / ratification failure in equilibrium
  \item Different behavior at varying levels of uncertainty
\end{itemize}
\end{frame}

\section{Conclusion}
\subsection{}
\begin{frame}{Future Work}
\begin{itemize}[<+->]
	\item Comparative statics on weighting function
	\item Empirical Tests
	\item Parallel models for countries with different government structures
	\item Asymmetric agreements
	\item Repeated model
		\begin{itemize}
			\item Implications for design of dispute settlement procedures
		\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Conclusion}
Resolution of `Protection for Sale' Puzzle
\pause
\begin{itemize}[<+->]
	\item Non-unitary legislature: more realistic lobbying process
	\item Separation of Powers: tariffs set in shadow of lobbying
	\item Uncertainty: smoother results, additional intuition
\end{itemize}
\end{frame}

\begin{frame}{Conclusion}
\begin{itemize}[<+->]
	\item Social welfare maximizers ($a \approx \infty$) set high tariffs to achieve low lobbying expenditures (and low $\ga_{ML}$) 
	\item Executives use trade agreement to manipulate lobbying incentives
		\begin{itemize}
			\item Trade agreement as political commitment device
		\end{itemize}
	\item Firms lobby for trade war / ratification failure and achieve equilibrium trade disruptions in some cases
		\begin{itemize}
			\item Can examine the endogenous dynamics behind politically-driven failures to cooperate
		\end{itemize}
\end{itemize}

\end{frame}

\end{document}

### 2016-05-10 presentation.tex
strip more out of old presentation

@@
 \usepackage{cite}
-\usepackage{times, verbatim,xcolor,bm}
+\usepackage{xcolor,bm}
 \usepackage{amsbsy,amssymb, amsmath, amsthm}
@@
 \begin{frame}
-\frametitle{Political Economy of Trade Agreements}
-In most models, a single actor in each country makes trade policy. Modeling policy-making power more richly:
+\frametitle{P}
+In 
 \pause
 \begin{itemize}[<+->]
-	\item reconciles `Protection for Sale' model to the data
-  \item generates lobbying for the purpose of disrupting trade agreements  
-	\item adds new role for trade agreements 
+	\item r
+  \item g
+	\item a
 \end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Higher trade agreement tariffs induce lobbies to decrease effort 
+	\item H
 		\begin{itemize}
-			\item Reduces probability of trade war / ratification failure
+			\item R
 		\end{itemize}
-	\item Executives negotiate tariffs to discourage lobbying
+	\item E
 		\begin{itemize}
-			\item Produces higher tariffs than executives prefer
-			\item Reduces equilibrium lobbying effort
-			\item Trade agreement as political commitment device
+			\item P
+			\item R
+			\item T
 		\end{itemize}
-	\item Tariff levels and optimal lobbying depend on how much political uncertainty is present
+	\item T
 \end{itemize}
@@
 \begin{enumerate}[<+->]
-	\item Background and Motivation
-	\item Economic and Political Structure
-	\item Results for a Special Case: Certainty
-	\item Full Results: Political Uncertainty
+	\item B
+	\item E
+	\item R
+	\item F
 	\item Conclusion
@@
 
-\begin{frame}{Standard Unitary Government Model}
-Grossman $\&$ Helpman government welfare function:
-				\[
-				  C + aW
-				\]
-\pause
-		\begin{itemize}[<+->]
-			\item Government auctions tariffs/subsidies: lobbies pay for $a$-weighted welfare loss
-			\item Estimated $a$'s far too large
-				\begin{itemize}
-					\item Implies that governments respond very little to lobbying effort
-					\item Inconsistent with observed large tariffs relative to small lobbying effort
-				\end{itemize}
-		\end{itemize}
-\end{frame}
-
-\begin{frame}{Trade Agreements and Separation of Powers}
-  \pause
-  Take special case of `Protection for Sale' model (single lobby) and generalize government structure
-  \pause
-		\begin{itemize}[<+->]
-			\item Executives can make trade agreement
-			\item Legislatures retain final authority: can break agreement and start trade war / fail to ratify
-			\item Trade war is subgame of the trade-agreement-setting game
-				\begin{itemize}
-  				\item Executives consider lobbying incentives and possibility of trade war when forming agreement
-				\end{itemize}
-		\end{itemize}
-\end{frame}
-
+\begin{comment}
 \subsection{}
@@
 \end{frame}
+\end{comment}
 
@@
 	\item $e_{tw}$: Lobbying effort for trade-war tariffs
-	\item $\bm{\tau^a} = (\tau^a,\tau^{*a})$: tariff under an agreement
-	\item $\bm{\tau^{\mathit{tw}}} = (\tau^{\mathit{tw}},\tau^{*\mathit{tw}})$: tariff when agreement is broken
+	\item $(\tau^a,\tau^{*a})$: trade agreement tariffs
+	\item $\tau^{\textit{ad}}$: tariff equivalent under anti-dumping duties
 \end{itemize}
@@
 
-\section{Certainty}
+\section{Results}
 \subsection{Results: The Certain Case}
@@
 
-\section{Full Results}
+\subsection{Full Results}
 \begin{frame}{Political Uncertainty Illustration}
@@
 
-\subsection{Ratification / Maintenance Stage}
 \begin{frame}{Timeline}
@@
 
-\subsection{Formation Stage}
-\begin{frame}{Timeline}
-\begin{enumerate}
-	\item \textbf{Formation}
-		\begin{enumerate}[i.]
-			\item Executives set trade policy in international agreement
-		\end{enumerate}
-	\item {\color{gray} \textbf{Ratification / Maintenance}}
-		\begin{enumerate}[i.]
-			\item {\color{gray} Firms lobby legislatures to break agreement}
-			\item {\color{gray} Legislatures decide to break or abide by agreement}
-		\end{enumerate}
-	\item {\color{gray} \textbf{Trade War} (if agreement is broken)}
-		\begin{enumerate}[i.]
-			\item {\color{gray} Firms lobby legislatures to set high trade-war tariff}
-			\item {\color{gray} Legislatures decide trade-war tariff}
-		\end{enumerate}
-	\item {\color{gray} Private actors make production, consumption decisions}
-\end{enumerate}
-\end{frame}
-
-\begin{frame}{Total Break Probability}
-$B(\bta) = b(e_b(\bta),\bta)$
-\pause
-\begin{itemize}[<+->]
-	\item Both direct and indirect effects of raising $\bta$ are negative
-		\begin{itemize}
-			\item $B(\bta)$ decreasing in $\bta$
-		\end{itemize}
-\end{itemize}
-\pause
-\vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
-   The total probability that the trade agreement will be broken is decreasing in the trade agreement tariffs.
-\end{beamerboxesrounded}
-
-\end{frame}
-
-\begin{frame}{Executives' Tradeoff}
-\[
-  \Pr\left[ \text{TradeWar}(\bta) \right] \bm{W_E}(\btn) + \left\{1- \Pr\left[ \text{TradeWar}(\bta) \right]\right\} \bm{W_E}(\bta)
-\]
-\pause
-\vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 5}
-    The executives face the following trade off when choosing $\bta$: higher tariffs decrease the probability that the trade agreement will be broken, but they also decrease welfare when the agreement is in force.
-\end{beamerboxesrounded}
-\end{frame}
-
-\begin{frame}{Trade Agreements}
-
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 4}
-  The executives maximize their welfare by either (a) trading off reductions in the probability that the agreement will be broken with reductions in welfare under the agreement or (b) raising tariffs sufficiently high to ensure that the trade agreement will remain in force.
-\end{beamerboxesrounded}
-\end{frame}
-
-\begin{comment}
-\begin{frame}{Comparing Government Structures}
-\begin{changemargin}{-1cm}{-1cm}
-\begin{table}
-\centering
-  \begin{tabular}{lrrrr}
-		\toprule
-			Structure & $\bta$ & Lobbying & $B(\bta)$ & $\expect[\bta]$ \\
-			\midrule
-			Unitary, No Agreement & ---- & 0.0017 & 0 & 0.129 \\
-			Unitary, Agreement & 0.118 & 0.0027 & 0 & 0.118 \\
-			\\
-			Exec-led Agreement (.25) & 0.078 & 0.0007 & 0.48 & 0.102 \\
-			Exec-led Agreement (.00) & 0.106 & 0.0000 & 0 & 0.106 \\
-			& {\color{gray}(.105)} & {\color{gray}(.0025)} & {\color{gray}(1)} & {\color{gray}(.129)} \\
-		\bottomrule
-	\end{tabular}
-	\end{table}
-\end{changemargin}
-\end{frame}
-
-\begin{frame}{Comparative Systems}
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Conjecture}
-    Lobbying effort and tariffs are reduced by the presence of executive branches who form a trade agreement.
-\end{beamerboxesrounded}
-
-\pause
-\vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Corollary}
-    Tariffs are lower in countries with separated powers than in those with unitary governments.
-\end{beamerboxesrounded}
-\end{frame}
-\end{comment}
-
-\begin{frame}[label=Uncertainty]
-\frametitle{Uncertainty}
-\begin{itemize}[<+->]
-	\item Added intuition for lobbying incentives and tariff-setting behavior
-  \item High tariffs, low but positive lobbying effort
-  \item Possibility of trade disruptions / ratification failure in equilibrium
-  \item Different behavior at varying levels of uncertainty
-\end{itemize}
-\end{frame}
-
 \section{Conclusion}
@@
 \begin{itemize}[<+->]
-	\item Comparative statics on weighting function
-	\item Empirical Tests
-	\item Parallel models for countries with different government structures
-	\item Asymmetric agreements
-	\item Repeated model
-		\begin{itemize}
-			\item Implications for design of dispute settlement procedures
-		\end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}{Conclusion}
-Resolution of `Protection for Sale' Puzzle
-\pause
-\begin{itemize}[<+->]
-	\item Non-unitary legislature: more realistic lobbying process
-	\item Separation of Powers: tariffs set in shadow of lobbying
-	\item Uncertainty: smoother results, additional intuition
+	\item C
+	\item E
+	\item P
+	\item A
 \end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Social welfare maximizers ($a \approx \infty$) set high tariffs to achieve low lobbying expenditures (and low $\ga_{ML}$) 
-	\item Executives use trade agreement to manipulate lobbying incentives
-		\begin{itemize}
-			\item Trade agreement as political commitment device
-		\end{itemize}
-	\item Firms lobby for trade war / ratification failure and achieve equilibrium trade disruptions in some cases
-		\begin{itemize}
-			\item Can examine the endogenous dynamics behind politically-driven failures to cooperate
-		\end{itemize}
+	\item S
+	\item E
+	\item F
 \end{itemize}

### 2016-05-11 presentation.tex
update lobby slide

@@
 Lobby chooses effort to maximize:
-\begin{multline*}
-  \left\{1-\Pr\left[ \text{TradeWar}(e_b,\bta)\right]\right\} \ \pi(\tau^a) \\
-     + \Pr\left[ \text{TradeWar}(e_b,\bta) \right] \left[ \pi(\tau^{\mathit{tw}}) - e_{tw} \right] - e_b
-\end{multline*}
+\[
+  \left\{1-\Pr\left[ \text{AD Renewal}\right]\right\} \ \pi(\tau^a) + \Pr\left[ \text{AD Renewal} \right]  \pi(\tau^{\mathit{ad}})  - e
+\]
 
-\vskip.2in
+\vskip.1in
 \begin{itemize}
-	\item $e_b$: Lobbying effort for break decision
-	\item $e_{tw}$: Lobbying effort for trade-war tariffs
-	\item $(\tau^a,\tau^{*a})$: trade agreement tariffs
-	\item $\tau^{\textit{ad}}$: tariff equivalent under anti-dumping duties
+	\item $e$: Lobbying effort
+	\item $\tau^a$: home import tariff under trade agreement
+	\item $\tau^{\textit{ad}}$: home import tariff equivalent under anti-dumping duties
 \end{itemize}
@@
 \begin{itemize}
-	\item Breaks agreement if median legislator prefers $\bm{\tau^{\mathit{tw}}}$ to $\bta$
+	\item Breaks agreement if median legislator prefers $\tau^{\mathit{ad}}$ to $\tau^a$
 \end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Given the $\bta$ it faces, lobby knows what $e_b$ is required to break the agreement
- 	\item Lobby pays this $e_b$ if: \hskip.2in $\bm{\pi}(\bm{\tau^{\mathit{tw}}}) \bm{- e_{tw}  - e_b > \pi}(\bm{\tau^a})$
+	\item Given the $(\tau^a,\tau^{*a})$ it faces, lobby knows what $e_b$ is required to break the agreement
+ 	\item Lobby pays this $e_b$ if: \hskip.2in $\pi(\tau^{\mathit{tw}}) - e > \pi(\tau^a)$
 \end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Set $\bta$ to make paying $e_b$ unprofitable
+	\item Set $(\tau^a,\tau^{*a})$ to make paying $e_b$ unprofitable
 		\begin{itemize}
@@
   \vskip.1in
-    $b(e_b,\bta,\btn,\ta)$ probability median legislator prefers $\tau^{tw}$ to $\tau^a$ for a given $\ta$
+    $b(e,\tau^a,\tau^{*a},\tau^{\textit{ad}},\ta)$ probability median legislator prefers $\tau^{tw}$ to $\tau^a$ for a given $\ta$
 \end{frame}

### 2016-05-13 presentation.tex
update model and uncertainty sections

@@
 
-\title[Temporary Trade Barriers: When Will They End?\hspace{2.15in}\insertframenumber/\inserttotalframenumber]{Temporary Trade Barriers: \\ When Will They End?}
+\title[Temporary Trade Barriers: When Will They End?\hspace{2.35in}\insertframenumber/\inserttotalframenumber]{Temporary Trade Barriers: \\ When Will They End?}
 \author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
@@
 \pause
-\begin{enumerate}
-	\item {\bfseries Formation}
-		\begin{enumerate}[i.]
+
+Taking trade agreement tariff and anti-dumping duties as given,
 \pause
-			\item Executives set trade policy in international agreement
-		\end{enumerate}
-	\pause
-	\item \textbf{Ratification / Maintenance}
-		\begin{enumerate}[i.]
-			\pause
-			\item Firms lobby legislatures to break agreement
-			\pause
-			\item Uncertainty is resolved
-			\pause
-			\item Legislatures decide to break or abide by agreement
-			\pause
-		\end{enumerate}
-	\item \textbf{Trade War} (if agreement is broken)
-	\pause
-		\begin{enumerate}[i.]
-			\item Firms lobby legislatures to set high trade-war tariff
-			\pause
-			\item Uncertainty is resolved
-			\pause
-			\item Legislatures decide trade-war tariff
-		\end{enumerate}
-\pause
+\begin{enumerate}[<+->]
+	\item \textbf{Import-competing firms lobby DOC/ITC to renew AD duties}
+	\item \textbf{Uncertainty is resolved}
+	\item \textbf{DOC/ITC decide whether to renew duties}
 	\item Private actors make production, consumption decisions
@@
 \begin{frame}{Political Structure}
-In each country (focus on Home):
+In Home country (foreign is passive):
 \pause
 \begin{itemize}[<+->]
-	\item A Unitary Executive
-		\begin{itemize}
-			\item Delegated authority to make trade agreement
-		\end{itemize}
-		%\pause
-	\item A Non-unitary Legislature
+	\item Dept. of Commerce / Int'l Trade Commission
 		\begin{itemize}[<+->]
-			\item Can withdraw delegation, break agreement, and set trade-war tariff
-			\item Susceptible to influence of lobbying
-			\item Decision determined by median legislator
+			\item Can renew AD duties
+			\item Susceptible to influence of lobbying, perhaps both direct and indirect
+			\item Modeled in reduced form
 		\end{itemize}
@@
 		\begin{itemize}
-			\item Represents import-competing sector, $X$ ($Y$ in foreign)
+			\item Represents import-competing sector, $X$
 		\end{itemize}	
@@
 \begin{frame}
-\frametitle{Executive Branch}
-Trade agreement negotiated by unitary executive:
-$$W_E = \mathit{CS}_X(\tau) + \mathit{CS}_Y(\tau^*) + \ga_E \pi_X(\tau) + \pi_Y(\tau^*) + \mathit{TR}(\tau)$$
+\frametitle{``Government''}
+Renewal decision determined by complex process including DOC, ITC, pressure via other political bodies. Reduced form:
+\[
+  W_G = \mathit{CS}_X(\tau) + \ga(e,\ta) \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
+\]
 
-\vskip.2in
 \begin{itemize}
@@
 	\item $\mathit{TR}(\tau)$: tariff revenue
-	\item $\ga_E$: weight on profits in the import-competing industry
 \end{itemize}
-
 \end{frame}
 
-\begin{frame}{Non-Unitary Legislature}
-  Decisions determined by preferences of Median Legislator:
+\begin{frame}
+\frametitle{``Government''}
 \[
-  W_{\mathit{ML}} = \mathit{CS}_X(\tau) + \mathit{CS}_Y(\tau^*) + \ga(e,\ta) \pi_X(\tau) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
+  W_G = \mathit{CS}_X(\tau) + \ga(e,\ta) \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
 \]
-\vskip-.1in
+
 \pause
@@
 			\pause
-			\item $\ta$: uncertain element in determination of ML's identity
+			\item $\ta$: uncertain element in $G$'s preferences
 		\end{itemize}
@@
 \vskip.1in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumptions on $\ga(e,\ta)$}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumption 1}
 \begin{enumerate}
@@
 	\item $\ga(e,\ta)$ is increasing and concave in $e$ for all $\ta \in \Theta$.
-  \pause
-  \item $\ga(e,\ta) \geq \ga_E \geq 1 \ \forall \ta$ 
 \end{enumerate}
@@
 
-\section{Results}
-\subsection{Results: The Certain Case}
+\section{Uncertainty}
+\subsection{}
 \begin{frame}{Timeline}
-\begin{enumerate}
-	\item \textbf{Formation}
-		\begin{enumerate}[i.]
-			\item Executives set trade policy in international agreement
-		\end{enumerate}
-	\item \textbf{Ratification / Maintenance}
-		\begin{enumerate}[i.]
-			\item Firms lobby legislatures to break agreement
-			\item Legislatures decide to break or abide by agreement
-		\end{enumerate}
-	\item {\color{gray} \textbf{Trade War} (if agreement is broken)}
-		\begin{enumerate}[i.]
-			\item {\color{gray} Firms lobby legislatures to set high trade-war tariff}
-			\item {\color{gray} Legislatures decide trade-war tariff}
-		\end{enumerate}
+\begin{enumerate}[<+->]
+	\item \textbf{Import-competing firms lobby DOC/ITC to renew AD duties}
+	\item {\color{gray} \textbf{Uncertainty is resolved}}
+	\item \textbf{DOC/ITC decide whether to renew duties}
 	\item {\color{gray} Private actors make production, consumption decisions}
 \end{enumerate}
+
 \end{frame}
 
-\begin{frame}{Highlight: Separation of Powers}
+\begin{frame}{Why uncertainty?}
 \pause
@@
 \begin{itemize}
-	\item Breaks agreement if median legislator prefers $\tau^{\mathit{ad}}$ to $\tau^a$
+	\item Renews AD duties if $G$ prefers $\tau^{\mathit{ad}}$ to $\tau^a$
 \end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Given the $(\tau^a,\tau^{*a})$ it faces, lobby knows what $e_b$ is required to break the agreement
- 	\item Lobby pays this $e_b$ if: \hskip.2in $\pi(\tau^{\mathit{tw}}) - e > \pi(\tau^a)$
+	\item Given $(\tau^a,\tau^{*a})$ and $\tau^{\mathit{ad}}$, lobby knows what $e$ is required to induce renewal
+ 	\item Lobby pays this $e$ if: \hskip.2in $\pi(\tau^{\mathit{ad}}) - e > \pi(\tau^a)$
 \end{itemize}
@@
 \pause
-\vskip.13in
-\textbf{Executives}
+\vskip.1in
+\textbf{In Equilibrium}
 \pause
 \begin{itemize}[<+->]
-	\item Set $(\tau^a,\tau^{*a})$ to make paying $e_b$ unprofitable
-		\begin{itemize}
-			\item[$\Rightarrow$] $e_b=0$, agreement remains in force
-		\end{itemize}
-	\item High tariffs, no lobbying, no trade disruptions
-\end{itemize}
-\end{frame}
-
-\subsection{Full Results}
-\begin{frame}{Political Uncertainty Illustration}
-\pause
-An Example (Bagwell $\&$ Staiger 2005)
-\pause
-\begin{itemize}[<+->]
-	\item $D(P_i) = 1 - P_i$
-	\item $Q_X(P_X) = \frac{P_X}{2}$, $Q_Y(P_Y) = P_Y$
-	\item $P_X^W = \frac{4-3\tau}{7}$, $P_X = \frac{4+4\tau}{7}$
-	\item $\ga(e,\ta) = 1.25 + e^{0.2} + \ta$ 
-		\begin{itemize}
-			\item $\ta \sim U[-0.25,0.25]$
-		\end{itemize}
-	\item $\ga_E = 1$
+	\item Firms only put forth effort when they know renewal will be granted
 \end{itemize}
@@
 
+\section{Results}
+\subsection{}
 \begin{frame}{Timeline}
-\begin{enumerate}
-	\item {\color{gray} \textbf{Formation}}
-		\begin{enumerate}[i.]
-			\item {\color{gray} Executives set trade policy in international agreement}
-		\end{enumerate}
-	\item \textbf{Ratification / Maintenance}
-		\begin{enumerate}[i.]
-			\item {\color{gray} Firms lobby legislatures to break agreement}
-			\item Legislatures decide to break or abide by agreement
-		\end{enumerate}
-	\item {\color{gray} \textbf{Trade War} (if agreement is broken)}
-		\begin{enumerate}[i.]
-			\item {\color{gray} Firms lobby legislatures to set high trade-war tariff}
-			\item {\color{gray} Legislatures decide trade-war tariff}
-		\end{enumerate}
-	\item {\color{gray} Private actors make production, consumption decisions}
+\begin{enumerate}[<+->]
+	\item \textbf{Import-competing firms lobby DOC/ITC to renew AD duties}
+	\item \textbf{Uncertainty is resolved}
+	\item \textbf{DOC/ITC decide whether to renew duties}
+	\item Private actors make production, consumption decisions
 \end{enumerate}
@@
 
-\begin{frame}{Legislature}
-  Legislature breaks trade agreement if median legislator's utility is higher under trade war than trade agreement
+\begin{frame}{Government}
+  $G$ breaks trade agreement if its utility is higher under AD duties than trade agreement tariff
   \begin{itemize}
-		\item Median legislator's identity is uncertain through $\ta$
+		\item Preferences are uncertain through $\ta$
 	\end{itemize}
@@
   \vskip.2in
-  Probability that Legislature breaks agreement: \\
+  Probability that $G$ breaks agreement: \\
 	\pause
   \vskip.1in
-    $b(e,\tau^a,\tau^{*a},\tau^{\textit{ad}},\ta)$ probability median legislator prefers $\tau^{tw}$ to $\tau^a$ for a given $\ta$
-\end{frame}
-
-\begin{frame}{Timeline}
-\begin{enumerate}
-	\item {\color{gray} \textbf{Formation}}
-		\begin{enumerate}[i.]
-			\item {\color{gray} Executives set trade policy in international agreement}
-		\end{enumerate}
-	\item \textbf{Ratification / Maintenance}
-		\begin{enumerate}[i.]
-			\item Firms lobby legislatures to break agreement
-			\item {\color{gray} Legislatures decide to break or abide by agreement}
-		\end{enumerate}
-	\item {\color{gray} \textbf{Trade War} (if agreement is broken)}
-		\begin{enumerate}[i.]
-			\item {\color{gray} Firms lobby legislatures to set high trade-war tariff}
-			\item {\color{gray} Legislatures decide trade-war tariff}
-		\end{enumerate}
-	\item {\color{gray} Private actors make production, consumption decisions}
-\end{enumerate}
+    $b(e,\tau^a,\tau^{*a},\tau^{\textit{ad}},\ta)$ probability median legislator prefers $\tau^{ad}$ to $\tau^a$ for a given $\ta$ and $e$
 \end{frame}

### 2016-05-13 presentation.tex
add first three results

@@
 \pause
-\textbf{Legislature}
+\textbf{Government}
 \pause
@@
 \begin{frame}{Government}
-  $G$ breaks trade agreement if its utility is higher under AD duties than trade agreement tariff
+  $G$ renews AD duties if its utility is higher under AD duties than trade agreement tariff
   \begin{itemize}
-		\item Preferences are uncertain through $\ta$
+		\item Preferences are ex-ante uncertain through $\ta$
+		\pause
+		\item When does $G$ renew AD duties? \\
+	\pause
+  \vskip.1in
+    $b(e,\tau^a,\tau^{\textit{ad}})$: probability $G$ prefers $\tau^{ad}$ to $\tau^a$ for a given effort level $e$
 \end{itemize}
@@
 \pause
-  \vskip.2in
-  Probability that $G$ breaks agreement: \\
-	\pause
-  \vskip.1in
-    $b(e,\tau^a,\tau^{*a},\tau^{\textit{ad}},\ta)$ probability median legislator prefers $\tau^{ad}$ to $\tau^a$ for a given $\ta$ and $e$
+\vskip.25in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 1}
+  The probability that $G$ renews AD duties is increasing and concave in lobbying effort $e$ $\left(\text{i.e.
+} \frac{\partial b}{\partial e} \geq 0, \ \frac{\partial^2 b}{\partial e^2} \leq 0  \right)$.
+\end{beamerboxesrounded}
+
+\end{frame}
+
+\begin{frame}{Home's Trade Agreement Tariff}
+
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 1}
+  The total probability that $G$ renews AD duties is decreasing in the home trade agreement tariff $\tau^a$.
+\end{beamerboxesrounded}
+
+\vskip.25in
+There's both a direct effect and an indirect effect through lobby's incentives, and both are negative:
+\[
+  \frac{\partial b}{\partial e} \frac{\partial e}{\partial \tau^a} + \frac{\partial b}{\partial \tau^a}
+\]
+\end{frame}
+
+\begin{frame}{Foreign's Trade Agreement Tariff}
+
+Assuming trading partner does not retaliate
+\begin{itemize}
+	\item No difference in foreign tariff under AD duty and $\tau^a$. So no effect on $G$'s incentives (either direct or indirect)
+\end{itemize}
+
+\vskip.25in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 2}
+  The total probability that $G$ renews AD duties is unaffected by foreign's trade agreement tariff $\tau^a$.
+\end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}{Profitability of Import-Competing Sector}
+
+Assume $\pi(\cdot)$ shifts up uniformly for all $\tau$.
+\begin{itemize}
+	\item Convexity of profits $\Rightarrow$ $G$'s marginal benefit of providing protection goes up
+	\item Convexity of profits $\Rightarrow$ return from lobbying increases
+\end{itemize}
+
+\vskip.25in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
+  The total probability that $G$ renews AD duties is increasing in the profitability of the import-competing sector.
+\end{beamerboxesrounded}
 \end{frame}

### 2016-05-13 presentation.tex
add two more results

@@
   $G$ renews AD duties if its utility is higher under AD duties than trade agreement tariff
+	\pause
   \begin{itemize}
@@
 
+\pause
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 1}
@@
 \vskip.25in
+\pause
 There's both a direct effect and an indirect effect through lobby's incentives, and both are negative:
@@
 Assuming trading partner does not retaliate
+\pause
 \begin{itemize}
@@
 \vskip.25in
+\pause
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 2}
@@
 
+\pause
 Assume $\pi(\cdot)$ shifts up uniformly for all $\tau$.
-\begin{itemize}
+\pause
+\begin{itemize}[<+->]
 	\item Convexity of profits $\Rightarrow$ $G$'s marginal benefit of providing protection goes up
@@
 \vskip.25in
+\pause
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
@@
 \end{beamerboxesrounded}
+\end{frame}
+
+[<+->]
+\begin{frame}{Exogenous Shifts in $\ga(e,\ta)$}
+
+\pause
+Assume $\ga(\cdot,\cdot)$ shifts up uniformly for all $(e,\ta)$ pairs.
+\pause
+\begin{itemize}[<+->]
+	\item $G$ gives more weight to firms' benefit
+	\item Lobbying incentives are unchanged
+\end{itemize}
+
+\vskip.25in
+\pause
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
+  The total probability that $G$ renews AD duties increases when the weighting function shifts up exogenously and uniformly.
+\end{beamerboxesrounded}
+\end{frame}
+
+\begin{frame}{Protection from AD Duties}
+
+\pause
+When $\tau^{\textit{ad}}$ increases, two effects on $G$'s incentives:
+\pause
+\begin{itemize}[<+->]
+	\item Social welfare decreases, pushes for decrease in renewal probability 
+	\item (Over-weighted) import-competing profits increase, pushes for increase in renewal probability 
+\end{itemize}
+
+\vskip.2in
+\pause
+Indirect effect is of same sign as direct effect
+\pause
+\begin{itemize}[<+->]
+	\item When $\tau^{\textit{ad}}$ (i.e. close to social optimum), second effect dominates $\Rightarrow$ increase in renewal probability
+	\item Effect may be concave
+\end{itemize}
+
 \end{frame}

### 2016-05-13 presentation.tex
add future work slide

@@
 \begin{frame}
-\frametitle{P}
-In 
+\frametitle{The Questions}
 \pause
 \begin{itemize}[<+->]
-	\item r
-  \item g
-	\item a
+	\item How long do deviations from trade agreement tariffs last? 
+  \item What are the determinants of these deviations?
+		\begin{itemize}
+			\item They don't happen for \textit{no} reason at all
+			\item Take political economy perspective
 		\end{itemize}
+	\item 
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Institutional Detail}
+\begin{enumerate}[<+->]
+	\item Temporary trade barriers have potential to be renewed
+		\begin{itemize}
+			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
+			\item For Safeguards, four then four; much rarer than AD
+		\end{itemize}
+	\item Authorized by WTO
+	\item Very little in the agreements to guide the process
+	\item WTO litigation has given governments a LOT of latitude on renewals
+	\item Conclusion
+\end{enumerate}
 \end{frame}
@@
 \end{itemize}
-\end{frame}
-
-\begin{frame}{Outline of Talk}
-\begin{enumerate}[<+->]
-	\item B
-	\item E
-	\item R
-	\item F
-	\item Conclusion
-\end{enumerate}
 \end{frame}
@@
 
+\begin{frame}{What's this uncertainty about?}
+\pause
+Lobby must be able to trigger the original AD duty
+\begin{itemize}
+	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
+	\item It could be justified, not motivated by politics/rent-seeking
+	\item But still, firms lobby for duties they don't get
+\end{itemize}
+
+\pause
+\vskip.1in
+So what's the uncertainty about?
+\pause
+\begin{itemize}[<+->]
+	\item Strength of evidence
+	\item Probability foreign will retaliate or initiate dispute (indirect)
+	\item $G$'s valuation of harm to industry, e.g. how politically important is industry?
+\end{itemize}
+
+\end{frame}
+
 \section{Results}
@@
 \begin{frame}{Future Work}
+\pause
 \begin{itemize}[<+->]
-	\item C
-	\item E
-	\item P
-	\item A
+	\item Comparative static on uncertainty measure
+	\item Empirical work
+	\item Extend model to include initial decision to grant protection.
+		\begin{itemize}
+			\item Explain variation in a lobby's incentives between original application of AD and renewal
+			\item Lobby's choice between investing in productive vs. rent-seeking behavior while protected
+		\end{itemize}
 \end{itemize}
@@
 
+\begin{comment}
 \begin{frame}{Conclusion}

### 2016-05-13 presentation.tex
final version for InsTED

@@
-%\documentclass{beamer} 
-\documentclass[handout]{beamer} 
+\documentclass{beamer} 
+%\documentclass[handout]{beamer} 
 \usetheme{Ilmenau}
@@
 \pause
-\begin{itemize}[<+->]
+\begin{enumerate}[<+->]
 	\item How long do deviations from trade agreement tariffs last? 
-  \item What are the determinants of these deviations?
+  \item What are the determinants of renewals?
 		\begin{itemize}
 			\item They don't happen for \textit{no} reason at all
-			\item Take political economy perspective
 		\end{itemize}
-	\item 
-\end{itemize}
+\end{enumerate}
 \end{frame}
@@
 \begin{frame}{Institutional Detail}
-\begin{enumerate}[<+->]
+\begin{itemize}[<+->]
 	\item Temporary trade barriers have potential to be renewed
@@
 	\item Very little in the agreements to guide the process
-	\item WTO litigation has given governments a LOT of latitude on renewals
-	\item Conclusion
-\end{enumerate}
+		\begin{itemize}
+			\item WTO litigation gives gov'ts a LOT of latitude
+		\end{itemize}
+	\item In U.S., for AD:
+		\begin{itemize}
+			\item DOC initiates, determines whether dumping would continue
+			\item ITC determines whether injury would recur / continue
+		\end{itemize}
+\end{itemize}
 \end{frame}
@@
 \begin{frame}{Preview of Results}
+
+\pause
+The probability that an AD duty gets renewed
+\pause
 \begin{itemize}[<+->]
-	\item H
-		\begin{itemize}
-			\item R
-		\end{itemize}
-	\item E
-		\begin{itemize}
-			\item P
-			\item R
-			\item T
-		\end{itemize}
-	\item T
+	\item Increases in lobbying effort
+	\item Decreases in the MFN tariff
+	\item Is invariant to the trading partner's tariff
+	\item Increases in the profitability of the import-competing sector
+	\item Increases in the strength of the lobby
+	\item May be concave in the AD duty
 \end{itemize}
@@
 \frametitle{``Government''}
+\pause
 Renewal decision determined by complex process including DOC, ITC, pressure via other political bodies. Reduced form:
+\pause
 \[
@@
 
-\begin{itemize}
+\pause
+\begin{itemize}[<+->]
 	\item $\mathit{CS_i(\cdot)}$: consumer surplus
@@
 \vskip.2in
+\pause
 Lobby chooses effort to maximize:
@@
 \vskip.1in
-\begin{itemize}
+\pause
+\begin{itemize}[<+->]
 	\item $e$: Lobbying effort
@@
 Lobby must be able to trigger the original AD duty
-\begin{itemize}
+\begin{itemize}[<+->]
 	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
@@
 
-[<+->]
 \begin{frame}{Exogenous Shifts in $\ga(e,\ta)$}

### 2017-09-18 draft.tex
add draft from SOP-RIE as starting place

\documentclass[10pt]{article}

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
%\linespread{1.5}
\usepackage{setspace}
\doublespacing

\usepackage{titling}

\usepackage[pdftex]{graphicx}

\usepackage[usenames,dvipsnames]{color}
\usepackage{cite}
\usepackage{times, verbatim,bm,pifont,pdfsync}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{tikz}
\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5,fill=white}
%non node/.style={circle,draw,inner sep=.1,fill=black}
}

% disables chapter, section and subsection numbering
%\setcounter{secnumdepth}{-1}

\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}
\usepackage[hang,flushmargin]{footmisc}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem*{lemma*}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\newtheorem{result}{Result}

\newcommand{\ve}{\theta}
\newcommand{\ta}{\theta}
\newcommand{\ov}{\overline}
\newcommand{\un}{\underline}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

\begin{document}
\title{\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}}
\thanksmarkseries{alph}
\author{Kristy Buzard\thanks{Syracuse University, Economics Department, 110 Eggers Hall, Syracuse, NY 13244, USA. Ph: 315-443-4079. Fax: 315-443-3717. Email: kbuzard@syr.edu. http://faculty.maxwell.syr.edu/kbuzard. I gratefully acknowledge funding from the W. Allen Wallis Institute of Political Economy.}} 
\date{\vskip-.1in \today}
\maketitle

\begin{center} {\bf Abstract} \end{center}

\begin{quote}
{This paper presents a model of international trade agreements in which the executive branches of each government negotiate agreements while the legislative branches, subject to political pressure from firms, can disrupt them. Lobbying is in the style of Grossman and Helpman (1994) with a new feature: all actors face uncertainty arising from the complexity of the legislative process. I demonstrate that the higher the executives set tariffs in a trade agreement, the less effort lobbies put forth to prevent its ratification. Thus trade agreements act as a domestic political commitment device: executives set relatively high tariffs to discourage lobbying and increase the chance that the agreement will be ratified. The model sheds light on the empirical puzzle surrounding governments' welfare weights in the Grossman and Helpman (1994) model and provides a new explanation for failures to ratify trade agreements.

\textit{JEL classification:} D72, D80, F13, F53, F55 \\
\textit{Keywords:} trade agreements, protection, lobbying, political economy, uncertainty}
\end{quote}

\bigskip
\section{Introduction}

%http://www.whitehouse.gov/sites/default/files/fact_sheet_increasing_us_auto_exports_us_korea_free_trade_agreement.pdf

Much of trade policy is determined in the context of international agreements that must be ratified by some domestic body. This paper sheds light on such a policy-making process by incorporating Protection-for-Sale (Grossman and Helpman 1994, hereafter PFS) style lobbying into a model of trade agreements in which the executive branches of the governments set tariff levels in anticipation of political pressure upon a ratifying body, assumed here to be a legislature. Important realism is achieved not only through the addition of the ratification constraint but also by the incorporation of political uncertainty into the model.

I show that the probability that the trade agreement is derailed increases in lobbying effort and decreases in the trade agreement tariff. Further, the lobby decreases its effort as the trade agreement tariff rises: it has less to lose the higher is the trade agreement tariff. When choosing the trade agreement tariffs, the executives therefore trade off the welfare they receive under the agreement with the probability that the agreement remains in force. Ultimately, I find that observed lobbying effort may often be low because the executives set trade agreement tariffs sufficiently high to reduce political pressure on the legislatures.

To see how this works, let's begin by considering the case of political certainty. I assume the executive is more pro-social than the legislature, as has been the case throughout the post-war period in the United States. Lobbies, assumed for simplicity to represent import-competing interests only, would like to prevent or derail a trade agreement that would reduce their tariff protection. They work toward this end by exerting effort to convince their respective legislatures to vote against or ``break'' the trade agreement.\footnote{In this model, non-ratification is equivalent to breaking a trade agreement once in place because tariffs in a ``trade war'' are assumed to be set non-cooperatively just as if there were no trade agreement. For simplicity, I refer to this as the ``break'' decision throughout.}

For any trade-agreement tariff set by the executives, a lobby can calculate the effort level required to shift the preferences of the median legislator just far enough so that he will choose the non-cooperative tariffs over the trade agreement tariffs. Because the lobby will pay this price so long as its benefit outweighs the cost, a trade war will occur unless the executives set the trade-agreement tariff so that lobbying is not worthwhile.

Thus, any trade agreement under political certainty involves a tariff high enough to disengage the lobby completely; that is, even welfare-maximizing executives set high tariffs and induce zero contributions in equilibrium because they set policy in the shadow of a ratification decision influenced by lobbying.

The fact that zero contributions are predicted in equilibrium is not particularly satisfying. The model becomes more realistic, has smoother results and delivers additional intuition when I allow all actors to be uncertain about the weight the median legislator places on the profits of the lobbying industry. Similar to probabilistic voting models that incorporate policy motivation as in Roemer (1997), this represents the idea that the lobbying and voting ``game'' that goes on within legislatures is often so complex that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote. One can conceptualize this uncertainty as being a result of the lobby's strategic choice to engage with only some key members of the legislature. For instance, the lobbied legislators may promise to deliver the votes of their non-lobbied colleagues but may not be able to do so with certainty because those colleagues are subject to cross-pressuring from various sources.

One contribution of this model is that it shows how trade agreements can act as a domestic political commitment device in a broad set of environments. The executives set trade-agreement tariffs with an eye to discouraging lobbying activity and the accompanying probability of abrogation. In addition to the standard terms-of-trade internalization, the executive's agenda-setting power allows it to reduce tariffs until lobbying activity is at the optimal level relative to a non-cooperative setting, reducing the amount of political pressure faced by the legislatures and the resultant expected tariffs.

This is not a time inconsistency \`{a} la Maggi and Rodr\'{i}guez-Clare (2007) where the welfare of the unitary policymaker is improved by changing firms' investment decisions via commitment to a trade agreement. Instead, this is an inconsistency between the preferences of the executive and legislative branches. Although the legislatures have the final word, the executives use the trade agreement to reduce lobbying effort, muting the legislature's protectionist bias and bringing the outcome more in line with their relatively liberal preferences.

A further contribution is the demonstration that lobbying effort and the probability of trade disruptions vary in nuanced ways with the amount of political uncertainty present. Lobbying incentives are crucial but their impact is not necessarily as straightforward as predicted by models with unitary governments. Gawande, Krishna and Olarreaga (2009) provide cross-country evidence that measures such as the number of checks and balances on the power of the legislature have predictive power for the PFS ``welfare-mindedness'' parameter. Thus, although empirical tests are outside the scope of this paper, there is suggestive evidence that political uncertainty is indeed empirically important.

To the best of my knowledge, this is also the first attempt to model lobbying specifically aimed at derailing trade agreements. Although this kind of politically-driven failure is not rare, prior models have not allowed exploration of the endogenous dynamics behind them.

The addition of a rich structure of government, tailored carefully to the trade policy making process, also helps shed light on the empirical puzzle surrounding the PFS model. Empirical tests of the model\footnote{cfr. Goldberg and Maggi (1999); Gawande and Bandyopadhyay (2000); Mitra, Thomakos and Ulubasoglu (2002); McCalman (2004).\label{fn:gh_lobby}} have consistently found the weight governments place on social welfare to be many times that which they place on lobbying effort, while estimates indicate that the deadweight losses caused by trade distortions are several orders of magnitude larger than lobbying expenditures.\footnote{Feenstra (1992) assembles estimates from the mid-1980s that place a floor of $\$$8 billion per year on the deadweight losses from protection, whereas Bombardini and Trebbi (2012) find that total annual lobbying expenditure on trade issues in 1999-2001 when this data first became available was about $\$$200 million.} This raises the question: how could governments value social welfare so highly, yet grant these quantities of protection at such a low price?

Attempts to more fully model the lobbying process have reduced the parameter estimates for the government's welfare considerations somewhat, but they still indicate that the U.S. government, for instance, values social welfare at least twenty times as much as contributions.\footnote{cfr. Gawande, Krishna and Robbins (2006); Mitra, Thomakos and Ulubasoglu (2006); Bombardini (2008); and Gawande, Krishna and Olarreaga (2012) among others. Gawande and Magee (2012) provide a summary of the extensive literature, while Imai, Katayama and Krishna (2009) argue that many of the classification schemes present serious challenges for the validity of results.} As suggested by Gawande and Hoekman (2006), in the non-unitary government model, these estimates and the stylized facts are not inconsistent. The ``missing contributions,'' can be explained as an equilibrium phenomenon arising from the agenda-setting power of the executive branch. In particular, in this model, there is no inconsistency for the 15$\%$ or so of sectors that receive protection but apparently put forth no lobbying effort. In this framework, even a welfare-maximizing executive and lobbying effort at zero can be reconciled with high tariff levels.

Although the political process here most closely matches that of the United States in the post-war era,\footnote{In particular, the legislatures' decision to abide by or break the trade agreement is modeled on the ``Fast Track / Trade Promotion Authority'' that the U.S. Congress periodically grants to the Executive branch.} the model is broadly applicable because the central dynamic that emerges---that trade agreements are formed in the \textit{shadow} of lobbying pressure instead of in direct response to it---appears to be present in a wide range of countries. The results apply beyond separation-of-powers presidential systems because the presence of veto points is what is essential for this dynamic to occur. Although the number of formal veto points tends to be lower in, for instance, parliamentary systems, veto points are typically not absent altogether (Henisz and Mansfield 2006). In reality, constraints on the executive are almost always present in democratic regimes, although they may operate in different ways.

\subsection{Related Literature}
This work rests on the foundation of Grossman and Helpman's (1994) `Protection for Sale.' Two related papers `Trade Wars and Trade Talks' (Grossman and Helpman (1995b)) and `The Politics of Free-Trade Agreements' (Grossman and Helpman (1995a)) first employed the PFS approach in the study of trade agreements. The first considers ``Trade Wars'' and ``Trade Talks'' separately, whereas my approach views the ``Trade War'' as a crucial subgame. The model of preferential trade agreements (Grossman and Helpman (1995a)), although treating the government as a unitary actor, is closer to this approach.

Another related literature considers the impact of exogenously-determined political uncertainty on the potential for trade cooperation. These studies (e.g. Feenstra and Lewis (1991); Milner and Rosendorff (2001); Bagwell and Staiger (2005); Beshkar (2010); Horn, Maggi and Staiger (2010); Beshkar and Bond (2012)) derive various implications for the design of international trade agreements using a Baldwin (1987)-style government welfare function with exogenous shocks to the political-pressure parameter.

Since trade policies are overwhelmingly determined in the context of trade agreements, it is useful to have a framework to bring together the endogenous political pressure of PFS-style modeling with the trade agreements approach. The government objective function introduced in this paper is intended to be a bridge between the two. This objective function starts from the Baldwin (1987) government objective function and adds flexibility: the weight the legislature places on profits is endogenous (PFS), potentially non-linear (Findlay and Wellisz 1982; Dixit, Grossman and Helpman 1997) and stochastic. Buzard (2016) is an example of how this modeling approach can be used to integrate  endogenous political activity and exogenous shocks into the analysis of questions regarding optimal trade agreement design.

Modeling the objective function so closely on the standard in the trade agreements literature allows for direct comparisons to the large body of work that studies exogenous shocks only, revealing cleanly the effects of the addition of endogenous lobbying. To preview, this model is closest to that of Bagwell and Staiger (2005), with two main changes: in place of their unitary government signing a trade agreement and having different preferences ex-ante and ex-post, this model has two branches of government with differing preferences, where the political economy weights of the legislature are determined endogenously.

Mansfield, Milner and Rosendorff (2000) study the impact of executive/legislative interactions on international agreements in the case of exogenously-determined preferences. They show that democracies trade more with each other because the domestic legislature only cooperates if the foreign government makes deep tariff cuts. Ethier (2002) treats the effect of a separation of powers between trade negotiators and the government officials who administer protection.

Milner and Rosendorff (1997) explore how uncertainty can affect trade policy and ratification failure when political preferences, and therefore uncertainty, are exogenous. In Le Breton and Salanie (2003), the lobby is uncertain about the preferences of a unitary decision maker. Le Breton and Zaporozhets (2007) replace the unitary decision maker with a legislature with multiple actors. In Song (2008), policy-making power is shared between an executive and a unitary legislature. The lobbies influence the preferences of the legislature in a context of unilateral policy making with no uncertainty, and Coates and Ludema (2001) study trade policy leadership with endogenous lobbying in the presence of political uncertainty with imperfect monitoring.

\section{The Model}
\label{sec:model}

\subsection{The Basic Setup}
\label{sec:basic}
I begin by describing the basic economic setting within which trade occurs. It is a three-good model with two countries: home (no asterisk) and foreign (asterisk). In each country, preferences are linear in good $N$, which is denoted the numeraire, while the demand functions for $X$ and $Y$ are assumed strictly decreasing and twice continuously differentiable. The demand functions for $X$ and $Y$ are taken to be identical and written $D(P_i)$ in home and $D(P_i^*)$ in foreign. $P_i$ ($P_i^*$) denotes the home (foreign) price of good $i \in \left\{N,X,Y\right\}$.

Good $N$ is produced with labor alone so that $Q_N = l_N$. I assume the aggregate labor supply is large enough to ensure that the output of good $N$ is enough to guarantee balanced trade. The supply functions for good $X$ are $Q_X(P_X)$ and $Q_X^*(P_X^*)$ and are assumed strictly increasing and twice continuously differentiable for all prices that elicit positive supply. For any such $P_X$, I assume $Q_X^*(P_X) > Q_X(P_X)$ so that the home country is a net importer of good $X$. The production structure for good $Y$ is symmetric, with demand and supply such that the economy is separable in goods $X$ and $Y$. The production of goods $X$ and $Y$ requires labor and a sector-specific factor that is available in inelastic supply and is non-tradable so that the income of owners of the specific factors is tied to the price of the good in whose production their factor is used.

For simplicity, I assume each government's only trade policy instrument is a specific tariff on its import-competing good: the home country levies a tariff $\tau$ on good $X$ while the foreign country applies a tariff $\tau^*$ to good $Y$. Local prices are then $P_X = P_X^W + \tau$, $P_X^* = P_X^W$, $P_Y = P_Y^W$ and $P_Y^* = P_Y^W + \tau^*$ where a $W$ superscript indicates world prices. Equilibrium prices are determined by the market clearing conditions
$$M_X(P_X)= D(P_X)-Q_X(P_X) = Q_X^*(P_X^*) - D(P_X^*) = E_X^*(P_X^*)$$
$$E_Y(P_Y)=Q_Y(P_Y)-D(P_Y) = D(P_Y^*)-Q_Y^*(P_Y) = M_Y^*(P_Y^*)$$
where e.g. $M_X$ are home-county imports and $E_X^*$ are foreign exports of good $X$. The price of the numeraire is equal to one in both countries and on the world market.

$P_X^W$ and $P_Y^W$ are decreasing in $\tau$ and $\tau^*$ respectively, while $P_X$ and $P_Y^*$ are increasing in the respective domestic tariff. This gives rise to a terms-of-trade externality. Profits in a sector are increasing in the price of its good and also in the domestic tariff. This fact, combined with the assumptions on specific factor ownership, motivates political activity by import-competing lobbies.

In each country, there is an executive who concludes trade agreements and a legislature that has final say on trade policy. To focus attention on protectionist political forces, highlight the model's central mechanisms and minimize the number of actors that must be modeled, I assume that only the import-competing industry in each country is politically-organized and that it is represented by a single lobbying organization.\footnote{The model extends easily to the case of multiple lobbies. To illustrate, adding an export lobby with no uncertainty predicts import lobbies remain disengaged while the executives can reduce tariffs by recruiting support from exporters. The Panama Trade Promotion Act follows this pattern, with virtually no lobbying against, significant lobbying in favor, and numerous industries receiving import protection.\label{fn:lobby}}

\begin{figure}
	\begin{center}
		\input{game-tree.tex}
	\end{center}
	\caption{Extensive Form\label{fig:ext}}
\end{figure}

Figure~\ref{fig:ext} illustrates the timing of the game from the perspective of the home country.\footnote{This extensive form is for the case where the foreign legislature does not break the trade agreement.} First, the executives set trade policy cooperatively within the context of an international agreement by choosing the trade agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$.\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} Then the lobbies attempt to persuade the legislators in their respective countries to break the trade agreement by choice of lobbying effort $e_b$. Next, nature determines with probabilities $o$ and $o^*$ whether each legislature will have the opportunity to take a vote to break the agreement. I assume that these probabilities are less than one-half and mutually exclusive.\footnote{While this assumption is made for purposes of exposition and tractability, one can think of $o$ and $o^*$ as being determined by events beyond the executives' or legislatures' control that determine whether or not the legislatures will be willing to consider the lobby's request; for example, they would be affected by the occurrence of an economic crisis that diverts the legislature's attention from less-pressing matters.} This allows me to focus on the key interaction between the domestic actors and abstract from the strategic interaction between the lobbies.\footnote{If the break decisions in the two countries are sequential with the executives behind a veil of ignorance about which legislature moves first, the end results are the same but additional intermediate results are needed. The optimization problem of the executives becomes more complex as they decide how best to exploit the second lobby's incentive to free ride on the effort of the first-mover lobby.}

After this, uncertainty about the the median legislator's identity is resolved. All players simultaneously observe the realization of the random variable $\ta_b$ that represents this uncertainty. The ``break stage'' concludes with the legislature making a choice to abide by the agreement or to break the agreement. In the event that the legislature breaks the agreement, there is a final stage of lobbying, resolution of the uncertainty surrounding this decision, and voting to set the trade-war tariffs $\btn$.\footnote{Alternatively, one can model the non-cooperative tariff as being determined by the break decision lobbying, through a separate process in the case of administered protection, or the ex-ante status quo. This does not change the fundamental dynamics of the model.} Finally, producers and consumers make their decisions.

\subsection{Preferences}
\label{sec:pref}
With the structure of politics and the economy symmetric and the latter fully separable, I focus on the home country's and the $X$-sector. The details are analogous for $Y$ and foreign. The home legislature's welfare function is
\begin{equation}
  W_{\mathit{ML}} = \mathit{CS}_X(\tau) + \ga(e,\ve) \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
  \label{eq:ml}
\end{equation}
where $\mathit{CS}$ is consumer surplus, $\pi$ are profits, $\ga(e,\ta)$ is the weight placed on profits in the import-competing industry, and $\mathit{TR}$ is tariff revenue.\footnote{Labor income $l$ could also be included in both median legislator and executive welfare. I omit it because its inclusion alters none of the results and only serves to complicate the exposition.} I model the decisions of the legislature as being taken by a median legislator with the weight the median legislator places on import-competing industry profits affected by the level of lobbying effort $e$ and a random variable $\ta$. I make the following assumptions on $\ga(e,\ta)$:

\begin{assumption}
  $\ga(e,\ta)$ is increasing and concave in $e$ for every $\ta \in \Theta$.
  \label{as:ga_c}
\end{assumption}

\begin{assumption}
  $\ga(e,\ta)$ is increasing in $\ta$.
  \label{as:ga_ta}
\end{assumption}

Assumption~\ref{as:ga_c} formalizes the intuition that the legislature favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity. It rules out higher effort making lower weights more likely and that the structure of uncertainty changes with increasing effort so that higher weights become more likely at an accelerating pace. Assumption~\ref{as:ga_ta} simply provides for an intuitive labeling so that larger realizations of $\ta$ increase the value of the political economy weight.

Given its expectations and the legislature's preferences, the home lobby chooses its lobbying effort ($e_b$ to influence the break decision and $e_n$ to influence the trade war tariff) to maximize the welfare function:
\begin{equation}
  \expect \left[U_L \right] = \Pr\left[ \text{TradeWar} \right] \left[ \pi(\tau^{\mathit{n}}) - e_n \right] + \Pr\left[ \text{TradeAgreement} \right] \pi(\tau^a) - e_b
  \label{eq:lv}
\end{equation}
where $\pi(\cdot)$ is the current-period profit and the subscript $X$ has been dropped for notational convenience.

In the first stage, the executives choose the trade agreement tariffs. With executive welfare in a trade war the disagreement point, the division of surplus according to the Nash bargaining solution is
\[
  V_E(\bta) + t = W_E(\btn) + \frac{1}{2} \left( MV(\bta) - W_E(\btn) - W_E^*(\btn) \right)
\]
\[
  V_E^*(\bta) - t = W_E^*(\btn) + \frac{1}{2} \left( MV(\bta) - W_E(\btn) - W_E^*(\btn) \right)
\]
where expectation operators are dropped for convenience, $MV(\bta)$ is the maximized joint value and $t$ is an intergovernmental transfer.\footnote{While direct monetary transfers have to date rarely been used in practice, it seems appropriate to interpret linked concessions on non-trade issues as indirect transfers (Klimenko, Ramey and Watson (2008); Maggi and Staiger (2011)). Here, transfers do not occur as long as the full set of symmetry assumptions are maintained but are an important consideration in asymmetric environments.} The solution to this system of equations determines the trade agreement tariffs.

I simplify the problem by assuming that political constraints prevent the executives from choosing asymmetric tariffs. This implies that the executives simply maximize their expected joint payoffs:
\begin{multline}
  \expect \left[W_E(\bta) \right] + \expect \left[ W_E^{*}(\bta) \right] = \Pr\left[ \text{TradeWar} \right] \left[W_E(\bm{\tau}^{\mathit{n}}) + W_E^*(\bm{\tau}^{\mathit{n}}) \right] + \\ \Pr\left[ \text{TradeAgreement} \right] \left[W_E(\bta) + W_E^*(\bta) \right]
  \label{eq:jv}
\end{multline}
The home executive's welfare is specified as
\[
  W_E(\bm{\tau}) = \mathit{CS}_X(\tau) + \ga_E \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
\]
This is identical to the legislature's welfare function except the weight the executive places on the profits of the import industry is not a function of lobbying effort. This setup does not require that the executives are not lobbied; the assumption is innocuous as long as the executives' preferences are not directly altered in a significant way by lobbying over trade. I make one more related assumption on $\ga(e,\ta)$:

\begin{assumption}
  $\ga(e,\ta) \geq \ga_E \geq 1 \ \forall e,\ta$.
  \label{as:ga_l_e}
\end{assumption}

That is, even for the least favorable outcome of the lobbying process, the legislature is more protectionist than the executive regardless of the lobby's effort choice. This is not essential but it simplifies the analysis, ensuring that trade agreement tariffs are smaller than trade war tariffs. It matches the empirical finding that politicians with larger constituencies are less sensitive to special interests and represents well the post-war U.S. where Congress has consistently been more protectionist than the President.\footnote{cfr. Lohmann and O'Halloran (1994) for the general argument, Destler (2005) on U.S. trade politics, and Grossman and Helpman (2005) for a formal model.}

\subsection{Information and Equilibrium Selection}
\label{sec:info}
I examine a simple class of equilibria that have three key features. First, information about political uncertainty is symmetric. However, in line with the literature, I assume the lobby's contribution is not observable to the foreign legislature. Thus the influence of one country's lobby on the other country's legislature occurs only through the tariffs selected.\footnote{cfr. Grossman and Helpman (1995b), page 685.} Since players in the same country can take advantage of more information than those who are in different countries, the solution concept is perfect public equilibrium (PPE).

Second, whenever there is a possibility of multiple equilibria, I focus on the one that maximizes the executives' welfare. Since I assume the executives are social welfare maximizers, this selection criterion puts results in terms of the maximal level of trade policy cooperation that is possible. It also allows the question of whether governments use trade agreements as political commitment devices to be answered in a straightforward way.

Finally, I assume that an external authority can ensure enforcement of the agreement.\footnote{Buzard (2015) considers a similar model in a repeated-game context and can therefore remove this restriction.}

\section{Main Results}
\label{sec:main}
To understand how the executives optimally structure trade agreements, I first examine the lobbies' incentives and the legislatures' decisions regarding breach of the agreement, including how trade-war tariffs are set.

\subsection{Trade-War Tariffs}
\label{sec:twt}
In the event that the trade agreement is broken, the legislature sets its tariff $\tau$ unilaterally by maximizing Equation~\ref{eq:ml} given $\tau^*$. Because there are no interactions between the home and foreign tariffs, the home country's tariff maximizes weighted home-country welfare in the $X$-sector only. Unilateral optimization leads to what I refer to as the (expected) Nash or trade-war tariffs $\tau^n$ as the solution to the following first order condition:\footnote{Note that the random variable in the median legislator's weight on import profits is written as $\ta_n$ at this stage to distinguish it from $\ta_b$ at the break stage: as two separate votes are taken, there are two distinct realizations of uncertainty.}
\begin{equation}
		\frac{\partial \mathit{CS}_X(\tau)}{\partial \tau^n} + \ga(e_n,\ve_n) \cdot \frac{\partial \pi_X(\tau)}{\partial \tau^n} +  \frac{\partial \mathit{TR}(\tau)}{\partial \tau^n} = 0 .
		\label{eq:legfoc}
\end{equation}

In the event of a trade war, the lobby chooses its effort $e_n$ given this tariff-setting behavior by maximizing its profits net of effort: $\pi\left(\tau^n\left(\ga\left(e_n,\ve_n\right)\right)\right) - e_n$. This implies a first order condition for the lobby of
\begin{equation}
	\frac{\partial \pi(\tau^n)}{\partial \tau^n}\frac{\partial \tau^n}{\partial \ga} \frac{\partial \ga}{\partial e_n} = 1
  \label{eq:lobtw}
\end{equation}
That is, the lobby equates the expected marginal increase in profits with its marginal payment.

Because profits are increasing in the tariff, trade war tariffs are increasing in the weight attached to the profits of the import-competing industry. This can be seen by rearranging Equation~\ref{eq:lobtw} as 
\begin{equation}
  \frac{\partial \tau^n}{\partial \ga} = \frac{1}{\frac{\partial \pi(\tau^n)}{\partial \tau^n} \frac{\partial \ga}{\partial e_n}}
	\label{eq:lem1}
\end{equation}
since $\frac{\partial \ga}{\partial e_n}$ is positive by Assumption~\ref{as:ga_c} and profits are increasing in the tariff. This expression demonstrates that the second order condition for the legislature's problem is always satisfied. By the implicit function theorem, $\frac{\partial \tau^n}{\partial \ga} = -\frac{\frac{\partial \text{Equation}~\ref{eq:legfoc}}{\partial \ga}}{\frac{\partial \text{Equation}~\ref{eq:legfoc}}{\partial \tau^n}} = -\frac{\frac{\partial \pi(\tau^n)}{\partial \tau^n}}{SOC}$ where ``SOC'' is the second derivative of the legislature's objective function that should be everywhere negative. Setting this expression equal to Equation~\ref{eq:lem1}, the second order condition must be satisfied since $\frac{\partial \ga}{\partial e_n}$ is positive by Assumption~\ref{as:ga_c}.

\bigskip
\subsection{To Break or Not to Break?}
\label{sec:break}
We can now proceed by backward induction to analyze the legislature's incentives to uphold or break the trade agreement. The legislature will break the agreement and set the tariff at $\tau^n$ if the median legislator's utility from the Nash tariffs is higher than his utility from the trade agreement tariffs, i.e. if
\begin{equation}
  W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right)
  \label{eq:lwcg}
\end{equation}

The outcome of the vote on whether or not to break the trade agreement is not known to \textit{any} player until the uncertainty over the identity of the median legislator is resolved at the moment the vote takes place. I represent the probability that the home legislature breaks the trade agreement and sets the tariff at $\tau^n$ as:\footnote{I suppress the Nash tariffs in the expression of the break probability since they do not vary from the point of view of earlier stages.}
\begin{multline}
  b(e_b,\bta) = \expect_{\ga|e_b} \bm{1} [ W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right) ] \\ = \Pr [ W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right) | e_b]
  \label{eq:b}
\end{multline}

We are now in a position to examine the legislature's decision more closely. Of central concern is how the probability that the legislature will break the trade agreement varies with lobbying effort:

\begin{result}
  The probability that the legislature breaks a trade agreement is increasing and concave in $e_b$.
  \label{res:bincC}
\end{result}

\noindent All proofs are in the Appendix. Lobbying affects only the weight the legislature places on the profits of the import-competing industry. These profits are higher in a trade war than a trade agreement. Assumption~\ref{as:ga_c} implies that the legislature becomes more favorably inclined---albeit at a decreasing rate---toward the high trade-war tariff and associated profits as lobbying increases and thus more likely to break the trade agreement.

Turning to the effects of the trade-agreement tariffs on the probability that the agreement will be abrogated, it is straightforward that the legislature always prefers lower levels of the foreign tariff:
\begin{lemma}
  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly increasing in $\tau^{*a}$.
  \label{lem:leg_astar}
\end{lemma}

The lower world price for home's export good has a larger negative effect on profits than the positive effect on consumer surplus. The net effect of an increase in foreign trade-agreement tariffs on home legislative welfare is negative, leading to an increased probability that the trade agreement will be broken.

The relationship between $\tau^a$ and break probability is more complex. For any effort level $e_b$, when the trade agreement tariff is very low, only a small set of realizations of $\ta_b$ associated with the lowest values of $\ga(e_b,\ta_b)$ will lead to approval of the trade agreement, implying a high break probability. As the trade agreement tariff rises, larger values of $\ga(e_b,\ta_b)$ are consistent with approving the trade agreement, so the set of $\ta_b$'s that lead to trade agreement approval is larger. That is, the break probability decreases as $\tau^a$ increases.

\begin{lemma}
  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly decreasing in $\tau^a$.
  \label{res:leg_a}
\end{lemma}

Since I focus on symmetric equilibria, any increase in $\tau^a$ is accompanied by an equal increase in $\tau^{*a}$. Combining the impact of the home and foreign tariff when the two are constrained to be equal:
\begin{lemma}
	Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly decreasing in $\bta$ (i.e. $\frac{\partial b(e,\bta)}{\partial  \tau^a} + \frac{\partial b(e,\bta)}{\partial  \tau^{*a}} \leq 0$).
	\label{res:bcomb}
\end{lemma}

\noindent The legislature's bias toward the import-competing industry overweights the negative impact of the home tariff on the break probability and ensures this result.

\subsubsection{Lobby}
\label{sec:lob_un}
The lobby chooses its level of effort as a function of $\bta$, given the implications of that choice on the legislature's probability of breaking the agreement. The lobby maximizes probability-weighted profits net of effort:
\[
  \max_{e_b} b(e_b,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e_b,\bta)] \pi(\tau^a) - e_b
\]
The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from a trade war weighted by the increase in the probability of provoking the trade war:
\begin{equation}
	\frac{\partial b(e_b,\bta)}{\partial e_b} \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
	\label{eq:lobbyfoc}
\end{equation}
Assumption~\ref{as:ga_l_e} and Result~\ref{res:bincC} ensure the second order condition. To guarantee an interior solution, we need
  \begin{equation}
	  \frac{\partial b(0,\bta)}{\partial e_b} \left[ \pi(\tau^n) -e_n- \pi(\tau^a) \right] > 1.
		\label{ine:lobint}	
  \end{equation}
If the executives were to set $\tau^a = \tau^n$, there would be no incentive for the lobby to make a positive contribution. There are some other cases in which it is in the executives' interest to set trade agreement tariffs so as to disengage the lobby. The following results only hold when the marginal impact of the first lobbying dollar on the break probability is sufficiently high to make engaging in the political process worthwhile for the lobby.

\begin{result}
  When the trade agreement remains in force with positive probability, lobbying effort is weakly decreasing in trade agreement tariffs.\footnote{See Section~\ref{sec:uncertainty} for a detailed account of behavior when the lobby is able to induce a trade war with probability 1.}
  \label{res:lobby}
\end{result}

\noindent Raising the trade agreement tariffs decreases the benefit of a break in the trade agreement by raising trade agreement profits. This key result implies that the executives can reduce lobbying effort by setting higher tariffs in their trade agreement. We will see in the next section how this shapes the executives' joint decision.

\subsection{The Trade Agreement}
\label{sec:ta}
I represent the probability that the trade agreement will be broken as $B(\bta)=b(e(\bta),\bta)$ where $e(\bta)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.

To solve for the trade agreement tariffs, one must maximize the following modified version of Equation \ref{eq:jv}:
\begin{equation}
    \left\{ o \cdot B(\bta) + o^* \cdot B^*(\bta) \right\} \bm{W_E}(\btn) + \left\{ 1- o \cdot B(\bta) - o^* \cdot B^*(\bta) \right\} \bm{W_E}(\bta)  
  \label{eq:jv2}
\end{equation}
where $\bm{W_E}(\cdot)$ is the sum of the home and foreign executives' utilities.

Of central concern is how the break probability varies as both a direct and indirect function of $\bta$ given the lobby's optimal response. Result~\ref{res:bcomB} takes into account both the direct and indirect effects:

\begin{result}
	The total probability that the trade agreement will be broken is decreasing in $\bta$ (i.e. $\frac{\partial B(\bta)}{\partial  \tau^a} + \frac{\partial B(\bta)}{\partial  \tau^{*a}} \leq 0$).
	\label{res:bcomB}
\end{result}

\noindent When the executives raise $\bta$ the legislature becomes less likely to abrogate the agreement, for three reasons. First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $B(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:bcomb}). Thus, beyond promising a lower tariff from the trading partner, we can think of the trade agreement as a sort of political commitment device that can be used to reduce political pressure and therefore get the legislature to maintain a lower tariff than it otherwise would.

We are now prepared to examine the executives' optimal choice of trade agreement tariffs. Because joint executive welfare is decreasing in trade agreement tariffs for $\bta$ above the executives' preferred tariffs, we have the following fundamental feature of the executives' problem:
\begin{lemma}
  The executives face the following trade off when choosing $\bta$: higher tariffs decrease the probability that the trade agreement will be broken but also decrease welfare when the agreement is in force.
  \label{res:to}
\end{lemma}
I show in the \hyperlink{int_soln}{Appendix} that it is never optimal in a symmetric equilibrium for the executives to choose $\bm{\tau^a}$ at or below the executives' most preferred level if the legislatures will have an opportunity to break the trade agreement. This is because there are only second-order losses from raising tariffs slightly from the most-preferred level yet there are first-order gains in reducing the probability that the agreement will be broken.

The executives will always choose $\bta < \btn$ unless the legislature breaks even agreements with tariffs very close to the Nash level with certainty. In this case the problem is not interesting so I ignore this case. Thus there is an interior solution in all cases of interest, but this solution may be of two different forms. The solution could be at the point that maximizes the concave portion of the executives' welfare function. For some specifications, however, high enough tariffs can disengage the lobby so that the probability that the trade agreement will be broken is zero. If this occurs at a low enough tariff level, executive welfare can be maximized at this point. 
\begin{result}
  The executives maximize their welfare by either (a) raising tariffs sufficiently high to ensure that the trade agreement will remain in force or (b) trading off reductions in the probability that the agreement will be broken with reductions in welfare under the agreement.
  \label{res:execsoln}
\end{result}
This accords well with observations of trade policy politics, in that some lobbies exert significant effort toward disrupting trade agreements whereas others apparently do not engage in the political process. The current model points to differences across industries in production and demand structure, as well as political weighting ($\ga$), to help explain these variations.

\section{An Example}
\label{sec:example}
In this simple parameterization of the model, the fundamentals are chosen to match Bagwell and Staiger (2005): $D(P_i) = 1 - P_i$, $Q_X(P_X) = \frac{P_X}{2}$, $Q_Y(P_Y) = P_Y$, $\Pi_X(P_X) = \frac{(P_X)^2}{4}$, and $\Pi_Y(P_Y) = \frac{(P_Y)^2}{2}$. Home-country imports of $X$ and exports of $Y$ are $M_X(P_X)= 1 - \frac{3}{2}P_X$ and $E_Y(P_Y)= 2P_Y -1$. Market clearing implies that world and home prices of $X$ are $P_X^W = \frac{4-3\tau}{7}$ and $P_X = \frac{4+4\tau}{7}$. Foreign is taken to be symmetric.

\subsection{Trade War Tariffs}
The median legislator's welfare can be written as 
\[
  W_{\mathit{ML}}^X(\tau,\ga(e,\ve)) + W_{\mathit{ML}}^Y(\tau^*) = \left\{\frac{9}{98} - \frac{5}{49}\tau - \frac{34}{49}\tau^2 +\frac{1}{98}\ga(e,\ve)\left[ 8 + 16\tau + 8\tau^2 \right] \right\}+ \frac{25}{98} - \frac{3}{49}\tau^* + \frac{9}{49}(\tau^*)^2.
\]
%where $W_{\mathit{ML}}^X(\tau,\ga(e,\ve))$ is the utility derived from consumer surplus, producer surplus and tariff revenues in the import-competing industry and $W_{\mathit{ML}}^Y(\tau^*)$ is the utility derived from consumer and producer surplus in the exporting industry.

The Nash tariff that results from unilateral maximization is\footnote{The second order condition is satisfied for all realizations of $\ga < 17/2$. Because $\ga = 7/4$ is enough to achieve the prohibitive tariff of $1/6$, I will assume this condition is satisfied.}
\[
  \tau^n = \frac{8\ga(e,\ve)-5}{68-8\ga(e,\ve)}
\]

To predict the Nash tariff, the political weighting function and form of political uncertainty must be specified. Take $\ga(e,\ve) = 1.25 + e^{.2} + \ta$ with $\ve$ distributed uniformly on $[-0.25,0.25]$. Facing this specification of the political process, the lobby maximizes its objective function at $e_n = 0.00166$, producing an expected Nash tariff of $0.129$. Net profits are $0.10239$ in terms of the numeraire and lobbying effort is $1.60\%$ of gross profits.

\subsection{Break Decision}

\begin{figure}
\begin{center}
\includegraphics[height=2.5in, width=3in]{brprob2.jpg}
\end{center}
\caption{Probability Trade Agreement will be Broken\label{fig:br}}
\end{figure}

\begin{comment}
\begin{figure}
\begin{center}
\includegraphics[height=2.50in, width=3in]{contributions.jpg}
\end{center}
\caption{Lobbying Effort\label{fig:cont}}
\end{figure}
%graph is created in lobby_fix.m
\end{comment}

\begin{comment}
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{brprob2.jpg}
  \caption{Probability Trade Agreement will be Broken}
  \label{fig:br}
  %\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{contributions.jpg}
  \caption{Lobbying Effort}
  \label{fig:cont}
  %\label{fig:sub2}
\end{subfigure}
%\caption{A figure with two subfigures}
%\label{fig:test}
\end{figure}
\end{comment}

Figure~\ref{fig:br} depicts the probability that the legislature will vote to break the trade agreement as a function of the tariff levels set in the trade agreement (with the restriction that $\tau^a = \tau^{*a}$) and the lobby's effort. It is strongly increasing in lobbying effort and decreasing in the level of tariffs set in the trade agreements.

Given the impact of lobbying on the legislature's break decision, the lobby's optimal contribution level is strongly decreasing in the trade agreement tariffs.%, as shown in Figure~\ref{fig:cont}.

\subsection{Trade Agreement}
The break probability never reaches zero for this parameterization so the executives' welfare function is concave everywhere. Assuming that each legislature has the opportunity to break the agreement with probability $\frac{1}{2}$ and that the executives are social-welfare maximizers, they set trade agreements tariffs of $\tau^a = \tau^{*a} = 0.078$, with lobbying expenditures at the trade maintenance phase of $0.0007$ and a total break probability of $0.505$. Total lobbying expenditure is $1.54\%$ of the expected profits of $0.98591$. The expected tariff is $0.103$.

We can compare this against different benchmarks. The most stark is the trade-war outcome, which is the outcome that would prevail in the absence of any trade agreement. The tariff in the executive-formed trade agreement is about 60$\%$ of the Nash tariff of $0.129$, and the expected tariff given the probability that the agreement will be broken is 80$\%$ of the Nash level. Lobbying expenditures in the agreement-maintenance phase are about 40$\%$ of the those in the Nash game, while expected expenditures in the executive-led trade-agreement scenario are 90$\%$ of what they would be if the legislatures set tariffs unilaterally. Although the welfare-maximizing governments here are not able to set and maintain tariffs at zero as they would like, they are able to achieve significant reductions in tariff levels through the use of the trade agreement.

Another benchmark is the scenario in which the legislatures make use of a trade agreement without the involvement of the executives. As in Bagwell and Staiger (2005), I find when maximizing their joint welfare in a legislature-led trade agreement, the cooperative tariff levels will be set at
\[
  \tau^L = \frac{4\ga(e,\ve)-4}{25-4\ga(e,\ve)}, \ \tau^{*L} = \frac{4\ga(e^*,\ve)-4}{25-4\ga(e^*,\ve)}
\]
The legislatures are able to use the agreement to internalize the terms of trade externality, making political influence more expensive for the lobbies. Lobbying expenditures rise to $0.0027$---60$\%$ higher than in the Nash case and $2.64\%$ of the gross profits of $0.10204$---while the agreement tariffs are set at $0.118$, only slightly lower than the Nash tariffs of $0.129$ and still higher than in the executive-led trade agreement. Comparing net expected profits across the three scenarios, they are highest in the Nash game, lowest under the trade agreement and intermediate when the legislatures make policy directly.

\section{Discussion}
\label{sec:dis}

\subsection{Separation of Powers}
\label{sec:sep_powers}
We can isolate the results that derive from the assumption that power over trade policy is shared between the executive and legislative branches if we assume that there is no uncertainty at the break stage.

When $\ga(e_b)$ is deterministic, the lobby knows the precise contribution it must make for any given trade agreement tariffs $\bta$ to induce the legislature to break the agreement. Here, the lobby's contribution \textit{increases} in $\bta$ since the higher are the trade agreement tariffs, the larger is the political weight that is required to induce the legislature to find them unsatisfactorily low. As long as trade war profits net of the required contribution are greater than trade agreement profits, the lobby will induce a trade war; otherwise, it is not in the lobby's interest to make any contribution. Facing this behavior, the executives set the lowest trade agreement tariffs that make it prohibitively expensive for the lobby to have the agreement broken.

In the example of Section~\ref{sec:example}, if the executives set the trade agreement facing no uncertainty, the tariff level is $0.106$, the lobby exerts zero effort, and the agreement remain in force with probability 1. If instead the executives were to set trade-agreement tariffs of $0.105$, the lobby would contribute $0.0025$ and the legislature would break the agreement with probability 1. This demonstrates both the agenda-setting power of the executives and the stark discontinuities induced when political uncertainty is not an issue.

This case highlights the manipulation of tariffs to discourage lobbying and the disconnect that can arise between the tariffs that are chosen and the preferences of governmental actors. The executives here prefers zero tariffs while the legislators prefer $\tau^a = 0.05$ when $e_b = 0$. However, the trade agreement tariffs are set at $0.106$ precisely to ensure that $e_b =0$ so that we have a legislature that upholds the agreement.

\subsection{The Role of Political Uncertainty}
\label{sec:uncertainty}
Adding political uncertainty allows for positive lobbying on the equilibrium path, but this is not the only additional insight. For simplicity, I assume uncertainty is mean-zero. Lobbying behavior in a trade war is not altered by mean-zero uncertainty and so neither are expected trade-war tariffs. At earlier stages, uncertainty alters optimizing behavior by both the lobby and the executives. Consider adding a very small amount of uncertainty to the example of the previous section: take $\ve$ distributed uniformly on $[-0.01,0.01]$. Here, the executives find it optimal to set the tariffs to completely disengage the lobby, ensuring the agreement remains in force. However, the tariff level will be different than when $\ta_b=0$ because instead of making the lobbying decision according to the certainty condition $\pi(\tau^n) - e_n - \pi(\tau^a) > e_b$, the lobby makes this decision according to Condition~\ref{ine:lobint}. Relative to the example with $\ta_b=0$, the tariff can be reduced slightly to $0.105$.

\begin{figure}
\begin{center}
\includegraphics[height=2.5in, width=3in]{lobby_br.jpg}
\end{center}
\caption{Lobby's Optimal Expenditure Function (Low and Intermediate Uncertainty)\label{fig:lobby_br}}
\end{figure}

Figure~\ref{fig:lobby_br} shows the lobby's reaction function at this very low level of uncertainty as well as the intermediate level when $\ve$ is distributed uniformly on $[-0.14,0.14]$ where the executives set the highest tariff level of $0.107$. For the former, the range of tariff levels to which the lobby responds with a contribution that leaves open the possibility of a break is very small: only those between 0.103 and 0.104. The lobby disengages completely at $\bta=0.105$. When uncertainty is increased to the interval $[-0.14,0.14]$, the lobby begins to leave open the possibility of a break at $\bta = 0.048$. It disengages at the optimal tariff level of $0.107$. At intermediate uncertainly levels, both portions of the best response curve are steeper and the lobby disengages at lower tariff levels---as low as $0.099$ when $\ve \sim U[-0.06,0.06]$.  The optimal tariff does not decrease monotonically.

This illustrates Part (a) of Result~\ref{res:execsoln}: here the executives maximize their welfare by raising tariffs to the point where the import-competing industry ceases to lobby and the agreement remains in force for sure. Although lobbying expenditures are zero, the potential for lobbying behavior is essential in shaping the trade agreement.

%\begin{figure}
%\begin{center}
%\includegraphics[height=3.8in, width=7in]{exec_welfare.jpg}
%\end{center}
%\caption{Differences in Executive Welfare when Uncertainty Increases\label{fig:exec_wel}}
%\end{figure}

When uncertainty rises above this threshold of $\ve \sim U[-0.14,0.14]$, the executives' choices are made according to Part (b) of Result~\ref{res:execsoln}: they trade off reductions in welfare under the agreement with reductions in the probability that the agreement will be abrogated by the legislature. %In terms of the lobby's best response function, the executives now choose the optimal point on the downward-sloping portion of the curve instead of the point where it reaches zero. In terms of the welfare function for the executives, shown in Figure~\ref{fig:exec_wel}, they are now choosing the point that maximizes the concave portion of the curve instead of the ``spike'' that is created when the lobbies disengage and the chance that the agreement will be abrogated is removed altogether.\footnote{Note that the initial, flat portion of the curve is where the tariff is low enough that the lobby buys a trade war with certainty; we then enter the concave portion where the main results of Section~\ref{sec:main} are applicable; finally, we see the upward spike where the probability of a trade war is reduced to zero and the executives' welfare declines after that because there is no further reduction in break probability as the tariff increases.}

We see from this example that variations in uncertainty lead to very different outcomes in terms of lobbying, trade agreement tariffs and the probability of disruption. The provided tariff levels are strongly influenced by lobbying incentives, but in more nuanced ways than those predicted by unitary models.

\subsection{Relation to Grossman and Helpman's `Protection for Sale'}
\label{sec:gh}
I have introduced a legislative welfare function that admits a wide range of political processes within a non-unitary legislature as well as unitary policy-making when special interests face non-constant returns to lobbying activity. The non-linear relationship between lobbying effort and tariffs follows Dixit, Grossman and Helpman (1997) and is a departure from the `Protection for Sale' welfare function, which assumes that a unitary government maximizes the sum of contributions and some fraction, $a$, of social welfare.

Although using the $\ga$-weighted government welfare function is a reduced-form approach in the sense that legislative dynamics are not fully modeled, a benefit is that it does not require returns to lobbying effort to be constant. The more flexible form of the weighting function also removes the equilibrium indeterminacies and inability to speak to distributional questions that are implied by the linear form and its transferable utility (Dixit, Grossman and Helpman 1997).

The elegant PFS form is able to capture key cross-industry predictions on import tariffs. A perhaps unintended byproduct in the subsequent literature seems to have arisen in the form of a focus on matching fine details of governments' welfare-mindedness using a model that has a very simple unitary government and is thus better suited for other purposes.

It is clear that trade policy is often shaped in a complicated process involving multiple actors (see, for instance, Destler (2005) for the U.S.). The model presented herein is a first attempt to more richly model the policy-making process and thus shed light on open questions surrounding how government preferences and the details of political institutions impact trade policy outcomes.

\begin{comment}
\section{Extensions}
\label{sec:ext}

This analysis has been undertaken with the assumption that the import-competing industry is distributed evenly across legislative districts. By varying the way in which those profits enter the welfare function of the median legislator (before lobbying takes place), I can provide results about how district composition affects trade policy.

There are also several directions to explore in comparing different government structures. I start by describing the value of a trade agreement in an institutional setting of divided government.
\begin{result}
  Lobbying effort is reduced by the presence of executive branches who form a trade agreement (where the counterfactual is legislatures setting unilateral trade policy).
\end{result}
\textcolor{blue}{Don't yet know what assumptions I need to make this work} \\

Comparing this model to the unitary-government model is a delicate task. The most straightforward approach from the current structure is to disregard the executives and allow the legislative branches to form a trade agreement cooperatively after lobbying takes place. Note that we can retain the stochastic nature of the tariff-setting, but there is no vehicle for the agreement to be broken. In this case, the trade agreement tariff in home, $\tau_U^a$ will maximize
\[
  W_X(\tau,\ga_E) + W_X^*(\tau) = \frac{9}{98} - \frac{5}{49}\tau - \frac{34}{49}\tau^2 +\frac{1}{98}\ga(e,\ve)\left[ 8 + 16\tau + 8\tau^2 \right] + \frac{25}{98} - \frac{3}{49}\tau + \frac{9}{49}(\tau)^2 
\]
and will thus be set at
\[
  \tau_U^a = \frac{4\ga(e,\ve)-4}{25-4\ga(e,\ve)}.
\]
$\tau_U^a < \tau^n$ for all $\ga(e,\ve) < 7/4$, while $\ga(e,\ve)=7/4$ results in the prohibitive tariff of $1/6$. This is the standard result that a trade agreement internalized the terms of trade externality and results in a lower tariff than unilateral policy making.

\textcolor{blue}{will an executive inserted into this situation set higher or lower tariffs, what will happen to $e$?}

What if we add executive branches with essentially the same preferences as the legislature? That is, set $\ga_E = \expect[\ga(e,\ve)]$. \textcolor{blue}{It's hard to say how $e$ should be chosen here...still need to figure that out. But if we can get around the weird time inconsistency problem...} What agreement tariffs will the executives choose? It's easy to see that they will not choose $\tau^a < \tau_U^a$, as $\tau_U^a$ is their ideal point if there were no possibility of the agreement being broken, and lower tariffs only incentivize more lobbying and a higher probability that the agreement will be broken.

Thus, if an interior solution exists \textcolor{blue}{[should have conditions to insert here]}, the executive will exploit the same trade-off explored earlier, raising $\tau^a$ a bit to reduce the probability that the agreement will be abrogated. So interestingly, we can see that executives with the same political preferences as the legislature will choose higher trade agreement tariffs than the legislature would by itself due to the possibility that the agreement can be broken and the impact of the tariff choice on lobbying. We will also therefore have a reduced level of contributions, and if a trade war were possible, lower trade war tariffs because of it.

Along these lines, allowing for asymmetries in the preferences and political processes between the countries will provide important insights as well.

I also plan to use the richness of this model to parse out how much of the changes in tariffs comes from the fact that the executives place lower weight on producer profits and how much comes from the fact that they make an agreement---that is, compare the effects of structure versus preferences.

\subsection{Asymmetric Trade Agreements}
\label{sec:asym}
The assumption that the legislatures do not have the opportunity to break a trade agreement simultaneously serves to simplify the analysis of the interaction between the lobbies and the consequences of relaxing it will be discussed in the following section. Maintaining it for now, however, facilitates examination of the assumption that trade agreements must be symmetric. This may be quite realistic in some settings where additional political constraints would make ``unfair'' arrangements unpalatable. However, it is important to point out that, for some parameter choices, the joint welfare of the executives is in fact maximized by an asymmetric agreement.

The parameterization from the example in Section~\ref{sec:example} is one such instance. The optimal unrestricted trade agreement is to set tariffs in one country (say home) at $0.062$ and those in the other (foreign) at 0. In this case, the equilibrium break probability in home, if the home legislature is afforded the opportunity, is zero, while the foreign legislature will break the agreement with probability 1 if given the chance. With the assumption from the example that each legislature gets the opportunity to repudiate the agreement half the time, this results in the trade agreement being broken with probability $0.50$, just less than the $0.505$ of the optimal symmetric agreement with both tariffs set at $0.078$. Because both the trade agreement tariffs and the expected chance that the agreement will remain in force are lower, expected welfare for the executives is higher.

What is behind the rather surprising result that a lower break probability can be achieved when both tariffs are strictly lower than in the symmetric agreement? Here, the executives relinquish any chance of passage of the trade agreement in the foreign country (in essence hoping that its legislature will not have a chance to act). Once they decide to pursue this course, it is optimal to reduce $\tau^{*a}$ to zero. This drastically reduces the home legislature's incentive to break the trade agreement. Because of the large direct impact of $\tau^{*a}$ in reducing the break probability, the home tariff is not required to make such a large contribution and can be lowered, which in turn reduces the lobby's incentive to exert effort (see Result~\ref{res:lobby}). This effect is strong enough that the executives can set a tariff level lower than that of the symmetric agreement that is sufficient to disengage the home lobby (see Inequality~\ref{ine:lobint}).

It is useful to keep in mind that this result occurs in a completely symmetric environment. Recall that, in general, the executives maximize joint welfare in Equation~\ref{eq:jv2}. If the chance that the legislatures will have the opportunity to break the agreement ($o$ and $o^*$) are not equal, or if another significant aspect of the economic or political situation is asymmetric, the importance of this result grows in a potentially substantial way. In particular, if only one country faces a legislative constraint, an asymmetric agreement seems highly likely as in the large body of literature investigating the Schelling conjecture.

\subsection{Break Opportunities in Both Countries}
\label{sec:two}
Although it changes their expected payoffs, extending the model to allow both legislatures the opportunity to break the trade agreement simultaneously does not impact the legislatures' incentives as each decision to break or not break the agreement is independent of the other.

However, the lobbies' incentives are altered because the total probability of a break with which they weight profits changes. Now, in addition to their own effort positively influencing their own legislature to break the agreement, the probability of a break in the trade agreement also increases in the effort of the other country's lobby. As might be expected, the lobbying effort in each country turns out to be a negative function of that in the trading partner; that is, to some extent, the lobbies have an incentive to free ride.

Without making stronger assumptions, it is not possible to say how much the effort of each lobby will be reduced therefore whether total lobbying effort rises or falls. What is clear is that the optimization of the executives becomes significantly more complex as they are now faced with the problem of how to best exploit the free-riding dynamics that occur between the lobbies. 
\end{comment}

\section{Conclusion}
\label{sec:concl}
I have shown that the legislature both breaks trade agreements with a higher probability and sets higher trade war tariffs when lobbying activity increases, while the probability with which it breaks agreements decreases in the domestic trade agreement tariff. Because the lobby decreases its effort in response to higher trade agreement tariffs, the executives face a trade-off between the welfare derived while a trade agreement is in force and the probability with which the agreement actually enters into force.

I have also shown that in a policy-making structure in which power is shared, a less politically-motivated executive can utilize an international trade agreement to reduce the political pressure on the ratifying body and therefore increase the probability that the agreement will remain in force. Thus, in a model with a richer description of government structure, a broad political-commitment role for trade agreements can arise.

The executives' incentive to raise tariffs in order to reduce lobbying effort provides insight into the empirical puzzle in the Protection for Sale literature that levels of protection and associated deadweight losses are too high relative to lobbying expenditure given the high estimates for governments' weighting of social welfare. The intuition is clear: the observed lobbying expenditure levels may in fact be low \textit{because} tariffs have been raised sufficiently high to prevent political pressure and the increased risk of a costly trade disruption it engenders.

That lobbying and tariff levels are related in systematic ways to the amount of political uncertainty present suggests interesting avenues for future empirical work. Several directions for future theoretical work also seem potentially fruitful, including removing the assumption of perfect enforceability and supporting cooperation through repeated interaction and generalizing the model to the case of multiple lobbies.

%\begin{comment}
\section{Appendix}
\label{sec:appendix}
\noindent \textbf{\hypertarget{Pr_bincC}{Proof of Result~\ref{res:bincC}}}:\\
Substituting from Equation~\ref{eq:ml}, Equation~\ref{eq:b} can be re-written as
\begin{multline}  
  b(e_b,\bta,\btn) = \Pr [ \mathit{CS}_X(\tau^n) + \ga(e_b,\ve_b) \cdot \pi_X(\tau^n) + \mathit{CS}_Y(\tau^{*n}) + \pi_Y(\tau^{*n}) + \mathit{TR}(\tau^n) >  \\ \mathit{CS}_X(\tau^a) + \ga(e_b,\ve_b) \cdot \pi_X(\tau^a) + \mathit{CS}_Y(\tau^{*a}) + \pi_Y(\tau^{*a}) + \mathit{TR}(\tau^a) ]
\end{multline}
Rearranging, we have $b(e_b,\bta,\btn) = $
\begin{multline}  
  \textstyle \Pr \Big[ \frac{\mathit{CS}_X(\tau^n) + \pi_X(\tau^n) + \mathit{CS}_Y(\tau^{*n}) + \pi_Y(\tau^{*n}) + \mathit{TR}(\tau^n)  -\mathit{CS}_X(\tau^a) - \pi_X(\tau^a) - \mathit{CS}_Y(\tau^{*a}) - \pi_Y(\tau^{*a}) - \mathit{TR}(\tau^a)}{\pi_X(\tau^a) - \pi_X(\tau^n)} + 1 \\ \textstyle < \ga(e_b,\ve_b) \Big]
  \label{eq:b_ex}
\end{multline}
%\noindent The left side of the inequality in Expression~\ref{eq:b_ex} does not depend on $e_b$. By Assumption~\ref{as:ga_c}, the right side of the inequality is increasing and concave in $e_b$. Thus $b(e_b,\bta,\btn)$ is increasing and concave in $e_b$.    $\hfill\blacksquare$
\noindent The left side of the inequality in Expression~\ref{eq:b_ex} does not depend on $e_b$. Call it $Z$. Thus we have $b(e_b,\bta,\btn) = \Pr [Z < \ga(e_b,\ve_b) ] = 1 - F_{\ga}(\ga=Z)$ where $F_{\ga}(\ga=Z) = F_{\ta}(\ta=h^{-1}(\ga,e))$ by the Change of Variables Theorem and Assumption~\ref{as:ga_ta} with $\ga = h(e,\ta)$ giving the change of variable.

Then $\frac{\partial b}{\partial e} = -\frac{\partial F_{\ta}(\ta=h^{-1}(\ga,e))}{\partial \ta}\frac{\partial h^{-1}(\ga,e)}{\partial e} = -f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial e}$ and $\frac{\partial^2 b}{\partial e^2} = -f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2}$. Because $\ga = h(e,\ta)$ is increasing and concave in $e \ \forall \ta$ by Assumption~\ref{as:ga_c}, its inverse is decreasing and convex $\left(\frac{\partial h^{-1}(\ga,e)}{\partial e}\leq 0; \ \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2} \geq 0 \right)$ The pdf of $\ta$ is non-negative, so $\frac{\partial b}{\partial e} \geq 0$ and $\frac{\partial^2 b}{\partial e^2} \leq 0$. $\hfill\blacksquare$

\vskip.4in
\noindent \textbf{\hypertarget{Pr_leg_astar}{Proof of Lemma~\ref{lem:leg_astar}}}:\\
It must be shown that the left hand side of the inequality in Expression~\ref{eq:b_ex} is decreasing in $\tau^{*a}$. The derivative of this quantity with respect to $\tau^{*a}$ is 
\begin{equation}
  \frac{-\left(\pi_X(\tau^a) - \pi_X(\tau^n)\right)\left(\frac{\partial \mathit{CS}_Y(\tau^{*a})}{\partial \tau^{*a}} + \frac{\partial \pi_Y(\tau^{*a})}{\partial \tau^{*a}}\right)}{\left(\pi_X(\tau^a) - \pi_X(\tau^n)\right)^2} = \frac{\frac{\partial \mathit{CS}_Y(\tau^{*a})}{\partial \tau^{*a}} + \frac{\partial \pi_Y(\tau^{*a})}{\partial \tau^{*a}}}{\pi_X(\tau^n) - \pi_X(\tau^a)}.
  \label{appex:astar}
\end{equation}

\noindent The price of good $Y$ is decreasing in $\tau^{*a}$, so consumer surplus is increasing and profits are decreasing in $\tau^{*a}$. Because $Y$ is being exported, the decrease in profits is larger than the increase in consumer surplus, making the numerator negative. Since profits in the denominator are increasing in $\tau$, the expression in Equation~\ref{appex:astar} is negative for all $\tau^{*a}$.  $\hfill\blacksquare$

\vskip.4in
\noindent \textbf{\hypertarget{Pr_leg_a}{Proof of Lemma~\ref{res:leg_a}}}:\\
Using the logic of the proof of Lemma~\ref{lem:leg_astar}, the effect on the break probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive. Labeling the numerator of that expression $\left[ W(\btn)-W(\bta)\right]$ (for the change in social welfare), this derivative can be written
\begin{equation}
  \frac{\left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - \left[ W(\btn)-W(\bta)\right] \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tau^n)\right)^2}.
  \label{appex:a}
\end{equation}

\noindent $\left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)$ is always positive by Assumption~\ref{as:ga_l_e}. Because the optimal unilateral tariff for large welfare-maximizing governments is positive (call it $\tau^O$), $\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right)$ is increasing up to $\tau^O$ and decreasing above it. Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter.

Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $W(\btn)-W(\bta)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere. With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.

It is also positive over the remaining $(\tau^O,\tau^n)$. To see this, add $\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a} \left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)$ to the first summand and subtract it from the second. For any particular value of $\tilde{\tau}^a$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\tau}^a$ the preferred unilateral tariff; this makes the derivative in the first summand zero. Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\tau}^a$ so that this term is always negative, thus ensuring the result.  $\hfill\blacksquare$

\vskip.4in
\noindent \textbf{\hypertarget{Pr_bcomb}{Proof of Lemma~\ref{res:bcomb}}}:\\
Again, I want to show how the inequality in Expression~\ref{eq:b_ex} changes, now with respect to both $\tau^a$ and $\tau^{*a}$, so I add the derivatives in Expressions~\ref{appex:astar} and \ref{appex:a} to get
\[
  \frac{\left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{W}_X(\bta)}{\partial \tau^{a}} + \frac{\partial \mathit{W}_X(\bta)}{\partial \tau^{*a}}\right) - \left[ W(\btn)-W(\bta)\right] \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)^2}.
\]
where $\frac{\partial \mathit{W}_X(\bta)}{\partial \tau^{a}} + \frac{\partial \mathit{W}_X(\bta)}{\partial \tau^{*a}} = \frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \mathit{CS}_Y(\tau^{*a})}{\partial \tau^{*a}} + \frac{\partial \pi_Y(\tau^{*a})}{\partial \tau^{*a}}$ is the total derivative of social welfare. Since social welfare is maximized at $\bta = (0,0)$,\footnote{Note, this is identical to the result that joint social welfare is maximized at zero tariffs because of symmetry.}  this is negative $\forall \bm{\tau} \in (\bm{0},\btn]$; note that it is 0 at $\bm{0}$ and vanishingly small for very small tariffs.

Thus the first summand in the numerator is zero at $\bta = \bm{0}$ and increasingly negative as $\bta$ increases. The second summand is positive everywhere because social welfare, $W$, is lowest at $\btn$ and profits are increasing everywhere. Thus the numerator is positive at $\bm{0}$ and at least for very small $\bta$

It is also positive for all other values of $\bta$ strictly below $\btn$. Just as in the proof of Lemma~\ref{res:leg_a}, one can add
$\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a} \left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)$ to the first summand and subtract it from the second. For any particular value of $\tilde{\bta}$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\bta}$ the politically optimal tariff; this makes the derivative in the first summand zero. Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\bta}$ so that this term is always negative, thus ensuring the result.

Because the denominator is positive, the entire expression is positive for all $\bta < \btn$.   $\hfill\blacksquare$

\vskip.4in
\noindent \textbf{\hypertarget{Pr_lobby}{Proof of Result~\ref{res:lobby}}}:\\
Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
  \[
		\frac{\partial e_b}{\partial \tau^a} + \frac{\partial e_b}{\partial \tau^{*a}} = - \left[ \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e_b}} + \frac{\frac{\partial FOC_L}{\partial \tau^{*a}}}{\frac{\partial FOC_L}{\partial e_b}} \right] = \frac{ \frac{\partial b}{\partial e_b} \frac{\partial \pi(\bta)}{\partial \tau^a} + \frac{\partial b}{\partial e_b} \frac{\partial \pi(\bta)}{\partial \tau^{*a}} - \left\{\frac{\partial^2 b}{\partial e_b \partial \tau^a} + \frac{\partial^2 b}{\partial e_b \partial \tau^{*a}}   \right\}\left[ \pi(\tau^n) - e_n - \pi(\tau^a) \right]}{\frac{\partial^2 b}{\partial e_b{}^2} \left[ \pi(\tau^n) - e_n - \pi(\tau^a) \right]}
	\]
Beginning with the denominator: because $\pi(\tau)$ is increasing everywhere, $\left[\pi(\tau^n) - e_n - \pi(\tau^a) \right]$ is positive for all but very large values of $\tau^a$, that is for all $\tau^a$ such that $\pi(\tau^n) - e_n > \pi(\tau^a)$. When $\tau^a$ rises above this level, it is no longer in the lobby's interest to ask to have the agreement broken so $e_b=0$ and $\frac{\partial e_b}{\partial \tau^a} = 0$. $\frac{\partial^2 b}{\partial e_b{}^2}$ negative by Result~\ref{res:bincC}, so the denominator is negative for all values of $\tau^a$ at which $e_b$ is not constant.

$\frac{\partial b}{\partial e_b}$ is positive, $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction, and $\frac{\partial \pi(\bta)}{\partial \tau^{*a}}$ is zero: separability between the sectors implies that profits in the import-competing sector do not depend on $\tau^{*a}$.

We can rewrite $\frac{\partial b(e,\bta)}{\partial  \tau^a} + \frac{\partial b(e,\bta)}{\partial  \tau^{*a}} = -\frac{\partial F_\ga (Z(\bta))}{\partial \tau^a} -\frac{\partial F_\ga (Z(\bta))}{\partial \tau^{*a}} = -\frac{\partial F_\ga (Z(\bta))}{\partial Z(\bta)}\left[\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \right] = - f_\ga \left[\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \right]$, where $F_\ga (Z(\bta))$ is the CDF of $\ga$ and $f_\ga (Z(\bta))$ is the pdf of $\ga$ and $Z(\bta)$ represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.

Then $\frac{\partial^2 b}{\partial e_b \partial \tau^a} + \frac{\partial^2 b}{\partial e_b \partial \tau^{*a}} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta))}{\partial \tau^a} + \frac{\partial F_\ga (Z(\bta))}{\partial \tau^{*a}} \right) = 
	   - f_\ga \left[\frac{\partial^2 Z(\bta)}{\partial \tau^a \partial e} + \frac{\partial^2 Z(\bta)}{\partial \tau^{*a} \partial e} \right] - \left[\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \right] \frac{\partial f_\ga}{\partial e} = - \left[\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \right] \frac{\partial f_\ga}{\partial e} 
$
where the above equality holds because $Z(\bta)$ does not depend on $e$. Lemma~\ref{res:bcomb} shows that $\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\left\{\frac{\partial^2 b}{\partial e_b \partial \tau^a} + \frac{\partial^2 b}{\partial e_b \partial \tau^{*a}} \right\} \leq 0$. Thus $\frac{\partial e_b}{\partial \tau^a} + \frac{\partial e_b}{\partial \tau^{*a}} \leq 0$.  $\hfill\blacksquare$

\vskip.4in	  	
\noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:bcomB}}}: \\
$	\frac{\partial B(\bta)}{\partial \tau^a} + \frac{\partial B(\bta)}{\partial  \tau^{*a}} = \frac{\partial b}{\partial  e_b}\frac{\partial e_b}{\partial \tau^a} + \frac{\partial b}{\partial  e_b}\frac{\partial  e_b}{\partial  \tau^{*a}} + \frac{\partial b}{\partial \tau^a} + \frac{\partial b}{\partial  \tau^{*a}} = \frac{\partial b}{\partial  e_b} \left\{ \frac{\partial e_b}{\partial \tau^a} + \frac{\partial  e_b}{\partial  \tau^{*a}} \right\} + \frac{\partial b}{\partial \tau^a} + \frac{\partial b}{\partial  \tau^{*a}}.$ $\frac{\partial b}{\partial  e_b}$ is positive by Result~\ref{res:bincC}. $\left\{ \frac{\partial e_b}{\partial \tau^a} + \frac{\partial  e_b}{\partial  \tau^{*a}} \right\}$ is negative by Result~\ref{res:lobby}. Taken together, the final two summands are negative by Lemma~\ref{res:bcomb}. Thus the entire expression is negative.   $\hfill\blacksquare$

\vskip.4in
\noindent \textbf{\hypertarget{int_soln}{Conditions for Interior Solution to Executives' Problem}} \\
The first order condition for maximizing joint surplus with respect to $\tau^a$ and $\tau^{*a}$ when the two are constrained to be equal is
\begin{multline*}
  \textstyle \left\{ 1 - o \cdot B(\bta) - o^* \cdot B^*(\bta) \right\} \left\{\frac{\partial \bm{W_E}(\bta)}{\partial \tau^a} + \frac{\partial \bm{W_E}(\bta)}{\partial \tau^{*a}} \right\} \\
     \textstyle + \left\{ o \cdot \left[\frac{\partial B(\bta) }{\partial \tau^a} + \frac{\partial B(\bta) }{\partial \tau^{*a}} \right] + o^* \cdot \left[\frac{\partial B^*(\bta)}{\partial \tau^a} + \frac{\partial B^*(\bta)}{\partial \tau^{*a}} \right] \right\} \left[ \bm{W_E}(\btn)- \bm{W_E}(\bta) \right] = 0
\end{multline*}
Because there is no benefit to setting $\bta$ below the executives' preferred level, which I will denote $\bm{\tau^E}$, I will take the choice space to be $[\bte,\btn]$. Note that for $\ga_E = 1$, $\bte=0$.

To demonstrate that the executives do not choose $\bta=\bte$, I must show that the left side of the above equation is positive at $\bta=\bte$. Assumption~\ref{as:ga_l_e} and Result~\ref{res:bcomB} combined with symmetry ensure that the first term of the second summand is negative. That executive welfare is maximized at $\bte$ ensures that the term multiplying it is also negative as well as that $\frac{\partial \bm{W_E}(\bte)}{\partial \tau^a} + \frac{\partial \bm{W_E}(\bte)}{\partial \tau^{*a}}$ is zero. Therefore the derivative of joint executive welfare is positive at $\bte$.  $\hfill\blacksquare$

\begin{comment}
\vskip.4in
\noindent \textbf{\hypertarget{pfs}{Connection to Grossman and Helpman's `Protection for Sale'}} \\
To see the relationship between the two forms, write the PFS welfare function (replacing $C$ with $e$) as
\[
  e + aW = e + a \left[ \mathit{CS}_X(\tau) + \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau) \right]
\]
The relationship between $e$ and the weight the legislature places on profits is endogenous; because the PFS government welfare function has such an elegant and completely specified form, it is possible to solve for equilibrium behavior to retrieve this relationship directly.

It is easy to describe the equilibrium behavior and thus how lobbying effort will be related to the weight on profits in equilibrium in the PFS model when there is one lobby who makes a take-it-or-leave-it offer. Take the case of no uncertainty and assume that the legislature chooses $\tau=0$ in the absence of lobbying and that $\ga(0)=1$. For any $\tau$ that the lobby desires, it must pay according to the  indifference condition $e(\tau) = a \left[ W(0) - W(\tau) \right]$. That is, the lobby must pay for the $a$-weighted welfare loss caused by the tariff it requests.

In the model of this paper, this indifference condition, rearranged to solve for $\ga(e)$, is
		    \[
		      \ga(e) = \frac{\mathit{CS}_X(0) + \pi_X(0) + \mathit{CS}_Y(0) + \pi_Y(0) + \mathit{TR}(0) - \mathit{CS}_X(\tau) - \mathit{CS}_Y(\tau^*) - \pi_Y(\tau^*) - \mathit{TR}(\tau)}{\pi_X(\tau)}
		    \] 
\end{comment}

%\section{Acknowledgements}
%The author thanks the following people for their insightful comments: Joel Watson, Jim Rauch, Marc Muendler, Lawrence Broz, Peter Cowhey, Kyle Bagwell, Andrei Levchenko, Bob Staiger, two anonymous referees, and seminar participants at UC San Diego, Syracuse, Georgetown, Florida International, Brandeis, BGSU, U Mass Amherst, Swarthmore, SUNY Oswego, Kenyon College, and PEIO 2013. All remaining errors are my own.

\section{References}
\singlespacing

\begin{list}{}{\setlength{\leftmargin}{0.0in}\setlength{\rightmargin}{0.0in}\setlength{\itemindent}{0.0in}\setlength{\itemsep}{0.1in}}

\item Aidt, T., Gassebner, M., 2010. Do Autocratic States Trade Less? The World Bank Economic Review 24, 38-76.

%\item Amador, M., and Bagwell, K., 2013. The Theory of Optimal Delegation with an Application to Tariff Caps. Econometrica 81, 1541-1599.

\item Ansolabehere, S., de Figueiredo, J., Snyder Jr., J., 2003. Why Is There so Little Money in U.S. Politics? Journal of Economic Perspectives 17, 105-130.

\item Bagwell, K., Staiger, R., 2005. Enforcement, Private Political Pressure, and the General Agreement on Tariffs and Trade/World Trade Organization Escape Clause. Journal of Legal Studies 34, 471-513.

\item Baldwin, R.E., 1987. Politically realistic objective functions and trade policy: PROFs and tariffs. Economic Letters 24, 287-90.

\item Beshkar, M., 2010. Trade skirmishes safeguards: A theory of the WTO dispute settlement process. Journal of International Economics 82, 35-48.

\item Beshkar, M. and Bond, E., 2012. Cap and Escape in Trade Agreements. Available at \url{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2145679}.

\item Bombardini, M., 2008. Firm Heterogeneity and Lobby Participation. Journal of International Economics 75, 329-348.

\item Bombardini, M., Trebbi, F., 2012. Competition and Political Organization: Together or Alone in Lobbying for Trade Policy? Journal of International Economics 87, 18-26.

\item Buzard, K., 2015. Self-enforcing Trade Agreements, Dispute Settlement and Separation of Powers. Available at: \url{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2333728}.

\item Buzard, K., 2016. Endogenous Politics and the Design of Trade Agreements. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/Endogenous-Politics.pdf}.

\item Coates, D., Ludema, R., 2001. A Theory of Trade Policy Leadership. Journal of Development Economics 65, 1-29.

%\item Dai, X., 2006. Dyadic Myth and Monadic Advantage: Conceptualizing the Effect of Democratic Constraints on Trade. Journal of Theoretical Politics 18, 267-297.

\item Destler, I.M., 2005. American Trade Politics. Institute for International Economics, Washington, DC.

\item Dixit, A., G. Grossman, Helpman, E., 1997. Common Agency and Coordination: General Theory and Application to Government Policy Making. Journal of Political Economy 105, 752-769.

\item Ethier, W., 2002. Unilateralism in a Multilateral World. The Economic Journal 112, 266-292.

%\item Ethier, W., 2012. The Political-Support Approach to Protection. Global Journal of Economics 1, 1-14.

\item Feenstra, R., 1992. How Costly is Protectionism? Journal of Economic Perspectives 6, 159-178.

\item Feenstra, R., Lewis, T., 1991. Negotiated Trade Restrictions with Private Political Pressure. Quarterly Journal of Economics 106, 1287-1307.

\item Findlay, R., Wellisz, S., 1982. Endogenous Tariffs and the Political Economy of Trade Restrictions and Welfare. In Jagdish Bhagwati (ed.) Import Competition and Response, Chicago, IL: University of Chicago, 1982

\item Frye, T., Mansfield, E., 2003. Fragmenting Protection: The Political Economy of Trade Policy in the Post-Communist World. British Journal of Political Science 33, 633-657.

\item Gawande, K., Bandyopadhyay, U., 2000. Is Protection for Sale? Evidence on the Grossman-Helpman Theory of Endogenous Protection. The Review of Economics and Statistics 82, 139-152.

\item Gawande, K., Hoekman, B., 2006. Lobbying and Agricultural Trade Policy in the United States. International Organization 60, 527-561.

\item Gawande, K., Magee, C., 2012. Free Riding on Protection for Sale. International Studies Quarterly 56, 735-747.

\item Gawande, K., Krishna, P., Robbins, M., 2006. Foreign Lobbies and U.S. Trade Policy. Review of Economics and Statistics 88, 563-571.

\item Gawande, K., Krishna, P., Olarreaga, M., 2009. What Governments Maximize and Why: The View from Trade. International Organization 63, 491-532.

\item Gawande, K., Krishna, P., Olarreaga, M., 2012. Lobbying Competition Over Trade Policy. International Economic Review 53, 115-132.

\item Goldberg, P., Maggi, G., 1999. Protection for Sale: An Empirical Investigation. American Economic Review 89, 1135-1155.

\item Grossman, G., Helpman, E., 1994. Protection for Sale. The American Economic Review 84, 833-850.

\item Grossman, G., Helpman, E., 1995a. The Politics of Free-Trade Agreements. The American Economic Review 85, 667-690.

\item Grossman, G., Helpman, E., 1995b. Trade Wars and Trade Talks. The Journal of Political Economy 103, 675-708.

\item Grossman, G., Helpman, E., 2005. A Protectionist Bias in Majoritarian Politics. The Quarterly Journal of Economics 120, 1239-1282.

\item Henisz, W., Mansfield, E., 2006. Votes and Vetoes: The Political Determinants of Commercial Openness. International Studies Quarterly 50, 189-211.

\item Horn, H., Maggi, G., Staiger, R. W., 2010. Trade Agreements as Endogenously Incomplete Contracts. American Economic Review 100, 394-419.

\item Imai, S., Katayama, H., Krishna, K., 2009. Is protection really for sale? A survey and directions for future research. International Review of Economics and Finance 18, 181-191.

%\item Kibris, A., 2012. Uncertainty and Ratification Failure. Public Choice 150, 439-467.

\item Klimenko, M., Ramey, G., Watson, J., 2008. Recurrent Trade Agreements and the Value of External Enforcement. Journal of International Economics 74, 475-499.

%\item Kono, D., 2006. Optimal Obfuscation: Democracy and Trade Policy Transparency. American Political Science Review 100, 369-384.

\item Laver, M., Shepsle, K., 1991. Divided Government: America is Not `Exceptional'. Governance: An International Journal of Policy and Administration 4, 250-269.

\item Le Breton, M., Salanie, F., 2003. Lobbying under Political Uncertainty. Journal of Public Economics 87, 2589-2610.

\item Le Breton, M., Zaporozhets, V., 2007. Legislative Lobbying under Political Uncertainty. Available at SSRN: \url{http://ssrn.com/abstract=1024686}.

\item Lohmann, S., O'Halloran, S., 1994. Divided Government and US Trade Policy. International Organization 48, 595-632.

\item Maggi, G., Rodr\'{i}guez-Clare, A., 2007. A Political-Economy Theory of Trade Agreements. The American Economic Review 97, 1374-1406.

\item Maggi, G., Staiger, R., 2011. The Role of Dispute Settlement Procedures in International Trade Agreements. Quarterly Journal of Economics 126, 475-515.

\item Mansfield, E., Milner, H., Rosendorff, B.P., 2000. Free to Trade: Democracies, Autocracies, and International Trade. The American Political Science Review 94, 305-321.

%\item Milner, H., Kubota, K., 2005. Why the Move to Free Trade? Democracy and Trade Policy in the Developing Countries. International Organization 59, 107-143.

\item Milner, H., Rosendorff, B.P., 1997. Democratic Politics and International trade Negotiations: Elections and Divided Government as Constraints on Trade Liberalization. Journal of Conflict Resolution 41, 117-147.

\item Milner, H., Rosendorff, B.P., 2001. The Optimal Design of International Trade Institutions: Uncertainty and Escape. International Organization 55, 829-857.

\item Mitra, D., Thomakos, D., Ulubasoglu, M., 2002. `Protection for Sale' in a Developing Country: Democracy vs. Dictatorship. Review of Economics and Statistics 84, 497-508.

\item Mitra, D., Thomakos, D., Ulubasoglu, M., 2006. Can We Obtain Realistic Parameter Estimates for the Protection for Sale Model? Canadian Journal of Economics 39, 187-210.

%\item Morrow, J., Siverson, R., Tabares, T., 1999. Correction to: ``The Political Determinants of International Trade,' American Political Science Review 94, 931-933.

\item McCalman, P., 2004. Protection for Sale and Trade Liberalization: an Empirical Investigation. Review of International Economics 12, 81-94.

%\item Paltseva, E., 2011. Protection for Sale to Oligopolists. Available at: \url{http://web.econ.ku.dk/okoep/Paltseva_P4S2O_June2011_1.pdf}.

\item Roemer, J., 1997. Political-economic Equilibrium when Parties Represent Constituents: The Unidimensional Case. Social Choice and Welfare 14, 479-502.

\item Song, Y., 2008. Protection for Sale: Agenda-Setting and Ratification in the Presence of Lobbying. Korea Institute for International Trade Policy Working Paper Series. Vol. 2008-22, August 2008.

%\item Tarar, A., 2001. International Bargaining with Two-Sided Domestic Constraints. Journal of Conflict Resolution 45, 320-340.

%\item Ward, M., Hoff, P., 2007. Persistent Patterns of International Commerce. Journal of Peace Research 44, 157-175.

\end{list}
%\end{comment}

\end{document}

### 2017-09-18 draft.tex
add game-tree.tex, modify title/abstract, remove pieces necessary for first compilation

@@
 \begin{document}
-\title{\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}}
+\title{\vskip-0.6in Temporary Trade Barriers: When Will They End?}%\protect\footnote{Formerly circulated under the title }}
 \thanksmarkseries{alph}
@@
 Email: kbuzard@syr.edu.
-http://faculty.maxwell.syr.edu/kbuzard.
-I gratefully acknowledge funding from the W.
-Allen Wallis Institute of Political Economy.}}
+http://faculty.maxwell.syr.edu/kbuzard.}}
 \date{\vskip-.1in \today}
@@
 \begin{quote}
-{This paper presents a model of international trade agreements in which the executive branches of each government negotiate agreements while the legislative branches, subject to political pressure from firms, can disrupt them.
-Lobbying is in the style of Grossman and Helpman (1994) with a new feature: all actors face uncertainty arising from the complexity of the legislative process.
-I demonstrate that the higher the executives set tariffs in a trade agreement, the less effort lobbies put forth to prevent its ratification.
-Thus trade agreements act as a domestic political commitment device: executives set relatively high tariffs to discourage lobbying and increase the chance that the agreement will be ratified.
-The model sheds light on the empirical puzzle surrounding governments' welfare weights in the Grossman and Helpman (1994) model and provides a new explanation for failures to ratify trade agreements.
+{Abstract
 
-\textit{JEL classification:} D72, D80, F13, F53, F55 \\
-\textit{Keywords:} trade agreements, protection, lobbying, political economy, uncertainty}
+\textit{JEL classification:} D72, F13, F55 \\
+\textit{Keywords:} temporary trade barriers, WTO, disputes, lobbying, political economy}
 \end{quote}
@@
 \section{Introduction}
-
-%http://www.whitehouse.gov/sites/default/files/fact_sheet_increasing_us_auto_exports_us_korea_free_trade_agreement.pdf
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[height=2.5in, width=3in]{brprob2.jpg}
-\end{center}
-\caption{Probability Trade Agreement will be Broken\label{fig:br}}
-\end{figure}
-
 \begin{comment}
@@
 \end{comment}
-
-\begin{comment}
-\begin{figure}
-\centering
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.4\linewidth]{brprob2.jpg}
-  \caption{Probability Trade Agreement will be Broken}
-  \label{fig:br}
-  %\label{fig:sub1}
-\end{subfigure}%
-\begin{subfigure}{.5\textwidth}
-  \centering
-  \includegraphics[width=.4\linewidth]{contributions.jpg}
-  \caption{Lobbying Effort}
-  \label{fig:cont}
-  %\label{fig:sub2}
-\end{subfigure}
-%\caption{A figure with two subfigures}
-%\label{fig:test}
-\end{figure}
-\end{comment}
-
-Figure~\ref{fig:br} depicts the probability that the legislature will vote to break the trade agreement as a function of the tariff levels set in the trade agreement (with the restriction that $\tau^a = \tau^{*a}$) and the lobby's effort.
-It is strongly increasing in lobbying effort and decreasing in the level of tariffs set in the trade agreements.
-
-Given the impact of lobbying on the legislature's break decision, the lobby's optimal contribution level is strongly decreasing in the trade agreement tariffs.%, as shown in Figure~\ref{fig:cont}.
 
@@
 Relative to the example with $\ta_b=0$, the tariff can be reduced slightly to $0.105$.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=2.5in, width=3in]{lobby_br.jpg}
-\end{center}
-\caption{Lobby's Optimal Expenditure Function (Low and Intermediate Uncertainty)\label{fig:lobby_br}}
-\end{figure}
-
-Figure~\ref{fig:lobby_br} shows the lobby's reaction function at this very low level of uncertainty as well as the intermediate level when $\ve$ is distributed uniformly on $[-0.14,0.14]$ where the executives set the highest tariff level of $0.107$.
-For the former, the range of tariff levels to which the lobby responds with a contribution that leaves open the possibility of a break is very small: only those between 0.103 and 0.104.
-The lobby disengages completely at $\bta=0.105$.
-When uncertainty is increased to the interval $[-0.14,0.14]$, the lobby begins to leave open the possibility of a break at $\bta = 0.048$.
-It disengages at the optimal tariff level of $0.107$.
-At intermediate uncertainly levels, both portions of the best response curve are steeper and the lobby disengages at lower tariff levels---as low as $0.099$ when $\ve \sim U[-0.06,0.06]$.
-The optimal tariff does not decrease monotonically.
-
-This illustrates Part (a) of Result~\ref{res:execsoln}: here the executives maximize their welfare by raising tariffs to the point where the import-competing industry ceases to lobby and the agreement remains in force for sure.
-Although lobbying expenditures are zero, the potential for lobbying behavior is essential in shaping the trade agreement.
-
-%\begin{figure}
-%\begin{center}
-%\includegraphics[height=3.8in, width=7in]{exec_welfare.jpg}
-%\end{center}
-%\caption{Differences in Executive Welfare when Uncertainty Increases\label{fig:exec_wel}}
-%\end{figure}
-
-When uncertainty rises above this threshold of $\ve \sim U[-0.14,0.14]$, the executives' choices are made according to Part (b) of Result~\ref{res:execsoln}: they trade off reductions in welfare under the agreement with reductions in the probability that the agreement will be abrogated by the legislature.
-%In terms of the lobby's best response function, the executives now choose the optimal point on the downward-sloping portion of the curve instead of the point where it reaches zero.
-In terms of the welfare function for the executives, shown in Figure~\ref{fig:exec_wel}, they are now choosing the point that maximizes the concave portion of the curve instead of the ``spike'' that is created when the lobbies disengage and the chance that the agreement will be abrogated is removed altogether.\footnote{Note that the initial, flat portion of the curve is where the tariff is low enough that the lobby buys a trade war with certainty; we then enter the concave portion where the main results of Section~\ref{sec:main} are applicable; finally, we see the upward spike where the probability of a trade war is reduced to zero and the executives' welfare declines after that because there is no further reduction in break probability as the tariff increases.}
-
-We see from this example that variations in uncertainty lead to very different outcomes in terms of lobbying, trade agreement tariffs and the probability of disruption.
-The provided tariff levels are strongly influenced by lobbying incentives, but in more nuanced ways than those predicted by unitary models.
 

### 2017-09-18 game-tree.tex
add game-tree.tex, modify title/abstract, remove pieces necessary for first compilation

\begin{comment}
\documentclass[10pt]{article}

\addtolength{\textwidth}{1.3in}
\addtolength{\oddsidemargin}{-.65in} %left margin
\addtolength{\evensidemargin}{-.65in}
\setlength{\textheight}{9in}
\setlength{\topmargin}{-.5in}
\setlength{\headheight}{0.0in}
\setlength{\footskip}{.375in}
\renewcommand{\baselinestretch}{1.0}
\usepackage{setspace}
\doublespacing

\usepackage{titling}

\usepackage[pdftex]{graphicx}

\usepackage[usenames,dvipsnames]{color}
\usepackage{cite}
\usepackage{times, verbatim,bm,pifont,pdfsync}
\usepackage{caption}
\usepackage{subcaption}

\usepackage{tikz}

% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1}

\usepackage{amsbsy,amssymb, amsmath, amsthm, MnSymbol,bbding}
\usepackage[hang,flushmargin]{footmisc}

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}

\newcommand{\ta}{\theta}
\newcommand{\al}{\alpha}
\newcommand{\Ta}{\Theta}
\newcommand{\expect}{\mathbb{E}}
\newcommand{\Bt}{B(\bm{\tau^a})}
\newcommand{\bta}{\bm{\tau^a}}
\newcommand{\bte}{\bm{\tau^E}}
\newcommand{\btn}{\bm{\tau^n}}
\newcommand{\ga}{\gamma}

\begin{document}
\end{comment}

\tikzset{
% Two node styles for game trees: solid and hollow
solid node/.style={circle,draw,inner sep=1.5,fill=black},
hollow node/.style={circle,draw,inner sep=1.5,fill=white}
%non node/.style={circle,draw,inner sep=.1,fill=black}
}
\begin{tikzpicture}[scale=1.5,font=\footnotesize, grow=right]
% Specify spacing for each level of the tree
\tikzstyle{level 1}=[level distance=10mm,sibling distance=8mm]
\tikzstyle{level 2}=[level distance=8mm,sibling distance=8mm]
% The Tree
\node(0)[solid node,label=above:{$E,E^*$}]{} 
child{node(1)[solid node,label=below:{$0$}]{}}
child{[white] node(2)[solid node,xshift=12,label=above:{L}]{}  
	child{[black] node(4)[solid node,label=below:{$0$}]{}}
	child{[white] node(5)[hollow node,xshift=12]{} 
	 child[sibling distance=11mm]{[black] node(22)[solid node]{}  }
	 child[sibling distance=11mm]{[black] node(23)[hollow node]{}  
		child[sibling distance=8mm]{[black] node(7)[solid node,label=below:{$-\infty$}]{}}
		child[sibling distance=8mm]{[white] node(8)[solid node,xshift=12]{}  
			child[sibling distance=10mm]{[black] node(10)[solid node]{}  }
			child[sibling distance=10mm]{[black] node(12)[solid node]{}  
				child[sibling distance=5mm]{[black] node(13)[solid node,label=below:{$0$}]{}}
				child{[white] node(15)[solid node,xshift=7]{} 
					child[sibling distance=5mm]{[black] node(19)[solid node,label=below:{$-\infty$}]{}}
					child{[white] node(21)[solid node,xshift=7]{} 
						child[sibling distance=5mm]{[black] node(16)[solid node,label=below:{$0$}]{} }
						child{[white] node(18)[hollow node,xshift=12,label=left:{}]{}  }
						child[sibling distance=5mm]{[black] node(17)[solid node,label=above:{$\infty$}]{} }
						edge from parent node[black, xshift=16]{$\ta_n$} 
						}
					child[sibling distance=5mm]{[black] node(21)[solid node,label=above:{$\infty$}]{} }
					edge from parent node[black, xshift=15]{$e_n$} 
				}
				child[sibling distance=5mm]{[black] node(14)[solid node,label=above:{$\infty$}]{} }
				}
			edge from parent node[black, xshift=20]{$\ta_b$} 
			}
		child[sibling distance=8mm]{[black] node(9)[solid node,label=above:{$\infty$}]{} }
		}
	 edge from parent node[black, xshift=20]{$e_b$} 	
	 }
	child{[black] node(6)[solid node,label=above:{$\infty$}]{}}
	edge from parent node[black, xshift=23]{$\bta$} 
	}
child{node(3)[solid node,label=above:{$\infty$}]{}
}
;
% information set
    \draw[solid,bend right](1)to(3);
		\draw[solid,bend right](4)to(6);
		\draw[solid,bend right](7)to(9);
		\draw[solid,bend right](13)to(14);
		\draw[solid,bend right](16)to(17);
		\draw[solid,bend right](19)to(21);
% labels
		\node[above,xshift=3,yshift=5]at(2){$L$}; 
		\node[above,xshift=1,yshift=5]at(23){$N$}; 
		\node[above,xshift=3,yshift=5]at(5){$N$}; 
		\node[above,xshift=6,yshift=5]at(8){$Leg$}; 
		\node[above,xshift=5,yshift=5]at(12){$L$};
		\node[above,xshift=13,yshift=-17]at(21){$Leg$}; 
		\node[above,xshift=7,yshift=5]at(15){$N$}; 
		\node[left, xshift=-2]at(18){$\tau^n$}; 
		\node[below left,yshift=-12]at(12){Break}; 
		\node[below left,yshift=4]at(10){Abide}; 
		\draw[solid](5)circle(.05cm);
		\draw[solid](0)circle(.15cm);
		\node[right]at (10) {$W_E\left(\bta\right),$};
		\node[right,yshift=-10]at (10) {$\pi\left(\tau^a\right)-e_b,$};
		\node[right,yshift=-20]at (10) {$W_{ML}\left(\ga(e_b,\ta_b),\bta\right)$};
		\node[right]at (18) {$W_E\left(\btn\right),$};
		\node[right,yshift=-10]at (18) {$\pi\left(\tau^n\right)-e_b -e_n,$};
		\node[right,yshift=-20]at (18) {$W_{ML}\left(\ga(e_n,\ta_n),\btn\right)$};
		\node[right,yshift=-5]at (22) {$W_E\left(\bta\right),$};
		\node[right,yshift=-15]at (22) {$\pi\left(\tau^a\right)-e_b,$};
		\node[right,yshift=-25]at (22) {$W_{ML}\left(\ga(e_b,\ta_b),\bta\right)$};
		\node[below left,xshift=-4,yshift=8]at(23){Opp.}; 
		\node[below left,xshift=-4,yshift=-10]at(23){(o)}; 
		\node[below left,xshift=-3,yshift=7]at(22){No opp.}; 
		\node[below left,xshift=6,yshift=20]at(22){(1-o)}; 
\end{tikzpicture}

%\end{document}

### 2017-09-18 draft.tex
remove un-needed material except for results, lit review and some of model

@@
 
-Much of trade policy is determined in the context of international agreements that must be ratified by some domestic body.
-This paper sheds light on such a policy-making process by incorporating Protection-for-Sale (Grossman and Helpman 1994, hereafter PFS) style lobbying into a model of trade agreements in which the executive branches of the governments set tariff levels in anticipation of political pressure upon a ratifying body, assumed here to be a legislature.
-Important realism is achieved not only through the addition of the ratification constraint but also by the incorporation of political uncertainty into the model.
+\subsection{Related Literature}
+\textbf{WILL NEED MAJOR OVERHAUL}
 
-I show that the probability that the trade agreement is derailed increases in lobbying effort and decreases in the trade agreement tariff.
-Further, the lobby decreases its effort as the trade agreement tariff rises: it has less to lose the higher is the trade agreement tariff.
-When choosing the trade agreement tariffs, the executives therefore trade off the welfare they receive under the agreement with the probability that the agreement remains in force.
-Ultimately, I find that observed lobbying effort may often be low because the executives set trade agreement tariffs sufficiently high to reduce political pressure on the legislatures.
-
-To see how this works, let's begin by considering the case of political certainty.
-I assume the executive is more pro-social than the legislature, as has been the case throughout the post-war period in the United States.
-Lobbies, assumed for simplicity to represent import-competing interests only, would like to prevent or derail a trade agreement that would reduce their tariff protection.
-They work toward this end by exerting effort to convince their respective legislatures to vote against or ``break'' the trade agreement.\footnote{In this model, non-ratification is equivalent to breaking a trade agreement once in place because tariffs in a ``trade war'' are assumed to be set non-cooperatively just as if there were no trade agreement.
-For simplicity, I refer to this as the ``break'' decision throughout.}
-
-For any trade-agreement tariff set by the executives, a lobby can calculate the effort level required to shift the preferences of the median legislator just far enough so that he will choose the non-cooperative tariffs over the trade agreement tariffs.
-Because the lobby will pay this price so long as its benefit outweighs the cost, a trade war will occur unless the executives set the trade-agreement tariff so that lobbying is not worthwhile.
-
-Thus, any trade agreement under political certainty involves a tariff high enough to disengage the lobby completely; that is, even welfare-maximizing executives set high tariffs and induce zero contributions in equilibrium because they set policy in the shadow of a ratification decision influenced by lobbying.
-
-The fact that zero contributions are predicted in equilibrium is not particularly satisfying.
-The model becomes more realistic, has smoother results and delivers additional intuition when I allow all actors to be uncertain about the weight the median legislator places on the profits of the lobbying industry.
-Similar to probabilistic voting models that incorporate policy motivation as in Roemer (1997), this represents the idea that the lobbying and voting ``game'' that goes on within legislatures is often so complex that none of the actors know precisely what the outcome will be---that is, no one can predict exactly which legislator will be the median and therefore what weight will be placed on import-industry profits at the time of the vote.
-One can conceptualize this uncertainty as being a result of the lobby's strategic choice to engage with only some key members of the legislature.
-For instance, the lobbied legislators may promise to deliver the votes of their non-lobbied colleagues but may not be able to do so with certainty because those colleagues are subject to cross-pressuring from various sources.
-
-One contribution of this model is that it shows how trade agreements can act as a domestic political commitment device in a broad set of environments.
-The executives set trade-agreement tariffs with an eye to discouraging lobbying activity and the accompanying probability of abrogation.
-In addition to the standard terms-of-trade internalization, the executive's agenda-setting power allows it to reduce tariffs until lobbying activity is at the optimal level relative to a non-cooperative setting, reducing the amount of political pressure faced by the legislatures and the resultant expected tariffs.
-
-This is not a time inconsistency \`{a} la Maggi and Rodr\'{i}guez-Clare (2007) where the welfare of the unitary policymaker is improved by changing firms' investment decisions via commitment to a trade agreement.
-Instead, this is an inconsistency between the preferences of the executive and legislative branches.
-Although the legislatures have the final word, the executives use the trade agreement to reduce lobbying effort, muting the legislature's protectionist bias and bringing the outcome more in line with their relatively liberal preferences.
-
-A further contribution is the demonstration that lobbying effort and the probability of trade disruptions vary in nuanced ways with the amount of political uncertainty present.
-Lobbying incentives are crucial but their impact is not necessarily as straightforward as predicted by models with unitary governments.
-Gawande, Krishna and Olarreaga (2009) provide cross-country evidence that measures such as the number of checks and balances on the power of the legislature have predictive power for the PFS ``welfare-mindedness'' parameter.
-Thus, although empirical tests are outside the scope of this paper, there is suggestive evidence that political uncertainty is indeed empirically important.
-
-To the best of my knowledge, this is also the first attempt to model lobbying specifically aimed at derailing trade agreements.
-Although this kind of politically-driven failure is not rare, prior models have not allowed exploration of the endogenous dynamics behind them.
-
-The addition of a rich structure of government, tailored carefully to the trade policy making process, also helps shed light on the empirical puzzle surrounding the PFS model.
-Empirical tests of the model\footnote{cfr.
-Goldberg and Maggi (1999); Gawande and Bandyopadhyay (2000); Mitra, Thomakos and Ulubasoglu (2002); McCalman (2004).\label{fn:gh_lobby}} have consistently found the weight governments place on social welfare to be many times that which they place on lobbying effort, while estimates indicate that the deadweight losses caused by trade distortions are several orders of magnitude larger than lobbying expenditures.\footnote{Feenstra (1992) assembles estimates from the mid-1980s that place a floor of $\$$8 billion per year on the deadweight losses from protection, whereas Bombardini and Trebbi (2012) find that total annual lobbying expenditure on trade issues in 1999-2001 when this data first became available was about $\$$200 million.} This raises the question: how could governments value social welfare so highly, yet grant these quantities of protection at such a low price?
-
-Attempts to more fully model the lobbying process have reduced the parameter estimates for the government's welfare considerations somewhat, but they still indicate that the U.S.
-government, for instance, values social welfare at least twenty times as much as contributions.\footnote{cfr.
-Gawande, Krishna and Robbins (2006); Mitra, Thomakos and Ulubasoglu (2006); Bombardini (2008); and Gawande, Krishna and Olarreaga (2012) among others.
-Gawande and Magee (2012) provide a summary of the extensive literature, while Imai, Katayama and Krishna (2009) argue that many of the classification schemes present serious challenges for the validity of results.} As suggested by Gawande and Hoekman (2006), in the non-unitary government model, these estimates and the stylized facts are not inconsistent.
-The ``missing contributions,'' can be explained as an equilibrium phenomenon arising from the agenda-setting power of the executive branch.
-In particular, in this model, there is no inconsistency for the 15$\%$ or so of sectors that receive protection but apparently put forth no lobbying effort.
-In this framework, even a welfare-maximizing executive and lobbying effort at zero can be reconciled with high tariff levels.
-
-Although the political process here most closely matches that of the United States in the post-war era,\footnote{In particular, the legislatures' decision to abide by or break the trade agreement is modeled on the ``Fast Track / Trade Promotion Authority'' that the U.S.
-Congress periodically grants to the Executive branch.} the model is broadly applicable because the central dynamic that emerges---that trade agreements are formed in the \textit{shadow} of lobbying pressure instead of in direct response to it---appears to be present in a wide range of countries.
-The results apply beyond separation-of-powers presidential systems because the presence of veto points is what is essential for this dynamic to occur.
-Although the number of formal veto points tends to be lower in, for instance, parliamentary systems, veto points are typically not absent altogether (Henisz and Mansfield 2006).
-In reality, constraints on the executive are almost always present in democratic regimes, although they may operate in different ways.
-
-\subsection{Related Literature}
 This work rests on the foundation of Grossman and Helpman's (1994) `Protection for Sale.' Two related papers `Trade Wars and Trade Talks' (Grossman and Helpman (1995b)) and `The Politics of Free-Trade Agreements' (Grossman and Helpman (1995a)) first employed the PFS approach in the study of trade agreements.
@@
 
+\textbf{REVISE GOVERNMENT STRUCTURE}
+
 In each country, there is an executive who concludes trade agreements and a legislature that has final say on trade policy.
@@
 
+\textbf{LOBBY'S OBJECTIVE IS DIFFERENT HERE}
+
 Given its expectations and the legislature's preferences, the home lobby chooses its lobbying effort ($e_b$ to influence the break decision and $e_n$ to influence the trade war tariff) to maximize the welfare function:
@@
 where $\pi(\cdot)$ is the current-period profit and the subscript $X$ has been dropped for notational convenience.
+
+\textbf{NOT SURE I KNOW EXACTLY WHAT THE GOVERNMENT'S OBJECTIVE IS, DIVIDED GOV'T EVEN?}
 
@@
 \label{sec:info}
+
+\textbf{NOT SURE AT ALL ABOUT THESE FEATURES; it's not a two-country model}
+
 I examine a simple class of equilibria that have three key features.
@@
 \begin{result}
-  When the trade agreement remains in force with positive probability, lobbying effort is weakly decreasing in trade agreement tariffs.\footnote{See Section~\ref{sec:uncertainty} for a detailed account of behavior when the lobby is able to induce a trade war with probability 1.}
+  When the trade agreement remains in force with positive probability, lobbying effort is weakly decreasing in trade agreement tariffs.
   \label{res:lobby}
@@
 \end{lemma}
-I show in the \hyperlink{int_soln}{Appendix} that it is never optimal in a symmetric equilibrium for the executives to choose $\bm{\tau^a}$ at or below the executives' most preferred level if the legislatures will have an opportunity to break the trade agreement.
-This is because there are only second-order losses from raising tariffs slightly from the most-preferred level yet there are first-order gains in reducing the probability that the agreement will be broken.
 
@@
 
-\section{An Example}
-\label{sec:example}
-In this simple parameterization of the model, the fundamentals are chosen to match Bagwell and Staiger (2005): $D(P_i) = 1 - P_i$, $Q_X(P_X) = \frac{P_X}{2}$, $Q_Y(P_Y) = P_Y$, $\Pi_X(P_X) = \frac{(P_X)^2}{4}$, and $\Pi_Y(P_Y) = \frac{(P_Y)^2}{2}$.
-Home-country imports of $X$ and exports of $Y$ are $M_X(P_X)= 1 - \frac{3}{2}P_X$ and $E_Y(P_Y)= 2P_Y -1$.
-Market clearing implies that world and home prices of $X$ are $P_X^W = \frac{4-3\tau}{7}$ and $P_X = \frac{4+4\tau}{7}$.
-Foreign is taken to be symmetric.
-
-\subsection{Trade War Tariffs}
-The median legislator's welfare can be written as 
-\[
-  W_{\mathit{ML}}^X(\tau,\ga(e,\ve)) + W_{\mathit{ML}}^Y(\tau^*) = \left\{\frac{9}{98} - \frac{5}{49}\tau - \frac{34}{49}\tau^2 +\frac{1}{98}\ga(e,\ve)\left[ 8 + 16\tau + 8\tau^2 \right] \right\}+ \frac{25}{98} - \frac{3}{49}\tau^* + \frac{9}{49}(\tau^*)^2.
-\]
-%where $W_{\mathit{ML}}^X(\tau,\ga(e,\ve))$ is the utility derived from consumer surplus, producer surplus and tariff revenues in the import-competing industry and $W_{\mathit{ML}}^Y(\tau^*)$ is the utility derived from consumer and producer surplus in the exporting industry.
-
-The Nash tariff that results from unilateral maximization is\footnote{The second order condition is satisfied for all realizations of $\ga < 17/2$.
-Because $\ga = 7/4$ is enough to achieve the prohibitive tariff of $1/6$, I will assume this condition is satisfied.}
-\[
-  \tau^n = \frac{8\ga(e,\ve)-5}{68-8\ga(e,\ve)}
-\]
-
-To predict the Nash tariff, the political weighting function and form of political uncertainty must be specified.
-Take $\ga(e,\ve) = 1.25 + e^{.2} + \ta$ with $\ve$ distributed uniformly on $[-0.25,0.25]$.
-Facing this specification of the political process, the lobby maximizes its objective function at $e_n = 0.00166$, producing an expected Nash tariff of $0.129$.
-Net profits are $0.10239$ in terms of the numeraire and lobbying effort is $1.60\%$ of gross profits.
-
-\subsection{Break Decision}
-
-\begin{comment}
-\begin{figure}
-\begin{center}
-\includegraphics[height=2.50in, width=3in]{contributions.jpg}
-\end{center}
-\caption{Lobbying Effort\label{fig:cont}}
-\end{figure}
-%graph is created in lobby_fix.m
-\end{comment}
-
-\subsection{Trade Agreement}
-The break probability never reaches zero for this parameterization so the executives' welfare function is concave everywhere.
-Assuming that each legislature has the opportunity to break the agreement with probability $\frac{1}{2}$ and that the executives are social-welfare maximizers, they set trade agreements tariffs of $\tau^a = \tau^{*a} = 0.078$, with lobbying expenditures at the trade maintenance phase of $0.0007$ and a total break probability of $0.505$.
-Total lobbying expenditure is $1.54\%$ of the expected profits of $0.98591$.
-The expected tariff is $0.103$.
-
-We can compare this against different benchmarks.
-The most stark is the trade-war outcome, which is the outcome that would prevail in the absence of any trade agreement.
-The tariff in the executive-formed trade agreement is about 60$\%$ of the Nash tariff of $0.129$, and the expected tariff given the probability that the agreement will be broken is 80$\%$ of the Nash level.
-Lobbying expenditures in the agreement-maintenance phase are about 40$\%$ of the those in the Nash game, while expected expenditures in the executive-led trade-agreement scenario are 90$\%$ of what they would be if the legislatures set tariffs unilaterally.
-Although the welfare-maximizing governments here are not able to set and maintain tariffs at zero as they would like, they are able to achieve significant reductions in tariff levels through the use of the trade agreement.
-
-Another benchmark is the scenario in which the legislatures make use of a trade agreement without the involvement of the executives.
-As in Bagwell and Staiger (2005), I find when maximizing their joint welfare in a legislature-led trade agreement, the cooperative tariff levels will be set at
-\[
-  \tau^L = \frac{4\ga(e,\ve)-4}{25-4\ga(e,\ve)}, \ \tau^{*L} = \frac{4\ga(e^*,\ve)-4}{25-4\ga(e^*,\ve)}
-\]
-The legislatures are able to use the agreement to internalize the terms of trade externality, making political influence more expensive for the lobbies.
-Lobbying expenditures rise to $0.0027$---60$\%$ higher than in the Nash case and $2.64\%$ of the gross profits of $0.10204$---while the agreement tariffs are set at $0.118$, only slightly lower than the Nash tariffs of $0.129$ and still higher than in the executive-led trade agreement.
-Comparing net expected profits across the three scenarios, they are highest in the Nash game, lowest under the trade agreement and intermediate when the legislatures make policy directly.
-
-\section{Discussion}
-\label{sec:dis}
-
-\subsection{Separation of Powers}
-\label{sec:sep_powers}
-We can isolate the results that derive from the assumption that power over trade policy is shared between the executive and legislative branches if we assume that there is no uncertainty at the break stage.
-
-When $\ga(e_b)$ is deterministic, the lobby knows the precise contribution it must make for any given trade agreement tariffs $\bta$ to induce the legislature to break the agreement.
-Here, the lobby's contribution \textit{increases} in $\bta$ since the higher are the trade agreement tariffs, the larger is the political weight that is required to induce the legislature to find them unsatisfactorily low.
-As long as trade war profits net of the required contribution are greater than trade agreement profits, the lobby will induce a trade war; otherwise, it is not in the lobby's interest to make any contribution.
-Facing this behavior, the executives set the lowest trade agreement tariffs that make it prohibitively expensive for the lobby to have the agreement broken.
-
-In the example of Section~\ref{sec:example}, if the executives set the trade agreement facing no uncertainty, the tariff level is $0.106$, the lobby exerts zero effort, and the agreement remain in force with probability 1.
-If instead the executives were to set trade-agreement tariffs of $0.105$, the lobby would contribute $0.0025$ and the legislature would break the agreement with probability 1.
-This demonstrates both the agenda-setting power of the executives and the stark discontinuities induced when political uncertainty is not an issue.
-
-This case highlights the manipulation of tariffs to discourage lobbying and the disconnect that can arise between the tariffs that are chosen and the preferences of governmental actors.
-The executives here prefers zero tariffs while the legislators prefer $\tau^a = 0.05$ when $e_b = 0$.
-However, the trade agreement tariffs are set at $0.106$ precisely to ensure that $e_b =0$ so that we have a legislature that upholds the agreement.
-
-\subsection{The Role of Political Uncertainty}
-\label{sec:uncertainty}
-Adding political uncertainty allows for positive lobbying on the equilibrium path, but this is not the only additional insight.
-For simplicity, I assume uncertainty is mean-zero.
-Lobbying behavior in a trade war is not altered by mean-zero uncertainty and so neither are expected trade-war tariffs.
-At earlier stages, uncertainty alters optimizing behavior by both the lobby and the executives.
-Consider adding a very small amount of uncertainty to the example of the previous section: take $\ve$ distributed uniformly on $[-0.01,0.01]$.
-Here, the executives find it optimal to set the tariffs to completely disengage the lobby, ensuring the agreement remains in force.
-However, the tariff level will be different than when $\ta_b=0$ because instead of making the lobbying decision according to the certainty condition $\pi(\tau^n) - e_n - \pi(\tau^a) > e_b$, the lobby makes this decision according to Condition~\ref{ine:lobint}.
-Relative to the example with $\ta_b=0$, the tariff can be reduced slightly to $0.105$.
-
-\subsection{Relation to Grossman and Helpman's `Protection for Sale'}
-\label{sec:gh}
-I have introduced a legislative welfare function that admits a wide range of political processes within a non-unitary legislature as well as unitary policy-making when special interests face non-constant returns to lobbying activity.
-The non-linear relationship between lobbying effort and tariffs follows Dixit, Grossman and Helpman (1997) and is a departure from the `Protection for Sale' welfare function, which assumes that a unitary government maximizes the sum of contributions and some fraction, $a$, of social welfare.
-
-Although using the $\ga$-weighted government welfare function is a reduced-form approach in the sense that legislative dynamics are not fully modeled, a benefit is that it does not require returns to lobbying effort to be constant.
-The more flexible form of the weighting function also removes the equilibrium indeterminacies and inability to speak to distributional questions that are implied by the linear form and its transferable utility (Dixit, Grossman and Helpman 1997).
-
-The elegant PFS form is able to capture key cross-industry predictions on import tariffs.
-A perhaps unintended byproduct in the subsequent literature seems to have arisen in the form of a focus on matching fine details of governments' welfare-mindedness using a model that has a very simple unitary government and is thus better suited for other purposes.
-
-It is clear that trade policy is often shaped in a complicated process involving multiple actors (see, for instance, Destler (2005) for the U.S.).
-The model presented herein is a first attempt to more richly model the policy-making process and thus shed light on open questions surrounding how government preferences and the details of political institutions impact trade policy outcomes.
-
-\begin{comment}
-\section{Extensions}
-\label{sec:ext}
-
-This analysis has been undertaken with the assumption that the import-competing industry is distributed evenly across legislative districts.
-By varying the way in which those profits enter the welfare function of the median legislator (before lobbying takes place), I can provide results about how district composition affects trade policy.
-
-There are also several directions to explore in comparing different government structures. I start by describing the value of a trade agreement in an institutional setting of divided government.
-\begin{result}
-  Lobbying effort is reduced by the presence of executive branches who form a trade agreement (where the counterfactual is legislatures setting unilateral trade policy).
-\end{result}
-\textcolor{blue}{Don't yet know what assumptions I need to make this work} \\
-
-Comparing this model to the unitary-government model is a delicate task.
-The most straightforward approach from the current structure is to disregard the executives and allow the legislative branches to form a trade agreement cooperatively after lobbying takes place.
-Note that we can retain the stochastic nature of the tariff-setting, but there is no vehicle for the agreement to be broken.
-In this case, the trade agreement tariff in home, $\tau_U^a$ will maximize
-\[
-  W_X(\tau,\ga_E) + W_X^*(\tau) = \frac{9}{98} - \frac{5}{49}\tau - \frac{34}{49}\tau^2 +\frac{1}{98}\ga(e,\ve)\left[ 8 + 16\tau + 8\tau^2 \right] + \frac{25}{98} - \frac{3}{49}\tau + \frac{9}{49}(\tau)^2
-\]
-and will thus be set at
-\[
-  \tau_U^a = \frac{4\ga(e,\ve)-4}{25-4\ga(e,\ve)}.
-\]
-$\tau_U^a < \tau^n$ for all $\ga(e,\ve) < 7/4$, while $\ga(e,\ve)=7/4$ results in the prohibitive tariff of $1/6$.
-This is the standard result that a trade agreement internalized the terms of trade externality and results in a lower tariff than unilateral policy making.
-
-\textcolor{blue}{will an executive inserted into this situation set higher or lower tariffs, what will happen to $e$?}
-
-What if we add executive branches with essentially the same preferences as the legislature?
-That is, set $\ga_E = \expect[\ga(e,\ve)]$.
-\textcolor{blue}{It's hard to say how $e$ should be chosen here...still need to figure that out.
-But if we can get around the weird time inconsistency problem...} What agreement tariffs will the executives choose?
-It's easy to see that they will not choose $\tau^a < \tau_U^a$, as $\tau_U^a$ is their ideal point if there were no possibility of the agreement being broken, and lower tariffs only incentivize more lobbying and a higher probability that the agreement will be broken.
-
-Thus, if an interior solution exists \textcolor{blue}{[should have conditions to insert here]}, the executive will exploit the same trade-off explored earlier, raising $\tau^a$ a bit to reduce the probability that the agreement will be abrogated.
-So interestingly, we can see that executives with the same political preferences as the legislature will choose higher trade agreement tariffs than the legislature would by itself due to the possibility that the agreement can be broken and the impact of the tariff choice on lobbying.
-We will also therefore have a reduced level of contributions, and if a trade war were possible, lower trade war tariffs because of it.
-
-Along these lines, allowing for asymmetries in the preferences and political processes between the countries will provide important insights as well.
-
-I also plan to use the richness of this model to parse out how much of the changes in tariffs comes from the fact that the executives place lower weight on producer profits and how much comes from the fact that they make an agreement---that is, compare the effects of structure versus preferences.
-
-\subsection{Asymmetric Trade Agreements}
-\label{sec:asym}
-The assumption that the legislatures do not have the opportunity to break a trade agreement simultaneously serves to simplify the analysis of the interaction between the lobbies and the consequences of relaxing it will be discussed in the following section.
-Maintaining it for now, however, facilitates examination of the assumption that trade agreements must be symmetric.
-This may be quite realistic in some settings where additional political constraints would make ``unfair'' arrangements unpalatable.
-However, it is important to point out that, for some parameter choices, the joint welfare of the executives is in fact maximized by an asymmetric agreement.
-
-The parameterization from the example in Section~\ref{sec:example} is one such instance.
-The optimal unrestricted trade agreement is to set tariffs in one country (say home) at $0.062$ and those in the other (foreign) at 0.
-In this case, the equilibrium break probability in home, if the home legislature is afforded the opportunity, is zero, while the foreign legislature will break the agreement with probability 1 if given the chance.
-With the assumption from the example that each legislature gets the opportunity to repudiate the agreement half the time, this results in the trade agreement being broken with probability $0.50$, just less than the $0.505$ of the optimal symmetric agreement with both tariffs set at $0.078$.
-Because both the trade agreement tariffs and the expected chance that the agreement will remain in force are lower, expected welfare for the executives is higher.
-
-What is behind the rather surprising result that a lower break probability can be achieved when both tariffs are strictly lower than in the symmetric agreement?
-Here, the executives relinquish any chance of passage of the trade agreement in the foreign country (in essence hoping that its legislature will not have a chance to act).
-Once they decide to pursue this course, it is optimal to reduce $\tau^{*a}$ to zero.
-This drastically reduces the home legislature's incentive to break the trade agreement.
-Because of the large direct impact of $\tau^{*a}$ in reducing the break probability, the home tariff is not required to make such a large contribution and can be lowered, which in turn reduces the lobby's incentive to exert effort (see Result~\ref{res:lobby}).
-This effect is strong enough that the executives can set a tariff level lower than that of the symmetric agreement that is sufficient to disengage the home lobby (see Inequality~\ref{ine:lobint}).
-
-It is useful to keep in mind that this result occurs in a completely symmetric environment.
-Recall that, in general, the executives maximize joint welfare in Equation~\ref{eq:jv2}.
-If the chance that the legislatures will have the opportunity to break the agreement ($o$ and $o^*$) are not equal, or if another significant aspect of the economic or political situation is asymmetric, the importance of this result grows in a potentially substantial way.
-In particular, if only one country faces a legislative constraint, an asymmetric agreement seems highly likely as in the large body of literature investigating the Schelling conjecture.
-
-\subsection{Break Opportunities in Both Countries}
-\label{sec:two}
-Although it changes their expected payoffs, extending the model to allow both legislatures the opportunity to break the trade agreement simultaneously does not impact the legislatures' incentives as each decision to break or not break the agreement is independent of the other.
-
-However, the lobbies' incentives are altered because the total probability of a break with which they weight profits changes.
-Now, in addition to their own effort positively influencing their own legislature to break the agreement, the probability of a break in the trade agreement also increases in the effort of the other country's lobby.
-As might be expected, the lobbying effort in each country turns out to be a negative function of that in the trading partner; that is, to some extent, the lobbies have an incentive to free ride.
-
-Without making stronger assumptions, it is not possible to say how much the effort of each lobby will be reduced therefore whether total lobbying effort rises or falls.
-What is clear is that the optimization of the executives becomes significantly more complex as they are now faced with the problem of how to best exploit the free-riding dynamics that occur between the lobbies.
-\end{comment}
-
 \section{Conclusion}
 \label{sec:concl}
-I have shown that the legislature both breaks trade agreements with a higher probability and sets higher trade war tariffs when lobbying activity increases, while the probability with which it breaks agreements decreases in the domestic trade agreement tariff.
-Because the lobby decreases its effort in response to higher trade agreement tariffs, the executives face a trade-off between the welfare derived while a trade agreement is in force and the probability with which the agreement actually enters into force.
 
-I have also shown that in a policy-making structure in which power is shared, a less politically-motivated executive can utilize an international trade agreement to reduce the political pressure on the ratifying body and therefore increase the probability that the agreement will remain in force.
-Thus, in a model with a richer description of government structure, a broad political-commitment role for trade agreements can arise.
-
-The executives' incentive to raise tariffs in order to reduce lobbying effort provides insight into the empirical puzzle in the Protection for Sale literature that levels of protection and associated deadweight losses are too high relative to lobbying expenditure given the high estimates for governments' weighting of social welfare.
-The intuition is clear: the observed lobbying expenditure levels may in fact be low \textit{because} tariffs have been raised sufficiently high to prevent political pressure and the increased risk of a costly trade disruption it engenders.
-
-That lobbying and tariff levels are related in systematic ways to the amount of political uncertainty present suggests interesting avenues for future empirical work.
-Several directions for future theoretical work also seem potentially fruitful, including removing the assumption of perfect enforceability and supporting cooperation through repeated interaction and generalizing the model to the case of multiple lobbies.
-
-%\begin{comment}
 \section{Appendix}
@@
 \noindent \textbf{\hypertarget{Pr_bincC}{Proof of Result~\ref{res:bincC}}}:\\
-Substituting from Equation~\ref{eq:ml}, Equation~\ref{eq:b} can be re-written as
-\begin{multline}  
-  b(e_b,\bta,\btn) = \Pr [ \mathit{CS}_X(\tau^n) + \ga(e_b,\ve_b) \cdot \pi_X(\tau^n) + \mathit{CS}_Y(\tau^{*n}) + \pi_Y(\tau^{*n}) + \mathit{TR}(\tau^n) >  \\ \mathit{CS}_X(\tau^a) + \ga(e_b,\ve_b) \cdot \pi_X(\tau^a) + \mathit{CS}_Y(\tau^{*a}) + \pi_Y(\tau^{*a}) + \mathit{TR}(\tau^a) ]
-\end{multline}
-Rearranging, we have $b(e_b,\bta,\btn) = $
-\begin{multline}  
-  \textstyle \Pr \Big[ \frac{\mathit{CS}_X(\tau^n) + \pi_X(\tau^n) + \mathit{CS}_Y(\tau^{*n}) + \pi_Y(\tau^{*n}) + \mathit{TR}(\tau^n)  -\mathit{CS}_X(\tau^a) - \pi_X(\tau^a) - \mathit{CS}_Y(\tau^{*a}) - \pi_Y(\tau^{*a}) - \mathit{TR}(\tau^a)}{\pi_X(\tau^a) - \pi_X(\tau^n)} + 1 \\ \textstyle < \ga(e_b,\ve_b) \Big]
-  \label{eq:b_ex}
-\end{multline}
-%\noindent The left side of the inequality in Expression~\ref{eq:b_ex} does not depend on $e_b$.
-By Assumption~\ref{as:ga_c}, the right side of the inequality is increasing and concave in $e_b$.
-Thus $b(e_b,\bta,\btn)$ is increasing and concave in $e_b$.
-$\hfill\blacksquare$
-\noindent The left side of the inequality in Expression~\ref{eq:b_ex} does not depend on $e_b$.
-Call it $Z$.
-Thus we have $b(e_b,\bta,\btn) = \Pr [Z < \ga(e_b,\ve_b) ] = 1 - F_{\ga}(\ga=Z)$ where $F_{\ga}(\ga=Z) = F_{\ta}(\ta=h^{-1}(\ga,e))$ by the Change of Variables Theorem and Assumption~\ref{as:ga_ta} with $\ga = h(e,\ta)$ giving the change of variable.
-
-Then $\frac{\partial b}{\partial e} = -\frac{\partial F_{\ta}(\ta=h^{-1}(\ga,e))}{\partial \ta}\frac{\partial h^{-1}(\ga,e)}{\partial e} = -f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial e}$ and $\frac{\partial^2 b}{\partial e^2} = -f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2}$.
-Because $\ga = h(e,\ta)$ is increasing and concave in $e \ \forall \ta$ by Assumption~\ref{as:ga_c}, its inverse is decreasing and convex $\left(\frac{\partial h^{-1}(\ga,e)}{\partial e}\leq 0; \ \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2} \geq 0 \right)$ The pdf of $\ta$ is non-negative, so $\frac{\partial b}{\partial e} \geq 0$ and $\frac{\partial^2 b}{\partial e^2} \leq 0$.
-$\hfill\blacksquare$
-
-\vskip.4in
-\noindent \textbf{\hypertarget{Pr_leg_astar}{Proof of Lemma~\ref{lem:leg_astar}}}:\\
-It must be shown that the left hand side of the inequality in Expression~\ref{eq:b_ex} is decreasing in $\tau^{*a}$. The derivative of this quantity with respect to $\tau^{*a}$ is 
-\begin{equation}
-  \frac{-\left(\pi_X(\tau^a) - \pi_X(\tau^n)\right)\left(\frac{\partial \mathit{CS}_Y(\tau^{*a})}{\partial \tau^{*a}} + \frac{\partial \pi_Y(\tau^{*a})}{\partial \tau^{*a}}\right)}{\left(\pi_X(\tau^a) - \pi_X(\tau^n)\right)^2} = \frac{\frac{\partial \mathit{CS}_Y(\tau^{*a})}{\partial \tau^{*a}} + \frac{\partial \pi_Y(\tau^{*a})}{\partial \tau^{*a}}}{\pi_X(\tau^n) - \pi_X(\tau^a)}.
-  \label{appex:astar}
-\end{equation}
-
-\noindent The price of good $Y$ is decreasing in $\tau^{*a}$, so consumer surplus is increasing and profits are decreasing in $\tau^{*a}$.
-Because $Y$ is being exported, the decrease in profits is larger than the increase in consumer surplus, making the numerator negative.
-Since profits in the denominator are increasing in $\tau$, the expression in Equation~\ref{appex:astar} is negative for all $\tau^{*a}$.
-$\hfill\blacksquare$
-
-\vskip.4in
-\noindent \textbf{\hypertarget{Pr_leg_a}{Proof of Lemma~\ref{res:leg_a}}}:\\
-Using the logic of the proof of Lemma~\ref{lem:leg_astar}, the effect on the break probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
-Labeling the numerator of that expression $\left[ W(\btn)-W(\bta)\right]$ (for the change in social welfare), this derivative can be written
-\begin{equation}
-  \frac{\left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - \left[ W(\btn)-W(\bta)\right] \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tau^n)\right)^2}.
-  \label{appex:a}
-\end{equation}
-
-\noindent $\left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)$ is always positive by Assumption~\ref{as:ga_l_e}.
-Because the optimal unilateral tariff for large welfare-maximizing governments is positive (call it $\tau^O$), $\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right)$ is increasing up to $\tau^O$ and decreasing above it.
-Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter.
-
-Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $W(\btn)-W(\bta)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere.
-With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.
-
-It is also positive over the remaining $(\tau^O,\tau^n)$.
-To see this, add $\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a} \left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)$ to the first summand and subtract it from the second.
-For any particular value of $\tilde{\tau}^a$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\tau}^a$ the preferred unilateral tariff; this makes the derivative in the first summand zero.
-Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\tau}^a$ so that this term is always negative, thus ensuring the result.
-$\hfill\blacksquare$
-
-\vskip.4in
-\noindent \textbf{\hypertarget{Pr_bcomb}{Proof of Lemma~\ref{res:bcomb}}}:\\
-Again, I want to show how the inequality in Expression~\ref{eq:b_ex} changes, now with respect to both $\tau^a$ and $\tau^{*a}$, so I add the derivatives in Expressions~\ref{appex:astar} and \ref{appex:a} to get
-\[
-  \frac{\left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{W}_X(\bta)}{\partial \tau^{a}} + \frac{\partial \mathit{W}_X(\bta)}{\partial \tau^{*a}}\right) - \left[ W(\btn)-W(\bta)\right] \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)^2}.
-\]
-where $\frac{\partial \mathit{W}_X(\bta)}{\partial \tau^{a}} + \frac{\partial \mathit{W}_X(\bta)}{\partial \tau^{*a}} = \frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \mathit{CS}_Y(\tau^{*a})}{\partial \tau^{*a}} + \frac{\partial \pi_Y(\tau^{*a})}{\partial \tau^{*a}}$ is the total derivative of social welfare.
-Since social welfare is maximized at $\bta = (0,0)$,\footnote{Note, this is identical to the result that joint social welfare is maximized at zero tariffs because of symmetry.}  this is negative $\forall \bm{\tau} \in (\bm{0},\btn]$; note that it is 0 at $\bm{0}$ and vanishingly small for very small tariffs.
-
-Thus the first summand in the numerator is zero at $\bta = \bm{0}$ and increasingly negative as $\bta$ increases.
-The second summand is positive everywhere because social welfare, $W$, is lowest at $\btn$ and profits are increasing everywhere.
-Thus the numerator is positive at $\bm{0}$ and at least for very small $\bta$
-
-It is also positive for all other values of $\bta$ strictly below $\btn$. Just as in the proof of Lemma~\ref{res:leg_a}, one can add
-$\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a} \left(\pi_X(\tau^n) - \pi_X(\tau^a)\right)$ to the first summand and subtract it from the second.
-For any particular value of $\tilde{\bta}$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\bta}$ the politically optimal tariff; this makes the derivative in the first summand zero.
-Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\bta}$ so that this term is always negative, thus ensuring the result.
-
-Because the denominator is positive, the entire expression is positive for all $\bta < \btn$.   $\hfill\blacksquare$
-
-\vskip.4in
-\noindent \textbf{\hypertarget{Pr_lobby}{Proof of Result~\ref{res:lobby}}}:\\
-Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
-  \[
-		\frac{\partial e_b}{\partial \tau^a} + \frac{\partial e_b}{\partial \tau^{*a}} = - \left[ \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e_b}} + \frac{\frac{\partial FOC_L}{\partial \tau^{*a}}}{\frac{\partial FOC_L}{\partial e_b}} \right] = \frac{ \frac{\partial b}{\partial e_b} \frac{\partial \pi(\bta)}{\partial \tau^a} + \frac{\partial b}{\partial e_b} \frac{\partial \pi(\bta)}{\partial \tau^{*a}} - \left\{\frac{\partial^2 b}{\partial e_b \partial \tau^a} + \frac{\partial^2 b}{\partial e_b \partial \tau^{*a}}   \right\}\left[ \pi(\tau^n) - e_n - \pi(\tau^a) \right]}{\frac{\partial^2 b}{\partial e_b{}^2} \left[ \pi(\tau^n) - e_n - \pi(\tau^a) \right]}
-	\]
-Beginning with the denominator: because $\pi(\tau)$ is increasing everywhere, $\left[\pi(\tau^n) - e_n - \pi(\tau^a) \right]$ is positive for all but very large values of $\tau^a$, that is for all $\tau^a$ such that $\pi(\tau^n) - e_n > \pi(\tau^a)$.
-When $\tau^a$ rises above this level, it is no longer in the lobby's interest to ask to have the agreement broken so $e_b=0$ and $\frac{\partial e_b}{\partial \tau^a} = 0$.
-$\frac{\partial^2 b}{\partial e_b{}^2}$ negative by Result~\ref{res:bincC}, so the denominator is negative for all values of $\tau^a$ at which $e_b$ is not constant.
-
-$\frac{\partial b}{\partial e_b}$ is positive, $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction, and $\frac{\partial \pi(\bta)}{\partial \tau^{*a}}$ is zero: separability between the sectors implies that profits in the import-competing sector do not depend on $\tau^{*a}$.
-
-We can rewrite $\frac{\partial b(e,\bta)}{\partial  \tau^a} + \frac{\partial b(e,\bta)}{\partial  \tau^{*a}} = -\frac{\partial F_\ga (Z(\bta))}{\partial \tau^a} -\frac{\partial F_\ga (Z(\bta))}{\partial \tau^{*a}} = -\frac{\partial F_\ga (Z(\bta))}{\partial Z(\bta)}\left[\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \right] = - f_\ga \left[\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \right]$, where $F_\ga (Z(\bta))$ is the CDF of $\ga$ and $f_\ga (Z(\bta))$ is the pdf of $\ga$ and $Z(\bta)$ represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
-
-Then $\frac{\partial^2 b}{\partial e_b \partial \tau^a} + \frac{\partial^2 b}{\partial e_b \partial \tau^{*a}} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta))}{\partial \tau^a} + \frac{\partial F_\ga (Z(\bta))}{\partial \tau^{*a}} \right) =
-	   - f_\ga \left[\frac{\partial^2 Z(\bta)}{\partial \tau^a \partial e} + \frac{\partial^2 Z(\bta)}{\partial \tau^{*a} \partial e} \right] - \left[\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \right] \frac{\partial f_\ga}{\partial e} = - \left[\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \right] \frac{\partial f_\ga}{\partial e}
-$
-where the above equality holds because $Z(\bta)$ does not depend on $e$.
-Lemma~\ref{res:bcomb} shows that $\frac{\partial Z(\bta)}{\partial \tau^a} + \frac{\partial Z(\bta)}{\partial \tau^{*a}} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\left\{\frac{\partial^2 b}{\partial e_b \partial \tau^a} + \frac{\partial^2 b}{\partial e_b \partial \tau^{*a}} \right\} \leq 0$.
-Thus $\frac{\partial e_b}{\partial \tau^a} + \frac{\partial e_b}{\partial \tau^{*a}} \leq 0$.
-$\hfill\blacksquare$
-
-\vskip.4in	  	
-\noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:bcomB}}}: \\
-$	\frac{\partial B(\bta)}{\partial \tau^a} + \frac{\partial B(\bta)}{\partial  \tau^{*a}} = \frac{\partial b}{\partial  e_b}\frac{\partial e_b}{\partial \tau^a} + \frac{\partial b}{\partial  e_b}\frac{\partial  e_b}{\partial  \tau^{*a}} + \frac{\partial b}{\partial \tau^a} + \frac{\partial b}{\partial  \tau^{*a}} = \frac{\partial b}{\partial  e_b} \left\{ \frac{\partial e_b}{\partial \tau^a} + \frac{\partial  e_b}{\partial  \tau^{*a}} \right\} + \frac{\partial b}{\partial \tau^a} + \frac{\partial b}{\partial  \tau^{*a}}.$ $\frac{\partial b}{\partial  e_b}$ is positive by Result~\ref{res:bincC}.
-$\left\{ \frac{\partial e_b}{\partial \tau^a} + \frac{\partial  e_b}{\partial  \tau^{*a}} \right\}$ is negative by Result~\ref{res:lobby}.
-Taken together, the final two summands are negative by Lemma~\ref{res:bcomb}.
-Thus the entire expression is negative.
-$\hfill\blacksquare$
-
-\vskip.4in
-\noindent \textbf{\hypertarget{int_soln}{Conditions for Interior Solution to Executives' Problem}} \\
-The first order condition for maximizing joint surplus with respect to $\tau^a$ and $\tau^{*a}$ when the two are constrained to be equal is
-\begin{multline*}
-  \textstyle \left\{ 1 - o \cdot B(\bta) - o^* \cdot B^*(\bta) \right\} \left\{\frac{\partial \bm{W_E}(\bta)}{\partial \tau^a} + \frac{\partial \bm{W_E}(\bta)}{\partial \tau^{*a}} \right\} \\
-     \textstyle + \left\{ o \cdot \left[\frac{\partial B(\bta) }{\partial \tau^a} + \frac{\partial B(\bta) }{\partial \tau^{*a}} \right] + o^* \cdot \left[\frac{\partial B^*(\bta)}{\partial \tau^a} + \frac{\partial B^*(\bta)}{\partial \tau^{*a}} \right] \right\} \left[ \bm{W_E}(\btn)- \bm{W_E}(\bta) \right] = 0
-\end{multline*}
-Because there is no benefit to setting $\bta$ below the executives' preferred level, which I will denote $\bm{\tau^E}$, I will take the choice space to be $[\bte,\btn]$.
-Note that for $\ga_E = 1$, $\bte=0$.
-
-To demonstrate that the executives do not choose $\bta=\bte$, I must show that the left side of the above equation is positive at $\bta=\bte$.
-Assumption~\ref{as:ga_l_e} and Result~\ref{res:bcomB} combined with symmetry ensure that the first term of the second summand is negative.
-That executive welfare is maximized at $\bte$ ensures that the term multiplying it is also negative as well as that $\frac{\partial \bm{W_E}(\bte)}{\partial \tau^a} + \frac{\partial \bm{W_E}(\bte)}{\partial \tau^{*a}}$ is zero.
-Therefore the derivative of joint executive welfare is positive at $\bte$.
-$\hfill\blacksquare$
-
-\begin{comment}
-\vskip.4in
-\noindent \textbf{\hypertarget{pfs}{Connection to Grossman and Helpman's `Protection for Sale'}} \\
-To see the relationship between the two forms, write the PFS welfare function (replacing $C$ with $e$) as
-\[
-  e + aW = e + a \left[ \mathit{CS}_X(\tau) + \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau) \right]
-\]
-The relationship between $e$ and the weight the legislature places on profits is endogenous; because the PFS government welfare function has such an elegant and completely specified form, it is possible to solve for equilibrium behavior to retrieve this relationship directly.
-
-It is easy to describe the equilibrium behavior and thus how lobbying effort will be related to the weight on profits in equilibrium in the PFS model when there is one lobby who makes a take-it-or-leave-it offer.
-Take the case of no uncertainty and assume that the legislature chooses $\tau=0$ in the absence of lobbying and that $\ga(0)=1$.
-For any $\tau$ that the lobby desires, it must pay according to the  indifference condition $e(\tau) = a \left[ W(0) - W(\tau) \right]$.
-That is, the lobby must pay for the $a$-weighted welfare loss caused by the tariff it requests.
-
-In the model of this paper, this indifference condition, rearranged to solve for $\ga(e)$, is
-		    \[
-		      \ga(e) = \frac{\mathit{CS}_X(0) + \pi_X(0) + \mathit{CS}_Y(0) + \pi_Y(0) + \mathit{TR}(0) - \mathit{CS}_X(\tau) - \mathit{CS}_Y(\tau^*) - \pi_Y(\tau^*) - \mathit{TR}(\tau)}{\pi_X(\tau)}
-		    \] 
-\end{comment}
-
-%\section{Acknowledgements}
-%The author thanks the following people for their insightful comments: Joel Watson, Jim Rauch, Marc Muendler, Lawrence Broz, Peter Cowhey, Kyle Bagwell, Andrei Levchenko, Bob Staiger, two anonymous referees, and seminar participants at UC San Diego, Syracuse, Georgetown, Florida International, Brandeis, BGSU, U Mass Amherst, Swarthmore, SUNY Oswego, Kenyon College, and PEIO 2013.
-All remaining errors are my own.
 
 \section{References}
-\singlespacing
-
-\begin{list}{}{\setlength{\leftmargin}{0.0in}\setlength{\rightmargin}{0.0in}\setlength{\itemindent}{0.0in}\setlength{\itemsep}{0.1in}}
-
-\item Aidt, T., Gassebner, M., 2010. Do Autocratic States Trade Less? The World Bank Economic Review 24, 38-76.
-
-%\item Amador, M., and Bagwell, K., 2013. The Theory of Optimal Delegation with an Application to Tariff Caps. Econometrica 81, 1541-1599.
-
-\item Ansolabehere, S., de Figueiredo, J., Snyder Jr., J., 2003. Why Is There so Little Money in U.S. Politics? Journal of Economic Perspectives 17, 105-130.
-
-\item Bagwell, K., Staiger, R., 2005.
-Enforcement, Private Political Pressure, and the General Agreement on Tariffs and Trade/World Trade Organization Escape Clause.
-Journal of Legal Studies 34, 471-513.
-
-\item Baldwin, R.E., 1987. Politically realistic objective functions and trade policy: PROFs and tariffs. Economic Letters 24, 287-90.
-
-\item Beshkar, M., 2010. Trade skirmishes safeguards: A theory of the WTO dispute settlement process. Journal of International Economics 82, 35-48.
-
-\item Beshkar, M. and Bond, E., 2012. Cap and Escape in Trade Agreements. Available at \url{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2145679}.
-
-\item Bombardini, M., 2008. Firm Heterogeneity and Lobby Participation. Journal of International Economics 75, 329-348.
-
-\item Bombardini, M., Trebbi, F., 2012. Competition and Political Organization: Together or Alone in Lobbying for Trade Policy? Journal of International Economics 87, 18-26.
-
-\item Buzard, K., 2015. Self-enforcing Trade Agreements, Dispute Settlement and Separation of Powers. Available at: \url{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2333728}.
-
-\item Buzard, K., 2016. Endogenous Politics and the Design of Trade Agreements. Available at: \url{https://kbuzard.expressions.syr.edu/wp-content/uploads/Endogenous-Politics.pdf}.
-
-\item Coates, D., Ludema, R., 2001. A Theory of Trade Policy Leadership. Journal of Development Economics 65, 1-29.
-
-%\item Dai, X., 2006. Dyadic Myth and Monadic Advantage: Conceptualizing the Effect of Democratic Constraints on Trade. Journal of Theoretical Politics 18, 267-297.
-
-\item Destler, I.M., 2005. American Trade Politics. Institute for International Economics, Washington, DC.
-
-\item Dixit, A., G. Grossman, Helpman, E., 1997. Common Agency and Coordination: General Theory and Application to Government Policy Making. Journal of Political Economy 105, 752-769.
-
-\item Ethier, W., 2002. Unilateralism in a Multilateral World. The Economic Journal 112, 266-292.
-
-%\item Ethier, W., 2012. The Political-Support Approach to Protection. Global Journal of Economics 1, 1-14.
-
-\item Feenstra, R., 1992. How Costly is Protectionism? Journal of Economic Perspectives 6, 159-178.
-
-\item Feenstra, R., Lewis, T., 1991. Negotiated Trade Restrictions with Private Political Pressure. Quarterly Journal of Economics 106, 1287-1307.
-
-\item Findlay, R., Wellisz, S., 1982.
-Endogenous Tariffs and the Political Economy of Trade Restrictions and Welfare.
-In Jagdish Bhagwati (ed.) Import Competition and Response, Chicago, IL: University of Chicago, 1982
-
-\item Frye, T., Mansfield, E., 2003. Fragmenting Protection: The Political Economy of Trade Policy in the Post-Communist World. British Journal of Political Science 33, 633-657.
-
-\item Gawande, K., Bandyopadhyay, U., 2000. Is Protection for Sale? Evidence on the Grossman-Helpman Theory of Endogenous Protection. The Review of Economics and Statistics 82, 139-152.
-
-\item Gawande, K., Hoekman, B., 2006. Lobbying and Agricultural Trade Policy in the United States. International Organization 60, 527-561.
-
-\item Gawande, K., Magee, C., 2012. Free Riding on Protection for Sale. International Studies Quarterly 56, 735-747.
-
-\item Gawande, K., Krishna, P., Robbins, M., 2006. Foreign Lobbies and U.S. Trade Policy. Review of Economics and Statistics 88, 563-571.
-
-\item Gawande, K., Krishna, P., Olarreaga, M., 2009. What Governments Maximize and Why: The View from Trade. International Organization 63, 491-532.
-
-\item Gawande, K., Krishna, P., Olarreaga, M., 2012. Lobbying Competition Over Trade Policy. International Economic Review 53, 115-132.
-
-\item Goldberg, P., Maggi, G., 1999. Protection for Sale: An Empirical Investigation. American Economic Review 89, 1135-1155.
-
-\item Grossman, G., Helpman, E., 1994. Protection for Sale. The American Economic Review 84, 833-850.
-
-\item Grossman, G., Helpman, E., 1995a. The Politics of Free-Trade Agreements. The American Economic Review 85, 667-690.
-
-\item Grossman, G., Helpman, E., 1995b. Trade Wars and Trade Talks. The Journal of Political Economy 103, 675-708.
-
-\item Grossman, G., Helpman, E., 2005. A Protectionist Bias in Majoritarian Politics. The Quarterly Journal of Economics 120, 1239-1282.
-
-\item Henisz, W., Mansfield, E., 2006. Votes and Vetoes: The Political Determinants of Commercial Openness. International Studies Quarterly 50, 189-211.
-
-\item Horn, H., Maggi, G., Staiger, R. W., 2010. Trade Agreements as Endogenously Incomplete Contracts. American Economic Review 100, 394-419.
-
-\item Imai, S., Katayama, H., Krishna, K., 2009. Is protection really for sale? A survey and directions for future research. International Review of Economics and Finance 18, 181-191.
-
-%\item Kibris, A., 2012. Uncertainty and Ratification Failure. Public Choice 150, 439-467.
-
-\item Klimenko, M., Ramey, G., Watson, J., 2008. Recurrent Trade Agreements and the Value of External Enforcement. Journal of International Economics 74, 475-499.
-
-%\item Kono, D., 2006. Optimal Obfuscation: Democracy and Trade Policy Transparency. American Political Science Review 100, 369-384.
-
-\item Laver, M., Shepsle, K., 1991. Divided Government: America is Not `Exceptional'. Governance: An International Journal of Policy and Administration 4, 250-269.
-
-\item Le Breton, M., Salanie, F., 2003. Lobbying under Political Uncertainty. Journal of Public Economics 87, 2589-2610.
-
-\item Le Breton, M., Zaporozhets, V., 2007. Legislative Lobbying under Political Uncertainty. Available at SSRN: \url{http://ssrn.com/abstract=1024686}.
-
-\item Lohmann, S., O'Halloran, S., 1994. Divided Government and US Trade Policy. International Organization 48, 595-632.
-
-\item Maggi, G., Rodr\'{i}guez-Clare, A., 2007. A Political-Economy Theory of Trade Agreements. The American Economic Review 97, 1374-1406.
-
-\item Maggi, G., Staiger, R., 2011. The Role of Dispute Settlement Procedures in International Trade Agreements. Quarterly Journal of Economics 126, 475-515.
-
-\item Mansfield, E., Milner, H., Rosendorff, B.P., 2000. Free to Trade: Democracies, Autocracies, and International Trade. The American Political Science Review 94, 305-321.
-
-%\item Milner, H., Kubota, K., 2005. Why the Move to Free Trade? Democracy and Trade Policy in the Developing Countries. International Organization 59, 107-143.
-
-\item Milner, H., Rosendorff, B.P., 1997.
-Democratic Politics and International trade Negotiations: Elections and Divided Government as Constraints on Trade Liberalization.
-Journal of Conflict Resolution 41, 117-147.
-
-\item Milner, H., Rosendorff, B.P., 2001. The Optimal Design of International Trade Institutions: Uncertainty and Escape. International Organization 55, 829-857.
-
-\item Mitra, D., Thomakos, D., Ulubasoglu, M., 2002. `Protection for Sale' in a Developing Country: Democracy vs. Dictatorship. Review of Economics and Statistics 84, 497-508.
-
-\item Mitra, D., Thomakos, D., Ulubasoglu, M., 2006. Can We Obtain Realistic Parameter Estimates for the Protection for Sale Model? Canadian Journal of Economics 39, 187-210.
-
-%\item Morrow, J., Siverson, R., Tabares, T., 1999. Correction to: ``The Political Determinants of International Trade,' American Political Science Review 94, 931-933.
-
-\item McCalman, P., 2004. Protection for Sale and Trade Liberalization: an Empirical Investigation. Review of International Economics 12, 81-94.
-
-%\item Paltseva, E., 2011. Protection for Sale to Oligopolists. Available at: \url{http://web.econ.ku.dk/okoep/Paltseva_P4S2O_June2011_1.pdf}.
-
-\item Roemer, J., 1997. Political-economic Equilibrium when Parties Represent Constituents: The Unidimensional Case. Social Choice and Welfare 14, 479-502.
-
-\item Song, Y., 2008. Protection for Sale: Agenda-Setting and Ratification in the Presence of Lobbying. Korea Institute for International Trade Policy Working Paper Series. Vol. 2008-22, August 2008.
-
-%\item Tarar, A., 2001. International Bargaining with Two-Sided Domestic Constraints. Journal of Conflict Resolution 45, 320-340.
-
-%\item Ward, M., Hoff, P., 2007. Persistent Patterns of International Commerce. Journal of Peace Research 44, 157-175.
-
-\end{list}
-%\end{comment}
 

### 2017-09-19 draft.tex
revise gov't structure in sec:basic (except extensive form)

@@
 
-\textbf{REVISE GOVERNMENT STRUCTURE}
+In the home country, there is a government agency that has the power to renew (or not) anti-dumping duties.
+To focus attention on protectionist political forces, highlight the model's central mechanisms and minimize the number of actors that must be modeled, we assume that only the import-competing industry is politically-organized and that it is represented by a single lobbying organization.\footnote{The model extends easily to the case of multiple lobbies.\label{fn:lobby}} Policy-makers and lobbyists in the foreign country are assumed to be passive.
 
-In each country, there is an executive who concludes trade agreements and a legislature that has final say on trade policy.
-To focus attention on protectionist political forces, highlight the model's central mechanisms and minimize the number of actors that must be modeled, I assume that only the import-competing industry in each country is politically-organized and that it is represented by a single lobbying organization.\footnote{The model extends easily to the case of multiple lobbies.
-To illustrate, adding an export lobby with no uncertainty predicts import lobbies remain disengaged while the executives can reduce tariffs by recruiting support from exporters.
-The Panama Trade Promotion Act follows this pattern, with virtually no lobbying against, significant lobbying in favor, and numerous industries receiving import protection.\label{fn:lobby}}
+\textbf{REVISE EXTENSIVE FORM}
 
@@
 
-Figure~\ref{fig:ext} illustrates the timing of the game from the perspective of the home country.\footnote{This extensive form is for the case where the foreign legislature does not break the trade agreement.} First, the executives set trade policy cooperatively within the context of an international agreement by choosing the trade agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$.\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} Then the lobbies attempt to persuade the legislators in their respective countries to break the trade agreement by choice of lobbying effort $e_b$.
-Next, nature determines with probabilities $o$ and $o^*$ whether each legislature will have the opportunity to take a vote to break the agreement.
-I assume that these probabilities are less than one-half and mutually exclusive.\footnote{While this assumption is made for purposes of exposition and tractability, one can think of $o$ and $o^*$ as being determined by events beyond the executives' or legislatures' control that determine whether or not the legislatures will be willing to consider the lobby's request; for example, they would be affected by the occurrence of an economic crisis that diverts the legislature's attention from less-pressing matters.} This allows me to focus on the key interaction between the domestic actors and abstract from the strategic interaction between the lobbies.\footnote{If the break decisions in the two countries are sequential with the executives behind a veil of ignorance about which legislature moves first, the end results are the same but additional intermediate results are needed.
-The optimization problem of the executives becomes more complex as they decide how best to exploit the second lobby's incentive to free ride on the effort of the first-mover lobby.}
+Figure~\ref{fig:ext} illustrates the timing of the game.
+Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of anti-dumping duties $\bta = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the anti-dumping duties by choice of lobbying effort $e$.
 
-After this, uncertainty about the the median legislator's identity is resolved.
-All players simultaneously observe the realization of the random variable $\ta_b$ that represents this uncertainty.
-The ``break stage'' concludes with the legislature making a choice to abide by the agreement or to break the agreement.
-In the event that the legislature breaks the agreement, there is a final stage of lobbying, resolution of the uncertainty surrounding this decision, and voting to set the trade-war tariffs $\btn$.\footnote{Alternatively, one can model the non-cooperative tariff as being determined by the break decision lobbying, through a separate process in the case of administered protection, or the ex-ante status quo.
-This does not change the fundamental dynamics of the model.} Finally, producers and consumers make their decisions.
+After this, uncertainty about the government agency's preferences is resolved.
+All players simultaneously observe the realization of the random variable $\ta$ that represents this uncertainty.
+The political stage concludes with the agency making a choice to renew the anti-dumping duties or let them expire.
+In the event that the anti-dumping duties expire, the home country's trade policy reverts to the trade agreement tariff $\tau^a$.
+Finally, producers and consumers make their decisions.
 

### 2017-09-19 draft.tex
revise start of sec:pref; change ML to G throughout

@@
 \label{sec:pref}
-With the structure of politics and the economy symmetric and the latter fully separable, I focus on the home country's and the $X$-sector.
-The details are analogous for $Y$ and foreign.
-The home legislature's welfare function is
+With foreign not active in setting policy and the structure the economy symmetric and fully separable, I focus on the home country and the $X$-sector, which is the only politically active sector.
+The government agency's welfare is given by
 \begin{equation}
-  W_{\mathit{ML}} = \mathit{CS}_X(\tau) + \ga(e,\ve) \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
+  W_{\mathit{G}} = \mathit{CS}_X(\tau) + \ga(e,\ve) \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
   \label{eq:ml}
@@
 \begin{equation}
-  W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right)
+  W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right)
   \label{eq:lwcg}
@@
 \begin{multline}
-  b(e_b,\bta) = \expect_{\ga|e_b} \bm{1} [ W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right) ] \\ = \Pr [ W_{ML}(\btn,\ga(e_b,\ve_b)) > W_{ML}\left(\bta,\ga(e_b,\ve_b)\right) | e_b]
+  b(e_b,\bta) = \expect_{\ga|e_b} \bm{1} [ W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right) ] \\ = \Pr [ W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right) | e_b]
   \label{eq:b}

### 2017-09-19 draft.tex
remove exec; start changing legislature to gov't agency

@@
 \end{equation}
-where $\mathit{CS}$ is consumer surplus, $\pi$ are profits, $\ga(e,\ta)$ is the weight placed on profits in the import-competing industry, and $\mathit{TR}$ is tariff revenue.\footnote{Labor income $l$ could also be included in both median legislator and executive welfare.
-I omit it because its inclusion alters none of the results and only serves to complicate the exposition.} I model the decisions of the legislature as being taken by a median legislator with the weight the median legislator places on import-competing industry profits affected by the level of lobbying effort $e$ and a random variable $\ta$.
+where $\mathit{CS}$ is consumer surplus, $\pi$ are profits, $\ga(e,\ta)$ is the weight placed on profits in the import-competing industry, and $\mathit{TR}$ is tariff revenue.\footnote{Labor income $l$ could also be included in government welfare.
+I omit it because its inclusion alters none of the results and only serves to complicate the exposition.} I model the decisions of the government agency as being taken by a median actor with the weight the median actor places on import-competing industry profits affected by the level of lobbying effort $e$ and a random variable $\ta$.
 I make the following assumptions on $\ga(e,\ta)$:
@@
 
-Assumption~\ref{as:ga_c} formalizes the intuition that the legislature favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity.
+Assumption~\ref{as:ga_c} formalizes the intuition that the government agency favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity.
 It rules out higher effort making lower weights more likely and that the structure of uncertainty changes with increasing effort so that higher weights become more likely at an accelerating pace.
@@
 
-Given its expectations and the legislature's preferences, the home lobby chooses its lobbying effort ($e_b$ to influence the break decision and $e_n$ to influence the trade war tariff) to maximize the welfare function:
+Given its expectations and the government agency's preferences, the home lobby chooses its lobbying effort ($e_b$ to influence the break decision and $e_n$ to influence the trade war tariff) to maximize the welfare function:
 \begin{equation}
@@
 where $\pi(\cdot)$ is the current-period profit and the subscript $X$ has been dropped for notational convenience.
-
-\textbf{NOT SURE I KNOW EXACTLY WHAT THE GOVERNMENT'S OBJECTIVE IS, DIVIDED GOV'T EVEN?}
-
-In the first stage, the executives choose the trade agreement tariffs.
-With executive welfare in a trade war the disagreement point, the division of surplus according to the Nash bargaining solution is
-\[
-  V_E(\bta) + t = W_E(\btn) + \frac{1}{2} \left( MV(\bta) - W_E(\btn) - W_E^*(\btn) \right)
-\]
-\[
-  V_E^*(\bta) - t = W_E^*(\btn) + \frac{1}{2} \left( MV(\bta) - W_E(\btn) - W_E^*(\btn) \right)
-\]
-where expectation operators are dropped for convenience, $MV(\bta)$ is the maximized joint value and $t$ is an intergovernmental transfer.\footnote{While direct monetary transfers have to date rarely been used in practice, it seems appropriate to interpret linked concessions on non-trade issues as indirect transfers (Klimenko, Ramey and Watson (2008); Maggi and Staiger (2011)).
-Here, transfers do not occur as long as the full set of symmetry assumptions are maintained but are an important consideration in asymmetric environments.} The solution to this system of equations determines the trade agreement tariffs.
-
-I simplify the problem by assuming that political constraints prevent the executives from choosing asymmetric tariffs. This implies that the executives simply maximize their expected joint payoffs:
-\begin{multline}
-  \expect \left[W_E(\bta) \right] + \expect \left[ W_E^{*}(\bta) \right] = \Pr\left[ \text{TradeWar} \right] \left[W_E(\bm{\tau}^{\mathit{n}}) + W_E^*(\bm{\tau}^{\mathit{n}}) \right] + \\ \Pr\left[ \text{TradeAgreement} \right] \left[W_E(\bta) + W_E^*(\bta) \right]
-  \label{eq:jv}
-\end{multline}
-The home executive's welfare is specified as
-\[
-  W_E(\bm{\tau}) = \mathit{CS}_X(\tau) + \ga_E \cdot \pi_X(\tau) + \mathit{CS}_Y(\tau^*) + \pi_Y(\tau^*) + \mathit{TR}(\tau)
-\]
-This is identical to the legislature's welfare function except the weight the executive places on the profits of the import industry is not a function of lobbying effort.
-This setup does not require that the executives are not lobbied; the assumption is innocuous as long as the executives' preferences are not directly altered in a significant way by lobbying over trade.
-I make one more related assumption on $\ga(e,\ta)$:
-
-\begin{assumption}
-  $\ga(e,\ta) \geq \ga_E \geq 1 \ \forall e,\ta$.
-  \label{as:ga_l_e}
-\end{assumption}
-
-That is, even for the least favorable outcome of the lobbying process, the legislature is more protectionist than the executive regardless of the lobby's effort choice.
-This is not essential but it simplifies the analysis, ensuring that trade agreement tariffs are smaller than trade war tariffs.
-It matches the empirical finding that politicians with larger constituencies are less sensitive to special interests and represents well the post-war U.S.
-where Congress has consistently been more protectionist than the President.\footnote{cfr.
-Lohmann and O'Halloran (1994) for the general argument, Destler (2005) on U.S.
-trade politics, and Grossman and Helpman (2005) for a formal model.}
 
@@
 \end{equation}
-Assumption~\ref{as:ga_l_e} and Result~\ref{res:bincC} ensure the second order condition. To guarantee an interior solution, we need
+Assumption [old assumption3] and Result~\ref{res:bincC} ensure the second order condition. To guarantee an interior solution, we need
   \begin{equation}
@@
 
-To solve for the trade agreement tariffs, one must maximize the following modified version of Equation \ref{eq:jv}:
+To solve for the trade agreement tariffs, one must maximize the following modified version of Equation ``Joint Value'' (removed):
 \begin{equation}

### 2017-09-25 draft.tex
revise rest of sec:pref

@@
 \newcommand{\bta}{\bm{\tau^a}}
+\newcommand{\btad}{\bm{\tau^{ad}}}
 \newcommand{\bte}{\bm{\tau^E}}
@@
 Figure~\ref{fig:ext} illustrates the timing of the game.
-Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of anti-dumping duties $\bta = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the anti-dumping duties by choice of lobbying effort $e$.
+Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of anti-dumping duties $\btad = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the anti-dumping duties by choice of lobbying effort $e$.
 
@@
 
-Assumption~\ref{as:ga_c} formalizes the intuition that the government agency favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity.
+Assumption~\ref{as:ga_c} means that the government agency favors the import-competing industry more the higher is its lobbying effort, but that there are diminishing returns to lobbying activity.
 It rules out higher effort making lower weights more likely and that the structure of uncertainty changes with increasing effort so that higher weights become more likely at an accelerating pace.
@@
 
-\textbf{LOBBY'S OBJECTIVE IS DIFFERENT HERE}
-
-Given its expectations and the government agency's preferences, the home lobby chooses its lobbying effort ($e_b$ to influence the break decision and $e_n$ to influence the trade war tariff) to maximize the welfare function:
+Given its expectations and the government agency's preferences, the home lobby chooses its lobbying effort $e$ to maximize the welfare function:
 \begin{equation}
-  \expect \left[U_L \right] = \Pr\left[ \text{TradeWar} \right] \left[ \pi(\tau^{\mathit{n}}) - e_n \right] + \Pr\left[ \text{TradeAgreement} \right] \pi(\tau^a) - e_b
+  \expect \left[U_L \right] = \Pr\left[ \text{AD Renewal} \right]  \pi_X(\tau^{\mathit{ad}}) +\left\{1-\Pr\left[ \text{AD Renewal}\right]\right\} \ \pi_X(\tau^a) - e
   \label{eq:lv}
 \end{equation}
-where $\pi(\cdot)$ is the current-period profit and the subscript $X$ has been dropped for notational convenience.
+where $\pi(\cdot)$ is the current-period profit.
 
@@
 
-Finally, I assume that an external authority can ensure enforcement of the agreement.\footnote{Buzard (2015) considers a similar model in a repeated-game context and can therefore remove this restriction.}
+Finally, I assume that an external authority can ensure enforcement of the agreement.
 

### 2017-09-25 draft.tex
remove trade war tariffs section

@@
 Profits in a sector are increasing in the price of its good and also in the domestic tariff.
-This fact, combined with the assumptions on specific factor ownership, motivates political activity by import-competing lobbies.
+This fact, combined with the assumptions on specific factor ownership, motivates political activity by the import-competing lobby.
 
@@
 \label{sec:main}
-To understand how the executives optimally structure trade agreements, I first examine the lobbies' incentives and the legislatures' decisions regarding breach of the agreement, including how trade-war tariffs are set.
-
-\subsection{Trade-War Tariffs}
-\label{sec:twt}
-In the event that the trade agreement is broken, the legislature sets its tariff $\tau$ unilaterally by maximizing Equation~\ref{eq:ml} given $\tau^*$.
-Because there are no interactions between the home and foreign tariffs, the home country's tariff maximizes weighted home-country welfare in the $X$-sector only.
-Unilateral optimization leads to what I refer to as the (expected) Nash or trade-war tariffs $\tau^n$ as the solution to the following first order condition:\footnote{Note that the random variable in the median legislator's weight on import profits is written as $\ta_n$ at this stage to distinguish it from $\ta_b$ at the break stage: as two separate votes are taken, there are two distinct realizations of uncertainty.}
-\begin{equation}
-		\frac{\partial \mathit{CS}_X(\tau)}{\partial \tau^n} + \ga(e_n,\ve_n) \cdot \frac{\partial \pi_X(\tau)}{\partial \tau^n} +  \frac{\partial \mathit{TR}(\tau)}{\partial \tau^n} = 0 .
-		\label{eq:legfoc}
-\end{equation}
-
-In the event of a trade war, the lobby chooses its effort $e_n$ given this tariff-setting behavior by maximizing its profits net of effort: $\pi\left(\tau^n\left(\ga\left(e_n,\ve_n\right)\right)\right) - e_n$.
-This implies a first order condition for the lobby of
-\begin{equation}
-	\frac{\partial \pi(\tau^n)}{\partial \tau^n}\frac{\partial \tau^n}{\partial \ga} \frac{\partial \ga}{\partial e_n} = 1
-  \label{eq:lobtw}
-\end{equation}
-That is, the lobby equates the expected marginal increase in profits with its marginal payment.
-
-Because profits are increasing in the tariff, trade war tariffs are increasing in the weight attached to the profits of the import-competing industry.
-This can be seen by rearranging Equation~\ref{eq:lobtw} as
-\begin{equation}
-  \frac{\partial \tau^n}{\partial \ga} = \frac{1}{\frac{\partial \pi(\tau^n)}{\partial \tau^n} \frac{\partial \ga}{\partial e_n}}
-	\label{eq:lem1}
-\end{equation}
-since $\frac{\partial \ga}{\partial e_n}$ is positive by Assumption~\ref{as:ga_c} and profits are increasing in the tariff.
-This expression demonstrates that the second order condition for the legislature's problem is always satisfied.
-By the implicit function theorem, $\frac{\partial \tau^n}{\partial \ga} = -\frac{\frac{\partial \text{Equation}~\ref{eq:legfoc}}{\partial \ga}}{\frac{\partial \text{Equation}~\ref{eq:legfoc}}{\partial \tau^n}} = -\frac{\frac{\partial \pi(\tau^n)}{\partial \tau^n}}{SOC}$ where ``SOC'' is the second derivative of the legislature's objective function that should be everywhere negative.
-Setting this expression equal to Equation~\ref{eq:lem1}, the second order condition must be satisfied since $\frac{\partial \ga}{\partial e_n}$ is positive by Assumption~\ref{as:ga_c}.
+To understand the government's decision about whether to renew a temporary trade barrier, I first examine the lobby's incentives.
 

### 2017-09-25 draft.tex
remove _b subscripts; turn result 1 into lemma 1

@@
 
-In the home country, there is a government agency that has the power to renew (or not) anti-dumping duties.
+In the home country, there is a government agency that has the power to renew (or not) antidumping duties.
 To focus attention on protectionist political forces, highlight the model's central mechanisms and minimize the number of actors that must be modeled, we assume that only the import-competing industry is politically-organized and that it is represented by a single lobbying organization.\footnote{The model extends easily to the case of multiple lobbies.\label{fn:lobby}} Policy-makers and lobbyists in the foreign country are assumed to be passive.
@@
 Figure~\ref{fig:ext} illustrates the timing of the game.
-Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of anti-dumping duties $\btad = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the anti-dumping duties by choice of lobbying effort $e$.
+Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of antidumping duties $\btad = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the antidumping duties by choice of lobbying effort $e$.
 
@@
 All players simultaneously observe the realization of the random variable $\ta$ that represents this uncertainty.
-The political stage concludes with the agency making a choice to renew the anti-dumping duties or let them expire.
-In the event that the anti-dumping duties expire, the home country's trade policy reverts to the trade agreement tariff $\tau^a$.
+The political stage concludes with the agency making a choice to renew the antidumping duties or let them expire.
+In the event that the antidumping duties expire, the home country's trade policy reverts to the trade agreement tariff $\tau^a$.
 Finally, producers and consumers make their decisions.
@@
 \label{sec:main}
+
+\textbf{ADD IN NARRATIVE DIRECTION}
+
 To understand the government's decision about whether to renew a temporary trade barrier, I first examine the lobby's incentives.
@@
 \bigskip
-\subsection{To Break or Not to Break?}
+\subsection{The Renewal Decision}
 \label{sec:break}
-We can now proceed by backward induction to analyze the legislature's incentives to uphold or break the trade agreement.
-The legislature will break the agreement and set the tariff at $\tau^n$ if the median legislator's utility from the Nash tariffs is higher than his utility from the trade agreement tariffs, i.e.
-if
+
+The government agency will renew the antidumping duty if the median actor's utility from the antidumping duty is higher than his utility from the trade agreement tariffs, i.e. if
 \begin{equation}
-  W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right)
+  W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right)
   \label{eq:lwcg}
@@
 
-The outcome of the vote on whether or not to break the trade agreement is not known to \textit{any} player until the uncertainty over the identity of the median legislator is resolved at the moment the vote takes place.
-I represent the probability that the home legislature breaks the trade agreement and sets the tariff at $\tau^n$ as:\footnote{I suppress the Nash tariffs in the expression of the break probability since they do not vary from the point of view of earlier stages.}
+The outcome of the decision on whether or not to renew the antidumping duties is not known to \textit{any} player until the uncertainty over the identity of the median governmental actor is resolved at the moment the decision is made.
+I represent the probability that antidumping duties are renewed as:
 \begin{multline}
-  b(e_b,\bta) = \expect_{\ga|e_b} \bm{1} [ W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right) ] \\ = \Pr [ W_G(\btn,\ga(e_b,\ve_b)) > W_G\left(\bta,\ga(e_b,\ve_b)\right) | e_b]
+  b(e,\bta) = \expect_{\ga|e} \bm{1} [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
   \label{eq:b}
@@
 
-We are now in a position to examine the legislature's decision more closely. Of central concern is how the probability that the legislature will break the trade agreement varies with lobbying effort:
+We are now in a position to examine the governments's decision more closely.
+Of central concern is how the probability that the government agency will renew the antidumping duties varies with lobbying effort:
 
-\begin{result}
-  The probability that the legislature breaks a trade agreement is increasing and concave in $e_b$.
+\begin{lemma}
+  The probability that the government agency renews the antidumping duties is increasing and concave in lobbying effort $e$, $\left(\text{i.e.
+} \frac{\partial b}{\partial e} \geq 0, \ \frac{\partial^2 b}{\partial e^2} \leq 0  \right)$.
   \label{res:bincC}
-\end{result}
+\end{lemma}
 
@@
 The relationship between $\tau^a$ and break probability is more complex.
-For any effort level $e_b$, when the trade agreement tariff is very low, only a small set of realizations of $\ta_b$ associated with the lowest values of $\ga(e_b,\ta_b)$ will lead to approval of the trade agreement, implying a high break probability.
-As the trade agreement tariff rises, larger values of $\ga(e_b,\ta_b)$ are consistent with approving the trade agreement, so the set of $\ta_b$'s that lead to trade agreement approval is larger.
+For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to approval of the trade agreement, implying a high break probability.
+As the trade agreement tariff rises, larger values of $\ga(e,\ta)$ are consistent with approving the trade agreement, so the set of $\ta$'s that lead to trade agreement approval is larger.
 That is, the break probability decreases as $\tau^a$ increases.
@@
 \[
-  \max_{e_b} b(e_b,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e_b,\bta)] \pi(\tau^a) - e_b
+  \max_{e} b(e,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e,\bta)] \pi(\tau^a) - e
 \]
@@
 \begin{equation}
-	\frac{\partial b(e_b,\bta)}{\partial e_b} \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
+	\frac{\partial b(e,\bta)}{\partial e} \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
 	\label{eq:lobbyfoc}
@@
   \begin{equation}
-	  \frac{\partial b(0,\bta)}{\partial e_b} \left[ \pi(\tau^n) -e_n- \pi(\tau^a) \right] > 1.
+	  \frac{\partial b(0,\bta)}{\partial e} \left[ \pi(\tau^n) -e_n- \pi(\tau^a) \right] > 1.
 		\label{ine:lobint}	

### 2017-09-27 draft.tex
fix typos scattered throughout notes, draft, outline

@@
 \begin{multline}
-  b(e,\bta) = \expect_{\ga|e} \bm{1} [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
+  b(e,\bta,\btad) = \expect_{\ga|e} \bm{1} [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
   \label{eq:b}
@@
 \begin{lemma}
-  The probability that the government agency renews the antidumping duties is increasing and concave in lobbying effort $e$, $\left(\text{i.e.
+  The probability that the government agency renews the antidumping duties is increasing and concave in lobbying effort $\left(\text{i.e.
 } \frac{\partial b}{\partial e} \geq 0, \ \frac{\partial^2 b}{\partial e^2} \leq 0  \right)$.

### 2017-09-27 presentation.tex
fix typos scattered throughout notes, draft, outline

@@
-\documentclass{beamer} 
-%\documentclass[handout]{beamer} 
+%\documentclass{beamer} 
+\documentclass[handout]{beamer} 
 \usetheme{Ilmenau}
@@
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 2}
-  The total probability that $G$ renews AD duties is unaffected by foreign's trade agreement tariff $\tau^a$.
+  The total probability that $G$ renews AD duties is unaffected by foreign's trade agreement tariff $\tau^{*a}$.
 \end{beamerboxesrounded}
@@
 \pause
+\textit{NOTE: this is not quite right, but some version of it will be} \\
 Assume $\pi(\cdot)$ shifts up uniformly for all $\tau$.
@@
 
-\begin{comment}
-\begin{frame}{Conclusion}
+\begin{frame}{Feedback, Comments from InsTED presentation}
 \begin{itemize}[<+->]
-	\item S
-	\item E
-	\item F
+	\item Could leverage 5-year renewal cycle vs. 4-year re-election cycle (Sarah Danzman, Indiana U)
+	\item Look for Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)
+	\item Need to have first stage (Jee-Hyeong, Gary Lyn)
+		\begin{itemize}
+			\item Look at Park and Blonigen (Jee-Hyeong)
+			\item Cost differential for firms to get initial duty vs. renewal?
+			\item Some firms choose not to pursue renewal when DOC contacts them 30-days before (Sasha)
+		\end{itemize}
+	\item Lobbying effort may be endogenous: if prob. of success is lower, maybe it's not worth providing effort (Mostafa)
+	\item Uncertainty could be, in part, about how mobile labor is (Kishore)
 \end{itemize}
@@
 \end{frame}
-\end{comment}
 

### 2017-09-28 draft.tex
broad reorganization of sec:main

@@
 
-\bigskip
-\subsection{The Renewal Decision}
-\label{sec:break}
+\vskip1in
 
@@
 
-Turning to the effects of the trade-agreement tariffs on the probability that the agreement will be abrogated, it is straightforward that the legislature always prefers lower levels of the foreign tariff:
-\begin{lemma}
-  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly increasing in $\tau^{*a}$.
-  \label{lem:leg_astar}
-\end{lemma}
-
-The lower world price for home's export good has a larger negative effect on profits than the positive effect on consumer surplus.
-The net effect of an increase in foreign trade-agreement tariffs on home legislative welfare is negative, leading to an increased probability that the trade agreement will be broken.
-
-The relationship between $\tau^a$ and break probability is more complex.
-For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to approval of the trade agreement, implying a high break probability.
-As the trade agreement tariff rises, larger values of $\ga(e,\ta)$ are consistent with approving the trade agreement, so the set of $\ta$'s that lead to trade agreement approval is larger.
-That is, the break probability decreases as $\tau^a$ increases.
-
-\begin{lemma}
-  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly decreasing in $\tau^a$.
-  \label{res:leg_a}
-\end{lemma}
-
-Since I focus on symmetric equilibria, any increase in $\tau^a$ is accompanied by an equal increase in $\tau^{*a}$.
-Combining the impact of the home and foreign tariff when the two are constrained to be equal:
-\begin{lemma}
-	Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly decreasing in $\bta$ (i.e.
-$\frac{\partial b(e,\bta)}{\partial  \tau^a} + \frac{\partial b(e,\bta)}{\partial  \tau^{*a}} \leq 0$).
-	\label{res:bcomb}
-\end{lemma}
-
-\noindent The legislature's bias toward the import-competing industry overweights the negative impact of the home tariff on the break probability and ensures this result.
-
-\subsubsection{Lobby}
-\label{sec:lob_un}
 The lobby chooses its level of effort as a function of $\bta$, given the implications of that choice on the legislature's probability of breaking the agreement.
@@
 
-\subsection{The Trade Agreement}
-\label{sec:ta}
 I represent the probability that the trade agreement will be broken as $B(\bta)=b(e(\bta),\bta)$ where $e(\bta)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.
@@
 \noindent When the executives raise $\bta$ the legislature becomes less likely to abrogate the agreement, for three reasons.
-First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $B(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:bcomb}).
+First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $B(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:leg_a}).
 Thus, beyond promising a lower tariff from the trading partner, we can think of the trade agreement as a sort of political commitment device that can be used to reduce political pressure and therefore get the legislature to maintain a lower tariff than it otherwise would.
@@
 
+\bigskip
+\subsection{Foreign Trade Agreement Tariffs}
+\label{sec:foreign}
+
+Turning to the effects of the trade-agreement tariffs on the probability that the agreement will be abrogated, it is straightforward that the legislature always prefers lower levels of the foreign tariff:
+\begin{lemma}
+  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly increasing in $\tau^{*a}$.
+  \label{lem:leg_astar}
+\end{lemma}
+
+The lower world price for home's export good has a larger negative effect on profits than the positive effect on consumer surplus.
+The net effect of an increase in foreign trade-agreement tariffs on home legislative welfare is negative, leading to an increased probability that the trade agreement will be broken.
+
+\bigskip
+\subsection{Home Trade Agreement Tariffs}
+\label{sec:home}
+
+The relationship between $\tau^a$ and break probability is more complex.
+For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to approval of the trade agreement, implying a high break probability.
+As the trade agreement tariff rises, larger values of $\ga(e,\ta)$ are consistent with approving the trade agreement, so the set of $\ta$'s that lead to trade agreement approval is larger.
+That is, the break probability decreases as $\tau^a$ increases.
+
+\begin{lemma}
+  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly decreasing in $\tau^a$.
+  \label{res:leg_a}
+\end{lemma}
+
 \section{Conclusion}

### 2017-09-28 draft.tex
fix lobby's problem, get rid of b( ) and ^n _n

@@
 
-\textbf{ADD IN NARRATIVE DIRECTION}
-
-To understand the government's decision about whether to renew a temporary trade barrier, I first examine the lobby's incentives.
-
-\vskip1in
-
 The government agency will renew the antidumping duty if the median actor's utility from the antidumping duty is higher than his utility from the trade agreement tariffs, i.e. if
@@
 \begin{multline}
-  b(e,\bta,\btad) = \expect_{\ga|e} \bm{1} [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
+  r(e,\bta,\btad) = \expect_{\ga|e} \bm{1} [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
   \label{eq:b}
@@
 
-We are now in a position to examine the governments's decision more closely.
-Of central concern is how the probability that the government agency will renew the antidumping duties varies with lobbying effort:
-
-\begin{lemma}
-  The probability that the government agency renews the antidumping duties is increasing and concave in lobbying effort $\left(\text{i.e.
-} \frac{\partial b}{\partial e} \geq 0, \ \frac{\partial^2 b}{\partial e^2} \leq 0  \right)$.
-  \label{res:bincC}
-\end{lemma}
-
-\noindent All proofs are in the Appendix.
-Lobbying affects only the weight the legislature places on the profits of the import-competing industry.
-These profits are higher in a trade war than a trade agreement.
-Assumption~\ref{as:ga_c} implies that the legislature becomes more favorably inclined---albeit at a decreasing rate---toward the high trade-war tariff and associated profits as lobbying increases and thus more likely to break the trade agreement.
-
-The lobby chooses its level of effort as a function of $\bta$, given the implications of that choice on the legislature's probability of breaking the agreement.
+The lobby chooses its level of effort as a function of the trade agreement tariffs and the antidumping duties, given the implications of that choice on the government agency's probability of breaking the agreement.
 The lobby maximizes probability-weighted profits net of effort:
 \[
-  \max_{e} b(e,\bta) \left[\pi(\tau^n) - e_n \right] + [1 - b(e,\bta)] \pi(\tau^a) - e
+  \max_{e} r(e,\bta,\btad) \pi(\tau^{ad}) + [1 - r(e,\bta,\btad)] \pi(\tau^a) - e
 \]
@@
 \begin{equation}
-	\frac{\partial b(e,\bta)}{\partial e} \left[ \pi(\tau^n) -e_n - \pi(\tau^a) \right] = 1 
+	\frac{\partial r(e,\bta,\btad)}{\partial e} \left[ \pi(\tau^{ad})  - \pi(\tau^a) \right] = 1 
 	\label{eq:lobbyfoc}
@@
   \begin{equation}
-	  \frac{\partial b(0,\bta)}{\partial e} \left[ \pi(\tau^n) -e_n- \pi(\tau^a) \right] > 1.
+	  \frac{\partial r(0,\bta)}{\partial e} \left[ \pi(\tau^{ad}) - \pi(\tau^a) \right] > 1.
 		\label{ine:lobint}	
   \end{equation}
-If the executives were to set $\tau^a = \tau^n$, there would be no incentive for the lobby to make a positive contribution.
+If the executives were to set $\tau^{ad} = \tau^a$, there would be no incentive for the lobby to make a positive contribution.
 There are some other cases in which it is in the executives' interest to set trade agreement tariffs so as to disengage the lobby.
@@
 
-I represent the probability that the trade agreement will be broken as $B(\bta)=b(e(\bta),\bta)$ where $e(\bta)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.
+I represent the probability that the trade agreement will be broken as $R(\bta)=r(e(\bta),\bta)$ where $e(\bta)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.
 
@@
 \begin{result}
-	The total probability that the trade agreement will be broken is decreasing in $\bta$ (i.e. $\frac{\partial B(\bta)}{\partial  \tau^a} + \frac{\partial B(\bta)}{\partial  \tau^{*a}} \leq 0$).
+	The total probability that the trade agreement will be broken is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} + \frac{\partial R(\bta)}{\partial  \tau^{*a}} \leq 0$).
 	\label{res:bcomB}
@@
 \noindent When the executives raise $\bta$ the legislature becomes less likely to abrogate the agreement, for three reasons.
-First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $B(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:leg_a}).
+First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:leg_a}).
 Thus, beyond promising a lower tariff from the trading partner, we can think of the trade agreement as a sort of political commitment device that can be used to reduce political pressure and therefore get the legislature to maintain a lower tariff than it otherwise would.
@@
 
+We are now in a position to examine the governments's decision more closely.
+Of central concern is how the probability that the government agency will renew the antidumping duties varies with lobbying effort:
+
+\begin{lemma}
+  The probability that the government agency renews the antidumping duties is increasing and concave in lobbying effort $\left(\text{i.e.
+} \frac{\partial b}{\partial e} \geq 0, \ \frac{\partial^2 b}{\partial e^2} \leq 0  \right)$.
+  \label{res:bincC}
+\end{lemma}
+
+\noindent All proofs are in the Appendix.
+Lobbying affects only the weight the legislature places on the profits of the import-competing industry.
+These profits are higher in a trade war than a trade agreement.
+Assumption~\ref{as:ga_c} implies that the legislature becomes more favorably inclined---albeit at a decreasing rate---toward the high trade-war tariff and associated profits as lobbying increases and thus more likely to break the trade agreement.
+
 \section{Conclusion}

### 2017-09-28 draft.tex
correct \tau^ad to not be bolded vector

@@
 \newcommand{\bta}{\bm{\tau^a}}
-\newcommand{\btad}{\bm{\tau^{ad}}}
+\newcommand{\tad}{\tau^{ad}}
 \newcommand{\bte}{\bm{\tau^E}}
@@
 Figure~\ref{fig:ext} illustrates the timing of the game.
-Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and levels of antidumping duties $\btad = \left(\tau^{ad},\tau^{*ad}\right)$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the antidumping duties by choice of lobbying effort $e$.
+Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and the antidumping duty level $\tad$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the antidumping duties by choice of lobbying effort $e$.
 
@@
 \begin{equation}
-  W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right)
+  W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right)
   \label{eq:lwcg}
@@
 \begin{multline}
-  r(e,\bta,\btad) = \expect_{\ga|e} \bm{1} [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\btad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
+  r(e,\bta,\tad) = \expect_{\ga|e} \bm{1} [ W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
   \label{eq:b}
@@
 \[
-  \max_{e} r(e,\bta,\btad) \pi(\tau^{ad}) + [1 - r(e,\bta,\btad)] \pi(\tau^a) - e
+  \max_{e} r(e,\bta,\tad) \pi(\tau^{ad}) + [1 - r(e,\bta,\tad)] \pi(\tau^a) - e
 \]
@@
 \begin{equation}
-	\frac{\partial r(e,\bta,\btad)}{\partial e} \left[ \pi(\tau^{ad})  - \pi(\tau^a) \right] = 1 
+	\frac{\partial r(e,\bta,\tad)}{\partial e} \left[ \pi(\tau^{ad})  - \pi(\tau^a) \right] = 1 
 	\label{eq:lobbyfoc}

### 2017-09-28 draft.tex
finish rewrite of intro to sec:main

@@
 \begin{equation}
-  W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right)
+  W_G(\tad,\tau^{*a},\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right)
   \label{eq:lwcg}
@@
 \begin{multline}
-  r(e,\bta,\tad) = \expect_{\ga|e} \bm{1} [ W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\tad,\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
+  r(e,\bta,\tad) = \expect_{\ga|e} \bm{1} [ W_G(\tad,\tau^{*a},\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) ] \\ = \Pr [ W_G(\tad,\tau^{*a},\ga(e,\ve)) > W_G\left(\bta,\ga(e,\ve)\right) | e]
   \label{eq:b}
@@
 The lobby chooses its level of effort as a function of the trade agreement tariffs and the antidumping duties, given the implications of that choice on the government agency's probability of breaking the agreement.
-The lobby maximizes probability-weighted profits net of effort:
+In effect, the lobby maximizes probability-weighted profits net of effort:
 \[
@@
 \]
-The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from a trade war weighted by the increase in the probability of provoking the trade war:
+The first order condition shows that the lobby balances the cost of an extra dollar of expenditure with the higher profits from anti-dumping duties weighted by the increase in the probability of receiving the extension of the antidumping duties:
 \begin{equation}
@@
 \end{equation}
-Assumption [old assumption3] and Result~\ref{res:bincC} ensure the second order condition. To guarantee an interior solution, we need
+Result~\ref{res:bincC} below and the fact that antidumping duties are necessarily larger than trade agreement tariffs ensure the second order condition. To guarantee an interior solution, we need
   \begin{equation}
-	  \frac{\partial r(0,\bta)}{\partial e} \left[ \pi(\tau^{ad}) - \pi(\tau^a) \right] > 1.
+	  \frac{\partial r(0,\bta,\tad)}{\partial e} \left[ \pi(\tau^{ad}) - \pi(\tau^a) \right] > 1.
 		\label{ine:lobint}	
   \end{equation}
-If the executives were to set $\tau^{ad} = \tau^a$, there would be no incentive for the lobby to make a positive contribution.
-There are some other cases in which it is in the executives' interest to set trade agreement tariffs so as to disengage the lobby.
-The following results only hold when the marginal impact of the first lobbying dollar on the break probability is sufficiently high to make engaging in the political process worthwhile for the lobby.
+It may be that either the antidumping duty is too low or the marginal impact of the first lobbying dollar is too small for it to be in the lobby's interest to exert effort.
+The main results of the paper only hold when the marginal impact of the first lobbying dollar on the renewal probability is sufficiently high to make engaging in the political process worthwhile for the lobby.
 
-\begin{result}
-  When the trade agreement remains in force with positive probability, lobbying effort is weakly decreasing in trade agreement tariffs.
-  \label{res:lobby}
-\end{result}
-
-\noindent Raising the trade agreement tariffs decreases the benefit of a break in the trade agreement by raising trade agreement profits.
-This key result implies that the executives can reduce lobbying effort by setting higher tariffs in their trade agreement.
-We will see in the next section how this shapes the executives' joint decision.
-
-I represent the probability that the trade agreement will be broken as $R(\bta)=r(e(\bta),\bta)$ where $e(\bta)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.
-
-To solve for the trade agreement tariffs, one must maximize the following modified version of Equation ``Joint Value'' (removed):
-\begin{equation}
-    \left\{ o \cdot B(\bta) + o^* \cdot B^*(\bta) \right\} \bm{W_E}(\btn) + \left\{ 1- o \cdot B(\bta) - o^* \cdot B^*(\bta) \right\} \bm{W_E}(\bta)  
-  \label{eq:jv2}
-\end{equation}
-where $\bm{W_E}(\cdot)$ is the sum of the home and foreign executives' utilities.
-
-Of central concern is how the break probability varies as both a direct and indirect function of $\bta$ given the lobby's optimal response.
-Result~\ref{res:bcomB} takes into account both the direct and indirect effects:
-
-\begin{result}
-	The total probability that the trade agreement will be broken is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} + \frac{\partial R(\bta)}{\partial  \tau^{*a}} \leq 0$).
-	\label{res:bcomB}
-\end{result}
-
-\noindent When the executives raise $\bta$ the legislature becomes less likely to abrogate the agreement, for three reasons.
-First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:leg_a}).
-Thus, beyond promising a lower tariff from the trading partner, we can think of the trade agreement as a sort of political commitment device that can be used to reduce political pressure and therefore get the legislature to maintain a lower tariff than it otherwise would.
-
-We are now prepared to examine the executives' optimal choice of trade agreement tariffs.
-Because joint executive welfare is decreasing in trade agreement tariffs for $\bta$ above the executives' preferred tariffs, we have the following fundamental feature of the executives' problem:
-\begin{lemma}
-  The executives face the following trade off when choosing $\bta$: higher tariffs decrease the probability that the trade agreement will be broken but also decrease welfare when the agreement is in force.
-  \label{res:to}
-\end{lemma}
-
-The executives will always choose $\bta < \btn$ unless the legislature breaks even agreements with tariffs very close to the Nash level with certainty.
-In this case the problem is not interesting so I ignore this case.
-Thus there is an interior solution in all cases of interest, but this solution may be of two different forms.
-The solution could be at the point that maximizes the concave portion of the executives' welfare function.
-For some specifications, however, high enough tariffs can disengage the lobby so that the probability that the trade agreement will be broken is zero.
-If this occurs at a low enough tariff level, executive welfare can be maximized at this point.
-\begin{result}
-  The executives maximize their welfare by either (a) raising tariffs sufficiently high to ensure that the trade agreement will remain in force or (b) trading off reductions in the probability that the agreement will be broken with reductions in welfare under the agreement.
-  \label{res:execsoln}
-\end{result}
-This accords well with observations of trade policy politics, in that some lobbies exert significant effort toward disrupting trade agreements whereas others apparently do not engage in the political process.
-The current model points to differences across industries in production and demand structure, as well as political weighting ($\ga$), to help explain these variations.
+I represent the total probability that the antidumping duties will be renewed as $R(\bta)=r(e(\bta,\tad),\bta,\tad)$ where $e(\bta,\tad)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.
+We next examine the question of how the total renewal probability varies as both a direct and indirect function of both trade agreement tariffs and antidumping duties, as well as industry profitability and political influence.
+Each result must take into account that the variable of interest can have both a direct effect on the renewal probability and an indirect effect through lobbying incentives.
 
@@
 
+\begin{result}
+  When the trade agreement remains in force with positive probability, lobbying effort is weakly decreasing in trade agreement tariffs.
+  \label{res:lobby}
+\end{result}
+
+\noindent Raising the trade agreement tariffs decreases the benefit of a break in the trade agreement by raising trade agreement profits.
+This key result implies that the executives can reduce lobbying effort by setting higher tariffs in their trade agreement.
+We will see in the next section how this shapes the executives' joint decision.
+
+Of central concern is how the break probability varies as both a direct and indirect function of $\bta$ given the lobby's optimal response.
+Result~\ref{res:bcomB} takes into account both the direct and indirect effects:
+
+\begin{result}
+	The total probability that the trade agreement will be broken is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} + \frac{\partial R(\bta)}{\partial  \tau^{*a}} \leq 0$).
+	\label{res:bcomB}
+\end{result}
+
+\noindent When the executives raise $\bta$ the legislature becomes less likely to abrogate the agreement, for three reasons.
+First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:leg_a}).
+Thus, beyond promising a lower tariff from the trading partner, we can think of the trade agreement as a sort of political commitment device that can be used to reduce political pressure and therefore get the legislature to maintain a lower tariff than it otherwise would.
+
 \section{Conclusion}

### 2017-10-03 draft.tex
reverse order of \tau^a and \tau^*a sections; write proof for lemma1

@@
 \bigskip
-\subsection{Foreign Trade Agreement Tariffs}
-\label{sec:foreign}
-
-Turning to the effects of the trade-agreement tariffs on the probability that the agreement will be abrogated, it is straightforward that the legislature always prefers lower levels of the foreign tariff:
-\begin{lemma}
-  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly increasing in $\tau^{*a}$.
-  \label{lem:leg_astar}
-\end{lemma}
-
-The lower world price for home's export good has a larger negative effect on profits than the positive effect on consumer surplus.
-The net effect of an increase in foreign trade-agreement tariffs on home legislative welfare is negative, leading to an increased probability that the trade agreement will be broken.
-
-\bigskip
 \subsection{Home Trade Agreement Tariffs}
@@
 
-The relationship between $\tau^a$ and break probability is more complex.
+Let's look first at the direct effect of changing $\tau^a$ on the renewal probability.
 For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to approval of the trade agreement, implying a high break probability.
@@
 \begin{lemma}
-  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly decreasing in $\tau^a$.
+  The direct effect of the home trade agreement tariff on the probability the legislature renews the antidumping duty is negative.
   \label{res:leg_a}
@@
 
+\bigskip
+\subsection{Foreign Trade Agreement Tariffs}
+\label{sec:foreign}
+
+Turning to the effects of the trade-agreement tariffs on the probability that the agreement will be abrogated, it is straightforward that the legislature always prefers lower levels of the foreign tariff:
+\begin{lemma}
+  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly increasing in $\tau^{*a}$.
+  \label{lem:leg_astar}
+\end{lemma}
+
+The lower world price for home's export good has a larger negative effect on profits than the positive effect on consumer surplus.
+The net effect of an increase in foreign trade-agreement tariffs on home legislative welfare is negative, leading to an increased probability that the trade agreement will be broken.
+
 \section{Conclusion}
@@
 \label{sec:appendix}
-\noindent \textbf{\hypertarget{Pr_bincC}{Proof of Result~\ref{res:bincC}}}:\\
+\noindent \textbf{\hypertarget{Pr_leg_a}{Proof of Lemma~\ref{res:leg_a}}}:
+
+Substituting from Equation~\ref{eq:ml}, Equation~\ref{eq:b} can be re-written as
+\begin{multline}  
+  r(e,\bta,\tad) = \Pr [ \mathit{CS}_X(\tad) + \ga(e,\ve) \cdot \pi_X(\tad) + \mathit{CS}_Y(\tau^{*a}) + \pi_Y(\tau^{*a}) + \mathit{TR}(\tad) >  \\ \mathit{CS}_X(\tau^a) + \ga(e,\ve) \cdot \pi_X(\tau^a) + \mathit{CS}_Y(\tau^{*a}) + \pi_Y(\tau^{*a}) + \mathit{TR}(\tau^a) ]
+\end{multline}
+Rearranging, we have $r(e_b,\bta,\tad) = $
+\begin{multline}  
+  \textstyle \Pr \Big[ \frac{\mathit{CS}_X(\tad) + \pi_X(\tad) + \mathit{CS}_Y(\tau^{*a}) + \pi_Y(\tau^{*a}) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \pi_X(\tau^a) - \mathit{CS}_Y(\tau^{*a}) - \pi_Y(\tau^{*a}) - \mathit{TR}(\tau^a)}{\pi_X(\tau^a) - \pi_X(\tad)} + 1 \\ \textstyle < \ga(e,\ve) \Big]
+  \label{eq:b_ex}
+\end{multline}
+
+The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
+Labeling the numerator of that expression $\left[ W(\tad,\tau^{*a})-W(\bta)\right]$ (for the change in social welfare), derivative of this quantity with respect to $\tau^{a}$ is
+\begin{equation}
+  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - \left[ W(\tad,\tau^{*a})-W(\bta)\right] \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \label{appex:a}
+\end{equation}
+
+\noindent $\left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ is always positive.
+Because the optimal unilateral tariff for large welfare-maximizing governments is positive (call it $\tau^O$), $\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right)$ is increasing up to $\tau^O$ and decreasing above it.
+Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter.
+
+Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $W(\tad,\tau^{*a})-W(\bta)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign).
+With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.
+
+It is also positive over the remaining $(\tau^O,\tad)$.
+To see this, add $\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a} \left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ to the first summand and subtract it from the second.
+For any particular value of $\tilde{\tau}^a$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\tau}^a$ the preferred unilateral tariff; this makes the derivative in the first summand zero.
+Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\tau}^a$ so that this term is always positive (inclusive of the leading negative sign).
+
+Since the denominator is a squared term of a strictly positive quantity, the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.
+$\hfill\blacksquare$
 

### 2017-10-04 draft.tex
sec:home nearly finishing, including proofs

@@
 
-We are now in a position to examine the governments's decision more closely.
-Of central concern is how the probability that the government agency will renew the antidumping duties varies with lobbying effort:
+All proofs are in the Appendix.
+
+The indirect effect is made up of two parts: the impact of raising the home trade agreement tariff on lobbying effort, and the impact of lobbying effort on the renewal probability.
+Starting with the question of how lobbying effort varies in the home trade agreement tariff, notice that raising the trade agreement tariffs decreases the benefit of a renewal in the trade agreement by raising trade agreement profits.
+This implies that lobbying effort is lower when trade agreement tariffs are higher.
+
+\begin{lemma}
+  Lobbying effort is weakly decreasing in trade agreement tariffs.
+  \label{res:lobby}
+\end{lemma}
+
+Turning to the second component of the indirect effect, it's useful to note that lobbying affects only the weight the government agency places on the profits of the import-competing industry.
+These profits are higher under antidumping duties than under the trade agreement tariff.
+Assumption~\ref{as:ga_c} implies that the government becomes more favorably inclined---albeit at a decreasing rate---toward the higher antidumping duties and associated profits as lobbying increases and thus more likely to break the trade agreement.
 
@@
 
-\noindent All proofs are in the Appendix.
-Lobbying affects only the weight the legislature places on the profits of the import-competing industry.
-These profits are higher in a trade war than a trade agreement.
-Assumption~\ref{as:ga_c} implies that the legislature becomes more favorably inclined---albeit at a decreasing rate---toward the high trade-war tariff and associated profits as lobbying increases and thus more likely to break the trade agreement.
-
-\begin{result}
-  When the trade agreement remains in force with positive probability, lobbying effort is weakly decreasing in trade agreement tariffs.
-  \label{res:lobby}
-\end{result}
-
-\noindent Raising the trade agreement tariffs decreases the benefit of a break in the trade agreement by raising trade agreement profits.
-This key result implies that the executives can reduce lobbying effort by setting higher tariffs in their trade agreement.
-We will see in the next section how this shapes the executives' joint decision.
-
-Of central concern is how the break probability varies as both a direct and indirect function of $\bta$ given the lobby's optimal response.
-Result~\ref{res:bcomB} takes into account both the direct and indirect effects:
+Result~\ref{res:bcomB} combines the direct and indirect effects to get the total effect of trade agreement tariffs on the renewal probability.
 
@@
 The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
-Labeling the numerator of that expression $\left[ W(\tad,\tau^{*a})-W(\bta)\right]$ (for the change in social welfare), derivative of this quantity with respect to $\tau^{a}$ is
+Labeling the numerator of that expression $Z(\tad,\bta)$, the derivative of this quantity with respect to $\tau^{a}$ is
 \begin{equation}
-  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - \left[ W(\tad,\tau^{*a})-W(\bta)\right] \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\tad,\bta) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
   \label{appex:a}
@@
 
-Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $W(\tad,\tau^{*a})-W(\bta)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign).
+Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\tad,\bta)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign).
 With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.
@@
 
+\vskip.4in
+\noindent \textbf{\hypertarget{Pr_lobby}{Proof of Lemma~\ref{res:lobby}}}:\\
+Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
+  \[
+		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial b}{\partial e} \frac{\partial \pi(\bta)}{\partial \tau^a} - \frac{\partial^2 b}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 b}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+	\]
+Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive.
+$\frac{\partial^2 b}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.
+
+Turning to the numerator: $\frac{\partial b}{\partial e_b}$ is positive and $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction so the first term is positive.
+
+We can rewrite $\frac{\partial b(e,\bta)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial Z(\tad,\bta)} \frac{\partial Z(\tad,\bta)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\tad,\bta)}{\partial \tau^a}$, where $F_\ga (Z(\tad,\bta))$ is the CDF of $\ga$ and $f_\ga (Z(\tad,\bta))$ is the pdf of $\ga$ and $Z(\tad,\bta)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+
+Then $\frac{\partial^2 b}{\partial e_b \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} \right) = 
+	   - f_\ga \frac{\partial^2 Z(\tad,\bta)}{\partial \tau^a \partial e} - [\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\tad,\bta)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
+where the above equality holds because $Z(\tad,\bta)$ does not depend on $e$.
+The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 b}{\partial e_b \partial \tau^a} \leq 0$.
+Thus $\frac{\partial e_b}{\partial \tau^a} \leq 0$.
+$\hfill\blacksquare$
+
+\vskip.4in
+\noindent \textbf{\hypertarget{Pr_bincC}{Proof of Result~\ref{res:bincC}}}:\\
+\noindent The left side of the inequality in Expression~\ref{eq:b_ex}, $Z(\tad,\bta)$, does not depend on $e$.
+Thus we have $r(e,\bta,\tad) = \Pr [Z < \ga(e,\ve) ] = 1 - F_{\ga}(\ga=Z)$ where $F_{\ga}(\ga=Z) = F_{\ta}(\ta=h^{-1}(\ga,e))$ by the Change of Variables Theorem and Assumption~\ref{as:ga_ta} with $\ga = h(e,\ta)$ giving the change of variable.
+
+Then $\frac{\partial b}{\partial e} = -\frac{\partial F_{\ta}(\ta=h^{-1}(\ga,e))}{\partial \ta}\frac{\partial h^{-1}(\ga,e)}{\partial e} = -f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial e}$ and $\frac{\partial^2 b}{\partial e^2} = -f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2}$.
+Because $\ga = h(e,\ta)$ is increasing and concave in $e \ \forall \ta$ by Assumption~\ref{as:ga_c}, its inverse is decreasing and convex $\left(\frac{\partial h^{-1}(\ga,e)}{\partial e}\leq 0; \ \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2} \geq 0 \right)$ The pdf of $\ta$ is non-negative, so $\frac{\partial b}{\partial e} \geq 0$ and $\frac{\partial^2 b}{\partial e^2} \leq 0$.
+$\hfill\blacksquare$
+
 \section{References}

### 2017-10-05 draft.tex
finish sec:home

@@
   The probability that the government agency renews the antidumping duties is increasing and concave in lobbying effort $\left(\text{i.e.
-} \frac{\partial b}{\partial e} \geq 0, \ \frac{\partial^2 b}{\partial e^2} \leq 0  \right)$.
+} \frac{\partial r}{\partial e} \geq 0, \ \frac{\partial^2 r}{\partial e^2} \leq 0  \right)$.
   \label{res:bincC}
@@
 \begin{result}
-	The total probability that the trade agreement will be broken is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} + \frac{\partial R(\bta)}{\partial  \tau^{*a}} \leq 0$).
+	The total probability that the trade agreement will be broken is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} \leq 0$).
 	\label{res:bcomB}
@@
 
-\noindent When the executives raise $\bta$ the legislature becomes less likely to abrogate the agreement, for three reasons.
-First, the legislature prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta)$ indirectly (Result~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the legislature's preferred tariff further (Lemma~\ref{res:leg_a}).
-Thus, beyond promising a lower tariff from the trading partner, we can think of the trade agreement as a sort of political commitment device that can be used to reduce political pressure and therefore get the legislature to maintain a lower tariff than it otherwise would.
+\noindent When $\tau^a$ is higher, the government agency becomes less likely to renew the antidumping duties, for three reasons.
+First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta)$ indirectly (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).
 
@@
 \vskip.4in
-\noindent \textbf{\hypertarget{Pr_bincC}{Proof of Result~\ref{res:bincC}}}:\\
+\noindent \textbf{\hypertarget{Pr_bincC}{Proof of Lemma~\ref{res:bincC}}}:\\
 \noindent The left side of the inequality in Expression~\ref{eq:b_ex}, $Z(\tad,\bta)$, does not depend on $e$.
@@
 
+\vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:bcomB}}}: \\
+$	\frac{\partial R(\bta)}{\partial \tau^a} = \frac{\partial b}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial b}{\partial \tau^a}$.
+$\frac{\partial b}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
+$\frac{\partial e}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:lobby}.
+$\frac{\partial b}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:leg_a}.
+Thus the entire expression is non-positive.
+$\hfill\blacksquare$
+
 \section{References}

### 2017-10-05 draft.tex
write sec:foreign; fix some b's throughout

@@
 \begin{result}
-	The total probability that the trade agreement will be broken is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} \leq 0$).
+	The total probability that the antidumping duties will be renewed is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} \leq 0$).
 	\label{res:bcomB}
@@
 
-Turning to the effects of the trade-agreement tariffs on the probability that the agreement will be abrogated, it is straightforward that the legislature always prefers lower levels of the foreign tariff:
-\begin{lemma}
-  Holding lobbying effort constant, the probability the legislature breaks a trade agreement is weakly increasing in $\tau^{*a}$.
-  \label{lem:leg_astar}
-\end{lemma}
+Turning to the effect of the foreign trade agreement tariffs on the probability that the antidumping duties will be renewed, it is perhaps not surprising that there is no effect:
+\begin{result}
+  The total probability that the antidumping duties will be renewed is constant in the foreign trade agreement tariff.
+  \label{res:leg_astar}
+\end{result}
 
-The lower world price for home's export good has a larger negative effect on profits than the positive effect on consumer surplus.
-The net effect of an increase in foreign trade-agreement tariffs on home legislative welfare is negative, leading to an increased probability that the trade agreement will be broken.
+Because the duties are a unilateral policy that we presume here are permissable under WTO rules, the decision to renew the duties or not does not change the level of the tariff applied by the foreign trading partner.
+That is, there is no incentive in terms of reciprocal treatment to deter the home government from renewing the duties.
 
@@
   \[
-		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial b}{\partial e} \frac{\partial \pi(\bta)}{\partial \tau^a} - \frac{\partial^2 b}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 b}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\bta)}{\partial \tau^a} - \frac{\partial^2 r}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
 	\]
 Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive.
-$\frac{\partial^2 b}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.
+$\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.
 
-Turning to the numerator: $\frac{\partial b}{\partial e_b}$ is positive and $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction so the first term is positive.
+Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction so the first term is positive.
 
-We can rewrite $\frac{\partial b(e,\bta)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial Z(\tad,\bta)} \frac{\partial Z(\tad,\bta)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\tad,\bta)}{\partial \tau^a}$, where $F_\ga (Z(\tad,\bta))$ is the CDF of $\ga$ and $f_\ga (Z(\tad,\bta))$ is the pdf of $\ga$ and $Z(\tad,\bta)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+We can rewrite $\frac{\partial r(e,\bta)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial Z(\tad,\bta)} \frac{\partial Z(\tad,\bta)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\tad,\bta)}{\partial \tau^a}$, where $F_\ga (Z(\tad,\bta))$ is the CDF of $\ga$ and $f_\ga (Z(\tad,\bta))$ is the pdf of $\ga$ and $Z(\tad,\bta)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
 
-Then $\frac{\partial^2 b}{\partial e_b \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} \right) = 
+Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} \right) = 
 	   - f_\ga \frac{\partial^2 Z(\tad,\bta)}{\partial \tau^a \partial e} - [\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\tad,\bta)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
 where the above equality holds because $Z(\tad,\bta)$ does not depend on $e$.
-The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 b}{\partial e_b \partial \tau^a} \leq 0$.
-Thus $\frac{\partial e_b}{\partial \tau^a} \leq 0$.
+The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
+Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.
 $\hfill\blacksquare$
@@
 
-Then $\frac{\partial b}{\partial e} = -\frac{\partial F_{\ta}(\ta=h^{-1}(\ga,e))}{\partial \ta}\frac{\partial h^{-1}(\ga,e)}{\partial e} = -f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial e}$ and $\frac{\partial^2 b}{\partial e^2} = -f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2}$.
-Because $\ga = h(e,\ta)$ is increasing and concave in $e \ \forall \ta$ by Assumption~\ref{as:ga_c}, its inverse is decreasing and convex $\left(\frac{\partial h^{-1}(\ga,e)}{\partial e}\leq 0; \ \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2} \geq 0 \right)$ The pdf of $\ta$ is non-negative, so $\frac{\partial b}{\partial e} \geq 0$ and $\frac{\partial^2 b}{\partial e^2} \leq 0$.
+Then $\frac{\partial r}{\partial e} = -\frac{\partial F_{\ta}(\ta=h^{-1}(\ga,e))}{\partial \ta}\frac{\partial h^{-1}(\ga,e)}{\partial e} = -f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial e}$ and $\frac{\partial^2 r}{\partial e^2} = -f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2}$.
+Because $\ga = h(e,\ta)$ is increasing and concave in $e \ \forall \ta$ by Assumption~\ref{as:ga_c}, its inverse is decreasing and convex $\left(\frac{\partial h^{-1}(\ga,e)}{\partial e}\leq 0; \ \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2} \geq 0 \right)$ The pdf of $\ta$ is non-negative, so $\frac{\partial r}{\partial e} \leq 0$ and $\frac{\partial^2 r}{\partial e^2} \leq 0$.
 $\hfill\blacksquare$
@@
 \noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:bcomB}}}: \\
-$	\frac{\partial R(\bta)}{\partial \tau^a} = \frac{\partial b}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial b}{\partial \tau^a}$.
-$\frac{\partial b}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
+$	\frac{\partial R(\bta)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$.
+$\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
 $\frac{\partial e}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:lobby}.
-$\frac{\partial b}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:leg_a}.
+$\frac{\partial r}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:leg_a}.
 Thus the entire expression is non-positive.
+$\hfill\blacksquare$
+
+\vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_astar}{Proof of Result~\ref{res:leg_astar}}}: \\
+$	\frac{\partial R(\bta)}{\partial \tau^{*a}} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^{*a}} + \frac{\partial r}{\partial \tau^{*a}}$.
+$\frac{\partial r}{\partial \tau^{*a}}$ is zero because Expression~\ref{eq:b_ex}, after simplification, is not a function of $\tau^{*a}$.
+$\frac{\partial e}{\partial \tau^{*a}}$ is also zero because Equation~\ref{eq:lobbyfoc} is not a function of $\tau^{*a}$.
+Thus the entire expression is zero.
 $\hfill\blacksquare$

### 2017-10-05 draft.tex
begin sec:gamma from sop-repeated text

@@
 \begin{lemma}
-  The direct effect of the home trade agreement tariff on the probability the legislature renews the antidumping duty is negative.
+  The direct effect of the home trade agreement tariff on the probability the government renews the antidumping duty is negative.
   \label{res:leg_a}
@@
 That is, there is no incentive in terms of reciprocal treatment to deter the home government from renewing the duties.
+
+\bigskip
+\subsection{Political Weighting Function}
+\label{sec:gamma}
+
+We next examine the weight the median decision-maker places on the profits of the import-competing sector.
+The value of the political weight $\ga(e,\ta)$ is endogenous to many of the decisions underpinning the equilibrium, but here we examine the effect of an exogenous shift in the weighting function itself, $\ga(\cdot,\ta)$.
+We start again with the direct effect:
+
+\begin{lemma}
+  The direct effect of exogenous positive shifts in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive.
+	  \label{res:eg}
+\end{lemma}
+
+In accordance with intuition, if there is a shift in the political weighting function so that the government agency weights the profits of the import-competing sector more heavily for a given amount of lobbying effort....
+
+%This translates in a straightforward way to an impact on the trade agreement tariff.
+
+%\begin{corollary}
+%  Exogenous positive shifts in the political weighting function $\ga(e)$ lead to higher trade agreement tariffs, \emph{ceteris paribus}.
+%  \label{cor:tg}
+%\end{corollary}
+
+%\noindent This makes sense given that an upward shift in the political weighting function in effect means that the lobby becomes more powerful---that is, it has a larger impact on the median legislator for a given level of effort.
+This is why the minimum effort level required to break the trade agreement is reduced, and therefore why the trade agreement tariff must be increased: when the lobby has to pay less to break the agreement for any given tariff level, the agreement must be made more agreeable to the lobby.
 

### 2017-10-09 draft.tex
fix missing \tad and order of \tad and \bta throughout text

@@
 
-I represent the total probability that the antidumping duties will be renewed as $R(\bta)=r(e(\bta,\tad),\bta,\tad)$ where $e(\bta,\tad)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.
+I represent the total probability that the antidumping duties will be renewed as $R(\bta,\tad)=r(e(\bta,\tad),\bta,\tad)$ where $e(\bta,\tad)$ is the best response function implicit in Equation \ref{eq:lobbyfoc}, the lobby's first order condition.
 We next examine the question of how the total renewal probability varies as both a direct and indirect function of both trade agreement tariffs and antidumping duties, as well as industry profitability and political influence.
@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta)}{\partial  \tau^a} \leq 0$).
+	The total probability that the antidumping duties will be renewed is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \tau^a} \leq 0$).
 	\label{res:bcomB}
@@
 \noindent When $\tau^a$ is higher, the government agency becomes less likely to renew the antidumping duties, for three reasons.
-First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta)$ indirectly (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).
+First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta,\tad)$ indirectly (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).
 
@@
 The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
-Labeling the numerator of that expression $Z(\tad,\bta)$, the derivative of this quantity with respect to $\tau^{a}$ is
+Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is
 \begin{equation}
-  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\tad,\bta) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
   \label{appex:a}
@@
 
-Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\tad,\bta)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign).
+Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\bta,\tad)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign).
 With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.
@@
 
-We can rewrite $\frac{\partial r(e,\bta)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\tad,\bta))}{\partial Z(\tad,\bta)} \frac{\partial Z(\tad,\bta)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\tad,\bta)}{\partial \tau^a}$, where $F_\ga (Z(\tad,\bta))$ is the CDF of $\ga$ and $f_\ga (Z(\tad,\bta))$ is the pdf of $\ga$ and $Z(\tad,\bta)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tau^a}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
 
-Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\tad,\bta))}{\partial \tau^a} \right) = 
-	   - f_\ga \frac{\partial^2 Z(\tad,\bta)}{\partial \tau^a \partial e} - [\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\tad,\bta)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
-where the above equality holds because $Z(\tad,\bta)$ does not depend on $e$.
-The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\tad,\bta)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
+Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
+	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - [\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
+where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
+The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
 Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.
@@
 \noindent \textbf{\hypertarget{Pr_bincC}{Proof of Lemma~\ref{res:bincC}}}:\\
-\noindent The left side of the inequality in Expression~\ref{eq:b_ex}, $Z(\tad,\bta)$, does not depend on $e$.
+\noindent The left side of the inequality in Expression~\ref{eq:b_ex}, $Z(\bta,\tad)$, does not depend on $e$.
 Thus we have $r(e,\bta,\tad) = \Pr [Z < \ga(e,\ve) ] = 1 - F_{\ga}(\ga=Z)$ where $F_{\ga}(\ga=Z) = F_{\ta}(\ta=h^{-1}(\ga,e))$ by the Change of Variables Theorem and Assumption~\ref{as:ga_ta} with $\ga = h(e,\ta)$ giving the change of variable.
@@
 \noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:bcomB}}}: \\
-$	\frac{\partial R(\bta)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$.
+$	\frac{\partial R(\bta,\tad)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$.
 $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
@@
 \noindent \textbf{\hypertarget{Pr_astar}{Proof of Result~\ref{res:leg_astar}}}: \\
-$	\frac{\partial R(\bta)}{\partial \tau^{*a}} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^{*a}} + \frac{\partial r}{\partial \tau^{*a}}$.
+$	\frac{\partial R(\bta,\tad)}{\partial \tau^{*a}} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^{*a}} + \frac{\partial r}{\partial \tau^{*a}}$.
 $\frac{\partial r}{\partial \tau^{*a}}$ is zero because Expression~\ref{eq:b_ex}, after simplification, is not a function of $\tau^{*a}$.

### 2017-10-09 draft.tex
rough in results and proofs for pi from sec:home

@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is decreasing in $\bta$ (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \tau^a} \leq 0$).
+	The total probability that the antidumping duties will be renewed is decreasing in $\tau^a$ (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \tau^a} \leq 0$).
 	\label{res:bcomB}
@@
 This is why the minimum effort level required to break the trade agreement is reduced, and therefore why the trade agreement tariff must be increased: when the lobby has to pay less to break the agreement for any given tariff level, the agreement must be made more agreeable to the lobby.
+
+\subsection{Profitability of Import Competing Sector}
+\label{sec:pi}
+
+\begin{lemma}
+  The direct effect of an increase in the import competing sector's profitability on the probability the government renews the antidumping duty is positive.
+  \label{res:pi_dir}
+\end{lemma}
+
+\begin{lemma}
+  Lobbying effort is weakly increasing in the import competing sector's profitability.
+  \label{res:pi_indir}
+\end{lemma}
+
+\begin{result}
+	The total probability that the antidumping duties will be renewed is increasing in $\pi$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$).
+	\label{res:pi_total}
+\end{result}
 
@@
 
+\vskip.4in
+\noindent \textbf{\hypertarget{Pr_leg_a}{Proof of Lemma~\ref{res:pi_dir}}}:
+
+The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
+Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is
+\begin{equation}
+  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \label{appex:a}
+\end{equation}
+
+\noindent $\left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ is always positive.
+Because the optimal unilateral tariff for large welfare-maximizing governments is positive (call it $\tau^O$), $\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right)$ is increasing up to $\tau^O$ and decreasing above it.
+Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter.
+
+Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\bta,\tad)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign).
+With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.
+
+It is also positive over the remaining $(\tau^O,\tad)$.
+To see this, add $\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a} \left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ to the first summand and subtract it from the second.
+For any particular value of $\tilde{\tau}^a$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\tau}^a$ the preferred unilateral tariff; this makes the derivative in the first summand zero.
+Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\tau}^a$ so that this term is always positive (inclusive of the leading negative sign).
+
+Since the denominator is a squared term of a strictly positive quantity, the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.
+$\hfill\blacksquare$
+
+\vskip.4in
+\noindent \textbf{\hypertarget{Pr_lobby}{Proof of Lemma~\ref{res:pi_indir}}}:\\
+Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
+  \[
+		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\bta)}{\partial \tau^a} - \frac{\partial^2 r}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+	\]
+Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive.
+$\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.
+
+Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction so the first term is positive.
+
+We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tau^a}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+
+Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
+	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - [\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
+where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
+The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
+Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.
+$\hfill\blacksquare$
+
+\vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:pi_total}}}: \\
+$	\frac{\partial R(\bta,\tad)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$.
+$\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
+$\frac{\partial e}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:lobby}.
+$\frac{\partial r}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:leg_a}.
+Thus the entire expression is non-positive.
+$\hfill\blacksquare$
+
 \section{References}

### 2017-10-09 draft.tex
begin mods to sec:pi proofs

@@
 \vskip.4in
-\noindent \textbf{\hypertarget{Pr_leg_a}{Proof of Lemma~\ref{res:pi_dir}}}:
+\noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:
 
@@
   \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
-  \label{appex:a}
+  \label{appex:pi}
 \end{equation}
@@
 \vskip.4in
-\noindent \textbf{\hypertarget{Pr_lobby}{Proof of Lemma~\ref{res:pi_indir}}}:\\
+\noindent \textbf{\hypertarget{Pr_pi_indir}{Proof of Lemma~\ref{res:pi_indir}}}:\\
 Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
@@
 \vskip.4in	  	
-\noindent \textbf{\hypertarget{Pr_bcomB}{Proof of Result~\ref{res:pi_total}}}: \\
+\noindent \textbf{\hypertarget{Pr_pi_total}{Proof of Result~\ref{res:pi_total}}}: \\
 $	\frac{\partial R(\bta,\tad)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$.

### 2017-10-09 draft.tex
make hypertargets to propositions from proofs work
search draft for 'break', change to renewal

@@
 
-The lobby chooses its level of effort as a function of the trade agreement tariffs and the antidumping duties, given the implications of that choice on the government agency's probability of breaking the agreement.
+The lobby chooses its level of effort as a function of the trade agreement tariffs and the antidumping duties, given the implications of that choice on the government agency's probability of renewing the duties.
 In effect, the lobby maximizes probability-weighted profits net of effort:
@@
 Let's look first at the direct effect of changing $\tau^a$ on the renewal probability.
-For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to approval of the trade agreement, implying a high break probability.
+For any effort level $e$, when the trade agreement tariff is very low, only a small set of realizations of $\ta$ associated with the lowest values of $\ga(e,\ta)$ will lead to the antidumping duties being re-approved, implying a high renewal probability.
 As the trade agreement tariff rises, larger values of $\ga(e,\ta)$ are consistent with approving the trade agreement, so the set of $\ta$'s that lead to trade agreement approval is larger.
-That is, the break probability decreases as $\tau^a$ increases.
+That is, the renewal probability decreases as $\tau^a$ increases.
 
 \begin{lemma}
-  The direct effect of the home trade agreement tariff on the probability the government renews the antidumping duty is negative.
+  The direct effect of the home trade agreement tariff on the probability the government renews the antidumping duty is negative. \hyperlink{Pr_leg_a}{Proof}
   \label{res:leg_a}
@@
 \begin{lemma}
-  Lobbying effort is weakly decreasing in trade agreement tariffs.
+  Lobbying effort is weakly decreasing in trade agreement tariffs. \hyperlink{Pr_lobby}{Proof}
   \label{res:lobby}
@@
 These profits are higher under antidumping duties than under the trade agreement tariff.
-Assumption~\ref{as:ga_c} implies that the government becomes more favorably inclined---albeit at a decreasing rate---toward the higher antidumping duties and associated profits as lobbying increases and thus more likely to break the trade agreement.
+Assumption~\ref{as:ga_c} implies that the government becomes more favorably inclined---albeit at a decreasing rate---toward the higher antidumping duties and associated profits as lobbying increases and thus more likely to renew the antidumping duties.
 
@@
 } \frac{\partial r}{\partial e} \geq 0, \ \frac{\partial^2 r}{\partial e^2} \leq 0  \right)$.
+\hyperlink{Pr_bincC}{Proof}
   \label{res:bincC}
@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is decreasing in $\tau^a$ (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \tau^a} \leq 0$).
+	The total probability that the antidumping duties will be renewed is decreasing in $\tau^a$ (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \tau^a} \leq 0$). \hyperlink{Pr_bcomB}{Proof}
 	\label{res:bcomB}
@@
 \begin{result}
-  The total probability that the antidumping duties will be renewed is constant in the foreign trade agreement tariff.
+  The total probability that the antidumping duties will be renewed is constant in the foreign trade agreement tariff. \hyperlink{Pr_astar}{Proof}
   \label{res:leg_astar}
@@
   The direct effect of exogenous positive shifts in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive.
+\hyperlink{Pr_eg}{Proof}
 	  \label{res:eg}
@@
 \begin{lemma}
-  The direct effect of an increase in the import competing sector's profitability on the probability the government renews the antidumping duty is positive.
+  The direct effect of an increase in the import competing sector's profitability on the probability the government renews the antidumping duty is positive. \hyperlink{Pr_pi_dir}{Proof}
   \label{res:pi_dir}
@@
 \begin{lemma}
-  Lobbying effort is weakly increasing in the import competing sector's profitability.
+  Lobbying effort is weakly increasing in the import competing sector's profitability. \hyperlink{Pr_pi_indir}{Proof}
   \label{res:pi_indir}
@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is increasing in $\pi$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$).
+	The total probability that the antidumping duties will be renewed is increasing in $\pi$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$). \hyperlink{Pr_pi_total}{Proof}
 	\label{res:pi_total}
@@
 
-The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
+The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the renewal probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
 Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is
@@
 \vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_eg}{Proof of Result~\ref{res:eg}}}: \\
+
+\vskip.4in	  	
 \noindent \textbf{\hypertarget{Pr_astar}{Proof of Result~\ref{res:leg_astar}}}: \\
@@
 
-The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the break probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
-Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is
+The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that this derivative is negative.
+The derivative is
 \begin{equation}

### 2017-10-10 draft.tex
update appex:pi eqn
rough in proof eqns for \ga results

@@
   The direct effect of exogenous positive shifts in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive.
-\hyperlink{Pr_eg}{Proof}
-	  \label{res:eg}
+\hyperlink{Pr_ga_dir}{Proof}
+	  \label{res:ga_dir}
 \end{lemma}
@@
 In accordance with intuition, if there is a shift in the political weighting function so that the government agency weights the profits of the import-competing sector more heavily for a given amount of lobbying effort....
+
+\begin{lemma}
+  Lobbying effort is weakly increasing in the uniform exogenous positive shifts of the political weighting function. \hyperlink{Pr_ga_indir}{Proof}
+  \label{res:ga_indir}
+\end{lemma}
+
+\begin{result}
+	The total probability that the antidumping duties will be renewed is increasing in $\ga$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$). \hyperlink{Pr_ga_total}{Proof}
+	\label{res:ga_total}
+\end{result}
 
@@
 \vskip.4in	  	
-\noindent \textbf{\hypertarget{Pr_eg}{Proof of Result~\ref{res:eg}}}: \\
-
-\vskip.4in	  	
 \noindent \textbf{\hypertarget{Pr_astar}{Proof of Result~\ref{res:leg_astar}}}: \\
@@
 \vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
+The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.
+
+This leaves room for very broad kinds of shifts in $\ga(\cdot)$.
+
+\vskip.4in
+\noindent \textbf{\hypertarget{Pr_ga_indir}{Proof of Lemma~\ref{res:ga_indir}}}:\\
+Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
+  \[
+		\frac{\partial e}{\partial \ga(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \ga(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
+		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \ga(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \ga(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+	\]
+
+\vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_ga_total}{Proof of Result~\ref{res:ga_total}}}: \\
+$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$.
+$\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
+$\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}.
+$\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}.
+Thus the entire expression is non-negative.
+$\hfill\blacksquare$
+
+\vskip.4in
 \noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:
@@
 \begin{equation}
-  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
   \label{appex:pi}
@@
   \[
-		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\bta)}{\partial \tau^a} - \frac{\partial^2 r}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+		\frac{\partial e}{\partial \pi(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \pi(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
+		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
 	\]
@@
 \noindent \textbf{\hypertarget{Pr_pi_total}{Proof of Result~\ref{res:pi_total}}}: \\
-$	\frac{\partial R(\bta,\tad)}{\partial \tau^a} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}$.
+$\frac{\partial R(\bta,\tad)}{\partial \pi(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \pi(\cdot)} + \frac{\partial r}{\partial \pi(\cdot)}$.
 $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
-$\frac{\partial e}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:lobby}.
-$\frac{\partial r}{\partial \tau^a}$ is non-positive by Lemma~\ref{res:leg_a}.
-Thus the entire expression is non-positive.
+$\frac{\partial e}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_indir}.
+$\frac{\partial r}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_dir}.
+Thus the entire expression is non-negative.
 $\hfill\blacksquare$

### 2017-10-10 draft.tex
rough in proofs for tau^ad; proof tad_dir and all but last line of tad_indir

@@
 
+\subsection{Antidumping Duties}
+\label{sec:tad}
+
+\begin{lemma}
+  The direct effect of an increase in the antidumping duty on the probability the government renews the antidumping duties is negative. \hyperlink{Pr_tad_dir}{Proof}
+  \label{res:tad_dir}
+\end{lemma}
+
+\begin{lemma}
+  Lobbying effort is weakly increasing in the antidumping duties. \hyperlink{Pr_tad_indir}{Proof}
+  \label{res:tad_indir}
+\end{lemma}
+
+\begin{result}
+	The total probability that the antidumping duties will be renewed is increasing in level of the antidumping duties $\tad$.
+(i.e.
+$\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$).
+\hyperlink{Pr_tad_total}{Proof}
+	\label{res:tad_total}
+\end{result}
+
 \section{Conclusion}
@@
 
-Since the denominator is a squared term of a strictly positive quantity, the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.
-$\hfill\blacksquare$
+Since the denominator is a squared term of a strictly positive quantity, the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.  $\hfill\blacksquare$
 
@@
   \[
-		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\bta)}{\partial \tau^a} - \frac{\partial^2 r}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+		\frac{\partial e}{\partial \tau^a} = - \frac{\frac{\partial FOC_L}{\partial \tau^a}}{\frac{\partial FOC_L}{\partial e}} = \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\tau^a)}{\partial \tau^a} - \frac{\partial^2 r}{\partial e \partial \tau^a} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
 	\]
@@
 
-Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\bta)}{\partial \tau^a}$ is positive by construction so the first term is positive.
+Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\tau^a)}{\partial \tau^a}$ is positive by construction so the first term is positive.
 
@@
 
+\vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_tad_dir}{Proof of Lemma~\ref{res:tad_dir}}}: \\
+The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tad$; to show that the renewal probability is decreasing in $\tad$, I must demonstrate that this derivative is positive.
+Again labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tad$ is
+
+\begin{equation}
+  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial \mathit{CS}_X(\tad)}{\partial \tad} + \frac{\partial \pi_X(\tad)}{\partial \tad} + \frac{\partial \mathit{TR}(\tad)}{\partial \tad}\right) + Z(\bta,\tad) \frac{\partial \pi_X(\tad)}{\partial \tad}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \label{appex:tad}
+\end{equation}
+
+\noindent $\left(\pi_X(\tau^a) - \pi_X(\tad)\right)$ is always negative.
+Because the optimal unilateral tariff for large welfare-maximizing governments is positive (call it $\tau^O$), $\left(\frac{\partial \mathit{CS}_X(\tad)}{\partial \tad} + \frac{\partial \pi_X(\tad)}{\partial \tad} + \frac{\partial \mathit{TR}(\tad)}{\partial \tad}\right)$ is increasing up to $\tau^O$ and decreasing above it.
+Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter.
+Note it seems unreasonable for $\tad$ to be smaller than $\tau^O$ but this can be proved for the general case so we will not assume it.
+
+$Z(\bta,\tad)$ is also always positive on $[0,\tau^O]$ since $\tad > \tau^a$ and on this range $\tad$ is closer to the optimum.
+Profits are increasing in $\tad$, so the second summand is positive on $[0,\tau^O]$.
+With a positive denominator, we thus have that the entire express is positive on $[0,\tau^O]$.
+
+It is also positive for all tariffs larger than $\tau^O$.
+To see this, add $\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tad)}{\partial \tad} \left(\pi_X(\tau^a) - \pi_X(\tad)\right)$ to the first summand and subtract it from the second.
+For any particular value of $\tilde{\tau}^{ad}$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\tau}^{ad}$ the preferred unilateral tariff; this makes the derivative in the first summand zero.
+Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\tau}^{ad}$ so that this term is always positive.
+Since the denominator is a squared term of a strictly negative quantity, the expression in Equation~\ref{appex:tad} is positive for all $\tau^{ad}$.
+$\hfill\blacksquare$
+
+\vskip.4in
+\noindent \textbf{\hypertarget{Pr_tad_indir}{Proof of Lemma~\ref{res:tad_indir}}}:\\
+Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
+  \[
+		\frac{\partial e}{\partial \tad} = - \frac{\frac{\partial FOC_L}{\partial \tad}}{\frac{\partial FOC_L}{\partial e}} =
+		- \frac{ \frac{\partial r}{\partial e} \frac{\partial \pi(\tad)}{\partial \tad} + \frac{\partial^2 r}{\partial e \partial \tad} \left[ \pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+	\]
+The denominator is again negative.
+
+Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\tad)}{\partial \tad}$ is positive by construction so the first term is positive.
+
+We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial  \tad} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tad} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \tad} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tad}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+
+Then $\frac{\partial^2 r}{\partial e \partial \tad} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tad} \right) = 
+	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tad \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} $
+where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
+The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
+Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.
+$\hfill\blacksquare$
+
+\vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_tad_total}{Proof of Result~\ref{res:tad_total}}}: \\
+$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$.
+$\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
+$\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}.
+$\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}.
+Thus the entire expression is non-negative.
+$\hfill\blacksquare$
+
 \section{References}

### 2017-10-11 draft.tex
fix one typo in proof of lemma 2

@@
 Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
-	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - [\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
+	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.

### 2017-10-11 draft.tex
finish \tad results; temp fix for proof of res:lobby

@@
 \begin{lemma}
-  Lobbying effort is weakly increasing in the antidumping duties. \hyperlink{Pr_tad_indir}{Proof}
+  Lobbying effort is weakly decreasing in the antidumping duties. \hyperlink{Pr_tad_indir}{Proof}
   \label{res:tad_indir}
@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is increasing in level of the antidumping duties $\tad$.
+	The total probability that the antidumping duties will be renewed is decreasing in level of the antidumping duties $\tad$.
 (i.e.
-$\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$).
+$\frac{\partial R(\bta,\tad)}{\partial \tad} \leq 0$).
 \hyperlink{Pr_tad_total}{Proof}
@@
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
-The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
+$\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$ as long as $\tau^a$ is weakly larger than the optimal unilateral tariff in the absence of lobbying, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
 Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.
@@
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
-The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
-Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.
+As long as $\tad$ is greater than the optimal unilateral tariff, $\frac{\partial Z(\bta,\tad)}{\partial \tad} \leq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tad} \geq 0$.
+Thus $\frac{\partial e}{\partial \tad} \leq 0$.
 $\hfill\blacksquare$
@@
 \noindent \textbf{\hypertarget{Pr_tad_total}{Proof of Result~\ref{res:tad_total}}}: \\
-$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$.
+$\frac{\partial R(\bta,\tad)}{\partial \tad} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \tad} + \frac{\partial r}{\partial \tad}$.
 $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
-$\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}.
-$\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}.
-Thus the entire expression is non-negative.
+$\frac{\partial e}{\partial \tad}$ is non-positive by Lemma~\ref{res:tad_indir}.
+$\frac{\partial r}{\partial \tad}$ is non-positive by Lemma~\ref{res:tad_dir}.
+Thus the entire expression is non-positive.
 $\hfill\blacksquare$

### 2017-10-12 draft.tex
move sec:tad below sec:foreign
revise proofs for \ga and \pi results

@@
 \bigskip
+\subsection{Antidumping Duties}
+\label{sec:tad}
+
+\begin{lemma}
+  The direct effect of an increase in the antidumping duty on the probability the government renews the antidumping duties is negative. \hyperlink{Pr_tad_dir}{Proof}
+  \label{res:tad_dir}
+\end{lemma}
+
+\begin{lemma}
+  Lobbying effort is weakly decreasing in the antidumping duties. \hyperlink{Pr_tad_indir}{Proof}
+  \label{res:tad_indir}
+\end{lemma}
+
+\begin{result}
+	The total probability that the antidumping duties will be renewed is decreasing in level of the antidumping duties $\tad$.
+(i.e.
+$\frac{\partial R(\bta,\tad)}{\partial \tad} \leq 0$).
+\hyperlink{Pr_tad_total}{Proof}
+	\label{res:tad_total}
+\end{result}
+
+\bigskip
 \subsection{Political Weighting Function}
@@
 	\label{res:pi_total}
-\end{result}
-
-\subsection{Antidumping Duties}
-\label{sec:tad}
-
-\begin{lemma}
-  The direct effect of an increase in the antidumping duty on the probability the government renews the antidumping duties is negative. \hyperlink{Pr_tad_dir}{Proof}
-  \label{res:tad_dir}
-\end{lemma}
-
-\begin{lemma}
-  Lobbying effort is weakly decreasing in the antidumping duties. \hyperlink{Pr_tad_indir}{Proof}
-  \label{res:tad_indir}
-\end{lemma}
-
-\begin{result}
-	The total probability that the antidumping duties will be renewed is decreasing in level of the antidumping duties $\tad$.
-(i.e.
-$\frac{\partial R(\bta,\tad)}{\partial \tad} \leq 0$).
-\hyperlink{Pr_tad_total}{Proof}
-	\label{res:tad_total}
 \end{result}
@@
 \vskip.4in	  	
-\noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
-The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.
-
-This leaves room for very broad kinds of shifts in $\ga(\cdot)$.
-
-\vskip.4in
-\noindent \textbf{\hypertarget{Pr_ga_indir}{Proof of Lemma~\ref{res:ga_indir}}}:\\
-Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
-  \[
-		\frac{\partial e}{\partial \ga(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \ga(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
-		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \ga(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \ga(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
-	\]
-
-\vskip.4in	  	
-\noindent \textbf{\hypertarget{Pr_ga_total}{Proof of Result~\ref{res:ga_total}}}: \\
-$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$.
-$\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
-$\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}.
-$\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}.
-Thus the entire expression is non-negative.
-$\hfill\blacksquare$
-
-\vskip.4in
-\noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:
-
-The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that this derivative is negative.
-The derivative is
-\begin{equation}
-  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
-  \label{appex:pi}
-\end{equation}
-
-\noindent $\left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ is always positive.
-Because the optimal unilateral tariff for large welfare-maximizing governments is positive (call it $\tau^O$), $\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right)$ is increasing up to $\tau^O$ and decreasing above it.
-Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter.
-
-Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\bta,\tad)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign).
-With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.
-
-It is also positive over the remaining $(\tau^O,\tad)$.
-To see this, add $\left(\tilde{\Gamma} - 1 \right) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a} \left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ to the first summand and subtract it from the second.
-For any particular value of $\tilde{\tau}^a$, one can choose the $\tilde{\Gamma}$ weight that would make $\tilde{\tau}^a$ the preferred unilateral tariff; this makes the derivative in the first summand zero.
-Having subtracted the same quantity from the second summand modifies the welfare difference in the second summand to be maximized at $\tilde{\tau}^a$ so that this term is always positive (inclusive of the leading negative sign).
-
-Since the denominator is a squared term of a strictly positive quantity, the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.
-$\hfill\blacksquare$
-
-\vskip.4in
-\noindent \textbf{\hypertarget{Pr_pi_indir}{Proof of Lemma~\ref{res:pi_indir}}}:\\
-Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
-  \[
-		\frac{\partial e}{\partial \pi(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \pi(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
-		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
-	\]
-Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive.
-$\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.
-
-Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\tau^a)}{\partial \tau^a}$ is positive by construction so the first term is positive.
-
-We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial  \tau^a} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \tau^a} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tau^a}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
-
-Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
-	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - [\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
-where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
-The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
-Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.
-$\hfill\blacksquare$
-
-\vskip.4in	  	
-\noindent \textbf{\hypertarget{Pr_pi_total}{Proof of Result~\ref{res:pi_total}}}: \\
-$\frac{\partial R(\bta,\tad)}{\partial \pi(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \pi(\cdot)} + \frac{\partial r}{\partial \pi(\cdot)}$.
-$\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
-$\frac{\partial e}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_indir}.
-$\frac{\partial r}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_dir}.
-Thus the entire expression is non-negative.
-$\hfill\blacksquare$
-
-\vskip.4in	  	
 \noindent \textbf{\hypertarget{Pr_tad_dir}{Proof of Lemma~\ref{res:tad_dir}}}: \\
@@
 
+\vskip.4in
+
+\newpage
+\noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
+The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.
+
+This leaves room for very broad kinds of shifts in $\ga(\cdot)$.
+
+\vskip.4in
+\noindent \textbf{\hypertarget{Pr_ga_indir}{Proof of Lemma~\ref{res:ga_indir}}}:\\
+Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
+  \[
+		\frac{\partial e}{\partial \ga(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \ga(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
+		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \ga(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \ga(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+	\]
+
+The denominator is negative as show in the Proof of Lemma~\ref{res:lobby}. The first term in the numerator is zero since the profit function does not vary in $\ga(\cdot,\cdot)$.
+
+\vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_ga_total}{Proof of Result~\ref{res:ga_total}}}: \\
+$\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \ga(\cdot)} + \frac{\partial r}{\partial \ga(\cdot)}$.
+$\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
+$\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}.
+$\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}.
+Thus the entire expression is non-negative.
+$\hfill\blacksquare$
+
+\vskip.4in
+\newpage
+\noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:
+
+The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that the following derivative is negative:
+\begin{equation}
+  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \label{appex:pi}
+\end{equation}
+
+This can be simplied to
+\[
+  \frac{\left(\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+\]
+
+%\noindent $\left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ is always positive.
+
+%Since the denominator is a squared term of a strictly positive quantity, %the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.
+$\hfill\blacksquare$
+
+\vskip.2in
+\noindent \textbf{\hypertarget{Pr_pi_indir}{Proof of Lemma~\ref{res:pi_indir}}}:\\
+Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
+  \[
+		\frac{\partial e}{\partial \pi(\cdot)} = - \frac{\frac{\partial FOC_L}{\partial \pi(\cdot)}}{\frac{\partial FOC_L}{\partial e}} =
+		- \frac{ \frac{\partial r}{\partial e} \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + \frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \left[\pi(\tad) - \pi(\tau^a) \right]}{\frac{\partial^2 r}{\partial e^2} \left[ \pi(\tad) - \pi(\tau^a) \right]}
+	\]
+Beginning with the denominator: $\tad > \tau^a$ and $\pi(\cdot)$ is increasing in $\tau$ so the expression is brackets is positive.
+$\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.
+
+Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is positive by assumption so the first term is positive.
+
+We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tau^a}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+
+Then $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} = - \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} \right) = 
+	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \pi(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} $
+where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. $-\frac{\partial Z(\bta,\tad)}{\partial \pi(
+cdot)} = - \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) \leq 0$ by assumption, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \leq 0$.
+Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.
+$\hfill\blacksquare$
+
+\vskip.4in	  	
+\noindent \textbf{\hypertarget{Pr_pi_total}{Proof of Result~\ref{res:pi_total}}}: \\
+$\frac{\partial R(\bta,\tad)}{\partial \pi(\cdot)} = \frac{\partial r}{\partial  e}\frac{\partial e}{\partial \pi(\cdot)} + \frac{\partial r}{\partial \pi(\cdot)}$.
+$\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
+$\frac{\partial e}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_indir}.
+$\frac{\partial r}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_dir}.
+Thus the entire expression is non-negative.
+$\hfill\blacksquare$
+
 \section{References}

### 2017-10-18 draft.tex
paste intro/conclusion material from presentation into draft

@@
 
+\begin{enumerate}
+	\item How long do deviations from trade agreement tariffs last? 
+  \item What are the determinants of renewals?
+		\begin{itemize}
+			\item They don't happen for \textit{no} reason at all
+		\end{itemize}
+\end{enumerate}
+
+\vskip.2in
+\begin{itemize}
+	\item Temporary trade barriers have potential to be renewed
+		\begin{itemize}
+			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
+			\item For Safeguards, four then four; much rarer than AD
+		\end{itemize}
+	\item Authorized by WTO
+	\item Very little in the agreements to guide the process
+		\begin{itemize}
+			\item WTO litigation gives gov'ts a LOT of latitude
+			\item Renewal decision determined by complex process including DOC, ITC, pressure via other political bodies.
+		\end{itemize}
+	\item In U.S., for AD:
+		\begin{itemize}
+			\item DOC initiates, determines whether dumping would continue
+						\begin{itemize}
+			\item Can renew AD duties
+			\item Susceptible to influence of lobbying, perhaps both direct and indirect
+			\item Modeled in reduced form
+		\end{itemize}
+
+			\item ITC determines whether injury would recur / continue
+		\end{itemize}
+\end{itemize}
+
+\vskip.2in
+The probability that an AD duty gets renewed
+
+\begin{itemize}
+	\item Increases in lobbying effort
+	\item Decreases in the MFN tariff
+	\item Is invariant to the trading partner's tariff
+	\item Increases in the profitability of the import-competing sector
+	\item Increases in the strength of the lobby
+	\item May be concave in the AD duty
+\end{itemize}
+
 \subsection{Related Literature}
 \textbf{WILL NEED MAJOR OVERHAUL}
+
+Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)
 
@@
 After this, uncertainty about the government agency's preferences is resolved.
+
+Lobby must be able to trigger the original AD duty
+\begin{itemize}
+	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
+	\item It could be justified, not motivated by politics/rent-seeking
+	\item But still, firms lobby for duties they don't get
+\end{itemize}
+
+\vskip.1in
+So what's the uncertainty about?
+
+\begin{itemize}
+	\item Strength of evidence
+	\item Probability foreign will retaliate or initiate dispute (indirect)
+	\item $G$'s valuation of harm to industry, e.g. how politically important is industry?
+	\item Uncertainty could be, in part, about how mobile labor is (Kishore)
+\end{itemize}
+
 All players simultaneously observe the realization of the random variable $\ta$ that represents this uncertainty.
@@
 
+			Future Work
+
+\begin{itemize}
+	\item Comparative static on uncertainty measure
+	\item Empirical work
+	\item Extend model to include initial decision to grant protection.
+		\begin{itemize}
+			\item Explain variation in a lobby's incentives between original application of AD and renewal
+			\item Lobby's choice between investing in productive vs. rent-seeking behavior while protected
+			\item Need to have first stage (Jee-Hyeong, Gary Lyn)
+		\begin{itemize}
+			\item Look at Park and Blonigen (Jee-Hyeong)
+			\item Cost differential for firms to get initial duty vs. renewal?
+			\item Some firms choose not to pursue renewal when DOC contacts them 30-days before (Sasha)
+		\end{itemize}
+	\item Lobbying effort may be endogenous: if prob. of success is lower, maybe it's not worth providing effort (Mostafa)
+		\end{itemize}
+\end{itemize}
+
 \section{Appendix}

### 2017-10-19 draft.tex
fix typos in proof of \pi results

@@
 The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to a positive shift in the $\pi(\cdot)$ function; to show that the renewal probability is increasing in such a positive shift, I must demonstrate that the following derivative is negative:
+\[
+  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+\]
+
+This can be simplied to
 \begin{equation}
-  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \frac{\left(\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
 \label{appex:pi}
 \end{equation}
-
-This can be simplied to
-\[
-  \frac{\left(\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
-\]
 
@@
 
-We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \tau^a}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
 
@@
 	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \pi(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} \frac{\partial f_\ga}{\partial e} $
-where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$. $-\frac{\partial Z(\bta,\tad)}{\partial \pi(
-cdot)} = - \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) \leq 0$ by assumption, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \leq 0$.
+where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
+$-\frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) \leq 0$ by assumption, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \leq 0$.
 Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.

### 2017-10-21 draft.tex
begin making Z/ZN distinction; fix proof of res:leg_a

@@
 The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tau^a$; to show that the renewal probability is decreasing in $\tau^a$, I must demonstrate that this derivative is positive.
-Labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is
+Labeling the left hand side of the inequality in Expression~\ref{eq:b_ex} $Z(\bta,\tad)$ and the numerator of that expression $ZN(\bta,\tad)$, the derivative of this quantity with respect to $\tau^{a}$ is
 \begin{equation}
-  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - Z(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \frac{\left(\pi_X(\tad) - \pi_X(\tau^a)\right)\left(\frac{\partial \mathit{CS}_X(\tau^{a})}{\partial \tau^{a}} + \frac{\partial \pi_X(\tau^a)}{\partial \tau^{a}} + \frac{\partial \mathit{TR}(\tau^{a})}{\partial \tau^{a}}\right) - ZN(\bta,\tad) \frac{\partial \pi_X(\tau^a)}{\partial \tau^a}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
   \label{appex:a}
@@
 Thus the first summand is increasing up until $\tau^O$ and decreasing thereafter.
-
-Because total social welfare is maximized at $\tau^a = \tau^{*a} = 0$, $Z(\bta,\tad)$ is always negative, whereas profits are increasing in $\tau^a$, so the second summand is positive everywhere (inclusive of the leading negative sign).
-With a positive denominator, we thus have that the derivative is positive on $[0,\tau^O]$.
 

### 2017-10-21 draft.tex
distinguish all Z/ZN in appendix; at least note where changes to proofs result

@@
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
-$\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$ as long as $\tau^a$ is weakly larger than the optimal unilateral tariff in the absence of lobbying, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
+The proof of Lemma~\ref{res:leg_a} shows that $\frac{\partial Z(\bta,\tad)}{\partial \tau^a} \geq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tau^a} \leq 0$.
 Thus $\frac{\partial e}{\partial \tau^a} \leq 0$.
@@
 The effect on the renewal probability is determined by the sign of the derivative of the left hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\tad$; to show that the renewal probability is decreasing in $\tad$, I must demonstrate that this derivative is positive.
-Again labeling the numerator of that expression $Z(\bta,\tad)$, the derivative of this quantity with respect to $\tad$ is
+Again labeling the numerator of that expression $ZN(\bta,\tad)$, the derivative of this quantity with respect to $\tad$ is
 
 \begin{equation}
-  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial \mathit{CS}_X(\tad)}{\partial \tad} + \frac{\partial \pi_X(\tad)}{\partial \tad} + \frac{\partial \mathit{TR}(\tad)}{\partial \tad}\right) + Z(\bta,\tad) \frac{\partial \pi_X(\tad)}{\partial \tad}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial \mathit{CS}_X(\tad)}{\partial \tad} + \frac{\partial \pi_X(\tad)}{\partial \tad} + \frac{\partial \mathit{TR}(\tad)}{\partial \tad}\right) + ZN(\bta,\tad) \frac{\partial \pi_X(\tad)}{\partial \tad}}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
   \label{appex:tad}
@@
 
-$Z(\bta,\tad)$ is also always positive on $[0,\tau^O]$ since $\tad > \tau^a$ and on this range $\tad$ is closer to the optimum.
+$ZN(\bta,\tad)$ is also always positive on $[0,\tau^O]$ since $\tad > \tau^a$ and on this range $\tad$ is closer to the optimum.
 Profits are increasing in $\tad$, so the second summand is positive on $[0,\tau^O]$.
@@
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
-As long as $\tad$ is greater than the optimal unilateral tariff, $\frac{\partial Z(\bta,\tad)}{\partial \tad} \leq 0$, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tad} \geq 0$.
-Thus $\frac{\partial e}{\partial \tad} \leq 0$.
+$\frac{\partial Z(\bta,\tad)}{\partial \tad} \geq 0$ by the proof of Lemma~\ref{res:tad_dir}, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \tad} \leq 0$.
+Thus the sign of $\frac{\partial e}{\partial \tad}$ is ambiguous.
 $\hfill\blacksquare$
@@
 \vskip.4in	  	
-
-\newpage
 \noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
@@
 \vskip.4in
-\newpage
 \noindent \textbf{\hypertarget{Pr_pi_dir}{Proof of Lemma~\ref{res:pi_dir}}}:
@@
 \[
-  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + Z(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \frac{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) + ZN(\bta,\tad) \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right)}{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
 \]
@@
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
-$-\frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - \left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) \leq 0$ by assumption, so $\frac{\partial f_\ga}{\partial e} \geq 0$ ensures that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \leq 0$.
+Refer to result in proof of Lemma~\ref{res:pi_dir}; then $\frac{\partial f_\ga}{\partial e} \geq 0$ implies that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \ldots$.
 Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.

### 2017-10-22 draft.tex
fix res:pi_dir and its proof

@@
 \begin{lemma}
-  The direct effect of an increase in the import competing sector's profitability on the probability the government renews the antidumping duty is positive. \hyperlink{Pr_pi_dir}{Proof}
+  The direct effect of a change in the import competing sector's profitability on the probability the government renews the antidumping duty has the same sign as the change in the gap between profits under antidumping duties and profits under the trade agreement tariff.
+\hyperlink{Pr_pi_dir}{Proof}
   \label{res:pi_dir}
@@
 \begin{equation}
-  \frac{\left(\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right)\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
+  \frac{\left[\mathit{CS}_X(\tad) + \mathit{TR}(\tad)  -\mathit{CS}_X(\tau^a) - \mathit{TR}(\tau^a) \right]\left(\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]\right) }{\left(\pi_X(\tau^a) - \pi_X(\tad)\right)^2}.
 \label{appex:pi}
@@
 
-%\noindent $\left(\pi_X(\tad) - \pi_X(\tau^a)\right)$ is always positive.
+Assume the tariff that maximizes the term in square brackets is small enough so that this term is negative.
+This should hold almost everywhere, as the tariff that maximizes that term is zero in most cases, and certainly smaller than $\tau^O$.
+Since the denominator is a squared term of a strictly positive quantity, the sign of the derivative is determined by the sign of $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$.
 
-%Since the denominator is a squared term of a strictly positive quantity, %the expression in Equation~\ref{appex:a} is positive for all $\tau^{a}$.
+When $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right] \geq 0$ the derivative is weakly negative and $\frac{\partial r}{\partial \pi(\cdot)}$ is weakly positive.
+
+When $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right] \leq 0$ the derivative is weakly positive and $\frac{\partial r}{\partial \pi(\cdot)}$ is weakly negative.
+
+Thus the derivative of the renewal probability has the same sign as $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$, which indicates how the gap between profits under antidumping duties and profits under the trade agreement tariff changes when the profit function changes.
 $\hfill\blacksquare$

### 2017-10-22 draft.tex
finish rewrite of \pi results and proofs

@@
 \begin{lemma}
-  Lobbying effort is weakly increasing in the import competing sector's profitability. \hyperlink{Pr_pi_indir}{Proof}
+  The effect of a change in the import competing sector's profitability on lobbying effort has the same sign as the change in the gap between profits under antidumping duties and profits under the trade agreement tariff.
+\hyperlink{Pr_pi_indir}{Proof}
   \label{res:pi_indir}
@@
 
+Notes:
+\begin{itemize}
+	\item For $\frac{\partial R}{\partial \pi} \geq 0$, need the return from lobbying to increase with increase in $\pi$ AND
+	\item government marginal benefit from protection to increase with $\pi$
+\end{itemize}
+
+\vskip.2in
+\begin{itemize}
+	\item Profit function convex $\Rightarrow$ also quasiconvex
+	\item But hit it with the right increasing monotone transformation and $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ can go either way
+	\item This is about how the differences change (CARDINAL)
+\end{itemize}
+
 \begin{result}
-	The total probability that the antidumping duties will be renewed is increasing in $\pi$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$). \hyperlink{Pr_pi_total}{Proof}
+	The total probability that the antidumping duties will be renewed increases (decreases) when there is an increase (decrease) in the gap between profits under antidumping duties and profits under the trade agreement tariff.
+\hyperlink{Pr_pi_total}{Proof}
 	\label{res:pi_total}
@@
 \noindent \textbf{\hypertarget{Pr_pi_indir}{Proof of Lemma~\ref{res:pi_indir}}}:\\
-Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
+Proof is via the Implicit Function Theorem for Banach spaces using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
   \[
@@
 $\frac{\partial^2 r}{\partial e^2}$ is negative by Result~\ref{res:bincC}, so the denominator is negative.
+Combining this with the leading negative sign, the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is determined by the sign of the numerator.
 
-Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is positive by assumption so the first term is positive.
+$\frac{\partial r}{\partial e}$ is positive by Lemma~\ref{res:bincC} and $\left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is positive as argued above.
 
-We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+$\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ may be either positive or negative, and its sign impacts $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)}$.
+To see how, we can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \pi(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
 
@@
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
-Refer to result in proof of Lemma~\ref{res:pi_dir}; then $\frac{\partial f_\ga}{\partial e} \geq 0$ implies that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \ldots$.
-Thus the sign of $\frac{\partial e}{\partial \pi(\cdot)}$ is ambiguous.
+The proof of Lemma~\ref{res:pi_dir} shows that $\frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)}$ has the opposite sign as $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$.
+When $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is weakly positive (negative), $\frac{\partial f_\ga}{\partial e} \geq 0$ implies that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \geq 0 \ \left(\leq 0\right)$.
+Thus $\frac{\partial e}{\partial \pi(\cdot)}$ has the same sign as $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$.
 $\hfill\blacksquare$
 
-\vskip.4in	  	
+\vskip.3in	  	
 \noindent \textbf{\hypertarget{Pr_pi_total}{Proof of Result~\ref{res:pi_total}}}: \\
@@
 $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
-$\frac{\partial e}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_indir}.
-$\frac{\partial r}{\partial \pi(\cdot)}$ is non-negative by Lemma~\ref{res:pi_dir}.
-Thus the entire expression is non-negative.
-$\hfill\blacksquare$
+$\frac{\partial r}{\partial \pi(\cdot)}$ and $\frac{\partial e}{\partial \pi(\cdot)}$ are both non-negative (non-positive) when $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is non-negative (non-positive) by Lemmas~\ref{res:pi_dir} and \ref{res:pi_indir}.
+Thus the sign of the entire expression is the same as the sign of $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$.$\hfill\blacksquare$
 

### 2017-10-22 draft.tex
start work on \ga proofs

@@
 
-The denominator is negative as show in the Proof of Lemma~\ref{res:lobby}. The first term in the numerator is zero since the profit function does not vary in $\ga(\cdot,\cdot)$.
+The denominator is negative as show in the Proof of Lemma~\ref{res:lobby}.
+The first term in the numerator is zero since the profit function does not vary in $\ga(\cdot,\cdot)$.
+Combining this with the leading negative sign and the fact that $\left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is positive, the sign of $\frac{\partial e}{\partial \ga(\cdot)}$ is determined by the sign of $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)}$.
+
+We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \ga(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \ga(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \ga(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \ga(\cdot)}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+
+Then $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} = - \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \ga(\cdot)} \right) = 
+	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \ga(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \ga(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \ga(\cdot)} \frac{\partial f_\ga}{\partial e} $
+where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
+
+The proof of Lemma~\ref{res:pi_dir} shows that $\frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)}$ has the opposite sign as $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$.
+When $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is weakly positive (negative), $\frac{\partial f_\ga}{\partial e} \geq 0$ implies that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \geq 0 \ \left(\leq 0\right)$.
+Thus $\frac{\partial e}{\partial \pi(\cdot)}$ has the same sign as $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$.
+$\hfill\blacksquare$
 

### 2017-10-24 draft.tex
small changes to \ga

@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is increasing in $\ga$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \pi} \geq 0$). \hyperlink{Pr_ga_total}{Proof}
+	The total probability that the antidumping duties will be renewed is increasing in $\ga$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \ga(\cdot)} \geq 0$). \hyperlink{Pr_ga_total}{Proof}
 	\label{res:ga_total}
@@
 \noindent \textbf{\hypertarget{Pr_ga_indir}{Proof of Lemma~\ref{res:ga_indir}}}:\\
-Proof is via the Implicit Function Theorem using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
+Proof is via the Implicit Function Theorem for Banach spaces using the lobby's first order condition, Equation~\ref{eq:lobbyfoc}, referred to here as $FOC_L$.
   \[

### 2017-10-27 presentation.tex
change date, etc for SEA presentation

@@
 \title[Temporary Trade Barriers: When Will They End?\hspace{2.35in}\insertframenumber/\inserttotalframenumber]{Temporary Trade Barriers: \\ When Will They End?}
-\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
-\date{May 13, 2016}
+\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University\newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
+\date{November 18, 2017}
 
@@
 \begin{itemize}
-	\item Renews AD duties if $G$ prefers $\tau^{\mathit{ad}}$ to $\tau^a$
+	\item AD duties renewed if $G$ prefers $\tau^{\mathit{ad}}$ to $\tau^a$
 \end{itemize}

### 2017-10-27 presentation.tex
simplify uncertainty slide

@@
 \pause
-Lobby must be able to trigger the original AD duty
-\begin{itemize}[<+->]
-	\item \textit{Can} think of non-adherence to MFN as eqm path dispute
-	\item It could be justified, not motivated by politics/rent-seeking
-	\item But still, firms lobby for duties they don't get
-\end{itemize}
-
-\pause
-\vskip.1in
-So what's the uncertainty about?
-\pause
 \begin{itemize}[<+->]
@@
 \begin{itemize}[<+->]
-	\item Could leverage 5-year renewal cycle vs. 4-year re-election cycle (Sarah Danzman, Indiana U)
+	%\item Could leverage 5-year renewal cycle vs. 4-year re-election cycle (Sarah Danzman, Indiana U)
 	\item Look for Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)

### 2017-10-31 presentation.tex
update presentation for jr seminar

@@
 \pause
-The probability that an AD duty gets renewed
+The probability that AD duties gets renewed
 \pause
 \begin{itemize}[<+->]
-	\item Increases in lobbying effort
-	\item Decreases in the MFN tariff
-	\item Is invariant to the trading partner's tariff
-	\item Increases in the profitability of the import-competing sector
-	\item Increases in the strength of the lobby
-	\item May be concave in the AD duty
+	\item increases in lobbying effort
+	\item decreases in the MFN tariff
+	\item is invariant to the trading partner's tariff
+	\item increases in the profitability of the import-competing sector
+	\item increases in the strength of the lobby
+	\item AD duties: complicated
 \end{itemize}
@@
 \begin{itemize}[<+->]
-	\item Dept. of Commerce / Int'l Trade Commission
+	\item Dept. of Commerce / Int'l Trade Commission ($G$)
 		\begin{itemize}[<+->]
@@
 \pause
-\vskip.1in
+\vskip.2in
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumption 1}
@@
 \begin{itemize}[<+->]
-	\item $e$: Lobbying effort
 	\item $\tau^a$: home import tariff under trade agreement
@@
 \subsection{}
+
+\begin{comment}
 \begin{frame}{Timeline}
@@
 \end{itemize}
+
+\pause
+\vskip.2in
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumption 2}
+\begin{enumerate}
+  \pause
+	\item $\ta$ is uniformly distributed on some $\Theta=\left[\underline{\ta},\overline{\ta}\right]$.
+\end{enumerate}
+\end{beamerboxesrounded}
 
@@
   \vskip.1in
-    $b(e,\tau^a,\tau^{\textit{ad}})$: probability $G$ prefers $\tau^{ad}$ to $\tau^a$ for a given effort level $e$
+    $r(e,\tau^a,\tau^{\textit{ad}})$: probability $G$ prefers $\tau^{ad}$ to $\tau^a$ for a given effort level $e$
 \end{itemize}
@@
 \vskip.25in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 1}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 3}
   The probability that $G$ renews AD duties is increasing and concave in lobbying effort $e$ $\left(\text{i.e.
-} \frac{\partial b}{\partial e} \geq 0, \ \frac{\partial^2 b}{\partial e^2} \leq 0  \right)$.
+} \frac{\partial r}{\partial e} \geq 0, \ \frac{\partial^2 r}{\partial e^2} \leq 0  \right)$.
 \end{beamerboxesrounded}
@@
 \[
-  \frac{\partial b}{\partial e} \frac{\partial e}{\partial \tau^a} + \frac{\partial b}{\partial \tau^a}
+  \frac{\partial r}{\partial e} \frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a}
 \]
@@
 \begin{itemize}
-	\item No difference in foreign tariff under AD duty and $\tau^a$. So no effect on $G$'s incentives (either direct or indirect)
+	\item No difference in foreign tariff under AD duties and $\tau^a$. So no effect on $G$'s incentives (either direct or indirect)
 \end{itemize}
@@
 
-\begin{frame}{Profitability of Import-Competing Sector}
+\begin{frame}{Protection through AD Duties}
 
 \pause
-\textit{NOTE: this is not quite right, but some version of it will be} \\
-Assume $\pi(\cdot)$ shifts up uniformly for all $\tau$.
+When $\tau^{\textit{ad}}$ increases, direct effect is negative: social welfare decreases, so $G$ less likely to renew
+
+\vskip.2in
 \pause
-\begin{itemize}[<+->]
-	\item Convexity of profits $\Rightarrow$ $G$'s marginal benefit of providing protection goes up
-	\item Convexity of profits $\Rightarrow$ return from lobbying increases
+Indirect effect is positive: higher $\tau^{\textit{ad}}$ increases incentive to exert lobbying effort
+
+\vskip.2in
+\pause
+Magnitudes are not directly comparable
+\begin{itemize}
+	\item Working to endogenize $\tau^{\textit{ad}}$
 \end{itemize}
 
-\vskip.25in
-\pause
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
-  The total probability that $G$ renews AD duties is increasing in the profitability of the import-competing sector.
-\end{beamerboxesrounded}
 \end{frame}
@@
 \pause
-Assume $\ga(\cdot,\cdot)$ shifts up uniformly for all $(e,\ta)$ pairs.
+Assume $\ga(\cdot,\cdot)$ increases weakly for all $(e,\ta)$ pairs.
 \pause
@@
 \pause
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 3}
-  The total probability that $G$ renews AD duties increases when the weighting function shifts up exogenously and uniformly.
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 4}
+  The total probability that $G$ renews AD duties increases when the weighting function shifts up exogenously.
 \end{beamerboxesrounded}
@@
 
-\begin{frame}{Protection from AD Duties}
+\begin{frame}{Profitability of Import-Competing Sector}
 
 \pause
-When $\tau^{\textit{ad}}$ increases, two effects on $G$'s incentives:
+Both lobby and $G$ care on the margin about the difference between profits under $\tau^{\textit{ad}}$ and $\tau^a$
 \pause
 \begin{itemize}[<+->]
-	\item Social welfare decreases, pushes for decrease in renewal probability 
-	\item (Over-weighted) import-competing profits increase, pushes for increase in renewal probability 
+	\item Shifts in the profit function matter to the extent they change this difference 
 \end{itemize}
 
-\vskip.2in
+\vskip.25in
 \pause
-Indirect effect is of same sign as direct effect
-\pause
-\begin{itemize}[<+->]
-	\item When $\tau^{\textit{ad}}$ (i.e. close to social optimum), second effect dominates $\Rightarrow$ increase in renewal probability
-	\item Effect may be concave
-\end{itemize}
-
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 5}
+  The total probability that $G$ renews AD duties increases (decreases) when there is an increase (decrease) in the gap between profits under $\tau^{\textit{ad}}$ and profits under $\tau^a$.
+\end{beamerboxesrounded}
 \end{frame}
@@
 
+\begin{comment}
 \begin{frame}{Feedback, Comments from InsTED presentation}
@@
 			\item Look at Park and Blonigen (Jee-Hyeong)
-			\item Cost differential for firms to get initial duty vs. renewal?
+			\item Cost differential for firms to get initial duties vs. renewal?
 			\item Some firms choose not to pursue renewal when DOC contacts them 30-days before (Sasha)

### 2017-11-04 presentation.tex
streamline presentation after jr seminar

@@
   \item What are the determinants of renewals?
-		\begin{itemize}
-			\item They don't happen for \textit{no} reason at all
-		\end{itemize}
 \end{enumerate}
@@
 	\item Authorized by WTO
-	\item Very little in the agreements to guide the process
-		\begin{itemize}
-			\item WTO litigation gives gov'ts a LOT of latitude
-		\end{itemize}
+	\item Agreements / litigation provide a LOT of latitude
 	\item In U.S., for AD:
@@
 \begin{frame}{Economy}
+Two countries: home and foreign (${}^*$)
 \begin{itemize}
-	\item Two countries: home and foreign (${}^*$)
-	\item Separable in three goods: $X$ and $Y$ (traded) and numeraire
-	\item Demand identical for both goods in both countries
-	\item Supply: $Q_X^*(P_X) > Q_X(P_X)$ $\forall P_X$; symmetric for $Y$ 
+	\item Symmetric and separable in $X$ and $Y$ (traded) and numeraire
 		\begin{itemize}
@@
 \begin{itemize}
-	\item Working to endogenize $\tau^{\textit{ad}}$
+	\item Work in progress: endogenize $\tau^{\textit{ad}}$
 \end{itemize}
@@
 \begin{itemize}[<+->]
+	\item Empirical work
 	\item Comparative static on uncertainty measure
-	\item Empirical work
 	\item Extend model to include initial decision to grant protection.

### 2017-11-06 draft.tex
fix small typos in appendix
add assumption on dist'n of theta

@@
   \label{as:ga_ta}
+\end{assumption}
+
+\begin{assumption}
+  $\ta$ is uniformly distributed on some $\Theta=\left[\underline{\ta},\overline{\ta}\right]$.
+  \label{as:ta}
 \end{assumption}
@@
 Profits are increasing in $\tad$, so the second summand is positive on $[0,\tau^O]$.
-With a positive denominator, we thus have that the entire express is positive on $[0,\tau^O]$.
+With a positive denominator, we thus have that the entire expression is positive on $[0,\tau^O]$.
 

### 2017-11-10 draft.tex
make distribution-related fixes to appendix

@@
 
-Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive and $\frac{\partial \pi(\tau^a)}{\partial \tau^a}$ is positive by construction so the first term is positive.
+Turning to the numerator: $\frac{\partial r}{\partial e}$ is positive by Lemma~\ref{res:bincC} below and $\frac{\partial \pi(\tau^a)}{\partial \tau^a}$ is positive by construction so the first term is positive.
 
@@
 Then $\frac{\partial^2 r}{\partial e \partial \tau^a} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tau^a} \right) = 
-	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tau^a \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
+	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial e \partial \tau^a } - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tau^a} \frac{\partial f_\ga}{\partial e} $
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
@@
 Then $\frac{\partial r}{\partial e} = -\frac{\partial F_{\ta}(\ta=h^{-1}(\ga,e))}{\partial \ta}\frac{\partial h^{-1}(\ga,e)}{\partial e} = -f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial e}$ and $\frac{\partial^2 r}{\partial e^2} = -f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2}$.
-Because $\ga = h(e,\ta)$ is increasing and concave in $e \ \forall \ta$ by Assumption~\ref{as:ga_c}, its inverse is decreasing and convex $\left(\frac{\partial h^{-1}(\ga,e)}{\partial e}\leq 0; \ \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2} \geq 0 \right)$ The pdf of $\ta$ is non-negative, so $\frac{\partial r}{\partial e} \leq 0$ and $\frac{\partial^2 r}{\partial e^2} \leq 0$.
+Because $\ga = h(e,\ta)$ is increasing and concave in $e \ \forall \ta$ by Assumption~\ref{as:ga_c}, its inverse is decreasing and convex $\left(\frac{\partial h^{-1}(\ga,e)}{\partial e}\leq 0; \ \frac{\partial^2 h^{-1}(\ga,e)}{\partial e^2} \geq 0 \right)$ The pdf of $\ta$ is non-negative, so $\frac{\partial r}{\partial e} \geq 0$ and $\frac{\partial^2 r}{\partial e^2} \leq 0$.
 $\hfill\blacksquare$
@@
 Then $\frac{\partial^2 r}{\partial e \partial \tad} = 	- \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \tad} \right) = 
-	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \tad \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} $
+	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial e \partial \tad } - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \tad} \frac{\partial f_\ga}{\partial e} $
 where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
@@
 $\frac{\partial r}{\partial  e}$ is non-negative by Lemma~\ref{res:bincC}.
-$\frac{\partial e}{\partial \tad}$ is non-positive by Lemma~\ref{res:tad_indir}.
 $\frac{\partial r}{\partial \tad}$ is non-positive by Lemma~\ref{res:tad_dir}.
-Thus the entire expression is non-positive.
+$\frac{\partial e}{\partial \tad}$ is ambiguous by Lemma~\ref{res:tad_indir}.
+Thus the sign of $\frac{\partial R(\bta,\tad)}{\partial \tad}$ may be either positive, zero or negative.
 $\hfill\blacksquare$
@@
 \noindent \textbf{\hypertarget{Pr_ga_dir}{Proof of Lemma~\ref{res:ga_dir}}}: \\
-The effect on the renewal probability is determined by the sign of the derivative of the right hand side of the inequality in Expression~\ref{eq:b_ex} with respect to $\ga(\cdot)$; to show that the renewal probability is increasing/non-decreasing(?) in $\ga(\cdot)$, I must demonstrate that this derivative is positive.
+\noindent The left side of the inequality in Expression~\ref{eq:b_ex}, $Z(\bta,\tad)$, does not depend on $e$.
+Thus we have $r(e,\bta,\tad) = \Pr [Z < \ga(e,\ve) ] = 1 - F_{\ga}(\ga=Z)$ where $F_{\ga}(\ga=Z) = F_{\ta}(\ta=h^{-1}(\ga,e))$ by the Change of Variables Theorem and Assumption~\ref{as:ga_ta} with $\ga = h(e,\ta)$ giving the change of variable.
 
-This leaves room for very broad kinds of shifts in $\ga(\cdot)$.
+Then $\frac{\partial r}{\partial \ga(\cdot)} = -\frac{\partial F_{\ta}(\ta=h^{-1}(\ga,e))}{\partial \ta}\frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)} = -f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)}$.
+Because $\ga = h(e,\ta)$ is increasing in both $e$ and $\ta$ by Assumption~\ref{as:ga_c}, $h^{-1}(\ga,e)$ decreases when $\ga(\cdot)$ increases for all $(e,\ta)$ pairs.
+The pdf of $\ta$ is non-negative, so $\frac{\partial r}{\partial \ga(\cdot)} \geq 0$.
+$\hfill\blacksquare$
 
@@
 The first term in the numerator is zero since the profit function does not vary in $\ga(\cdot,\cdot)$.
-Combining this with the leading negative sign and the fact that $\left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is positive, the sign of $\frac{\partial e}{\partial \ga(\cdot)}$ is determined by the sign of $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)}$.
+Combining this with the leading negative sign and the fact that $\left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is positive, the sign of $\frac{\partial e}{\partial \ga(\cdot)}$ is determined by the sign of $\frac{\partial^2 r}{\partial \ga(\cdot) \partial e}$.
 
-We can rewrite $\frac{\partial r(e,\bta,\tad)}{\partial \ga(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial \ga(\cdot)} = -\frac{\partial F_\ga (Z(\bta,\tad))}{\partial Z(\bta,\tad)} \frac{\partial Z(\bta,\tad)}{\partial \ga(\cdot)} = - f_\ga \frac{\partial Z(\bta,\tad)}{\partial \ga(\cdot)}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
+From the proof of Lemma~\ref{res:ga_dir}, we have $\frac{\partial r(e,\bta,\tad)}{\partial \ga(\cdot)} =  -f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)}$, where $F_\ga (Z(\bta,\tad))$ is the CDF of $\ga$ and $f_\ga (Z(\bta,\tad))$ is the pdf of $\ga$ and $Z(\bta,\tad)$ again represents the left hand side of the inequality in Expression~\ref{eq:b_ex}.
 
-Then $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} = - \frac{\partial}{\partial e} \left( \frac{\partial F_\ga (Z(\bta,\tad))}{\partial \ga(\cdot)} \right) = 
-	   - f_\ga \frac{\partial^2 Z(\bta,\tad)}{\partial \ga(\cdot) \partial e} - \frac{\partial Z(\bta,\tad)}{\partial \ga(\cdot)} \frac{\partial f_\ga}{\partial e} = - \frac{\partial Z(\bta,\tad)}{\partial \ga(\cdot)} \frac{\partial f_\ga}{\partial e} $
-where the above equality holds because $Z(\bta,\tad)$ does not depend on $e$.
+Then $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} = - \frac{\partial}{\partial e} \left( f_\ta(\ta) \frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)} \right) = 
+	   - f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial \ga(\cdot) \partial e} - \frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)} \frac{\partial f_\ta}{\partial e} = - f_\ta(\ta) \frac{\partial^2 h^{-1}(\ga,e)}{\partial \ga(\cdot) \partial e} $
+where the above equality holds because the pdf of $\ta$ does not depend on $e$.
+When $\ga(\cdot)$ shifts up, $\frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)}$ becomes less negative, so $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} \leq 0$.
 
-The proof of Lemma~\ref{res:pi_dir} shows that $\frac{\partial Z(\bta,\tad)}{\partial \pi(\cdot)}$ has the opposite sign as $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$.
-When $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ is weakly positive (negative), $\frac{\partial f_\ga}{\partial e} \geq 0$ implies that $\frac{\partial^2 r}{\partial e \partial \pi(\cdot)} \geq 0 \ \left(\leq 0\right)$.
-Thus $\frac{\partial e}{\partial \pi(\cdot)}$ has the same sign as $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$.
 $\hfill\blacksquare$

### 2017-11-10 draft.tex
revise results statements to match appendix

@@
 \noindent When $\tau^a$ is higher, the government agency becomes less likely to renew the antidumping duties, for three reasons.
-First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying, reducing $R(\bta,\tad)$ indirectly (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).
+First, the government prefers a higher domestic tariff (Lemma~\ref{res:leg_a}); second, the higher tariff discourages lobbying (Lemma~\ref{res:lobby}); and finally, the lower lobbying effort directly reduces the government's preferred tariff further (Lemma~\ref{res:bincC}).
 
@@
 \begin{lemma}
-  Lobbying effort is weakly decreasing in the antidumping duties. \hyperlink{Pr_tad_indir}{Proof}
+  Higher antidumping duties may lead to either an increase or decrease in lobbying effort. \hyperlink{Pr_tad_indir}{Proof}
   \label{res:tad_indir}
@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is decreasing in level of the antidumping duties $\tad$.
-(i.e.
-$\frac{\partial R(\bta,\tad)}{\partial \tad} \leq 0$).
+	The total probability that the antidumping duties will be renewed is most likely to decrease in level of the antidumping duties but it can increase in the antidumping duties if the indirect effect is positive and large enough to outweigh the direct effect.
 \hyperlink{Pr_tad_total}{Proof}
@@
 \begin{lemma}
-  Lobbying effort is weakly increasing in the uniform exogenous positive shifts of the political weighting function. \hyperlink{Pr_ga_indir}{Proof}
+  Lobbying effort is weakly decreasing in exogenous positive shifts of the political weighting function. \hyperlink{Pr_ga_indir}{Proof}
   \label{res:ga_indir}
@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is increasing in $\ga$. (i.e. $\frac{\partial R(\bta,\tad)}{\partial  \ga(\cdot)} \geq 0$). \hyperlink{Pr_ga_total}{Proof}
+	The total probability that the antidumping duties will be renewed is increasing in $\ga(\cdot)$ if the direct effect dominates and is decreasing in $\ga(\cdot)$ if the indirected effect dominates.
+\hyperlink{Pr_ga_total}{Proof}
 	\label{res:ga_total}
@@
 When $\ga(\cdot)$ shifts up, $\frac{\partial h^{-1}(\ga,e)}{\partial \ga(\cdot)}$ becomes less negative, so $\frac{\partial^2 r}{\partial e \partial \ga(\cdot)} \leq 0$.
+Thus $\frac{\partial e}{\partial \ga(\cdot)} \leq 0$.
 
@@
 $\frac{\partial e}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_indir}.
-$\frac{\partial r}{\partial \ga(\cdot)}$ is non-negative by Lemma~\ref{res:ga_dir}.
-Thus the entire expression is non-negative.
+$\frac{\partial r}{\partial \ga(\cdot)}$ is non-positive by Lemma~\ref{res:ga_dir}.
+Thus the sign of $\frac{\partial R(\bta,\tad)}{\partial \ga(\cdot)}$ can be positive, zero or negative.
 $\hfill\blacksquare$

### 2017-11-10 draft.tex
fill in text in rest of body sections

@@
 
+\newpage
 \begin{enumerate}
@@
 
+The level at which the antidumpting duties are set is likely to be related to some of the variables under consideration here, as the duties are determined five (or more) years earlier through a process similar to the renewal process.
+Endogenizing the level of the antidumping duties, as well as the fact of their application in the first place, is planned as an important extension.
+
+Even in the case where we take the antidumping duties as exogenous, the prediction is not clear cut.
+The direct effect is negative, as the government becomes less willing to protect the industries as the higher duties increasingly harm social welfare.
+
 \begin{lemma}
@@
 \end{lemma}
+
+However, the indirect effect of raising antidumping duties is ambiguous.
+Higher duties mean the return to a positive renewal decision is larger and thus the lobby has a larger incentive to exert effort; at the same time, the marginal impact of lobbying on the renewal probability falls as the antidumping duties increase and this blunts lobbying incentives.
+We can't say whether lobbying expenditure will rise or fall without knowing the magnitude of these two effects.
 
@@
 
+Because the direct effect of increasing antidumping duties to reduce the renewal probability, the only way the total effect of increasing antidumping duties leads to a larger probability of renewal is if the lobbying response is positive and large in magnitude.
+
 \begin{result}
-	The total probability that the antidumping duties will be renewed is most likely to decrease in level of the antidumping duties but it can increase in the antidumping duties if the indirect effect is positive and large enough to outweigh the direct effect.
+	The total probability that the antidumping duties will be renewed is most likely to decrease in the level of the antidumping duties but it can increase in the antidumping duties if the indirect effect is positive and large enough to outweigh the direct effect.
 \hyperlink{Pr_tad_total}{Proof}
@@
 The value of the political weight $\ga(e,\ta)$ is endogenous to many of the decisions underpinning the equilibrium, but here we examine the effect of an exogenous shift in the weighting function itself, $\ga(\cdot,\ta)$.
-We start again with the direct effect:
+The type of shift we analyze is one in which the value of $\ga(\cdot,\ta)$ weakly increases for every value of $e$.
+
+The direct effect is positive.
+This is quite intuitive: when the government places a higher weight on the industry's profits for a given lobbying effort, it is more likely to renew the antidumping duties because the industry's profits are now more important relative to social welfare.
 
 \begin{lemma}
-  The direct effect of exogenous positive shifts in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive.
+  The direct effect of an exogenous positive shift in the political weighting function $\ga(\cdot,\ta)$ on the probability the government renews the antidumping duty is positive.
 \hyperlink{Pr_ga_dir}{Proof}
@@
 
-In accordance with intuition, if there is a shift in the political weighting function so that the government agency weights the profits of the import-competing sector more heavily for a given amount of lobbying effort....
+Perhaps not surprisingly, the lobby's incentives move in the opposite direction.
+A shift in $\ga(\cdot,\ta)$ does not directly change the lobby's payoff.
+But it makes its marginal unit of effort more productive, so the lobby optimally reduces effort (i.e.
+the marginal cost of a unit of effort stays the same, so the lobby reduces effort when the increase in $\ga(\cdot,\ta)$ improves the marginal benefit).
 
@@
 \end{lemma}
+
+The total effect of the positive shift in $\ga(\cdot,\ta)$ depends on which of the direct or indirect effects is larger.
 
@@
 
+Finally we turn to questions of the lobbying sector's profitability.
+Profitability can shift in many ways, and they can affect incentives in many ways.
+In terms of the impact on both the government and lobby's decisions around renewal of temporary trade barriers, it turns out that changes in the gap between the profits under the antidumping duties and under the trade agreement tariff are a sufficient statistic.
+So we examine any change to profitability that affects this gap in a clear way.
+
+If profitability changes in such a way that the lobbying sector will now be even more profitable under the antidumping duties compared to the trade agreement tariff, the government becomes more likely to renew the antidumping duties.
+This shift improves the evaluation of the antidumping duties both in terms of the social welfare calculation and in terms of the lobby's benefit, but the lobby's benefit is weighted more heavily so the balance is tipped in favor of renewal.
+
 \begin{lemma}
@@
 \end{lemma}
+
+From the lobby's perspective, an increase in the profit gap increases its incentives to exert lobbying effort; at the same time, because the government's renewal probability hinges on how much it over-weights profits, it becomes more worthwhile to exert lobbying effort to influence the government's decision-making weight directly.
 
@@
 
-Notes:
-\begin{itemize}
-	\item For $\frac{\partial R}{\partial \pi} \geq 0$, need the return from lobbying to increase with increase in $\pi$ AND
-	\item government marginal benefit from protection to increase with $\pi$
-\end{itemize}
-
-\vskip.2in
-\begin{itemize}
-	\item Profit function convex $\Rightarrow$ also quasiconvex
-	\item But hit it with the right increasing monotone transformation and $\frac{\partial }{\partial \pi(\cdot)} \left[\pi_X(\tad) - \pi_X(\tau^a) \right]$ can go either way
-	\item This is about how the differences change (CARDINAL)
-\end{itemize}
+The direct and indirect effect combine so that the change in total probability depends only on the change in the profit gap under the antidumping duties and the trade agreement tariff.
 
@@
 \end{result}
+
+The bottom line: in order for the total probability of renewal to go up, it must be that the shift in profitability leads to an increase in the government's marginal benefit from protection as well as the returns from lobbying.
+To think about changes to profitability, we can imagine transformations of the (convex) profit function.
+Different increasing transformations could leave the profit function more or less convex than the original.
+Both the government and the lobby care about $\pi_X(\tad) - \pi_X(\tau^a)$---that is, cardinal information is important.
+So we must pay attention to how this difference changes when the profit function changes in order to make predictions about the impact on the renewal of antidumping duties.
 

### 2017-11-10 draft.tex
paste extended abstract into draft as intro starting point

@@
 \section{Introduction}
+Today's world trading system is largely governed by a system in which countries commit to tariff bindings and yet raise their tariffs above those bindings through a variety of temporary trade barriers on a not-infrequent basis (Bown 2011).
+A significant literature has explored the question of which industries receive protection through temporary trade barriers and under what conditions this happens.
+This project asks a related but distinct question: given that a product receives protection, what determines the duration of the protection it receives?
+
+This question can be addressed in the context of renewals of trade remedies under the WTO agreements.
+Normally, temporary measures such as anti-dumping and counter-vailing duties are imposed with a five-year sunset provision that is subject to renewal by the U.S.
+International Trade Commission.
+Conditional on a temporary trade barrier being granted and applied, one would like to know what determines whether a renewal order is granted so that the measure continues in force.
+
+In many countries, the crucial actors in the imposition of temporary trade barriers are advocates for the industry that would be protected and an administrative body that has been granted authority to make decisions about whether a given temporary trade barrier is WTO-legal.
+In the United States, this body is the International Trade Commission (ITC).
+For ease of exposition and because I would ultimately like to test this theory using U.S.
+data, I will refer to the actors in this model as industries and the ITC.
+
+In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, I assume that all actors take most-favored-nation (MFN) tariffs as given.
+
+In the first phase, when no temporary trade barrier is in place, an industry exerts effort to convince the ITC to enact a temporary trade barrier for its product.
+The ITC then must decide whether to maintain the MFN tariff or impose the temporary trade barrier.
+Importantly, we assume that the decisions of the ITC are not deterministic, with the amount of uncertainty varying by industry.
+
+Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision under the WTO.
+At this point, the interaction is similar to that during the first phase, with the industry first exerting effort and then the ITC deciding whether to extend the temporary trade barrier or to revert to the MFN tariff.
+The essential strategic difference is that at this point the level of the temporary trade barrier is taken as exogenously set at the level determined in the first round of interaction.
+
+An industry's decision about how much, if any, effort to exert depends on a number of factors.
+Among them are the gap between the applied tariff it faces and the protection it would receive under a temporary trade barrier, the cost of seeking the temporary trade barrier, and, crucially, the probability that its request will be granted.
+That is, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the ITC's decision-making process.
+
+Thus we turn to the question of how the ITC decides whether to grant a temporary trade barrier.
+The imposition of a temporary trade barrier, or continuation of one already in place, is not in general costless.
+We might assume then that the ITC only grants renewals when it finds the benefits outweigh the costs.
+If the ITC's rulings are uncertain from the point of view of industry, it must be that the industry cannot perfectly predict the outcome of any given proceeding.
+That is, the industry does not know with precision how the ITC weighs the costs and benefits of granting protection.
+
+There are several possible sources of this uncertainty.
+The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a temporary trade barrier.
+Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners.
+Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to up- and down-stream industries, consumers and trading relations.
+This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question.
+
+An important question in this model is why an industry that receives protection as a result of the original interaction concerning the imposition of the temporary trade barrier would fail to get it renewed.
+At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome.
+Moreover, having the level of the temporary trade barrier set by the original interaction serves to reduce the industry's incentive to exert effort on the margin.
+
+In addition, some factors that affect both the ITC's and the industry's decision-making can change significantly over the course of a five-year period.
+Most of these factors display at least some variation across industries.
+
+Because a temporary trade barrier insulates an industry from competition, when receiving such protection, an industry should be able to increase profits.
+The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary.
+Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection.
+These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the ITC.
+
+Another interesting dimension along which there is uncertainty for the ITC is in its evaluation of the probability with which trading partners will dispute or retaliate against a temporary trade barrier.
+This not only varies across temporary trade barriers, but may vary across time.
+In particular, the ITC can observe whether a dispute has been filed during the first five years of a temporary trade barrier and update its beliefs about future retaliation in a way that varies across industries.
+
+There is much to be learned about the workings of the world trading system by examining the duration of deviations from base tariff commitments.
+I plan a project whose first stage is theoretical with a second, later stage in which the theory is tested on a data set of renewal decisions for anti-dumping measures.
 
 \newpage
+\subsection{Outline}
 \begin{enumerate}
-	\item How long do deviations from trade agreement tariffs last? 
   \item What are the determinants of renewals?
-		\begin{itemize}
-			\item They don't happen for \textit{no} reason at all
-		\end{itemize}
 \end{enumerate}
@@
 \section{References}
+Bown, Chad P., ``Taking Stock of Antidumping, Safeguards and Countervailing Duties, 1990-2009,'' The World Economy v34, n12 (December 2011): 1955-1998.
 

### 2017-11-10 draft.tex
rework extended abstract into updated intro

@@
 This question can be addressed in the context of renewals of trade remedies under the WTO agreements.
-Normally, temporary measures such as anti-dumping and counter-vailing duties are imposed with a five-year sunset provision that is subject to renewal by the U.S.
-International Trade Commission.
+Normally, temporary measures such as anti-dumping and counter-vailing duties are imposed with a sunset provision that is subject to renewal.
 Conditional on a temporary trade barrier being granted and applied, one would like to know what determines whether a renewal order is granted so that the measure continues in force.
+In fact, this very particular institutional environment allows us to examine questions about the determinants of protection that are usually much more difficult to answer by holding fixed some of the key elements.
 
-In many countries, the crucial actors in the imposition of temporary trade barriers are advocates for the industry that would be protected and an administrative body that has been granted authority to make decisions about whether a given temporary trade barrier is WTO-legal.
-In the United States, this body is the International Trade Commission (ITC).
+In many countries, the crucial actors in the imposition of temporary trade barriers are advocates for the industry that would be protected and some constellation of administrative bodies that have been granted authority to make decisions about whether a given temporary trade barrier is WTO-legal.
 For ease of exposition and because I would ultimately like to test this theory using U.S.
-data, I will refer to the actors in this model as industries and the ITC.
+data, I will refer to the actors in this model as industries and the government, and I will focus on antidumping duties because antidumping duties are both imposed and renewed most frequently and thus provided the largest sample size.
 
-In this model, there are two phases of interaction between any given industry seeking protection and the ITC. In both cases, I assume that all actors take most-favored-nation (MFN) tariffs as given.
+In this model, there are two phases of interaction between any given industry seeking protection and the government.
+In both cases, I assume that all actors take most-favored-nation (MFN) tariffs as given.
 
-In the first phase, when no temporary trade barrier is in place, an industry exerts effort to convince the ITC to enact a temporary trade barrier for its product.
-The ITC then must decide whether to maintain the MFN tariff or impose the temporary trade barrier.
-Importantly, we assume that the decisions of the ITC are not deterministic, with the amount of uncertainty varying by industry.
+In the first phase, when no temporary trade barrier is in place, an industry exerts effort to convince the government to enact a temporary trade barrier for its product.
+The government must then decide whether to maintain the MFN tariff or impose the temporary trade barrier.
+Importantly, we assume that the decisions of the government are not deterministic, with the amount of uncertainty varying by industry.
 
-Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision under the WTO.
+Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision for antidumping duties under the WTO.
 At this point, the interaction is similar to that during the first phase, with the industry first exerting effort and then the ITC deciding whether to extend the temporary trade barrier or to revert to the MFN tariff.
 The essential strategic difference is that at this point the level of the temporary trade barrier is taken as exogenously set at the level determined in the first round of interaction.
+It is the second phase that is modeled in the current paper, with the addition of the first phase acknowledged as a very important and imminent extension.
 
@@
 Among them are the gap between the applied tariff it faces and the protection it would receive under a temporary trade barrier, the cost of seeking the temporary trade barrier, and, crucially, the probability that its request will be granted.
-That is, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the ITC's decision-making process.
+That is, the industry's incentives to seek protection, and the intensity with which it does so, depend on how much uncertainty it faces in the government's decision-making process.
 
-Thus we turn to the question of how the ITC decides whether to grant a temporary trade barrier.
+Thus we turn to the question of how the government decides whether to grant a temporary trade barrier.
 The imposition of a temporary trade barrier, or continuation of one already in place, is not in general costless.
-We might assume then that the ITC only grants renewals when it finds the benefits outweigh the costs.
-If the ITC's rulings are uncertain from the point of view of industry, it must be that the industry cannot perfectly predict the outcome of any given proceeding.
-That is, the industry does not know with precision how the ITC weighs the costs and benefits of granting protection.
+We might assume then that the government only grants renewals when it finds the benefits outweigh the costs.
+If the government's rulings are uncertain from the point of view of industry, it must be that the industry cannot perfectly predict the outcome of any given proceeding.
+That is, the industry does not know with precision how the government weighs the costs and benefits of granting protection.
 
 There are several possible sources of this uncertainty.
-The industrial group may not be able to predict directly the quality of evidence the ITC requires in order to be willing to provide protection through a temporary trade barrier.
-Indirectly, this may reflect the ITC's preferences about the costs of disputes and retaliation by trade partners.
-Industry may also not be fully informed about how the ITC weighs the potential harms to the industry versus those to up- and down-stream industries, consumers and trading relations.
+The industrial group may not be able to predict directly the quality of evidence the government requires in order to be willing to provide protection through a temporary trade barrier.
+Indirectly, this may reflect the government's preferences about the costs of disputes and retaliation by trade partners.
+Industry may also not be fully informed about how the government weighs the potential harms to the industry versus those to up- and down-stream industries, consumers and trading relations.
 This may be derived from factors such as the political influence of the industry, how central it is to the economy, and whether there is active lobbying by producers downstream of the product in question.
 
-An important question in this model is why an industry that receives protection as a result of the original interaction concerning the imposition of the temporary trade barrier would fail to get it renewed.
-At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome.
-Moreover, having the level of the temporary trade barrier set by the original interaction serves to reduce the industry's incentive to exert effort on the margin.
-
-In addition, some factors that affect both the ITC's and the industry's decision-making can change significantly over the course of a five-year period.
-Most of these factors display at least some variation across industries.
-
-Because a temporary trade barrier insulates an industry from competition, when receiving such protection, an industry should be able to increase profits.
-The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary.
-Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection.
-These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the ITC.
-
-Another interesting dimension along which there is uncertainty for the ITC is in its evaluation of the probability with which trading partners will dispute or retaliate against a temporary trade barrier.
-This not only varies across temporary trade barriers, but may vary across time.
-In particular, the ITC can observe whether a dispute has been filed during the first five years of a temporary trade barrier and update its beliefs about future retaliation in a way that varies across industries.
-
-There is much to be learned about the workings of the world trading system by examining the duration of deviations from base tariff commitments.
-I plan a project whose first stage is theoretical with a second, later stage in which the theory is tested on a data set of renewal decisions for anti-dumping measures.
-
-\newpage
 \subsection{Outline}
-\begin{enumerate}
-  \item What are the determinants of renewals?
-\end{enumerate}
 
@@
 \begin{itemize}
-	\item Temporary trade barriers have potential to be renewed
-		\begin{itemize}
-			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
-			\item For Safeguards, four then four; much rarer than AD
-		\end{itemize}
 	\item Authorized by WTO
@@
 \end{itemize}
+
+There is much to be learned about the workings of the world trading system by examining the duration of deviations from base tariff commitments.
+I plan a project whose first stage is theoretical with a second, later stage in which the theory is tested on a data set of renewal decisions for anti-dumping measures.
 
@@
 
+An important question in this model is why an industry that receives protection as a result of the original interaction concerning the imposition of the temporary trade barrier would fail to get it renewed.
+At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome.
+Moreover, having the level of the temporary trade barrier set by the original interaction serves to reduce the industry's incentive to exert effort on the margin.
+
+In addition, some factors that affect both the ITC's and the industry's decision-making can change significantly over the course of a five-year period.
+Most of these factors display at least some variation across industries.
+
+Because a temporary trade barrier insulates an industry from competition, when receiving such protection, an industry should be able to increase profits.
+The amount that profits increase will vary by industry, and the decisions about how to use the extra profits will also plausibly vary.
+Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection.
+These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the ITC.
+
+Another interesting dimension along which there is uncertainty for the ITC is in its evaluation of the probability with which trading partners will dispute or retaliate against a temporary trade barrier.
+This not only varies across temporary trade barriers, but may vary across time.
+In particular, the ITC can observe whether a dispute has been filed during the first five years of a temporary trade barrier and update its beliefs about future retaliation in a way that varies across industries.
+
 \begin{itemize}

### 2017-11-10 draft.tex
finish abstract and conclusion

@@
 \begin{quote}
-{Abstract
+{Under WTO law, temporary trade barriers such as antidumping duties must be removed after a period of four or five years.
+However, under rather vague legal conditions, they can be renewed.
+This institutional environment provides the structure to carefully study the determinants of the \textit{length} of protection.
+We present a theoretical political-economy model of the renewal process and find that the probability a temporary trade barrier will be renewed decreases in the level of trade agreement tariffs and is also likely to decrease in the level of the anti-dumping duties.
+An increase in an industry's profitability is shown to increase the probability of renewal also increases.
+Lobbying effort also increases the probability for a fixed strength of the lobby, while the strength of the lobby itself has more nuanced effects on the renewal probability.
 
@@
 
-Given that the industry receives temporary protection in the first phase of interaction, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision for antidumping duties under the WTO.
-At this point, the interaction is similar to that during the first phase, with the industry first exerting effort and then the ITC deciding whether to extend the temporary trade barrier or to revert to the MFN tariff.
+Given that the industry receives temporary protection in the first phase of interaction and the protection remains in place until expiry, there will be another phase of interaction when the trade barrier expires, here modeled as five years later to match the typical five years sunset provision for antidumping duties under the WTO.
+At this point, the interaction is similar to that during the first phase, with the industry first exerting effort and then the government deciding whether to extend the temporary trade barrier or to revert to the MFN tariff.
 The essential strategic difference is that at this point the level of the temporary trade barrier is taken as exogenously set at the level determined in the first round of interaction.
@@
 
-\subsection{Outline}
+Interestingly, there are very few stipulations in the General Agreement on Tariffs and Trade (GATT) / World Trade Organization (WTO) to guide the renewal process.
+WTO-level litigation has not provided significant additional structure, so governments appear to have significant latitude in their decision-making process regarding renewals of temporary trade barriers.
+These decisions are often made via complex processes, adding to uncertainty.
 
-\vskip.2in
-\begin{itemize}
-	\item Authorized by WTO
-	\item Very little in the agreements to guide the process
-		\begin{itemize}
-			\item WTO litigation gives gov'ts a LOT of latitude
-			\item Renewal decision determined by complex process including DOC, ITC, pressure via other political bodies.
-		\end{itemize}
-	\item In U.S., for AD:
-		\begin{itemize}
-			\item DOC initiates, determines whether dumping would continue
-						\begin{itemize}
-			\item Can renew AD duties
-			\item Susceptible to influence of lobbying, perhaps both direct and indirect
-			\item Modeled in reduced form
-		\end{itemize}
+In the United States, for the renewal of antidumping duties, the Department of Commerce must initiate a renewal proceeding and determine whether dumping would continue of the duties are not renewed.
+The International Trade Commission determines whether injury would recur or continue.
+These bodies are likely susceptible to the influence of lobbying both directly from industry and consumer groups and indirectly via other political bodies such as Congress as well as other parts of the Executive branch.
 
-			\item ITC determines whether injury would recur / continue
-		\end{itemize}
-\end{itemize}
-
-\vskip.2in
-The probability that an AD duty gets renewed
-
-\begin{itemize}
-	\item Increases in lobbying effort
-	\item Decreases in the MFN tariff
-	\item Is invariant to the trading partner's tariff
-	\item Increases in the profitability of the import-competing sector
-	\item Increases in the strength of the lobby
-	\item May be concave in the AD duty
-\end{itemize}
+Given this complicated decision-making process with few guidelines provided at the international level, I present a theoretical model to guide our thinking about what elements impact renewal decisions.
+I find that the probability that antidumping duties will be renewed is invariant to foreign tariffs, decreases in most-favored nation tariffs and is likely to decrease in the level of the anti-dumping duties.
+The probability increases in lobbying effort, but the overall impact of the strength of the lobby depends on whether the positive direct effect outweighs the negative indirect effect on the lobby's incentives.
+If the industry becomes more (less) profitable in the sense that the gap between profits under the antidumping duties and profits under the trade agreement tariffs increases (decreases), the probability of renewal also increases.
 
 There is much to be learned about the workings of the world trading system by examining the duration of deviations from base tariff commitments.
-I plan a project whose first stage is theoretical with a second, later stage in which the theory is tested on a data set of renewal decisions for anti-dumping measures.
+After extending this model to include the stage at which antidumping duties are set, I plan to take this model to a data set of renewal decisions for anti-dumping measures.
 
+\begin{comment}
 \subsection{Related Literature}
@@
 
-Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)
+%Kara Reynold's ``Political Economy of Antidumping Reviews (Shushanik)
 
@@
 
-Mansfield, Milner and Rosendorff (2000) study the impact of executive/legislative interactions on international agreements in the case of exogenously-determined preferences.
-They show that democracies trade more with each other because the domestic legislature only cooperates if the foreign government makes deep tariff cuts.
-Ethier (2002) treats the effect of a separation of powers between trade negotiators and the government officials who administer protection.
-
 Milner and Rosendorff (1997) explore how uncertainty can affect trade policy and ratification failure when political preferences, and therefore uncertainty, are exogenous.
@@
 The lobbies influence the preferences of the legislature in a context of unilateral policy making with no uncertainty, and Coates and Ludema (2001) study trade policy leadership with endogenous lobbying in the presence of political uncertainty with imperfect monitoring.
+\end{comment}
 
@@
 
+\begin{comment}
 \textbf{REVISE EXTENSIVE FORM}
@@
 Figure~\ref{fig:ext} illustrates the timing of the game.
+\end{comment}
+
  Taking the trade-agreement tariffs $\bta = \left(\tau^a,\tau^{*a}\right)$\footnote{I use the convention throughout of representing a vector of tariffs for both countries $(\tau,\tau^*)$ as a single bold $\bm{\tau}$.} and the antidumping duty level $\tad$ as given, the import-competing firms jointly attempt to persuade the government agency to renew the antidumping duties by choice of lobbying effort $e$.
@@
 
+\begin{comment}
 Lobby must be able to trigger the original AD duty
@@
 \end{itemize}
+\end{comment}
 
@@
 Finally, producers and consumers make their decisions.
+
+Although political uncertainty is important in informing the lobby's behavior, the player that has more information moves last in the game so subgame perfect Nash equilibrium is the appropriate solution concept.
 
@@
 \begin{assumption}
-  $\ta$ is uniformly distributed on some $\Theta=\left[\underline{\ta},\overline{\ta}\right]$.
+  The pdf of the induced distribution on $\ga(e,\ta)$ is weakly increasing in $e$.
   \label{as:ta}
@@
 Assumption~\ref{as:ga_ta} simply provides for an intuitive labeling so that larger realizations of $\ta$ increase the value of the political economy weight.
+Assumption~\ref{as:ta} is a restriction either on the distribution of uncertainty or on how it enters $\ga(e,\cdot)$ so that higher values of the political economy weight become more likely at higher values of lobbying effort.
 
@@
 
+\begin{comment}
 \subsection{Information and Equilibrium Selection}
@@
 \textbf{NOT SURE AT ALL ABOUT THESE FEATURES; it's not a two-country model}
-
-I examine a simple class of equilibria that have three key features.
-First, information about political uncertainty is symmetric.
-However, in line with the literature, I assume the lobby's contribution is not observable to the foreign legislature.
-Thus the influence of one country's lobby on the other country's legislature occurs only through the tariffs selected.\footnote{cfr.
-Grossman and Helpman (1995b), page 685.} Since players in the same country can take advantage of more information than those who are in different countries, the solution concept is perfect public equilibrium (PPE).
 
@@
 Finally, I assume that an external authority can ensure enforcement of the agreement.
+\end{comment}
 
@@
 
-Because the duties are a unilateral policy that we presume here are permissable under WTO rules, the decision to renew the duties or not does not change the level of the tariff applied by the foreign trading partner.
+Because the duties are a unilateral policy that we presume here are permissible under WTO rules, the decision to renew the duties or not does not change the level of the tariff applied by the foreign trading partner.
 That is, there is no incentive in terms of reciprocal treatment to deter the home government from renewing the duties.
@@
 
-The level at which the antidumpting duties are set is likely to be related to some of the variables under consideration here, as the duties are determined five (or more) years earlier through a process similar to the renewal process.
+The level at which the antidumping duties are set is likely to be related to some of the variables under consideration here, as the duties are determined five (or more) years earlier through a process similar to the renewal process.
 Endogenizing the level of the antidumping duties, as well as the fact of their application in the first place, is planned as an important extension.
@@
 \begin{result}
-	The total probability that the antidumping duties will be renewed is increasing in $\ga(\cdot)$ if the direct effect dominates and is decreasing in $\ga(\cdot)$ if the indirected effect dominates.
+	The total probability that the antidumping duties will be renewed is increasing in $\ga(\cdot)$ if the direct effect dominates and is decreasing in $\ga(\cdot)$ if the indirect effect dominates.
 \hyperlink{Pr_ga_total}{Proof}
@@
 \label{sec:concl}
+This is very much work in progress.
+The next stage is to extend the model to include the initial decision to grant protection.
+This is important because of course the imposition of the original protective measure is related to the incentives to renew it, so the endogeneity should be taken into account.
 
-			Future Work
-
-An important question in this model is why an industry that receives protection as a result of the original interaction concerning the imposition of the temporary trade barrier would fail to get it renewed.
+What's more, we'd like to know why an industry that receives protection as a result of the original interaction concerning the imposition of the temporary trade barrier would fail to get it renewed---or, even more interesting, choose not to pursue a renewal when contacted by the Department of Commerce just before the antidumping duties expire.
 At the most basic level, if we assume the industry faces the same uncertainty and responds in the same way, it could get a different draw and thus a different outcome.
@@
 
-In addition, some factors that affect both the ITC's and the industry's decision-making can change significantly over the course of a five-year period.
+In addition, some factors that affect both the government's and the industry's decision-making can change significantly over the course of a five-year period.
 Most of these factors display at least some variation across industries.
@@
 Some industries may use this opportunity to become more competitive and thus less interested in seeking protection while others may use the added profits to become more politically powerful and thus better able to gain future protection.
-These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the ITC.
+These decisions, and the basic question of whether protection and technological upgrading are complements or substitutes, feeds back into the decision-making process of the government.
 
-Another interesting dimension along which there is uncertainty for the ITC is in its evaluation of the probability with which trading partners will dispute or retaliate against a temporary trade barrier.
+Another interesting dimension along which there is uncertainty for the government is in its evaluation of the probability with which trading partners will dispute or retaliate against a temporary trade barrier.
 This not only varies across temporary trade barriers, but may vary across time.
-In particular, the ITC can observe whether a dispute has been filed during the first five years of a temporary trade barrier and update its beliefs about future retaliation in a way that varies across industries.
+In particular, the government can observe whether a dispute has been filed during the first five years of a temporary trade barrier and update its beliefs about future retaliation in a way that varies across industries.
 
-\begin{itemize}
-	\item Comparative static on uncertainty measure
-	\item Empirical work
-	\item Extend model to include initial decision to grant protection.
-		\begin{itemize}
-			\item Explain variation in a lobby's incentives between original application of AD and renewal
-			\item Lobby's choice between investing in productive vs. rent-seeking behavior while protected
-			\item Need to have first stage (Jee-Hyeong, Gary Lyn)
-		\begin{itemize}
-			\item Look at Park and Blonigen (Jee-Hyeong)
-			\item Cost differential for firms to get initial duty vs. renewal?
-			\item Some firms choose not to pursue renewal when DOC contacts them 30-days before (Sasha)
-		\end{itemize}
-	\item Lobbying effort may be endogenous: if prob. of success is lower, maybe it's not worth providing effort (Mostafa)
-		\end{itemize}
-\end{itemize}
+All of this will then be taken to the data in the form of the World Bank's Temporary Trade Barriers Database.
 
@@
 
-This can be simplied to
+This can be simplified to
 \begin{equation}

### 2017-11-11 presentation.tex
update presentation for SEAs

@@
 		\begin{itemize}
-			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
-			\item For Safeguards, four then four; much rarer than AD
+			\item For anti-dumping (AD) duties, initial five year term, renewal for five years
+			\item For safeguards, four then four; much rarer than AD
 		\end{itemize}
-	\item Authorized by WTO
-	\item Agreements / litigation provide a LOT of latitude
 	\item In U.S., for AD:
@@
 			\item ITC determines whether injury would recur / continue
+		\end{itemize}
+	\item Authorized by WTO
+		\begin{itemize}
+			\item Agreements / litigation provide a LOT of latitude
 		\end{itemize}
@@
 \begin{itemize}[<+->]
+	\item is invariant to the trading partner's tariff
+	\item decreases in the MFN tariff
 	\item increases in lobbying effort	
-	\item decreases in the MFN tariff
-	\item is invariant to the trading partner's tariff
 	\item increases in the profitability of the import-competing sector
-	\item increases in the strength of the lobby
-	\item AD duties: complicated
+	\item strength of the lobby and AD duties: complicated
 \end{itemize}
@@
 \begin{itemize}[<+->]
+	\item Lobby
+		\begin{itemize}
+			\item Represents import-competing sector, $X$
+		\end{itemize}	
 	\item Dept. of Commerce / Int'l Trade Commission ($G$)
@@
 			\item Can renew AD duties
-			\item Susceptible to influence of lobbying, perhaps both direct and indirect
+			\item Susceptible to influence of lobbying, perhaps both directly and indirectly
 			\item Modeled in reduced form
@@
 %\pause
-	\item A Single Lobby
-		\begin{itemize}
-			\item Represents import-competing sector, $X$
-		\end{itemize}	
+
 \end{itemize}
@@
 \vskip.2in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumption 1}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumptions}
 \begin{enumerate}
@@
 	\item $\ga(e,\ta)$ is increasing and concave in $e$ for all $\ta \in \Theta$.
+	\item $\ga(e,\ta)$ is increasing in $\ta$.
 \end{enumerate}
@@
   \pause
-	\item $\ta$ is uniformly distributed on some $\Theta=\left[\underline{\ta},\overline{\ta}\right]$.
+	\item   The pdf of the induced distribution on $\ga(e,\ta)$ is weakly increasing in $e$.
 \end{enumerate}
@@
 \vskip.25in
-\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 3}
+\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma}
   The probability that $G$ renews AD duties is increasing and concave in lobbying effort $e$ $\left(\text{i.e.
@@
 \pause
-Indirect effect is positive: higher $\tau^{\textit{ad}}$ increases incentive to exert lobbying effort
+Indirect effect is ambiguous: higher $\tau^{\textit{ad}}$ can increase or decrease incentive to exert lobbying effort
 
@@
 \pause
-Magnitudes are not directly comparable
+	The total probability that $G$ renews AD duties only increases if indirect effect is positive / large enough to outweigh direct effect.
 \begin{itemize}
@@
 \pause
-Assume $\ga(\cdot,\cdot)$ increases weakly for all $(e,\ta)$ pairs.
+Assume $\ga(\cdot,\cdot)$ increases weakly for all $(e,\ta)$ pairs
 \pause
@@
 	\item $G$ gives more weight to firms' benefit
-	\item Lobbying incentives are unchanged
+	\item Lobbying incentives are muted
 \end{itemize}
@@
 \begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 4}
-  The total probability that $G$ renews AD duties increases when the weighting function shifts up exogenously.
+  The total probability that $G$ renews AD duties increases when the weighting function shifts up exogenously if the direct effect dominates.
 \end{beamerboxesrounded}

### 2018-02-08 outline.tex
remove trade war tariffs section
remove _b subscripts; turn result 1 into lemma 1
fix typos scattered throughout notes, draft, outline
add feedback from SEAs

@@
 \vskip.5in
+\section{Feedback}
+SEAs, Tampa, November 2017
+\begin{itemize}
+	\item Maybe I should be using incidence of AD duties instead of $\tau^{ad}$
+	\item Comments from Michael Anderson
+		\begin{itemize}
+			\item Similar results to application of ADDs
+			\item Steel industry doesn't face a lot of uncertainty at ITC (``magnet test'' joke)
+			\item Profits / cyclical effects
+			\item Show patterns of ADD renewals: industry by industry, what are gaps between $\tau^{ad}$ and $\tau^a$, correlation with duration
+			\item Should $\theta$ be endogenized?
+		\end{itemize}
+\end{itemize}
+
+\vskip.5in
 \section{Decision-maker's Condition}
@@
 
-\vskip1in
+\vskip.5in
 Next steps:
@@
 	\item How do I make this vary across industry? $\pi$ function, $\ga$, $\ta$, $\tau^a$, $\tau^{AD}$
+\end{enumerate}
+
+\vskip.5in
+To-do on draft:
+\begin{enumerate}
+	\item Large vs. small country
+	\item Import tariffs only okay?
+	\item Subscript lobby's $\pi(\cdot)$ with $X$ everywhere
+	\item Revise sec:info after results
+	\item Add proof of Lemma 1 (corresponds to Result 1 in older paper)
+	\item SPNE?
 \end{enumerate}

### 2018-10-28 outline.tex
add four-stage model (ITC sets AD duties as well as renewal decision) to notes

@@
 
+\subsection{Lobbying for the level of $\tau^{AD}$}
+This is a four-stage game.
+The lobby chooses $e^{AD}$ to affect the level of $\tau^{AD}$.
+Then the ITC chooses $\tau^{AD}$.
+Then the lobby chooses $e$ to affect the ITC's decision to renew $\tau^{AD}$ or go back to $\tau^a$ and finally the ITC decides whether or not to renew the anti-dumping duties.
+\begin{itemize}
+	\item ITC's decision to renew the anti-dumping duty or not is a function of lobby's choice of $e \ \left(\frac{\partial r}{\partial e} \neq 0\right)$, it's own $\tau^{ad} \ \left(\frac{\partial r}{\partial \tau^{ad}} \neq 0\right)$, and exogenous $\tau^a, \ga$, and $\pi \ \left(\frac{\partial r}{\partial \tau^a} \neq \frac{\partial r}{\partial \ga} \neq \frac{\partial r}{\partial \pi} \neq  0\right)$:
+		\[
+		  \frac{\partial r}{\partial e} \frac{\partial e}{\partial \tau^a} + \frac{\partial r}{\partial \tau^a} + \left[ \frac{\partial r}{\partial e} \frac{\partial e}{\partial \tau^{ad}} + \frac{\partial r}{\partial \tau^{ad}}\right] \frac{\partial \tau^{ad}}{\partial \tau^a} + \left[ \frac{\partial r}{\partial e} \frac{\partial e}{\partial \tau^{ad}} + \frac{\partial r}{\partial \tau^{ad}}\right] \frac{\partial \tau^{ad}}{\partial e^{ad}} \frac{\partial e^{ad}}{\partial \tau^a}
+		\]
+		Where the first three terms are, respectively
+			\begin{itemize}
+				\item the impact of the lobby's effort decision on the ITC's renew (break) decision
+				\item the direct effect of the change in $\tau^a$ on the lobby's effort decision
+				\item the direct effect of the change in $\tau^a$ on the ITC's break decision
+			\end{itemize}
+	\item The lobby makes its decision $e$ as a function of $\tau^{ad} \ \left(\frac{\partial e}{\partial \tau^{ad}} \neq 0\right)$, and exogenous $\tau^a, \ga$, and $\pi \ \left(\frac{\partial e}{\partial \tau^a} \neq \frac{\partial e}{\partial \ga} \neq \frac{\partial e}{\partial \pi} \neq  0\right)$
+		\begin{itemize}
+			\item The lobby cares that $e$ has an impact on $r$
+			\item This is noted by $\frac{\partial r}{\partial e} \neq 0$
+		\end{itemize}
+	\item If the ITC sets $\tau^{ad}$ in a vacuum, then $\tau^{ad}$ is a function of exogenous $\tau^a, \ga$, and $\pi \ \left(\frac{\partial \tau^{ad}}{\partial \tau^a} \neq \frac{\partial \tau^{ad}}{\partial \ga} \neq \frac{\partial \tau^{ad}}{\partial \pi} \neq  0\right)$
+		\begin{itemize}
+			\item ITC cares that $\tau^{ad}$ has an impact on $e \ \left( \frac{\partial e}{\partial \tau^{ad}} \neq 0 \right)$
+			\item ITC cares that $\tau^{ad}$ has an impact on $r \ \left( \frac{\partial r}{\partial \tau^{ad}} \neq 0, \text{ i.e.
+} \frac{\partial r}{\partial e}\frac{\partial e}{\partial \tau^{ad}} \neq 0\right)$
+		\end{itemize}
+	\item Now lobby chooses $e^{ad}$ to influence $\tau^{ad}$.
+Then $e^{ad}$ is a function of exogenous $\tau^a, \ga$, and $\pi \ \left(\frac{\partial e^{ad}}{\partial \tau^a} \neq \frac{\partial e^{ad}}{\partial \ga} \neq \frac{\partial e^{ad}}{\partial \pi} \neq  0\right)$
+		\begin{itemize}
+			\item UH OH! I forgot that $e^{ad}$ influences all sorts of things above. Have to fix!
+			\item lobby cares that $e^{ad}$ has an impact on $\tau^{ad} \ \left( \frac{\partial \tau^{ad}}{\partial e^{ad}} \neq 0 \right)$
+			\item lobby cares that $e^{ad}$ has an impact on $e \ \left( \frac{\partial e}{\partial \tau^{ad}} \frac{\partial \tau^{ad}}{\partial e^{ad}} \neq 0 \right)$
+			\item lobby cares that $e^{ad}$ has an impact on $r \ \left( \frac{\partial r}{\partial e^{ad}} \neq 0, \text{ i.e.
+} \frac{\partial r}{\partial e}\frac{\partial e}{\partial \tau^{ad}} \frac{\partial \tau^{ad}}{\partial e^{ad}} \neq 0\right)$
+		\end{itemize}
+\end{itemize}
+
 \vskip.5in
